### 2022-07-22 paper/paper.tex
move paper

\documentclass{ieeeaccess}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{mathtools}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage[flushleft]{threeparttable}
\usepackage{bm}
\usepackage[inline]{enumitem} 
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{amssymb}
% \usepackage{fontspec}
% \setmainfont{TeX Gyre Termes}
\setcounter{MaxMatrixCols}{30}
\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
% \newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
% \newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
% \newtheorem{condition}[theorem]{Condition}
% \newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
% \newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
% \newtheorem{example}[theorem]{Example}
% \newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}{Notation}
\newtheorem{problem}[theorem]{Problem}
% \newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
% \newtheorem{summary}[theorem]{Summary}
\newtheorem{assumption}{Assumption}[section]
\newtheorem{ramark}{Remark}[section]
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}
% \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
% \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
% \doi{10.1109/ACCESS.2017.DOI}

% \title{Preparation of Papers for IEEE ACCESS}
% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
% Jr}.\authorrefmark{3},
% \IEEEmembership{Member, IEEE}}
% \address[1]{National Institute of Standards and 
% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
% 80309 USA}
% \tfootnote{This paragraph of the first footnote will contain support 
% information, including sponsor and financial support acknowledgment. For 
% example, ``This work was supported in part by the U.S. Department of 
% Commerce under Grant BS123456.''}

% \markboth
% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}

% \corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}
% .

% \begin{abstract}

% \end{abstract}

% \begin{keywords}
% Enter key words or phrases in alphabetical 
% order, separated by commas. For a list of suggested keywords, send a blank 
% e-mail to keywords@ieee.org or visit \underline
% {http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
% \end{keywords}

% \titlepgskip=-15pt

% \maketitle

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV). Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents (cite:MAS). However, the cost is that the design of such a multi-agent system becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, and cooperation between agents. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS). Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios. Although there are many types of UVs to make up such a system, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV). Additionally, the complementarity between them also makes such a system more potential. In other words, UAV is widely used in reconnaissance due to the high mobility. However, the carrying capacity of UAV is very low compared to UGV since there is no ground support. In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed. For these reasons, a hybrid UAV-UGV system will be more practical.

To construct an unmanned HMAS, it must be capable of perception, decision-making and execution. Perception is to obtain information through the sensor, decision-making is to make decisions through the sensor information, and execution is to execute the decision-making content through the actuator. To limit the scope of this paper, we focus on decision-making and execution for an UAVs-UGVs search and rescue system.

The four more specific main problem in decision-making and execution are task allocation problem (cite: task allocation), path planning problem (cite: path planning), local motion planning problem and tracking control problem. These four problems form a hierarchical structure in order. First, the UAVs-UGVs search and rescue system needs to be able to assign different tasks to agents to perform. After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it. To make agent move on the path, a motion corresponding to the actual mechanical system of the agent needs to be planned. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two problems. But to illustrate how the whole system works, the first two problems are also briefly stated.
% An unmanned search and rescue system needs to be able to assign different tasks to agents to perform. This problem is called the task allocation problem, which attempts to achieve an optimal allocation given the objective function and some constraints (cite: task allocation). After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it. This problem is called the path planning problem, which attempts to achieve an optimal path given the objective function and some constraints (cite: path planning).

To discuss the local motion planning problem and tracking control problem, a real mechanical system to which each agent corresponds must be considered. To meet the need for search mobility, we choose quadrotor aircraft as UAV. The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control). In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV. Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system. However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved. The local motion planning of the walking of biped robot, i.e., stable walking parttern generation, is discussed in this paper. Related researches can be found in (cite: walking parttern).

The local motion planning is the bridge between path planning and tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same. The reason is that path planning algorithm usually treats the agent as a point, while the actual agent is a mechanical system for the tracking control design. Although there are some literatures (ref:kinodynamic path planning) about path planning with the constraints of kinodynamic of the actual mechanical system, this paper splits it into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
% The aforemention two problems are widely studied in the field of computer science and field of control respectively but fewer papers point out their relationship with respect to specific agents (UAV and robot in this paper). Therefore, this paper will focus on this issue.

Tracking Problem ...

To the best of the authors' knowledge, most of the literature focus on only one specific problem, and few literatures illustrate the relationship between these problems for an unmanned HMAS. This leads us to propose an architecture of UAV-robot team system (URTS) for search and rescue although this paper mainly focuses on the local motion planning and tracking control problem.
% Based on the foregoing, an UAV-robot team system (URTS) is discussed in this paper.

% \PARstart{W}{ith}

The contributions of this study are described as follows:
\begin{enumerate}
    \item contribution 1 ...
\end{enumerate}

The remainder of the paper is organized as follows. In Section II, ...

\textbf{Notation 1:} 
% $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
$A^T$: transpose of A. $(a_n)$: sequence. $(a_{k_n})$: subsequence. $\vert{S}\vert$: size of a set $S$. $\otimes$: Kronecker product. $I_n$: n-dimension identity matrix. $x(t)\in L_2\begin{bmatrix}
    0,t_f 
\end{bmatrix}$ if $\int^{t_f}_{0}x^T(t)x(t)dt<\infty$.

\section{PRELIMINARIES OF search and rescue URTS}
The URTS will start with a given search and rescue area, and ends with searching task completed. The URTS is composed of $N$ teams and a ground station. Each team contains $1$ UAV and $M-1$ robots. The $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,M$ and $j=1,2,...,N$. The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

To complete search tasks, each team is designed to be responsible for a small area of the overall search area, and each agent will be assigned an appropriate path to cover the area. To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target. It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents. If each agent can only perform one task at a time, then there exist many feasible way of task allocation. Usually we want this allocation to be optimal, which can be achieved by solving the dynamic task allocation problem.

If a task is to reach a location of certain goal, there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, so each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby. That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

We need to design some behavior to follow the path found by path planning algorithm especially for agents with complex mechanical systems like robots. Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path). Furthermore, agents in a search and rescue system are not always following a trajectory. Sometimes they need the behavior such as stop to look around, get supplies and put supplies. To meet these needs, a behavioral layer is necessary. The behavior layer gives an appropriate behavior to fulfill an actual requirement. In order to make an behavior, we must design a corresponding motion which is handled by local motion planning. The motion is a desired reference trajectory for an actual mechanical system to follow. Finally, a tracking controller is designed to follow the desired reference trajectory.

To clarify this issue, a more detailed system architecture for each agent is needed. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents and an occupy map. The visual object recognition block provides distance information and object information through sensor info. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

% To determine the behavior, agent needs the information about enviroment. The sensing data which include external enviroment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).

\begin{figure}[htbp]
\centering
\includegraphics[scale=.5]{fig/sys.pdf}\caption{The system architecture of agent in URTS. The 2 blocks on left side are used to convert low-level sensor information into high-level information, such as map, start point and object information. The 5 blocks on right side are the flow of an agent performing a search and rescue mission. From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agent and task is more than one, and each agent has different capabilities (e.g. moving speed or load capacity) and status (e.g. their own position or the amount of supplies carried), and each task has different characteristics (e.g. Urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation. This problem is refered as Task Allocation Problem or Multi-robot Task Allocation (MRTA) Problem. A problem formulation and problem modeling can be found in \cite{Khamis2015}. Although there are many different problem definitions and many problem models to solve this issue, the common goal is to find a set of task-agent pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue. In other words, every agent knows a destinition it need to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}

\subsection{Path Planning}
After a target point is assigned for each agent, next step is to find a collision-free path from current position to it. There are several path planning algorithm to handle this problem, in this article, a roadmap-based path planning algorithm is used. This method attempts to discretize the search space into interconnected roads and find the path on it. According to the roadmap construction method, it can be divided into deterministic and sample-based. According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}. Multi-query planner divides pathfinding into learning phase in which a roadmap is bulit and query phase in which a graph search algorithm is used to find a best path within paths. Some representative planners are Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}. Relatively speaking, single-query planner completes pathfinding by constructing and querying at the same time, that is to say, the roadmap will be constructed incrementally and toward the goal. Some representative planners such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}. However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner. Some common dynamic planner also can be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning to deal with. The reason is that URTS is a large-scale system, which makes the environment in which it is located changes more violently and will leads to many corresponding behaviors which path constraints will not necessarily be the same (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot). In this case, Path Planning becomes a higher-level planner which regard agent as a point without kinodynamic constraints while the decision of the behavior and the corresponding motion will be handed over to the next two layers: Behavior Layer and Local Motion Planning.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$. Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques. Goal configuration is obtained by previous layer: Task Allocation. Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline. It's a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$. For a simpler explanation of how the URTS works, the following assumption is made.
\begin{assumption}
    The locating ability of the URTS is perfect so every agent can know its current configuration $q_{start}$.
\end{assumption}
\begin{assumption}
    A Task Allocation algorithm is already designed so that every agent can know its goal configuration $q_{goal}$.
\end{assumption}
\begin{assumption}
    The URTS is supposed to have an perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtain.
\end{assumption}
\begin{assumption} \label{asm:collision}
    UAVs do not consider obstacle collisions because there are few obstacles in the air. Hence, the path of UAVs can be directly assigned rather found by planner. Robots do not consider obstacle collisions in the direction perpendicular to the ground. 
\end{assumption}
From above assumption, a path of agent can be expressed as a sequence
\begin{equation}
    (\sigma_n), n\in\mathbb{Z}\cap[1,k_f], \sigma_n\in\mathcal{C}
\end{equation}
where $k_f$ is the time step when reaching goal. Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually. Let $(\sigma_{k_n})$ be the subsequence of $(\sigma_n)$, where $k_n$ is the time step when a replanning decision is occured. Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$. For agents, the replanning decision can be a goal changing that made by human or Task Allocation. For robot, it can be a collision detecting by a dynamic roadmap-based planner. The results path $(\sigma_n)$ is passed to next layer, Behavior Layer.

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path Planning tells agents where to go but not how. Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are called "moving" in this paper. Besides, the agents do not always moving. Somtimes they has to suspending to take a action such like getting and putting supplies, rotating in place to collect more environment info, or some unexpected situations occur such like no path found, the robot falls. These behaviors without changing position are called an "action" in this paper. More behaviors can be added so that the agent can have more way to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
It is to say that the path $(\sigma_n)$ is divided into many segments which corresponding to a specific behavior. The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.5]{fig/behavior.pdf}\caption{The structure of Behavior Layer. The leaf of the tree structure are the possible behaviors an agent can take. The behavior to be take at every moment will be decided in this block.}%
    \label{fig:behavior}
\end{figure*}

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve that behavior. Local Motion Planning is like Path Planning but its scale is smaller and its resolution and precision must be higher. Collision checking is needed since we consider agent as a point or a cube in Path Planning and it's a real body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often the same notion in other literature. Therefore, the output of this block is also a path but with a sampling period which often be referred as a reference trajectory $r(t)$. $r(t)$ describes the position and orientation that needed to be reach by a machine system govern by a dynamic equation. Then, Tracking Control block will track $r(t)$ to really do that behavior. Note that the path and trajectory are distinguished in some literature. Different from path (e.g., $(\sigma_n)$), a trajectory (e.g., $r(t)$) has consider the time in physic world. The flowchart of Local Motion Planning block is shown in Fig. \ref{fig:LocalMotionPlanning}

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/LMP.pdf}\caption{The flowchart of local motion planning. The corresponding motion design will be executed according to the behavior determined by the behavior layer.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

In Fig. \ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are added to illustrate the flow of this block. The terminator, exception, represents an exceptional condition that performs unconsidered behaviors. To limit the scope of this article, we only focus on the motion design of Flying (for UAV) and Walking (for robot) behavior which belong to Moving behavior. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block. It then convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.

\section{system description of UAV-Robot Team System}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot, the motion design of Flying and Walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.4]{fig/FandW.pdf}\caption{The flowchart of Flying and Walking. In both two blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final output is all reference path $r[k]$, but its actual size and dimensions will be different.}
    \label{fig:FandW}
\end{figure*}

Before the discussion of the motion design of these two behavior, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there all exists an inevitable kinematic constraint on curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant. At the same time, the assumption \ref{asm:cc again} makes sure the error will not causing collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion design process of these two behaviors as shown in Fig. \ref{fig:FandW}.

\subsection{motion design of flying of UAV}
A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
\begin{equation} \label{eq:uav} 
    \begin{split}
        \begin{bmatrix}
            f \\ \tau
        \end{bmatrix}&=\begin{bmatrix}
            mI & 0 \\ 0 & J
        \end{bmatrix}\begin{bmatrix}
            \ddot{X} \\ \ddot{\Theta}
        \end{bmatrix}+\begin{bmatrix}
            0 \\ \dot{\Theta}\times(J\dot{\Theta})
        \end{bmatrix}+\begin{bmatrix}
            f_g \\ 0
        \end{bmatrix}
        \\
        &+\begin{bmatrix}
            K_F & 0 \\
            0 & K_\tau
        \end{bmatrix}\begin{bmatrix}
            \dot{X} \\ \dot{\Theta}
        \end{bmatrix}
        % form 2
        % &R(\Theta)=\begin{bmatrix*}[l]
        %     \cos\theta\cos\phi & \sin\phi\sin\theta\cos\psi-\cos\phi\sin\psi & R_1 \\
        %     \cos\theta\sin\phi & R_2 & R_3 \\
        %     -\sin\theta & \sin\phi\cos\theta & R_4
        % \end{bmatrix*}
        % \\
        % &R_1=\cos\phi\sin\theta\cos\psi+\sin\phi\sin\psi
        % \\
        % &R_2=\sin\phi\sin\theta\sin\psi+\cos\phi\cos\psi
        % \\
        % &R_3=\cos\phi\sin\theta\sin\psi-\sin\phi\cos\psi
        % \\
        % &R_4=\cos\phi\cos\theta
    \end{split}
\end{equation}
where $J=\begin{bmatrix}
    J_{x} & 0 & 0 \\
    0 & J_{y} & 0 \\
    0 & 0 & J_{z}
\end{bmatrix}$, $K_F=\begin{bmatrix}
    K_{x} & 0 & 0 \\
    0 & K_{y} & 0 \\
    0 & 0 & K_{z}
\end{bmatrix}$, $K_\tau=\begin{bmatrix}
    K_{\tau_x} & 0 & 0 \\
    0 & K_{\tau_y} & 0 \\
    0 & 0 & K_{\tau_z}
\end{bmatrix}$, $f =\begin{bmatrix}
    f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
    0 \\ 0 \\ F
\end{bmatrix}$, $\tau=\begin{bmatrix}
    \tau_x \\ \tau_y \\ \tau_z
\end{bmatrix}$, $X=\begin{bmatrix}
    x \\ y \\ z
\end{bmatrix}$, $\Theta=\begin{bmatrix}
    \phi \\ \theta \\ \psi
\end{bmatrix}$, $f_g=\begin{bmatrix}
    0 \\ 0 \\ -mg
\end{bmatrix}$, $R(\Theta)=R_z(\psi)R_y(\theta)R_x(\phi)$, $R_z(\psi)=\begin{bmatrix} % form 1
    \cos\psi & -\sin\psi & 0 \\
    \sin\psi & \cos\psi & 0 \\
    0 & 0 & 1
\end{bmatrix}$, $R_y(\theta)=\begin{bmatrix}
    \cos\theta & 0 & \sin\theta \\
    0 & 1 & 0 \\
    -\sin\theta & 0 & \cos\theta
\end{bmatrix}$, $R_x(\phi)=\begin{bmatrix}
    1 & 0 & 0 \\
    0 & \cos\phi & -\sin\phi \\
    0 & \sin\phi & \cos\phi
\end{bmatrix}$.
% where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
$m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust. This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction. Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.
% For ease of discussion later, let us convert (\ref{eq:uav}) into the following form:
% \begin{equation}
%     F_w=M(X_w)\ddot{X_w}+C(\dot{X_w})+G(X_w)+F(\dot{X_w})
% \end{equation

Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed by linear interpolation and spline interpolation which give the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density. $(\sigma_n')$ is the position reference path $\begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k]
\end{bmatrix}^T$. Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are set. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.

% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.5]{fig/flying.pdf}\caption{flowchart of UAV flying}%
%     \label{fig:flying}
% \end{figure}

% task space $\mathcal{T}\subset\mathbb{R}^6$.
% The terminologies, task space and joint space, are often used in reference designed in robotics. Task space is the space which the task be assigned and joint space is the space of robot joints. The forward kinematic is the mapping from joint space to task space and inverse kinematic is the inverse mapping. Since the reference of robot is in joint space ...

\subsection{motion of walking of robot}
By Lagrange equation, the dynamic model of biped robot can be formulated as:
\begin{equation} \label{eq:robot} 
    \begin{split}
        & \tau = M(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
    \end{split}
\end{equation}
where $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector. The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}. For robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space. Furthermore, the walking of biped-robot suffers from the falling problem, i.e, how to find a stable walking parttern prevent robot from falling. These make the design of walking motion more difficult. In this paper, a three-dimensional linear inverted pendulum Mode (3D-LIPM) \cite{kajita2001real} is used to design the walking motion.

Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame as in \cite{ourrobot}, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon which is the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} ($\widehat{Y_b}$ direction as same form):
\begin{equation}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
It can be seen that ZMP is related to 12 link masses, moment of inertia, positions, accelerations, and angular velocities. This makes the analytical solution of reference $q_r(t)$ impossible. However, an approximate solution can be derived through 3D-LIPM which will find CoM reference first and then obtain $q_r(t)$ by using inverse kinemic (IK) given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model. Although the actual dynamic model is different from 3D-LIPM so there is an error between them, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

Following the same step in UAV, the smoothed path $(\sigma_n')$ for robot can be obtained at first. For ease of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$. Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance. Despite that, $(\sigma_n')$ tells the robot the position to go so the forward direction of robot can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the robot will move forward (rather than sideways or backward). To keep torso upright, the direction of $\widehat{Z_b}$ is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$. Given $\widehat{X_g}$ and $\widehat{Z_g}$, $\widehat{Y_b}$ can be obtained obviously through cross product. Since the origin of body frame $\{ \widehat{X_g}, \widehat{Y_g}, \widehat{Z_g} \}$ is CoM, the sequence of CoM orientation $(CO_n)$ can be obtained through the above steps.

\begin{remark}
    A frame in $\mathbb{R}^3$ can be determined by given the "position" and "orientation" with respect to a reference frame. That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK. Hence, we need to find the  position path and orientation path which compose the desired path.
\end{remark}

Let us denote the $x$ and $y$ component of $\sigma_n'$ in $(\sigma_n')$ as the sequence $(\sigma^{1}_{n}), \sigma^{1}_{n}\in\mathbb{R}^2$. The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation between $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is feet width (or shoulder width). Then the $x$ and $y$ component of left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively. Finally, left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding $z$ component which is given by ground height.

After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed. Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component are given by step height. By using spline interpolation, we have the left and right ankle position path $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$. The ankle orientation path is found by gradient of ground. Finally, the ankle path is found by combining the position and orientation path together. So far, the remaining work is to find out the CoM path and then to combine with the ankle path to calculate the joint path through IK.

To obtain CoM postion path, ZMP path need to obatin first. ZMP path is obatin through ankle path since ZMP needs to lie in the support face and ankle path point out when a feet is stand on the ground. After that, ZMP path is used to produce CoM postion path by 3D-LIPM as follow:
\begin{equation} \label{eq:LIPM}
    \begin{split}
        & \ddot{x} = \frac{g}{z_c}(x - p_x) \\
        & \ddot{y} = \frac{g}{z_c}(y - p_y)
    \end{split}
\end{equation}
where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, $z_c$ is the CoM height, and $(p_x,p_y)$ is the position of ZMP. To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
\begin{equation} \label{eq:output tracking}
    \begin{split}
        & \dot{\bar{x}} = A\bar{x} + Bu \\
        & p_x = C\bar{x}
    \end{split}
\end{equation}
where $\bar{x} = \begin{bmatrix}
    x \\ \dot{x} \\ \ddot{x}
\end{bmatrix}$, $A = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}$, $B = \begin{bmatrix}
    0 \\ 0 \\ 1
\end{bmatrix}$, and $C = \begin{bmatrix}
    1 & 0 & -z_c/g
\end{bmatrix}$. Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference path so that the state variable $x$ is found, which is the CoM position path we want. Unlike conventional methods, the problem is solved by optimal control. The system is discretized first and the discrete LQ tracker is employed to achieve the output tracking. The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}. The CoM position path in the $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form.

By combining the CoM position and orientation path, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot is found by solving IK.

\section{Reference Tracking control}
00
After the reference trajectory is set, the last step is to design a controller for a agent to track it. To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
\begin{equation} \label{eq:agent} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t)
\end{equation}
where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector. Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor. Besides, its integration $\int_{0}^{t} x(\tau) d\tau$ and differentiation $\dot{x}(t)$ can also be measured by sensor respectively for PID control. Then, the output equation can be formulated as:
\begin{equation} \label{eq:agent output}
    y(t) = C\pmb{x}(t)
\end{equation}
where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is a known output matrix, and $\pmb{x}(t)=\begin{bmatrix}
    \int_{0}^{t} x^T(\tau) d\tau & x^T(t) & \dot{x}^T(t)
\end{bmatrix}^T$. Futhermore, to make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For agent, there exists
    \begin{enumerate*}
        \item coupling effect due to co-channel interference in communication between agents and
        \item cyber-attack on communication network between agents and ground station.
    \end{enumerate*}
    \item For UAV, there exists wind disturbance \cite{9075385}.
    \item For robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
Suppose the above disturbances can be equivalently expressed as the disturbances $d_i(t), i=1,2$ in the nominal model (\ref{eq:agent}) and (\ref{eq:agent output}), the real agent model is given as:
\begin{equation} \label{eq:nonlinear sys} 
    \begin{split}
        & M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t) = u(t)\\
        & y(t) = C\pmb{x}(t) + d_2(t)
    \end{split}
\end{equation}
For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed. Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.

\subsection{$H_\infty$ observer-based PID FTC for linear system}
Given a linear system with fault signals:
\begin{equation} \label{eq:4}
    \begin{split}
        & \dot{x}(t)=Ax(t)+B(u(t)+f_1(t)) \\
        & y(t)=Cx(t)+f_2(t)   
    \end{split}  
\end{equation}
where $x(t)\in\mathbb{R}^n$, $u(t)\in\mathbb{R}^m$, $y(t)\in\mathbb{R}^l$, and $f_i:\mathbb{R}\rightarrow \mathbb{R}^{n_i}, f_i(t)\in C^{1}, i=1,2$ with $n_1=m$ and $n_2 = l$.

\textit{
    \begin{remark}
        The fault signal $f_i(t), i=1,2$ are assumed to be smooth rather than bounded, which will make the proposed method more general for practical scenario.
    \end{remark}
}

To deal with the fault signals, an active fault tolerance control is introduced \cite{9306757}. In general, constructing a model for an unknown signal is impossible. However, a smooth model can be used to describe a signal under the smooth assumption. Unlike previous work, a finite-difference-method-based method is proposed to reduce the approximation error between origin fault signal and its smooth model.

From finite difference method, the derivative of the fault signals $\dot{f}_i(t), i=1,2$ with uniform grid $h$ can be expressed as:
\begin{equation} \label{eq:df}
    \dot{f}_i(t)=\sum_{k\in{Z_0}}\frac{a_k f_i(t-kh)}{h} + R_{p-1}(t), Z_0\subset\mathbb{Z}
\end{equation}
where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference. For constructing a state-space representation, the derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed. For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$. Then, we can obtain the following equation by (\ref{eq:df}) by changing index $k$ to $j$:
\begin{equation} \label{eq:df1}
    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t), j=0,1,\dots,p-1
\end{equation}
where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
\begin{equation} \label{eq:7}
    \dot{F}_i(t)=A_iF_i(t)+v_i(t)
\end{equation}
where $v_i(t)=\begin{bmatrix}
    \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
\end{bmatrix}^T$, $F_i(t)=\begin{bmatrix}
    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n_i}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
\begin{equation} \label{eq:8}
    f_i(t)=C_iF_i(t)
\end{equation}
where $C_i=\begin{bmatrix}
    1 & 0 & \dots & 0
\end{bmatrix}\otimes I_{n_i}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:4}), we get:
\begin{equation} \label{eq:9}
    \begin{split}
        & \dot{\bar{x}} = \bar{A}\bar{x}+\bar{B}u+\bar{v} \\
        & y=\bar{C}\bar{x}
    \end{split}
\end{equation}
where $\bar{x} = \begin{bmatrix}
    x \\ F_1 \\ F_2
\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
    A & BC_1 & 0 \\
    0 & A_1 & 0 \\
    0 & 0 & A_2
\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
    B \\ 0 \\ 0
\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
    C & 0 & C_2
\end{bmatrix}$, and $\bar{v}=\begin{bmatrix}
    0 \\ v_1 \\ v_2
\end{bmatrix}$. Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimat them and origin state simutaniously:
\begin{equation} \label{eq:10}
    \begin{split}
        & \dot{\hat{\bar{x}}}=\bar{A}\hat{\bar{x}}+\bar{B}u+{L}(y-\hat{y}) \\
        & \hat{y}=\bar{C}\hat{\bar{x}}  
    \end{split}
\end{equation}
\begin{assumption}
    The augmented system (\ref{eq:9}) is observable.
\end{assumption}
The PID FTC law is given as:
\begin{equation} \label{eq:11}
    u=K\hat{\bar{x}}
\end{equation}
where $K = \begin{bmatrix}
    K_I & K_P & K_D & K_{F_1} & K_{F_2}
\end{bmatrix}$ is total control gain, $K_P,K_I,K_D$ are PID control gain, and $K_{F_i}, i=1,2$ are fault control gain. Let us define the estimation error $\hat{\bar{e}}=\bar{x}-\hat{\bar{x}}$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
\begin{equation} \label{eq:aug}
    \dot{\tilde{x}} = \tilde{A}\tilde{x}+\tilde{v}
\end{equation}
where $\tilde{x}=\begin{bmatrix}
    \bar{x} \\ \hat{\bar{e}}
\end{bmatrix}$, $\tilde{A}=\begin{bmatrix}
    \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
\end{bmatrix}$, and $\tilde{v}=\begin{bmatrix}
    \bar{v} \\ 0
\end{bmatrix}$

The tracking control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
\begin{equation} \label{Hinf}
    H_{\infty}(K, L) = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2 
\end{equation}
where $t_f$ is the final time, $Q > 0$ is the weighting matrix of tracking and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated. If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy. To find these gains, the following theroem is given.
\begin{theorem} \label{theorem1}
    If
    $$\begin{bmatrix}
        & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
        & \ast  & M_{22} & 0 & P_2 \\
        & \ast & \ast & -I & 0 \\
        & \ast & \ast & \ast & -\rho^2 
    \end{bmatrix}\leq 0 $$
    where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$. Then system (\ref{eq:aug}) achieve $H_\infty$ observer-base stabilized control performance (\ref{Hinf}).
\end{theorem}
\begin{proof}
    proof...
\end{proof}

\subsection{$H_\infty$ observer-based feedback linearization-based PID FTC for agents}
If we can transform the nonlinear system (\ref{eq:nonlinear sys}) to a linear system, the tracking problems for UAV and robot can be solved by Theorem \ref{theorem1}. An feedback linearization-based control law is uesd to solve this issue, which is given as follow:
% To obtain state variable by output measurement, an observer is proposed:
% \begin{equation} \label{eq:nonlinear obs} 
%     \begin{split}
%         & u(t) = M(\hat{x}(t))\ddot{\hat{x}(t)} + H(\hat{x}(t),\dot{\hat{x}(t)})\\
%         & \hat{y}(t) = C\hat{x}(t)
%     \end{split}
% \end{equation}
\begin{equation} \label{eq:control}
    u(t)= M(x_e(t))(\ddot{r}(t) + u_{fb}(t)) + H(x_e(t),\dot{x}_e(t))    
    % & u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F} \\ 
\end{equation}
where $x_e(t)=x(t) + \Delta e(t)$, $\Delta e(t)=e(t)-\hat{e}(t)$ is the error between tracking error $e(t) = x(t) - r(t)\in\mathbb{R}^n$ and estimation of tracking error $\hat{e}(t)$, $u_{fb}(t)$ is feedback control law, and the other term in (\ref{eq:control}) is feed-foward control law for canceling nonlinearity. Substitute (\ref{eq:control}) into state equation (\ref{eq:nonlinear sys}), we get:
\begin{equation}\begin{split} \label{eq:21}
    & M(x_e(t))(\ddot{r}(t) + u_{fb}) + H(x_e(t),\dot{x}_e(t)) \\
    & = M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t)       
\end{split}
\end{equation}
By subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides of (\ref{eq:21}):
\begin{equation} \label{eq:22}
    -\Delta M \ddot{r}(t) + M(x_e(t))u_{fb} = M(x(t))\ddot{e}(t) + \Delta H + d_1(t)
\end{equation}
where $\Delta M = M(x(t)) - M(x_e(t)), \Delta H = H(x(t),\dot{x}(t)) - H(x_e(t),\dot{x}_e(t))$ is the error terms due to difference between true state and estimated state. By Multipling $M(x(t))^{-1}$ from the left and right sides of (\ref{eq:22}) with arrangment, we have:
\begin{equation} \label{eq:23}
    \ddot{e}(t) = u_{fb}(t) + d_3(t)
\end{equation}
where $d_3(t) = -M(x(t))^{-1}(\Delta M(\ddot{r}(t)+u_{fb}) + \Delta H + d_1(t))$. Let $\pmb{e}(t)=\begin{bmatrix}
    \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
\end{bmatrix}\in\mathbb{R}^{3n}$, (\ref{eq:23}) can be rewrited as:
\begin{equation} \label{eq:24}
    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t))
\end{equation}
where $ A = A_0\otimes I_n, B = B_0\otimes I_n$
with $A_0 = \begin{bmatrix}
    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
\end{bmatrix}, B_0 = \begin{bmatrix}
0 \\ 0 \\ 1
\end{bmatrix} $. Since $C$ is known, we can let $\pmb{y}(t) = y(t) - C\pmb{r}(t)\in\mathbb{R}^{ln}$ where $\pmb{r}(t) = \begin{bmatrix}
    \int_{0}^{t} r^T(\tau) d\tau & r^T(t) & \dot{r}^T(t)
\end{bmatrix}^T$. Then, the output equation in (\ref{eq:nonlinear sys}) can be modified as:
\begin{equation} \label{eq:25}
    \pmb{y}(t) = C\pmb{e}(t) + d_2(t)
\end{equation}
% where $d_4(t) = \Delta C + d_3(t)$ with $\Delta C = C(x(t)-\hat{x}(t))$. 
Combining (\ref{eq:24}) and (\ref{eq:25}), we obtain the linearized system:
\begin{equation} \label{eq:linear sys}
    \begin{split}
        & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t)) \\
        & \pmb{y}(t)=C\pmb{e}(t)+d_2(t)   
    \end{split}  
\end{equation}
By Theorem \ref{theorem1}, the form show that the system (\ref{eq:nonlinear sys}) can achieve $H_\infty$ performance with the observer
\begin{equation} \label{eq:linear obs}
    \begin{split}
        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t) + \bar{B}u_{fb}(t) + L(\pmb{y}(t)-\hat{y}(t)) \\
        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)   
    \end{split}  
\end{equation}
and the control law (\ref{eq:control})
where $\hat{\bar{e}}(t)=\begin{bmatrix}
    \hat{\pmb{e}} \\ \hat{F}_1 \\ \hat{F}_2
\end{bmatrix}$, $\hat{\pmb{e}} = \begin{bmatrix}
    \int_{0}^{t} \hat{e}(\tau) d\tau \\ \hat{e}(t) \\ \dot{\hat{e}}(t)
\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
    A & BC_1 & 0 \\
    0 & A_1 & 0 \\
    0 & 0 & A_2
\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
    B \\ 0 \\ 0
\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
    C & 0 & C_2
\end{bmatrix}$, and $u_{fb}=K\hat{\bar{e}}$.
\textit{
    \begin{remark}
        Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
    \end{remark}
}

Although the control gain and observer gain that satisfy the specification can already be found by Theorem \ref{theorem1}, the calculation speed can be further improved by reducing the dimensionality of the system. Since the feedback linearization eliminates the nonlinearity and some degree of coupling of the system (\ref{eq:4}), it can be further split into $n$ subsystems if the output matrix $C$ have the same form to $A$ and $B$, i.e., $C = C_0\otimes I_n$, where $n$ is dimension of state vector and $C_0\in\mathbb{R}^{l\times 3}$.
Due to the fact that $d_3(t)\in\mathbb{R}^n, d_4(t)\in\mathbb{R}^{ln}$, the n subsystems are obtained from (\ref{eq:linear sys}):
\begin{equation} \label{eq:linear subsys}
    \begin{split}
        & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fd,i}(t)+d_{3,i}(t)) \\
        & \pmb{y}_i(t)=C_0\pmb{e}_i(t)+d_{2,i}(t)   
    \end{split}
\end{equation}
where subscript $i = 1, 2, ..., n$ denote the element in the corresponding vector. By Theorem \ref{theorem1} again, the form show that the subsystems (\ref{eq:linear subsys}) can achieve $H_\infty$ performance. Let $K_i$ be the control gain of subsystems, the origin control gain $K$ of origin agent system can be obtained by $K = \begin{bmatrix}
    \mathit{v}_1 & \mathit{v}_2 & ... & \mathit{v}_n
\end{bmatrix}^T, \mathit{v}_i=K_i\otimes\mathbf{e}_i$ where $\mathbf{e}_i$ is standard unit vectors in $\mathbb{R}^n$. The origin observer gain $L$ can be obtained in the same way. In this case, the calculate speed is improved ...
\textit{
    \begin{remark}
        This method can regard as designing the control and observer gain to each state variable, which is a common control method in practice. However, the gains are not directly adjusted but indirectly designed through prescribed specifications (\ref{Hinf}). Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i$). Depending on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i$ and attenuation levels $\rho_i$ for each subsystem.
    \end{remark}
}

\subsection{UAV reference trajectory design and overall flowchart}
Although the design of the agent controller and observer has been completed, the trajectory design of UAV is not done yet. Since the UAV is an underactuated system, the "virtual" control input for UAV $u(t)=\begin{bmatrix}
    f_x & f_y & f_z & \tau_x & \tau_y & \tau_z 
\end{bmatrix}^T\in\mathbb{R}^6$ that obtained from Theorem \ref{theorem1} needs to convert to actual control input $u'(t)=\begin{bmatrix}
    F & \tau_x & \tau_y & \tau_z 
\end{bmatrix}^T\in\mathbb{R}^4$. As the same time, the extra two degrees of freedom are used to find the remaining two reference trajectories $\phi_r(t)$ and $\theta_r(t)$ through inverse dynamics. In simple terms, we want to find a total force $F$ and its angles $\phi_r$, $\theta_r$ and $\psi_r$ from the three component forces $f_x$, $f_y$ and $f_z$. By substituting $\Theta=\begin{bmatrix}
    \phi_r \\ \theta_r \\ \psi_r
\end{bmatrix}$ into $\begin{bmatrix}
        f_x \\ f_y \\ f_z
    \end{bmatrix} = R(\Theta)\begin{bmatrix}
        0 \\ 0 \\ F
\end{bmatrix} $ from UAV dynacmis (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.

The overall flowchart of Tracking Control is shown in Fig. \ref{fig:tracking}.

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.5]{fig/tracking.pdf}\caption{flowchart of Tracking Control}%
    \label{fig:tracking}
\end{figure*}

The reference generator for robot is an identity function since it is a fully actuated system. The sensing information includes the agent's own information and environmental info, which is passed back to the high-level block for positioning, mapping and object recognition. Self information is passed to the observer for estimation and tracking error correction.

\section{simulation results}

\section{conclusion}
% \subsection{tracking control of UAV-robot team}
% Since the dynamical system of UAV (\ref{eq:uav}) and robot (\ref{eq:robot}) are nonlinear, it is not easy to design the controller relative to the linear system
% Use feedback linearization, dynamic of UAV and robot become the form (\ref{eq:4})...

% \subsection{reference trajectories design of UAV-robot team}
% \textit{Assumption :} The behavior of uavs and robots is always at "fly" and "walk" respectively during the whole process. 
% \textit{Assumption :} Robots always walking on a flat ground.
% \subsection{path planning of UAV-robot team}
% In order to facilitate the verification of the feasibility of URTS, the following assumptions are given

% \nocite{*}
\bibliographystyle{unsrt}
\bibliography{citation}

\EOD

\end{document}

### 2022-07-22 paper/paper.tex
11 test
M(r(t)) better

@@
 \section{Reference Tracking control}
-00
-After the reference trajectory is set, the last step is to design a controller for a agent to track it.
+After the reference trajectory $r(t)$ is set, the last step is to design a controller for a agent to track it.
 To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
@@
 where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector.
+In order to transform the tracking control problem into a stability problem, we define the tracking error $e(t)\triangleq x(t)-r(t)$.
 Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor.

### 2022-07-22 test/Robot/oneRobot/oneRobot2.m

@@ -120,7 +120,7 @@ if EXE.TRAJ
     %% set disturbance
     rb.tr.f1    = repmat(.2*sin(1*rb.tr.t), sys_a.DIM, 1);
     % rb.tr.f2    = repmat(.01*sin(1*rb.tr.t), sys_s.DIM, 1);
-    rb.tr.f2    = 0.01*ones(sys_s.DIM, rb.tr.LEN);
+    rb.tr.f2    = 0.1*ones(sys_s.DIM, rb.tr.LEN);
 
     rb = rb.trajectory();
     rb.Save('tr');

### 2022-07-22 paper/paper.tex
tilde x

--- 2022-07-22 paper/paper.tex
@@
 The URTS will start with a given search and rescue area, and ends with searching task completed.
-The URTS is composed of $N$ teams and a ground station.
-Each team contains $1$ UAV and $M-1$ robots.
-The $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,M$ and $j=1,2,...,N$.
+The URTS is composed of $N_j$ teams and a ground station.
+Each team contains $1$ UAV and $N_i-1$ robots.
+Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_i$ and $j=1,2,...,N_j$.
 The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$.
@@
 \section{Reference Tracking control}
-00
-After the reference trajectory is set, the last step is to design a controller for a agent to track it.
+After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it.
 To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
@@
 where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector.
-Suppose the state $x(t)$ is unavailable, i.e., $x(t)$ needs to be obtained by sensor.
-Besides, its integration $\int_{0}^{t} x(\tau) d\tau$ and differentiation $\dot{x}(t)$ can also be measured by sensor respectively for PID control.
-Then, the output equation can be formulated as:
-\begin{equation} \label{eq:agent output}
-    y(t) = C\pmb{x}(t)
+The control law is given as:
+\begin{equation} \label{eq:control}
+    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
 \end{equation}
-where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is a known output matrix, and $\pmb{x}(t)=\begin{bmatrix}
-    \int_{0}^{t} x^T(\tau) d\tau & x^T(t) & \dot{x}^T(t)
-\end{bmatrix}^T$. Futhermore, to make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
+where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms to canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law.
+To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
 \begin{enumerate}
-    \item For agent, there exists
-    \begin{enumerate*}
-        \item coupling effect due to co-channel interference in communication between agents and
-        \item cyber-attack on communication network between agents and ground station.
-    \end{enumerate*}
+    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9448458}.
+    \item For agent, there exists cyber-attack on communication network between agents and ground station.
+    \item For agent, there exists sensor noise.
     \item For UAV, there exists wind disturbance \cite{9075385}.
@@
 \end{enumerate}
+Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
+Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command.
+In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}).
+Therefore, through appropriate conversion, the above disturbances can be equivalent to an disturbance force $d_1(t)$.
+The nominal system (\ref{eq:agent}) then be rewrited as the real system:
+% The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
+\begin{equation} \label{eq:agent d1} 
+    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + d_1(t)
+\end{equation}
 % \subsubsection{Internal uncertainties}
@@
 % where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
-Suppose the above disturbances can be equivalently expressed as the disturbances $d_i(t), i=1,2$ in the nominal model (\ref{eq:agent}) and (\ref{eq:agent output}), the real agent model is given as:
-\begin{equation} \label{eq:nonlinear sys} 
+Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(r(t))\ddot{x}(t)$ from the left and right sides, we have:
+\begin{equation} \label{eq:agent1}
     \begin{split}
-        & M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t) = u(t)\\
-        & y(t) = C\pmb{x}(t) + d_2(t)
+        & (M(x(t))-M(r(t)))\ddot{x}(t) + H(x(t),\dot{x}(t)) \\
+        & =(M(r(t))(\ddot{r}(t)-\ddot{x}(t)) + M(r(t))u_{fb}(t) \\
+        & + H(r(t),\dot{r}(t)) + d_1(t)
     \end{split}
 \end{equation}
-For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed.
-Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.
+By Multipling $M(r(t))^{-1}$ from the left and right sides and with some arrangments, we have:
+\begin{equation} \label{eq:23}
+    \ddot{e}(t) = u_{fb}(t) + f_1(t)
+\end{equation}
+where $f_1(t) = M(r(t))^{-1}(-\Delta M(\ddot{x}(t)) -\Delta H + d_1(t))$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensationand, and $e(t)= x(t)-r(t)$ is the tracking error.
+% \textit{
+%     \begin{remark}
+%         Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
+%     \end{remark}
+% }
+Let $\pmb{e}(t)=\begin{bmatrix}
+    \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
+\end{bmatrix}\in\mathbb{R}^{3n}$, (\ref{eq:23}) can be rewrited as:
+\begin{equation} \label{eq:linear f1}
+    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t))
+\end{equation}
+where $ A = A_0\otimes I_n, B = B_0\otimes I_n$
+with $A_0 = \begin{bmatrix}
+    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
+\end{bmatrix}, B_0 = \begin{bmatrix}
+0 \\ 0 \\ 1
+\end{bmatrix}$.
 
-\subsection{$H_\infty$ observer-based PID FTC for linear system}
-Given a linear system with fault signals:
+Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the fault tolerance stable control problem of linear system (\ref{eq:linear f1}).
+The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make it stable.
+In a real system, the feedback information is measured by sensor, i.e, the state $\pmb{e}(t)$ in (\ref{eq:linear f1}) is unavailable.
+As mentioned before, the external disturbances on sensor also need to be considered.
+Since the sensor information (\ref{eq:agent output}) will transmitted back to the ground station through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are considered.
+The total effect can be equivalent to an sensor fault signal $f_2(t)$.
+The measurement output equation is formulated as:
+\begin{equation} \label{eq:agent output}
+    y(t) = C\pmb{e}(t) + f_2(t)
+\end{equation}
+where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is output matrix. By combining (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have:
 \begin{equation} \label{eq:4}
     \begin{split}
-        & \dot{x}(t)=Ax(t)+B(u(t)+f_1(t)) \\
-        & y(t)=Cx(t)+f_2(t)   
+        & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t)) \\
+        & y(t) = C\pmb{e}(t) + f_2(t)   
     \end{split}  
@@
 where $x(t)\in\mathbb{R}^n$, $u(t)\in\mathbb{R}^m$, $y(t)\in\mathbb{R}^l$, and $f_i:\mathbb{R}\rightarrow \mathbb{R}^{n_i}, f_i(t)\in C^{1}, i=1,2$ with $n_1=m$ and $n_2 = l$.
-
+% For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed.
+Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.
 \textit{
@@
     \begin{split}
-        & \dot{\bar{x}} = \bar{A}\bar{x}+\bar{B}u+\bar{v} \\
-        & y=\bar{C}\bar{x}
+        & \dot{\bar{e}}(t) = \bar{A}\bar{e}(t)+\bar{B}u_{fb}(t)+\bar{v}(t) \\
+        & y(t)=\bar{C}\bar{e}(t)
     \end{split}
 \end{equation}
-where $\bar{x} = \begin{bmatrix}
-    x \\ F_1 \\ F_2
+where $\bar{e}(t) = \begin{bmatrix}
+    \pmb{e}(t) \\ F_1 \\ F_2
 \end{bmatrix}$, $\bar{A}=\begin{bmatrix}
@@
     C & 0 & C_2
-\end{bmatrix}$, and $\bar{v}=\begin{bmatrix}
-    0 \\ v_1 \\ v_2
+\end{bmatrix}$, and $\bar{v}(t)=\begin{bmatrix}
+    0 \\ v_1(t) \\ v_2(t)
 \end{bmatrix}$. Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimat them and origin state simutaniously:
@@
     \begin{split}
-        & \dot{\hat{\bar{x}}}=\bar{A}\hat{\bar{x}}+\bar{B}u+{L}(y-\hat{y}) \\
-        & \hat{y}=\bar{C}\hat{\bar{x}}  
+        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{x}}(t)+\bar{B}u_{fb}(t)+{L}(y(t)-\hat{y}(t)) \\
+        & \hat{y}(t)=\bar{C}\hat{\bar{x}}(t)  
     \end{split}
@@
 \begin{equation} \label{eq:11}
-    u=K\hat{\bar{x}}
+    u_{fd}(t)=K\hat{\bar{e}}(t)
 \end{equation}
@@
 \end{bmatrix}$ is total control gain, $K_P,K_I,K_D$ are PID control gain, and $K_{F_i}, i=1,2$ are fault control gain.
-Let us define the estimation error $\hat{\bar{e}}=\bar{x}-\hat{\bar{x}}$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
+Let us define the estimation error $\tilde{e}=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
 \begin{equation} \label{eq:aug}
-    \dot{\tilde{x}} = \tilde{A}\tilde{x}+\tilde{v}
+    \dot{\tilde{x}}(t) = \tilde{A}\tilde{x}(t)+\tilde{v}(t)
 \end{equation}
-where $\tilde{x}=\begin{bmatrix}
-    \bar{x} \\ \hat{\bar{e}}
+where $\tilde{x}(t)=\begin{bmatrix}
+    \bar{e}(t) \\ \tilde{e}(t)
 \end{bmatrix}$, $\tilde{A}=\begin{bmatrix}
     \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
-\end{bmatrix}$, and $\tilde{v}=\begin{bmatrix}
-    \bar{v} \\ 0
+\end{bmatrix}$, and $\tilde{v}(t)=\begin{bmatrix}
+    \bar{v}(t) \\ 0
 \end{bmatrix}$
@@
 \end{equation}
-where $t_f$ is the final time, $Q > 0$ is the weighting matrix of tracking and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
+where $t_f$ is the final time, $Q > 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
 
-\subsection{$H_\infty$ observer-based feedback linearization-based PID FTC for agents}
-If we can transform the nonlinear system (\ref{eq:nonlinear sys}) to a linear system, the tracking problems for UAV and robot can be solved by Theorem \ref{theorem1}.
-An feedback linearization-based control law is uesd to solve this issue, which is given as follow:
-% To obtain state variable by output measurement, an observer is proposed:
-% \begin{equation} \label{eq:nonlinear obs} 
-%     \begin{split}
-%         & u(t) = M(\hat{x}(t))\ddot{\hat{x}(t)} + H(\hat{x}(t),\dot{\hat{x}(t)})\\
-%         & \hat{y}(t) = C\hat{x}(t)
-%     \end{split}
+% \begin{equation}      
+%     u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F}
 % \end{equation}
-\begin{equation} \label{eq:control}
-    u(t)= M(x_e(t))(\ddot{r}(t) + u_{fb}(t)) + H(x_e(t),\dot{x}_e(t))    
-    % & u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F} \\ 
-\end{equation}
-where $x_e(t)=x(t) + \Delta e(t)$, $\Delta e(t)=e(t)-\hat{e}(t)$ is the error between tracking error $e(t) = x(t) - r(t)\in\mathbb{R}^n$ and estimation of tracking error $\hat{e}(t)$, $u_{fb}(t)$ is feedback control law, and the other term in (\ref{eq:control}) is feed-foward control law for canceling nonlinearity.
-Substitute (\ref{eq:control}) into state equation (\ref{eq:nonlinear sys}), we get:
-\begin{equation}\begin{split} \label{eq:21}
-    & M(x_e(t))(\ddot{r}(t) + u_{fb}) + H(x_e(t),\dot{x}_e(t)) \\
-    & = M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) + d_1(t)       
-\end{split}
-\end{equation}
-By subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides of (\ref{eq:21}):
-\begin{equation} \label{eq:22}
-    -\Delta M \ddot{r}(t) + M(x_e(t))u_{fb} = M(x(t))\ddot{e}(t) + \Delta H + d_1(t)
-\end{equation}
-where $\Delta M = M(x(t)) - M(x_e(t)), \Delta H = H(x(t),\dot{x}(t)) - H(x_e(t),\dot{x}_e(t))$ is the error terms due to difference between true state and estimated state.
-By Multipling $M(x(t))^{-1}$ from the left and right sides of (\ref{eq:22}) with arrangment, we have:
-\begin{equation} \label{eq:23}
-    \ddot{e}(t) = u_{fb}(t) + d_3(t)
-\end{equation}
-where $d_3(t) = -M(x(t))^{-1}(\Delta M(\ddot{r}(t)+u_{fb}) + \Delta H + d_1(t))$. Let $\pmb{e}(t)=\begin{bmatrix}
-    \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
-\end{bmatrix}\in\mathbb{R}^{3n}$, (\ref{eq:23}) can be rewrited as:
-\begin{equation} \label{eq:24}
-    \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t))
-\end{equation}
-where $ A = A_0\otimes I_n, B = B_0\otimes I_n$
-with $A_0 = \begin{bmatrix}
-    0 & 1 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0
-\end{bmatrix}, B_0 = \begin{bmatrix}
-0 \\ 0 \\ 1
-\end{bmatrix} $. Since $C$ is known, we can let $\pmb{y}(t) = y(t) - C\pmb{r}(t)\in\mathbb{R}^{ln}$ where $\pmb{r}(t) = \begin{bmatrix}
-    \int_{0}^{t} r^T(\tau) d\tau & r^T(t) & \dot{r}^T(t)
-\end{bmatrix}^T$. Then, the output equation in (\ref{eq:nonlinear sys}) can be modified as:
-\begin{equation} \label{eq:25}
-    \pmb{y}(t) = C\pmb{e}(t) + d_2(t)
-\end{equation}
-% where $d_4(t) = \Delta C + d_3(t)$ with $\Delta C = C(x(t)-\hat{x}(t))$. 
-Combining (\ref{eq:24}) and (\ref{eq:25}), we obtain the linearized system:
-\begin{equation} \label{eq:linear sys}
-    \begin{split}
-        & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+d_3(t)) \\
-        & \pmb{y}(t)=C\pmb{e}(t)+d_2(t)   
-    \end{split}  
-\end{equation}
-By Theorem \ref{theorem1}, the form show that the system (\ref{eq:nonlinear sys}) can achieve $H_\infty$ performance with the observer
-\begin{equation} \label{eq:linear obs}
-    \begin{split}
-        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t) + \bar{B}u_{fb}(t) + L(\pmb{y}(t)-\hat{y}(t)) \\
-        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)   
-    \end{split}  
-\end{equation}
-and the control law (\ref{eq:control})
-where $\hat{\bar{e}}(t)=\begin{bmatrix}
-    \hat{\pmb{e}} \\ \hat{F}_1 \\ \hat{F}_2
-\end{bmatrix}$, $\hat{\pmb{e}} = \begin{bmatrix}
-    \int_{0}^{t} \hat{e}(\tau) d\tau \\ \hat{e}(t) \\ \dot{\hat{e}}(t)
-\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
-    A & BC_1 & 0 \\
-    0 & A_1 & 0 \\
-    0 & 0 & A_2
-\end{bmatrix}$, $\bar{B}=\begin{bmatrix}
-    B \\ 0 \\ 0
-\end{bmatrix}$, $\bar{C}=\begin{bmatrix}
-    C & 0 & C_2
-\end{bmatrix}$, and $u_{fb}=K\hat{\bar{e}}$.
-\textit{
-    \begin{remark}
-        Although the error terms $\Delta e$, $\Delta M$ and $\Delta H$ caused by the difference between state $x(t)$ and estimated state $\hat{x}(t)$ are not necessarily bounded, they can still be estimated as long as they are smooth.
-    \end{remark}
-}
 

### 2022-07-28 paper/paper.tex
introduction

@@
 Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV).
-Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents (cite:MAS).
-However, the cost is that the design of such a multi-agent system becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, and cooperation between agents.
+Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
+However, the cost is that the design of such a multi-agent system becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents.
 In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS).
@@
 In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed.
-For these reasons, a hybrid UAV-UGV system will be more practical.
+For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
 
-To construct an unmanned HMAS, it must be capable of perception, decision-making and execution.
-Perception is to obtain information through the sensor, decision-making is to make decisions through the sensor information, and execution is to execute the decision-making content through the actuator.
-To limit the scope of this paper, we focus on decision-making and execution for an UAVs-UGVs search and rescue system.
+To construct an unmanned HMAS, the three key capabilities are perception, decision-making and control.
+Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision-making content through the actuator.
+To limit the scope of this paper, we focus on decision-making and control only.
+The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
+Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc (cite: task allocation).
+Path planning is to optimally plan paths to each agent, subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc (cite: path planning).
+Collision avoidance is to avoid collision with obstacles.
+Although collision avoidance is often concerned in path planning part, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.
 
-The four more specific main problem in decision-making and execution are task allocation problem (cite: task allocation), path planning problem (cite: path planning), local motion planning problem and tracking control problem.
-These four problems form a hierarchical structure in order.
-First, the UAVs-UGVs search and rescue system needs to be able to assign different tasks to agents to perform.
+To discuss an unmanned HMAS more concretely, we consider an UAVs-UGVs team system for search and rescue.
+For the need for search mobility, we choose quadrotor aircraft as UAV.
+In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV.
+Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.
+
+To the best of the authors' knowledge, most of the literature focus on only one specific problem, and few literatures illustrate the relationship between these problems for an unmanned HMAS.
+This leads us to propose an system architecture of UAV-robot team system (URTS) for search and rescue usage.
+The flowchart of decision-making and control process of URTS is given.
+We divide it into five hierarchical blocks, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
+First, the UTRS needs to be able to assign different tasks to agents to perform.
 After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it.
-To make agent move on the path, a motion corresponding to the actual mechanical system of the agent needs to be planned.
+To make agent move on the path, a behavior corresponding to the environment needs to be determined.
+Then, a local motion corresponding to the behavior of the agent needs to be planned.
 Finally, a controller must be designed to track the trajectory of the motion.
@@
 But to illustrate how the whole system works, the first two problems are also briefly stated.
-% An unmanned search and rescue system needs to be able to assign different tasks to agents to perform.
-This problem is called the task allocation problem, which attempts to achieve an optimal allocation given the objective function and some constraints (cite: task allocation).
-After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it.
-This problem is called the path planning problem, which attempts to achieve an optimal path given the objective function and some constraints (cite: path planning).
 
-To discuss the local motion planning problem and tracking control problem, a real mechanical system to which each agent corresponds must be considered.
+% To discuss the local motion planning problem and tracking control problem, the real mechanical system for each agent corresponds must be considered.
 To meet the need for search mobility, we choose quadrotor aircraft as UAV.
@@
 The reason is that path planning algorithm usually treats the agent as a point, while the actual agent is a mechanical system for the tracking control design.
-Although there are some literatures (ref:kinodynamic path planning) about path planning with the constraints of kinodynamic of the actual mechanical system, this paper splits it into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
-% The aforemention two problems are widely studied in the field of computer science and field of control respectively but fewer papers point out their relationship with respect to specific agents (UAV and robot in this paper).
-Therefore, this paper will focus on this issue.
+Although there are some literatures (ref:kinodynamic path planning) about path planning with the constraints of kinodynamic of the actual mechanical system, this paper splits the step of path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
+Through this decomposition, we can focus on the local motion design of specific behaviors.
+The planning of flying motion for UAV and walking motion for robot is studied in this paper, especially the latter.
+Due to the challenge of the local motion planning of the walking of biped robot, i.e., stable walking parttern generation, it is a popular research topic (cite: walking parttern).
 
-Tracking Problem ...
+The tracking control is ...
+The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control)
+the control problem of robot
+FTC
+disturbance
 
-To the best of the authors' knowledge, most of the literature focus on only one specific problem, and few literatures illustrate the relationship between these problems for an unmanned HMAS.
-This leads us to propose an architecture of UAV-robot team system (URTS) for search and rescue although this paper mainly focuses on the local motion planning and tracking control problem.
 % Based on the foregoing, an UAV-robot team system (URTS) is discussed in this paper.
@@
 Then the respective motion of behavior is designed.
-The final output is all reference path $r[k]$, but its actual size and dimensions will be different.}
+The final outputs of Flying and Walking are all reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
     \label{fig:FandW}
@@
 Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
-The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed by linear interpolation and spline interpolation which give the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
+The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed by linear interpolation and then cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
 $(\sigma_n')$ is the position reference path $\begin{bmatrix}
@@
 
-Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame as in \cite{ourrobot}, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero.
-More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon which is the convex hull of face of supported foots.
+Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}.
+Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero.
+More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
 The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} ($\widehat{Y_b}$ direction as same form):
@@
 Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance.
-Despite that, $(\sigma_n')$ tells the robot the position to go so the forward direction of robot can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the robot will move forward (rather than sideways or backward).
-To keep torso upright, the direction of $\widehat{Z_b}$ is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$.
-Given $\widehat{X_g}$ and $\widehat{Z_g}$, $\widehat{Y_b}$ can be obtained obviously through cross product.
-Since the origin of body frame $\{ \widehat{X_g}, \widehat{Y_g}, \widehat{Z_g} \}$ is CoM, the sequence of CoM orientation $(CO_n)$ can be obtained through the above steps.
+Despite that, $(\sigma_n')$ tells the robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the robot will move forward (rather than sideways or backward).
+To keep torso upright, the $\widehat{Z_b}$ direction is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$.
+Given $\widehat{X_b}$ and $\widehat{Z_b}$, $\widehat{Y_b}$ can be obtained obviously through cross product.
+The sequence of body frame, i.e., CoM orientation path $(CO_n)$ can be obtained through the above steps.
 
@@
 Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component are given by step height.
-By using spline interpolation, we have the left and right ankle position path $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
+By using cubic spline interpolation, we have the left and right ankle position path $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
 The ankle orientation path is found by gradient of ground.
@@
 
-To obtain CoM postion path, ZMP path need to obatin first.
-ZMP path is obatin through ankle path since ZMP needs to lie in the support face and ankle path point out when a feet is stand on the ground.
-After that, ZMP path is used to produce CoM postion path by 3D-LIPM as follow:
+To obtain CoM postion path $(CP_n)$, ZMP path need to obtain first.
+ZMP path can be obtained through ankle path since ZMP needs to lie in the support face and ankle path point out when a feet is stand on the ground.
+Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
 \begin{equation} \label{eq:LIPM}
@@
 \end{equation}
-where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, $z_c$ is the CoM height, and $(p_x,p_y)$ is the position of ZMP.
+where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP.
+Since $z_c,g,(p_x,p_y)$ are given, $(x,y)$ can be solved.
 To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference path so that the state variable $x$ is found, which is the CoM position path we want.
+Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference path so that the solution of ODE (\ref{eq:LIPM}) $x$, i.e., the CoM position path we want is found.
 Unlike conventional methods, the problem is solved by optimal control.
@@
 The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}.
-The CoM position path in the $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form.
+The $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form.
+The CoM position path $(CP_n)$ then be obtained by combining $x$, $y$ and $z_c$.
 
-By combining the CoM position and orientation path, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot is found by solving IK.
+By combining the CoM orientation $(CO_n)$ and position $(CP_n)$ path, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot is found by solving IK.
 
@@
 \end{equation}
-where $u(t)\in\mathbb{R}^m$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector.
+where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector.
 The control law is given as:
@@
 By Multipling $M(r(t))^{-1}$ from the left and right sides and with some arrangments, we have:
-\begin{equation} \label{eq:23}
+\begin{equation} \label{eq:error, state eq}
     \ddot{e}(t) = u_{fb}(t) + f_1(t)
 \end{equation}
-where $f_1(t) = M(r(t))^{-1}(-\Delta M(\ddot{x}(t)) -\Delta H + d_1(t))$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensationand, and $e(t)= x(t)-r(t)$ is the tracking error.
+where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))$ is the unknown actuator fault signal.
+$\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
 % \textit{
@@
     \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
-\end{bmatrix}\in\mathbb{R}^{3n}$, (\ref{eq:23}) can be rewrited as:
+\end{bmatrix}\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
 \begin{equation} \label{eq:linear f1}
@@
 Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the fault tolerance stable control problem of linear system (\ref{eq:linear f1}).
-The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make it stable.
+The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
 In a real system, the feedback information is measured by sensor, i.e, the state $\pmb{e}(t)$ in (\ref{eq:linear f1}) is unavailable.
-As mentioned before, the external disturbances on sensor also need to be considered.
-Since the sensor information (\ref{eq:agent output}) will transmitted back to the ground station through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are considered.
-The total effect can be equivalent to an sensor fault signal $f_2(t)$.
-The measurement output equation is formulated as:
+At the same time, the external disturbances on sensor also need to be considered as mentioned before.
+Since the sensor information (\ref{eq:agent output}) will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are concerned.
+Suppose the total effect can be equivalent to an unknown sensor fault signal $f_2(t)\in \mathbb{R}^{n}$ with same size as $f_1(t)$, the measurement output equation can be described as:
 \begin{equation} \label{eq:agent output}
-    y(t) = C\pmb{e}(t) + f_2(t)
+    y(t) = C\pmb{e}(t) + B_2f_2(t)
 \end{equation}
-where $y(t)\in\mathbb{R}^l$ is output vector, $C\in\mathbb{R}^{l\times 3n}$ is output matrix. By combining (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have:
-\begin{equation} \label{eq:4}
+where $y(t)\in\mathbb{R}^l$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, and $B_2\in\mathbb{R}^{l\times n}$ is the input matrix of $f_2(t)$.
+By putting (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have the following system:
+\begin{equation} \label{eq:error}
     \begin{split}
         & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t)) \\
-        & y(t) = C\pmb{e}(t) + f_2(t)   
+        & y(t) = C\pmb{e}(t) + B_2f_2(t)   
     \end{split}  
 \end{equation}
-where $x(t)\in\mathbb{R}^n$, $u(t)\in\mathbb{R}^m$, $y(t)\in\mathbb{R}^l$, and $f_i:\mathbb{R}\rightarrow \mathbb{R}^{n_i}, f_i(t)\in C^{1}, i=1,2$ with $n_1=m$ and $n_2 = l$.
-% For designing a tracking controller under unknown external disturbance and making the tracking performance of the agent system (\ref{eq:nonlinear sys}) meet a specified specification, an $H_\infty$ observer-based feedback linearization-based PID(FL-PID) fault tolerance control(FTC) is proposed.
-Before continuing, the analysis of a linear system version, i.e., after feedback linearization is given first.
-\textit{
-    \begin{remark}
-        The fault signal $f_i(t), i=1,2$ are assumed to be smooth rather than bounded, which will make the proposed method more general for practical scenario.
-    \end{remark}
-}
+% where $f_i(t)\in \mathbb{R}^{n_i}, i=1,2$ with $n_1=n$ and $n_2 = n$.
 
-To deal with the fault signals, an active fault tolerance control is introduced \cite{9306757}.
-In general, constructing a model for an unknown signal is impossible.
-However, a smooth model can be used to describe a signal under the smooth assumption.
-Unlike previous work, a finite-difference-method-based method is proposed to reduce the approximation error between origin fault signal and its smooth model.
-
-From finite difference method, the derivative of the fault signals $\dot{f}_i(t), i=1,2$ with uniform grid $h$ can be expressed as:
+To deal with the fault signals, an active fault tolerance control (FTC) is introduced \cite{9306757}.
+First, we need a model of the fault signal.
+In general, constructing a model for an unknown signal is impossible since there is no information about it.
+Hence, the following assumption is maded:
+\begin{assumption} \label{asm:smooth}
+    The first $p-1$ derivatives of the fault signals $f_i(t), i=1,2$ all exist and are continuous, i.e., $f_i(t)\in C^{p-1}$.
+\end{assumption}
+Under the assumption, now we can construct a "smooth" model by finite difference method.
+To obtain a state-space representation, the derivative of the fault signals $\dot{f}_i(t)$ with uniform grid $h$ are needed, which can be expressed as:
 \begin{equation} \label{eq:df}
@@
 where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference.
-For constructing a state-space representation, the derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed.
+The derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed.
 For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$.
-Then, we can obtain the following equation by (\ref{eq:df}) by changing index $k$ to $j$:
+By changing index $k$ to $j$, the derivative of $f_i(t-jh),k\in{Z_0}$ can be obtained by (\ref{eq:df}):
 \begin{equation} \label{eq:df1}
@@
     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
-\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n_i}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
+\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
 \begin{equation} \label{eq:8}
@@
     1 & 0 & \dots & 0
-\end{bmatrix}\otimes I_{n_i}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:4}), we get:
+\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:error}), we get:
 \begin{equation} \label{eq:9}
@@
     0 \\ v_1(t) \\ v_2(t)
-\end{bmatrix}$. Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimat them and origin state simutaniously:
+\end{bmatrix}$.
+\textit{
+    \begin{remark}
+        The equation (\ref{eq:df}) is derived by Taylor expansion, so assumption \ref{asm:smooth} is nessasry.
+Unlike previous work, a finite-difference-method-based modeling method is proposed, which reduce the approximation error between origin fault signal and its smooth model.
+Besides, the fault signals $f_i(t)$ are assumed to be of differentiability class $C^{p-1}$ rather than bounded, which will make the proposed method more general for practical scenario.
+    \end{remark}
+}
+Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC:
 \begin{equation} \label{eq:10}
     \begin{split}
-        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{x}}(t)+\bar{B}u_{fb}(t)+{L}(y(t)-\hat{y}(t)) \\
-        & \hat{y}(t)=\bar{C}\hat{\bar{x}}(t)  
+        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t)+\bar{B}u_{fb}(t)+{L}(y(t)-\hat{y}(t)) \\
+        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)  
     \end{split}
@@
     K_I & K_P & K_D & K_{F_1} & K_{F_2}
-\end{bmatrix}$ is total control gain, $K_P,K_I,K_D$ are PID control gain, and $K_{F_i}, i=1,2$ are fault control gain.
+\end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
 Let us define the estimation error $\tilde{e}=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
@@
 
-The tracking control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
+In order to enable the designed control gain $K$ and observer gain $L$ to achieve a specific stablized performance for the system (\ref{eq:aug}) under the disturbance $\bar{v}(t)$, the $H_\infty$ observer-based stabilized control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
 \begin{equation} \label{Hinf}
-    H_{\infty}(K, L) = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2 
+    \begin{split}     
+        & H_{\infty}(K, L) \\
+        & = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
+    \end{split}
 \end{equation}
@@
     If
-    $$\begin{bmatrix}
+    \begin{equation} \label{LMI}
+        \begin{bmatrix}
             & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
@@
             & \ast & \ast & \ast & -\rho^2 
-    \end{bmatrix}\leq 0 $$
+        \end{bmatrix}\leq 0
+    \end{equation}
     where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$.
-Then system (\ref{eq:aug}) achieve $H_\infty$ observer-base stabilized control performance (\ref{Hinf}).
+Then system (\ref{eq:aug}) achieve the $H_\infty$ observer-based stabilized control performance (\ref{Hinf}).
 \end{theorem}
@@
 
-Although the control gain and observer gain that satisfy the specification can already be found by Theorem \ref{theorem1}, the calculation speed can be further improved by reducing the dimensionality of the system.
-Since the feedback linearization eliminates the nonlinearity and some degree of coupling of the system (\ref{eq:4}), it can be further split into $n$ subsystems if the output matrix $C$ have the same form to $A$ and $B$, i.e., $C = C_0\otimes I_n$, where $n$ is dimension of state vector and $C_0\in\mathbb{R}^{l\times 3}$.
-Due to the fact that $d_3(t)\in\mathbb{R}^n, d_4(t)\in\mathbb{R}^{ln}$, the n subsystems are obtained from (\ref{eq:linear sys}):
+Although the control gain and observer gain that satisfy with the specification can already be found by Theorem \ref{theorem1}, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{LMI}).
+Observing the matrices $A,B,C,B_2$ in linear system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ have the same form to $A,B$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l\times 3},B_{2,0}\in\mathbb{R}^{l\times 1}$.
+Due to the fact that $f_1(t)\in\mathbb{R}^n, f_2(t)\in\mathbb{R}^{n}$, the n subsystems are obtained from (\ref{eq:error}):
 \begin{equation} \label{eq:linear subsys}
     \begin{split}
-        & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fd,i}(t)+d_{3,i}(t)) \\
-        & \pmb{y}_i(t)=C_0\pmb{e}_i(t)+d_{2,i}(t)   
+        & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fd,i}(t)+f_{1,i}(t)) \\
+        & \pmb{y}_i(t)=C_0\pmb{e}_i(t)+B_{2,0}f_{2,i}(t)   
     \end{split}
@@
 where subscript $i = 1, 2, ..., n$ denote the element in the corresponding vector.
-By Theorem \ref{theorem1} again, the form show that the subsystems (\ref{eq:linear subsys}) can achieve $H_\infty$ performance.
-Let $K_i$ be the control gain of subsystems, the origin control gain $K$ of origin agent system can be obtained by $K = \begin{bmatrix}
+By Theorem \ref{theorem1} again, the form shows that the subsystems (\ref{eq:linear subsys}) can achieve the $H_\infty$ observer-based stabilized control performance.
+Let $K_i$ be the control gain of the $i$th subsystems, the origin control gain $K$ of the origin agent system can be obtained by $K = \begin{bmatrix}
     \mathit{v}_1 & \mathit{v}_2 & ... & \mathit{v}_n
-\end{bmatrix}^T, \mathit{v}_i=K_i\otimes\mathbf{e}_i$ where $\mathbf{e}_i$ is standard unit vectors in $\mathbb{R}^n$.
+\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$ where $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$.
 The origin observer gain $L$ can be obtained in the same way.
-In this case, the calculate speed is improved ...
+In this case, the calculate speed can be improved since the dimensionality is decrease.
 \textit{
@@
 However, the gains are not directly adjusted but indirectly designed through prescribed specifications (\ref{Hinf}).
-Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i$).
-Depending on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i$ and attenuation levels $\rho_i$ for each subsystem.
+Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i, i=1,2,\dots,n$).
+Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation levels $\rho_i$ for each subsystem.
     \end{remark}
@@
 
-\subsection{UAV reference trajectory design and overall flowchart}
 Although the design of the agent controller and observer has been completed, the trajectory design of UAV is not done yet.
@@
     f_x & f_y & f_z & \tau_x & \tau_y & \tau_z 
-\end{bmatrix}^T\in\mathbb{R}^6$ that obtained from Theorem \ref{theorem1} needs to convert to actual control input $u'(t)=\begin{bmatrix}
+\end{bmatrix}^T\in\mathbb{R}^6$ obtained from Theorem \ref{theorem1} needs to convert to actual control input $u'(t)=\begin{bmatrix}
     F & \tau_x & \tau_y & \tau_z 
 \end{bmatrix}^T\in\mathbb{R}^4$.
-As the same time, the extra two degrees of freedom are used to find the remaining two reference trajectories $\phi_r(t)$ and $\theta_r(t)$ through inverse dynamics.
-In simple terms, we want to find a total force $F$ and its angles $\phi_r$, $\theta_r$ and $\psi_r$ from the three component forces $f_x$, $f_y$ and $f_z$.
+At the same time, the extra two degrees of freedom are used to find the remaining two reference trajectories $\phi_r$ and $\theta_r$ through inverse dynamics.
+That is to say, we want to find a total force $F$ and its angles $\phi_r$, $\theta_r$ and $\psi_r$ from the three component forces $f_x$, $f_y$ and $f_z$.
 By substituting $\Theta=\begin{bmatrix}
@@
         0 \\ 0 \\ F
-\end{bmatrix} $ from UAV dynacmis (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
+\end{bmatrix} $ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
 
-The overall flowchart of Tracking Control is shown in Fig. \ref{fig:tracking}.
+The overall flowchart of Tracking Control is shown in Fig.
+\ref{fig:tracking}.
+The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u(t)$ according to the result of Local Motion Planning $r'(t)$ and Theorem \ref{theorem1} $u'(t)$.
+The reference generator for robot is an identity function since it is a fully actuated system.
+Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)=\begin{bmatrix}
+    \int_{0}^{t}r(\tau)d\tau & r(t) & \dot{r}(t)
+\end{bmatrix}$.
+$\pmb{r}(t)$ then pass to sensor to calculate the PID tracking error $\pmb{e}(t)$.
+The sensor measure not only the agent's own information (e.g., position, velocity or $\pmb{e}(t)$) but environmental information.
+The environmental information is passed back to the high-level block for positioning, mapping and object recognition.
+The measurement output $y(t)$ is input to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
+The differentiation of $\pmb{r}(t)$, $\pmb{\dot{r}}(t)$, is input to controller for feedforward control.
 
@@
     \centering
-    \includegraphics[scale=.5]{fig/tracking.pdf}\caption{flowchart of Tracking Control}%
+    \includegraphics[scale=.5]{fig/tracking.pdf}\caption{The flowchart of tracking control.
+The control scheme of UAV and robot is only different from the block, reference generator.
+The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
+By introducing this block, a general feedforward-linearized PID FTC for an agent in URTS is proposed.}%
     \label{fig:tracking}
 \end{figure*}
-
-The reference generator for robot is an identity function since it is a fully actuated system.
-The sensing information includes the agent's own information and environmental info, which is passed back to the high-level block for positioning, mapping and object recognition.
-Self information is passed to the observer for estimation and tracking error correction.
 

### 2022-07-31 paper/paper.tex
paper, 2step ok.

@@
 The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
-Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc (cite: task allocation).
+Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}.
 Path planning is to optimally plan paths to each agent, subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc (cite: path planning).
@@
 This leads us to propose an system architecture of UAV-robot team system (URTS) for search and rescue usage.
-The flowchart of decision-making and control process of URTS is given.
-We divide it into five hierarchical blocks, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
-First, the UTRS needs to be able to assign different tasks to agents to perform.
+The flowchart of decision-making and control process of URTS is also given.
+We divide it into five main hierarchical blocks, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
+It is because the UTRS needs to be able to assign different tasks to agents to perform first.
 After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it.
@@
 Finally, a controller must be designed to track the trajectory of the motion.
-In order to further limit the scope of the study, we will focus on the latter two problems.
-But to illustrate how the whole system works, the first two problems are also briefly stated.
+In order to further limit the scope of the study, we will focus on the latter two blocks.
+But to illustrate how the whole system works, the first three problems are also briefly stated.
 
@@
 The reason is that path planning algorithm usually treats the agent as a point, while the actual agent is a mechanical system for the tracking control design.
-Although there are some literatures (ref:kinodynamic path planning) about path planning with the constraints of kinodynamic of the actual mechanical system, this paper splits the step of path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
+A mechanical system means that there exist kinodynamic constraints.
+It makes certain paths impossible to follow for an agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
+Although there are some literatures tackle the path planning with the kinodynamic constraints of an actual mechanical system \cite{9384209}, this paper splits the step of path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
 Through this decomposition, we can focus on the local motion design of specific behaviors.
-The planning of flying motion for UAV and walking motion for robot is studied in this paper, especially the latter.
+The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter.
 Due to the challenge of the local motion planning of the walking of biped robot, i.e., stable walking parttern generation, it is a popular research topic (cite: walking parttern).
 
-The tracking control is ...
+The tracking control is to control an agent to follow a desired trajectory.
+There are many control strategy for MAS.
+According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}.
+Centralized control means there exist a powerful central controller in MAS to gather the state information and sent the control command back to each agent to reach a global goal.
+Due to the powerful nature of the central controller, control commands can be determined well and quickly.
+But when it fails, the whole system will be completely paralyzed.
+In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information.
+Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided
+
+Besides, the formation control is also a topic in MAS (cite:formation control).
+Its purpose is to keep a MAS in a formation while moving.
+Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible.
+Because there are many different sacles and types of tasks that must be handled in a disaster relief environment, agents in URTS need to organize multiple teams of different sacles and types to deal with.
+In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.
+
+The external disturbances during tracking control must also be considered. The agent
+
 The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control)
@@
 % $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
-$A^T$: transpose of A. $(a_n)$: sequence. $(a_{k_n})$: subsequence. $\vert{S}\vert$: size of a set $S$. $\otimes$: Kronecker product. $I_n$: n-dimension identity matrix. $x(t)\in L_2\begin{bmatrix}
+$A^T$: transpose of A.
+$A > 0$: a positive definite matrix.
+$(a_n)$: sequence.
+$(a_{k_n})$: subsequence.
+$\vert{S}\vert$: size of a set $S$.
+$\otimes$: Kronecker product.
+$I_n$: n-dimension identity matrix.
+$x(t)\in L_2\begin{bmatrix}
     0,t_f 
-\end{bmatrix}$ if $\int^{t_f}_{0}x^T(t)x(t)dt<\infty$.
+\end{bmatrix}$ if $\int^{t_f}_{0}x^T(t)x(t)dt<\infty$. $Sym(A)$: sum of a matrix $A$ and its tranposed, i.e., $Sym(A) = A+A^T$.
 
@@
     \centering
-    \includegraphics[scale=.5]{fig/behavior.pdf}\caption{The structure of Behavior Layer.
+    \includegraphics[scale=.5]{fig/behavior.pdf}\caption{The structure of behavior layer.
 The leaf of the tree structure are the possible behaviors an agent can take.
@@
 \ref{fig:LocalMotionPlanning}
-
 \begin{figure*}[htbp]
@@
 \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
-
 \begin{figure*}[htbp]
@@
 \end{figure*}
-
 Before the discussion of the motion design of these two behavior, the following assumption is maded.
@@
 \end{bmatrix}$, $\bar{C}=\begin{bmatrix}
-    C & 0 & C_2
+    C & 0 & B_2C_2
 \end{bmatrix}$, and $\bar{v}(t)=\begin{bmatrix}
@@
     \begin{split}
-        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t)+\bar{B}u_{fb}(t)+{L}(y(t)-\hat{y}(t)) \\
+        & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t)+\bar{B}u_{fb}(t)-{L}(y(t)-\hat{y}(t)) \\
         & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)  
@@
 The PID FTC law is given as:
-\begin{equation} \label{eq:11}
-    u_{fd}(t)=K\hat{\bar{e}}(t)
+\begin{equation} \label{eq:Kx}
+    u_{fb}(t)=K\hat{\bar{e}}(t)
 \end{equation}
@@
 \end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
-Let us define the estimation error $\tilde{e}=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:11}):
+Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:Kx}):
 \begin{equation} \label{eq:aug}
@@
 \end{bmatrix}$, and $\tilde{v}(t)=\begin{bmatrix}
-    \bar{v}(t) \\ 0
+    \bar{v}(t) \\ \bar{v}(t)
 \end{bmatrix}$
 
-In order to enable the designed control gain $K$ and observer gain $L$ to achieve a specific stablized performance for the system (\ref{eq:aug}) under the disturbance $\bar{v}(t)$, the $H_\infty$ observer-based stabilized control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
+In order to enable the designed control gain $K$ and observer gain $L$ to achieve a specific stablized performance for the system (\ref{eq:aug}) under the disturbance $\bar{v}(t)$, the $H_\infty$ observer-based stablized control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
 \begin{equation} \label{Hinf}
@@
         & H_{\infty}(K, L) \\
-        & = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u^T(t)Ru(t))dt - V(\tilde{x}_0)}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
+        & = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u_{fb}^T(t)Ru_{fb}(t))dt - V(\tilde{x}(0))}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
     \end{split}
 \end{equation}
-where $t_f$ is the final time, $Q > 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
+where $t_f$ is the final time, $Q \leq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
-To find these gains, the following theroem is given.
+Before analyzing the $H_\infty$ observer-based stablized control problem in (\ref{Hinf}), the following lemmas are given:
+\begin{lemma}[\cite{boyd1994linear}] \label{lemma1}
+    For any matriices $X$ and $Y$ with appropriate dimensions, and matrix $R=R^T>0$ the following inequality holds:
+    \begin{equation} \label{}
+        X^T Y + Y^T X \leq X^T R^{-1}X + Y^T R Y
+    \end{equation}  
+\end{lemma}
+\begin{lemma}[Schur Complement\cite{boyd1994linear}] \label{lemma2}
+    For the matrices $X=X^T,Y=Y^T$ and matrix $R$ with appropriate dimensions the following statement is true:
+    \begin{equation} \label{}
+        \begin{bmatrix}
+            X & R \\ R^T & Y 
+        \end{bmatrix} > 0 \Leftrightarrow Y>0, X-RY^{-1}R^T>0
+    \end{equation}
+\end{lemma}
+Then, the following theorem is given.
 \begin{theorem} \label{theorem1}
-    If
-    \begin{equation} \label{LMI}
-        \begin{bmatrix}
-            & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
-            & \ast  & M_{22} & 0 & P_2 \\
-            & \ast & \ast & -I & 0 \\
-            & \ast & \ast & \ast & -\rho^2 
-        \end{bmatrix}\leq 0
+    If there exists matrices $P=P^T>0, K$ and a scalar $\rho>0$ such that the following matrix inequality hold:
+    \begin{equation} \label{BMI1}
+        Q + P\tilde{A} + \tilde{A}^T P + \tilde{K}^TR\tilde{K} + \frac{1}{\rho^2}PP \leq 0
     \end{equation}
-    where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$.
-Then system (\ref{eq:aug}) achieve the $H_\infty$ observer-based stabilized control performance (\ref{Hinf}).
+    where $\tilde{K}=\begin{bmatrix}
+        K & -K
+    \end{bmatrix}$, then the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) holds.
 \end{theorem}
 \begin{proof}
-    proof...
+    Choose the Lyapunov function $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)$ for the augmented system (\ref{eq:aug}) with $P=P^T>0$, we have:
+    \begin{equation} \label{pf:1}
+        \begin{split}
+            & \int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u_{fb}^T(t)Ru_{fb}(t))dt \\
+            & = V(\tilde{x}(0)) - V(\tilde{x}(t_f)) + \int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) \\
+            & + u_{fb}^T(t)Ru_{fb}(t) + \dot{V}(\tilde{x}(t)))dt \\
+            & \leq V(\tilde{x}(0)) + \int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + \\
+            & u_{fb}^T(t)Ru_{fb}(t) + Sym(\dot{\tilde{x}}^T(t)P\tilde{x}(t)))dt
+        \end{split}
+    \end{equation}. By (\ref{eq:aug}) and Lemma \ref{lemma1}, we have:
+    \begin{equation} \label{pf:2}
+        \begin{split}
+            & Sym(\dot{\tilde{x}}^T(t)P\tilde{x}(t)) \\
+            & = Sym((\tilde{A}\tilde{x}(t)+\tilde{v}(t))^TP\tilde{x}(t)) \\
+            & = \tilde{x}^T(t)(P\tilde{A} + \tilde{A}^T P + \frac{1}{\rho^2}PP)\tilde{x}(t) + \rho^2\tilde{v}^T(t)\tilde{v}(t)
+        \end{split}
+    \end{equation}. Substituting (\ref{pf:2}) and (\ref{eq:Kx}) into (\ref{pf:1}), we get:
+    \begin{equation*} \label{pf:3}
+        \begin{split}
+            & \int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t))dt + u_{fb}^T(t)Ru_{fb}(t))dt \\
+            & \leq V(\tilde{x}(0)) + \int_{0}^{t_f}(\tilde{x}^T(t)(Q + P\tilde{A} + \tilde{A}^T P +\tilde{K}^TR\tilde{K}\\
+            & + \frac{1}{\rho^2}PP)\tilde{x}(t) + \rho^2\tilde{v}^T(t)\tilde{v}(t))dt
+        \end{split}
+    \end{equation*}. Thus, if (\ref{BMI1}) holds then (\ref{Hinf}) holds
 \end{proof}
 
-% \begin{equation}      
-%     u_{fb} = K_I\int_{0}^{t} e(\tau) d\tau + K_P e(t) + K_D \dot{e}(t) + K_F\hat{F}
+Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the variables.
+To solve the issue, a two-step design is exploit.
+
+\textit{Step 1:} First, let $P=\begin{bmatrix}
+        P_1 & 0 \\ 0 & P_2
+\end{bmatrix}, Q=\begin{bmatrix}
+        Q_1 & 0 \\ 0 & Q_2
+\end{bmatrix}$ where $P_1,Q_1$ are for stablized control error and $P_2,Q_2$ are for estimated error. Substituting it into (\ref{BMI1}), we get:
+\begin{equation} \label{eq:M}
+    \begin{split}
+        & \begin{bmatrix}
+            Q_1 & 0 \\ 0 & Q_2
+        \end{bmatrix} + Sym(\begin{bmatrix}
+            P_1 & 0 \\ 0 & P_2
+        \end{bmatrix}\begin{bmatrix}
+            \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
+        \end{bmatrix})  \\
+        & + \begin{bmatrix}
+            K^TRK & -K^TRK \\ -K^TRK & K^TRK
+        \end{bmatrix} + \frac{1}{\rho^2}\begin{bmatrix}
+            P_1P_1 & 0 \\ 0 & P_2P_2
+        \end{bmatrix} \\
+        & = \begin{bmatrix}
+            M_{11} & -P_1\bar{B}K - K^TRK \\ * & M_{22}
+        \end{bmatrix} < 0
+    \end{split}
+\end{equation}
+where $M_{11}=Q_1+Sym(P_1(\bar{A}+\bar{B}K)) + K^TRK + \frac{1}{\rho^2}P_1P_1$, $M_{22}=Q_2+Sym(P_2(\bar{A}+L\bar{C})) + K^TRK + \frac{1}{\rho^2}P_2P_2$. By the fact that $\begin{bmatrix}
+    M_{11} & -P_1\bar{B}K - K^TRK \\ * & M_{22}
+\end{bmatrix} < 0 \Rightarrow M_{11}<0, M_{22}<0$, the inequality $M_{11}<0$ is used to find $P_1,K,\rho$. Premultiplying and
+postmultiplying $M_{11}<0$ by $W_1=P_1^{-1}$ and applying Lemma \ref{lemma2}, we obtain:
+\begin{equation} \label{eq:step1}
+    \begin{bmatrix}
+        Sym(\bar{A}W_1+\bar{B}Y_1) & W_1\sqrt[1/2]{Q_1} & Y_1^T & I \\
+        * & -I & 0 & 0 \\
+        * & * & -R^{-1} & 0 \\
+        * & * & * & -\rho^2I\\
+    \end{bmatrix} < 0
+\end{equation}
+where $Y_1=KW_1$. By solving the LMI (\ref{eq:step1}), we can obtain $W_1,Y_1,\rho$.
+
+\textit{Step 2:} Substituting $P_1=W^{-1}$, $K=Y_1W_1^{-1}$ and $\rho$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
+\begin{equation} \label{eq:step2}
+    \begin{bmatrix}
+        M_{11} & -P_1\bar{B}K - K^TRK & P_2 \\
+        * & Q_2+Sym(P_2\bar{A}+Y_2\bar{C}) + K^TRK & 0 \\
+        * & * & -\rho^2I
+    \end{bmatrix} < 0
+\end{equation}
+where $Y_2=P_2L$. By solving the LMI (\ref{eq:step2}), we can obtain $P_2,Y_2$.
+
+Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:aug}).
+
+% The design procedure of the $H_\infty$ observer-based stablized control scheme for the augmented system (\ref{eq:aug}) is organized as follows.
+% \begin{enumerate}
+%     \item ...
+% \end{enumerate}
+% \begin{theorem} \label{theorem2}
+%     Given matrices $W_1=W_1^T>0,Q_1=Q_1^T>0,Q_2=Q_2^T>0,K$,$L$ and a scalar $\rho>0$, the following LMI:
+%     \begin{equation} \label{LMI2}
+%         \begin{bmatrix}
+%             & M_{11} & -\bar{B}Y1 & W_1\sqrt{Q_1} & 0 \\
+%             & \ast  & M_{22} & 0 & P_2 \\
+%             & \ast & \ast & -I & 0 \\
+%             & \ast & \ast & \ast & -\rho^2 
+%         \end{bmatrix}\leq 0
 %     \end{equation}
-
-Although the control gain and observer gain that satisfy with the specification can already be found by Theorem \ref{theorem1}, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{LMI}).
+%     where $M_{11}=\bar{A}W_1+\bar{B}Y_1 + (\bar{A}W_1+\bar{B}Y_1)^T + \frac{1}{\rho^1}I$, $M_{22}=P_2\bar{A}+Y_2\bar{C} + (P_2\bar{A}+Y_2\bar{C})^T+Q_2$, is equivalent to the BMI (\ref{BMI1})
+% \end{theorem}
+% \begin{proof}
+%     Let $W_1=P_1^{-1}$. By $\tilde{A}$ in (\ref{eq:aug}) and (\ref{eq:PQ}), and multiplying (\ref{BMI1}) left and right by $\begin{bmatrix}
+%         W_1 & 0 \\ 0 & I
+%     \end{bmatrix}$, we have:
+%     \begin{equation} \label{}
+%         \begin{bmatrix}
+%             W_1Q_1W_1 & 0 \\ 0 & Q_2
+%         \end{bmatrix})
+%         Sym(\begin{bmatrix}
+%             I & 0 \\ 0 & P_2
+%         \end{bmatrix})\begin{bmatrix}
+%             \bar{A}+\bar{B}K & -\bar{B}K \\ 0 & \bar{A}+L\bar{C}
+%         \end{bmatrix} + \frac{1}{\rho^2}\begin{bmatrix}
+%             I & 0 \\ 0 & P_2P_2
+%         \end{bmatrix} + 
+%     \end{equation}
+% \end{proof}
+Although the control gain and observer gain that satisfy with the specification can already be found through the previous steps, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{BMI1}).
 Observing the matrices $A,B,C,B_2$ in linear system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ have the same form to $A,B$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l\times 3},B_{2,0}\in\mathbb{R}^{l\times 1}$.
@@
     \begin{split}
-        & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fd,i}(t)+f_{1,i}(t)) \\
+        & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fb,i}(t)+f_{1,i}(t)) \\
         & \pmb{y}_i(t)=C_0\pmb{e}_i(t)+B_{2,0}f_{2,i}(t)   
@@
 where subscript $i = 1, 2, ..., n$ denote the element in the corresponding vector.
-By Theorem \ref{theorem1} again, the form shows that the subsystems (\ref{eq:linear subsys}) can achieve the $H_\infty$ observer-based stabilized control performance.
+By Theorem \ref{theorem1} again, the form shows that the subsystems (\ref{eq:linear subsys}) can achieve the $H_\infty$ observer-based stablized control performance.
 Let $K_i$ be the control gain of the $i$th subsystems, the origin control gain $K$ of the origin agent system can be obtained by $K = \begin{bmatrix}
@@
 Besides, $K_i, i=1,2,\dots,n$ do not have to be the same value (so do $L_i, i=1,2,\dots,n$).
-Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation levels $\rho_i$ for each subsystem.
+Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation level $\rho_i$ for each subsystem.
     \end{remark}
@@
 
-Although the design of the agent controller and observer has been completed, the trajectory design of UAV is not done yet.
+Even though the design of the agent controller and observer has been completed, the trajectory design of UAV is not done yet.
 Since the UAV is an underactuated system, the "virtual" control input for UAV $u(t)=\begin{bmatrix}

### 2022-08-02 paper/paper.tex
abstract

@@
 % \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
-% \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-% \doi{10.1109/ACCESS.2017.DOI}
-
-% \title{Preparation of Papers for IEEE ACCESS}
+
+\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
+\doi{10.1109/ACCESS.2017.DOI}
+
+\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
 % \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
@@
 
-% \begin{abstract}
-
-% \end{abstract}
-
-% \begin{keywords}
-% Enter key words or phrases in alphabetical 
-% order, separated by commas. For a list of suggested keywords, send a blank 
-% e-mail to keywords@ieee.org or visit \underline
-% {http://www.ieee.org/organizations/pubs/ani\_prod/keywrd98.txt}
-% \end{keywords}
-
-% \titlepgskip=-15pt
-
-% \maketitle
+\begin{abstract}
+In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage.
+The system architecture of URTS is proposed to illustrate the issues that need to be addressed in URTS and the relationships between them.
+Then we focus on two issues, local motion planning and tracking control.
+We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot.
+The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail.
+By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS.
+A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation.
+The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
+Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved.
+Simulations are given ...
+\end{abstract}
+
+\begin{keywords}
+biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, search and rescue, smoothing signal model, UAV, UAVs-UGVs team system
+\end{keywords}
+
+\titlepgskip=-15pt
+
+\maketitle
 
@@
 Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
-However, the cost is that the design of such a multi-agent system becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents.
+However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents.
 In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS).
-Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios.
-Although there are many types of UVs to make up such a system, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV).
-Additionally, the complementarity between them also makes such a system more potential.
-In other words, UAV is widely used in reconnaissance due to the high mobility.
-However, the carrying capacity of UAV is very low compared to UGV since there is no ground support.
-In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed.
-For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
-
-To construct an unmanned HMAS, the three key capabilities are perception, decision-making and control.
+Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.
+
+To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control.
 Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision-making content through the actuator.
@@
 
-To discuss an unmanned HMAS more concretely, we consider an UAVs-UGVs team system for search and rescue.
+Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV).
+Additionally, the complementarity between them also makes such a system more potential.
+In other words, UAV is widely used in reconnaissance due to the high mobility.
+However, the carrying capacity of UAV is very low compared to UGV since there is no ground support.
+In contrast, UGV has higher carrying capacity but is easily restricted by ground obstacles and cannot move at high speed.
+For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
+To discuss more concretely, we consider an UAVs-UGVs team system for search and rescue.
 For the need for search mobility, we choose quadrotor aircraft as UAV.
-In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV.
-Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.
-
-To the best of the authors' knowledge, most of the literature focus on only one specific problem, and few literatures illustrate the relationship between these problems for an unmanned HMAS.
-This leads us to propose an system architecture of UAV-robot team system (URTS) for search and rescue usage.
+In order to deal with the complex terrain of the search and rescue environment, we choose biped robot as UGV.
+Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.
+
+To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent search and rescue system, such as task allocation problem, path planning problem or control problem.
+Additionally, few literatures illustrate the relationship between these problems.
+This leads us to propose an system architecture of UAVs-robots team system (URTS) for search and rescue usage.
 The flowchart of decision-making and control process of URTS is also given.
-We divide it into five main hierarchical blocks, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
+We divide it into five main hierarchical processes, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
 It is because the UTRS needs to be able to assign different tasks to agents to perform first.
-After a task is assigned, if the task is to reach a target location, a path needs to be planned to reach it.
-To make agent move on the path, a behavior corresponding to the environment needs to be determined.
+After a task is assigned, if the task is to reach a target location, a path to reach it needs to be planned.
+To make agent move on the path, a behavior corresponding to the environment is required to determine.
 Then, a local motion corresponding to the behavior of the agent needs to be planned.
 Finally, a controller must be designed to track the trajectory of the motion.
-In order to further limit the scope of the study, we will focus on the latter two blocks.
+In order to further limit the scope of the study, we will focus on the latter two processes.
 But to illustrate how the whole system works, the first three problems are also briefly stated.
@@
 However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved.
-The local motion planning of the walking of biped robot, i.e., stable walking parttern generation, is discussed in this paper.
-Related researches can be found in (cite: walking parttern).
+The local motion planning of the walking of biped robot, i.e., stable walking pattern generation, is discussed in this paper.
+Related researches can be found in (cite: walking pattern).
 
 The local motion planning is the bridge between path planning and tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same.
-The reason is that path planning algorithm usually treats the agent as a point, while the actual agent is a mechanical system for the tracking control design.
+The reason is that path planning algorithm usually treats the agent as a point, while the actual agent in the physical world is a mechanical system for the tracking control design.
 A mechanical system means that there exist kinodynamic constraints.
-It makes certain paths impossible to follow for an agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
-Although there are some literatures tackle the path planning with the kinodynamic constraints of an actual mechanical system \cite{9384209}, this paper splits the step of path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
-Through this decomposition, we can focus on the local motion design of specific behaviors.
+This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
+Although there are some literatures directly tackle the kinodynamic constraints path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
+Through this decomposition, we can focus on the local motion planning of specific behaviors.
 The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter.
-Due to the challenge of the local motion planning of the walking of biped robot, i.e., stable walking parttern generation, it is a popular research topic (cite: walking parttern).
+The local motion planning of walking of biped robot, i.e., stable walking pattern generation, is a popular research topic due to its challenge(cite: walking pattern).
 
@@
 In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information.
-Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided
+Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided.
 
@@
 Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible.
-Because there are many different sacles and types of tasks that must be handled in a disaster relief environment, agents in URTS need to organize multiple teams of different sacles and types to deal with.
+It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
 In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.
 
-The external disturbances during tracking control must also be considered. The agent
-
-The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control)
-the control problem of robot
-FTC
-disturbance
+The external disturbances during tracking control must also be considered. The agent ...
+% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
+% the control problem of robot
+
+Fault-tolerant contrl (FTC) ...
+
+Based on the foregoing, a robust $H_\infty$ decentralized fault-tolerant tracking control strategy is proposed to deal with the control problem in URTS.
 
 % Based on the foregoing, an UAV-robot team system (URTS) is discussed in this paper.
-
-% \PARstart{W}{ith}
 
@@
 $A > 0$: a positive definite matrix.
-$(a_n)$: sequence.
-$(a_{k_n})$: subsequence.
+$(a_n)$: a sequence.
+$(a_{k_n})$: a subsequence of a sequence $(a_n)$.
+$[a_{j,k}]$: A matrix with the entries $a_{j,k}$ in the $j$th row and $k$th column.
 $\vert{S}\vert$: size of a set $S$.
@@
 \section{PRELIMINARIES OF search and rescue URTS}
-The URTS will start with a given search and rescue area, and ends with searching task completed.
-The URTS is composed of $N_j$ teams and a ground station.
-Each team contains $1$ UAV and $N_i-1$ robots.
-Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_i$ and $j=1,2,...,N_j$.
+The URTS will start with a given search and rescue area, and end with mission completed.
+The URTS is composed of $N_T$ teams and a ground station.
+Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots.
+Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
 The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$.
@@
 To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target.
-It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents.
+% It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents.
 If each agent can only perform one task at a time, then there exist many feasible way of task allocation.
@@
 
-If a task is to reach a location of certain goal, there must exist multiple feasible paths.
-Similar to task allocation, we usually want to find an optimal path.
-Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, so each agent will also sense distance-related information about its surrounding and send it back to the ground station.
-The ground station will combine this information with the goal assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby.
-That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
-
-We need to design some behavior to follow the path found by path planning algorithm especially for agents with complex mechanical systems like robots.
+If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
+% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
+% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
+Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station.
+The ground station will combine this information with the goal location assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby.
+% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
+
+We need to determine specific behavior to follow the path found by path planning algorithm according to the situation of the environment especially for agents with complex mechanical systems like robots.
 Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path).
-Furthermore, agents in a search and rescue system are not always following a trajectory.
+Furthermore, agents in URTS are not always following the path.
 Sometimes they need the behavior such as stop to look around, get supplies and put supplies.
 To meet these needs, a behavioral layer is necessary.
-The behavior layer gives an appropriate behavior to fulfill an actual requirement.
+% The behavior layer decides an appropriate behavior based on the circumstances.
+
 In order to make an behavior, we must design a corresponding motion which is handled by local motion planning.
 The motion is a desired reference trajectory for an actual mechanical system to follow.
-Finally, a tracking controller is designed to follow the desired reference trajectory.
-
-To clarify this issue, a more detailed system architecture for each agent is needed.
+Finally, a tracking controller is designed to follow this desired reference trajectory.
+
+The agents overall have the same system architecture in URTS except for some subprocess differences.
 Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig.
 \ref{fig:sys}.
-The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents and an occupy map.
-The visual object recognition block provides distance information and object information through sensor info.
+The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$.
+The visual object recognition block provides distance information and object information through the analysis of sensor information.
 The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it).
@@
 
-% To determine the behavior, agent needs the information about enviroment.
-The sensing data which include external enviroment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).
+% To determine the behavior, agent needs the information about environment.
+The sensing data which include external environment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).
 
@@
 In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
-However, the number of agent and task is more than one, and each agent has different capabilities (e.g.
+However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g.
 moving speed or load capacity) and status (e.g.
@@
 Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation.
-This problem is refered as Task Allocation Problem or Multi-robot Task Allocation (MRTA) Problem.
+This problem is refered as task allocation problem or multi-robot task allocation problem.
 A problem formulation and problem modeling can be found in \cite{Khamis2015}.
@@
 In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue.
-In other words, every agent knows a destinition it need to go at every moment.
+In other words, every agent knows a destinition $q_{goal}$ it need to go at every moment.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
 After a target point is assigned for each agent, next step is to find a collision-free path from current position to it.
-There are several path planning algorithm to handle this problem, in this article, a roadmap-based path planning algorithm is used.
+There must exist multiple feasible paths to go.
+Similar to task allocation, we usually want to find an optimal path.
+There are several path planning algorithm to handle this problem.
+Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper uses it as the path planning method of UTRS.
 This method attempts to discretize the search space into interconnected roads and find the path on it.
-According to the roadmap construction method, it can be divided into deterministic and sample-based.
+% According to the roadmap construction method, it can be divided into deterministic and sample-based.
+
 According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}.
-Multi-query planner divides pathfinding into learning phase in which a roadmap is bulit and query phase in which a graph search algorithm is used to find a best path within paths.
-Some representative planners are Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
-Relatively speaking, single-query planner completes pathfinding by constructing and querying at the same time, that is to say, the roadmap will be constructed incrementally and toward the goal.
-Some representative planners such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}.
+Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
+Single-query planner will complete pathfinding by constructing and querying simultaneously,
+%  i.e., the roadmap will be constructed incrementally and toward the goal, 
+such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}.
 However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner.
-Some common dynamic planner also can be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.
-
-Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning to deal with.
-The reason is that URTS is a large-scale system, which makes the environment in which it is located changes more violently and will leads to many corresponding behaviors which path constraints will not necessarily be the same (e.g., curvature constraints of two behavior: running and walking are expected to be different for robot).
-In this case, Path Planning becomes a higher-level planner which regard agent as a point without kinodynamic constraints while the decision of the behavior and the corresponding motion will be handed over to the next two layers: Behavior Layer and Local Motion Planning.
+Some common dynamic planner can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.
+All of the above common roadmap-based planners can be applied to the URTS.
+
+Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with.
+The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary.
+(e.g., curvature constraints of two behavior: running and walking are expected to be different for robot).
+In this case, a unified planner will become overly complex and impracticable.
+For this reason, we divide path planning into three subprocess, i.e., Path Planning, Behavior Layer and Local Motion Planning.
+Then, the global planner, Path Planning block, will regard agent as a point without kinodynamic constraints.
+The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
 % In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
@@
 Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques.
-Goal configuration is obtained by previous layer: Task Allocation.
+Goal configuration is obtained by previous block, Task Allocation.
 Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
-It's a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
+$\mathcal{C}$ is a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
 For a simpler explanation of how the URTS works, the following assumption is made.
@@
 \end{assumption}
-\begin{assumption} \label{asm:collision}
+\begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
     UAVs do not consider obstacle collisions because there are few obstacles in the air.
@@
 \end{assumption}
-From above assumption, a path of agent can be expressed as a sequence
+From above assumptions, a path of agent can be expressed as a sequence
 \begin{equation}
@@
 For robot, it can be a collision detecting by a dynamic roadmap-based planner.
-The results path $(\sigma_n)$ is passed to next layer, Behavior Layer.
+The results path $(\sigma_n)$ is passed to next block, Behavior Layer.
 
@@
 Besides, the agents do not always moving.
-Somtimes they has to suspending to take a action such like getting and putting supplies, rotating in place to collect more environment info, or some unexpected situations occur such like no path found, the robot falls.
+Somtimes they has to suspend to take a action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
 These behaviors without changing position are called an "action" in this paper.
@@
 \end{equation}
-It is to say that the path $(\sigma_n)$ is divided into many segments which corresponding to a specific behavior.
+It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior.
+Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set.
 The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig.
@@
 After a specific behavior is determined, the next step is to design a motion to achieve that behavior.
-Local Motion Planning is like Path Planning but its scale is smaller and its resolution and precision must be higher.
-Collision checking is needed since we consider agent as a point or a cube in Path Planning and it's a real body here.
+Local Motion Planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher.
+Collision checking is needed since we consider agent as a point in Path Planning block and it is a real body here.
 Furthermore, the kinodynamic constraint is handled in this block.
 Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often the same notion in other literature.
-Therefore, the output of this block is also a path but with a sampling period which often be referred as a reference trajectory $r(t)$.
-$r(t)$ describes the position and orientation that needed to be reach by a machine system govern by a dynamic equation.
+Therefore, the output of this block is also a path but with a timescale, i.e., sampling period.
+This path is often referred as a reference trajectory $r(t)$.
+$r(t)$ describes the position and orientation that needed to be reach over time by a machine system govern by a dynamic equation.
 Then, Tracking Control block will track $r(t)$ to really do that behavior.
 Note that the path and trajectory are distinguished in some literature.
-Different from path (e.g., $(\sigma_n)$), a trajectory (e.g., $r(t)$) has consider the time in physic world.
+Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has consider the time in physic world.
 The flowchart of Local Motion Planning block is shown in Fig.
@@
     \includegraphics[scale=.4]{fig/LMP.pdf}\caption{The flowchart of local motion planning.
-The corresponding motion design will be executed according to the behavior determined by the behavior layer.}
+The corresponding motion planning will be executed according to the behavior determined by the behavior layer.
+The terminator, exception, represents an exceptional condition that performs unconsidered behaviors.
+The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
+$r[k]$ will convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
     \label{fig:LocalMotionPlanning}
@@
 \ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are added to illustrate the flow of this block.
-The terminator, exception, represents an exceptional condition that performs unconsidered behaviors.
-To limit the scope of this article, we only focus on the motion design of Flying (for UAV) and Walking (for robot) behavior which belong to Moving behavior.
-The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
-It then convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.
+To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
+They are belong to moving behavior in Fig.
+\ref{fig:LocalMotionPlanning}.
 
@@
 In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first.
-After the system description of UAV and robot, the motion design of Flying and Walking as shown in Fig.
+After the system description of UAV and robot, the motion planning of flying and walking as shown in Fig.
 \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
@@
 \end{figure*}
-Before the discussion of the motion design of these two behavior, the following assumption is maded.
+Before the discussion of the motion planning of these two behavior, the following assumption is maded.
 \textit{
@@
 Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant.
-At the same time, the assumption \ref{asm:cc again} makes sure the error will not causing collision.
+At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not causing collision.
 As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$.
-The post-process will appear in the begining of motion design process of these two behaviors as shown in Fig.
+The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig.
 \ref{fig:FandW}.
 
-\subsection{motion design of flying of UAV}
+\subsection{motion planning of flying of UAV}
 A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
@@
 Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.
-% For ease of discussion later, let us convert (\ref{eq:uav}) into the following form:
-% \begin{equation}
-%     F_w=M(X_w)\ddot{X_w}+C(\dot{X_w})+G(X_w)+F(\dot{X_w})
-% \end{equation
 
 Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
-The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed by linear interpolation and then cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
+The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
 $(\sigma_n')$ is the position reference path $\begin{bmatrix}
@@
 \end{bmatrix}^T$.
-Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are set.
+Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered.
 $\phi_r[k]$ is set to zero since no need for spinning when flying.
@@
 For robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space.
-Furthermore, the walking of biped-robot suffers from the falling problem, i.e, how to find a stable walking parttern prevent robot from falling.
+Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern prevent robot from falling.
 These make the design of walking motion more difficult.
-In this paper, a three-dimensional linear inverted pendulum Mode (3D-LIPM) \cite{kajita2001real} is used to design the walking motion.
+In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion.
 
@@
 This makes the analytical solution of reference $q_r(t)$ impossible.
-However, an approximate solution can be derived through 3D-LIPM which will find CoM reference first and then obtain $q_r(t)$ by using inverse kinemic (IK) given step size, step height, step period and CoM height.
+However, an approximate solution can be derived through 3D-LIPM.
+It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinemic (IK) given step size, step height, step period and CoM height.
 Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model.
@@
 
+\textit{
     \begin{remark}
@@
 That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK.
-Hence, we need to find the  position path and orientation path which compose the desired path.
+Hence, we need to find the  position path and orientation path, which compose the desired path.
     \end{remark}
+}
 
@@
 Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component are given by step height.
-By using cubic spline interpolation, we have the left and right ankle position path $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
+By using cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
 The ankle orientation path is found by gradient of ground.
-Finally, the ankle path is found by combining the position and orientation path together.
+Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together.
 So far, the remaining work is to find out the CoM path and then to combine with the ankle path to calculate the joint path through IK.
@@
 To obtain CoM postion path $(CP_n)$, ZMP path need to obtain first.
-ZMP path can be obtained through ankle path since ZMP needs to lie in the support face and ankle path point out when a feet is stand on the ground.
+ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path point out when a feet is stand on the ground.
 Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
@@
 where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP.
-Since $z_c,g,(p_x,p_y)$ are given, $(x,y)$ can be solved.
+Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x,y)$ can be solved.
 To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference path so that the solution of ODE (\ref{eq:LIPM}) $x$, i.e., the CoM position path we want is found.
+Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution of ODE $x$ in (\ref{eq:LIPM}), i.e., the CoM position path we want is found.
 Unlike conventional methods, the problem is solved by optimal control.
@@
 The CoM position path $(CP_n)$ then be obtained by combining $x$, $y$ and $z_c$.
+% $\bar{x}$ in (\ref{eq:output tracking}),
 
@@
 \end{equation}
-where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms to canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law.
+where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness.
 To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
@@
 Therefore, through appropriate conversion, the above disturbances can be equivalent to an disturbance force $d_1(t)$.
-The nominal system (\ref{eq:agent}) then be rewrited as the real system:
+The nominal system (\ref{eq:agent}) then be rewrited as the following real system:
 % The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
@@
 \end{equation}
-where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))$ is the unknown actuator fault signal.
-$\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
+where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))$ is the unknown actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
 % \textit{
@@
 
-Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the fault tolerance stable control problem of linear system (\ref{eq:linear f1}).
+Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the stable control problem of the linear system (\ref{eq:linear f1}) with fault signal.
 The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
@@
 
-To deal with the fault signals, an active fault tolerance control (FTC) is introduced \cite{9306757}.
+To deal with the fault signals, an active fault-tolerant control (FTC) is introduced \cite{9306757}.
 First, we need a model of the fault signal.
@@
 \end{assumption}
-Under the assumption, now we can construct a "smooth" model by finite difference method.
+Under the assumption, now we can construct a smoothing signal model by finite difference method.
 To obtain a state-space representation, the derivative of the fault signals $\dot{f}_i(t)$ with uniform grid $h$ are needed, which can be expressed as:
@@
 For the convenience of analysis, let us choose $Z_0=\{ 0,1,\dots,p-1 \}$.
-By changing index $k$ to $j$, the derivative of $f_i(t-jh),k\in{Z_0}$ can be obtained by (\ref{eq:df}):
+By changing index $k$ to $j$, the derivative of $f_i(t-jh),j\in{Z_0}$ can be obtained by (\ref{eq:df}):
 \begin{equation} \label{eq:df1}
-    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t), j=0,1,\dots,p-1
+    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t)
 \end{equation}
@@
     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
-\end{bmatrix}^T$, and $A_i=(a_{j,k})\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
+\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
 \begin{equation} \label{eq:8}
@@
     \begin{remark}
-        The equation (\ref{eq:df}) is derived by Taylor expansion, so assumption \ref{asm:smooth} is nessasry.
+        The equation (\ref{eq:df}) is derived by Taylor expansion, so Assumption \ref{asm:smooth} is nessasry.
 Unlike previous work, a finite-difference-method-based modeling method is proposed, which reduce the approximation error between origin fault signal and its smooth model.
@@
     M_{11} & -P_1\bar{B}K - K^TRK \\ * & M_{22}
-\end{bmatrix} < 0 \Rightarrow M_{11}<0, M_{22}<0$, the inequality $M_{11}<0$ is used to find $P_1,K,\rho$. Premultiplying and
+\end{bmatrix} < 0 \Rightarrow M_{11}<0, M_{22}<0$, the inequality $M_{11}<0$ is used to find $P_1,K$. Premultiplying and
 postmultiplying $M_{11}<0$ by $W_1=P_1^{-1}$ and applying Lemma \ref{lemma2}, we obtain:
@@
 \end{equation}
-where $Y_1=KW_1$. By solving the LMI (\ref{eq:step1}), we can obtain $W_1,Y_1,\rho$.
-
-\textit{Step 2:} Substituting $P_1=W^{-1}$, $K=Y_1W_1^{-1}$ and $\rho$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
+where $Y_1=KW_1$. By solving the LMI (\ref{eq:step1}), we can obtain $W_1,Y_1$.
+
+\textit{Step 2:} Substituting $P_1=W^{-1}$ and $K=Y_1W_1^{-1}$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
 \begin{equation} \label{eq:step2}
@@
 Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:aug}).
+
+For the optimal $H_\infty$ observer-based stablized control specification for (\ref{eq:aug}), we need to solve the following LMIs-constrained optimization problem:
+\begin{equation}
+    \begin{split}
+        & \rho^*=\min \rho \\
+        & s.t.
+    \end{split}
+\end{equation}
+...
 
@@
     \centering
-    \includegraphics[scale=.5]{fig/tracking.pdf}\caption{The flowchart of tracking control.
+    \includegraphics[scale=.42]{fig/tracking.pdf}\caption{The flowchart of tracking control.
 The control scheme of UAV and robot is only different from the block, reference generator.

### 2022-08-03 paper/paper.tex
tracking merge

@@
 In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage.
-The system architecture of URTS is proposed to illustrate the issues that need to be addressed in URTS and the relationships between them.
+The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them.
 Then we focus on two issues, local motion planning and tracking control.
@@
 The tracking control is to control an agent to follow a desired trajectory.
-There are many control strategy for MAS.
+There are many control strategies for MAS.
 According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}.
-Centralized control means there exist a powerful central controller in MAS to gather the state information and sent the control command back to each agent to reach a global goal.
+Centralized control means there exist a powerful central controller in MAS to gather the state information and send the control command back to each agent to reach a global goal.
 Due to the powerful nature of the central controller, control commands can be determined well and quickly.
@@
 It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
-In this situation, it is more reasonable to treat each agent as an independent individual and design an independent trajectory for the agent to follow.
+In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for the agent to follow.
 
@@
 
-In order to make an behavior, we must design a corresponding motion which is handled by local motion planning.
+In order to make a behavior, we must design a corresponding motion which is handled by local motion planning.
 The motion is a desired reference trajectory for an actual mechanical system to follow.
@@
 The visual object recognition block provides distance information and object information through the analysis of sensor information.
-The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot sees a obstacle and decides to climb through it).
+The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it).
 The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.
@@
 Urgency, position, amout of supplies needed).
-Therefore, the results of task allocation can be "good or bad", which makes us want to find the optimal allocation.
-This problem is refered as task allocation problem or multi-robot task allocation problem.
-A problem formulation and problem modeling can be found in \cite{Khamis2015}.
-Although there are many different problem definitions and many problem models to solve this issue, the common goal is to find a set of task-agent pairs to achieve a specific cost function.
+Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation.
+This problem is refered as a task allocation problem or multi-robot task allocation problem.
+A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}.
+Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function.
 In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue.
-In other words, every agent knows a destinition $q_{goal}$ it need to go at every moment.
+In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
 Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
-Single-query planner will complete pathfinding by constructing and querying simultaneously,
+Single-query planner will complete the pathfinding by constructing and querying simultaneously,
 %  i.e., the roadmap will be constructed incrementally and toward the goal, 
 such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}.
-However, the environment is dynamic rather static for URTS so some extra structure need to impose on aforementioned planner.
-Some common dynamic planner can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.
+However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner.
+Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.
 All of the above common roadmap-based planners can be applied to the URTS.
@@
 In this case, a unified planner will become overly complex and impracticable.
-For this reason, we divide path planning into three subprocess, i.e., Path Planning, Behavior Layer and Local Motion Planning.
-Then, the global planner, Path Planning block, will regard agent as a point without kinodynamic constraints.
+For this reason, we divide path planning into three subprocesses, i.e., Path Planning, Behavior Layer and Local Motion Planning.
+Then, the global planner, Path Planning block, will regard an agent as a point without kinodynamic constraints.
 The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
@@
 Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques.
-Goal configuration is obtained by previous block, Task Allocation.
+Goal configuration is obtained by the previous block, Task Allocation.
 Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
-$\mathcal{C}$ is a space contain all possible configuration of agent which composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
+$\mathcal{C}$ is a space contain all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
 For a simpler explanation of how the URTS works, the following assumption is made.
@@
 \begin{assumption}
-    The URTS is supposed to have an perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtain.
+    The URTS is supposed to have a perfect real-time mapping ability so a real-time configuration space $\mathcal{C}$ can be obtained.
 \end{assumption}
@@
     UAVs do not consider obstacle collisions because there are few obstacles in the air.
-Hence, the path of UAVs can be directly assigned rather found by planner.
+Hence, the path of UAVs can be directly assigned rather than found by planner.
 Robots do not consider obstacle collisions in the direction perpendicular to the ground.
@@
 Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$.
-For agents, the replanning decision can be a goal changing that made by human or Task Allocation.
+For agents, the replanning decision can be a goal changing that is made by human or Task Allocation.
 For robot, it can be a collision detecting by a dynamic roadmap-based planner.
-The results path $(\sigma_n)$ is passed to next block, Behavior Layer.
+The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.
 
@@
 Besides, the agents do not always moving.
-Somtimes they has to suspend to take a action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
+Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
 These behaviors without changing position are called an "action" in this paper.
-More behaviors can be added so that the agent can have more way to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control.
+More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control.
 The sequence of these behaviors be expressed as:
@@
 Furthermore, the kinodynamic constraint is handled in this block.
-Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often the same notion in other literature.
+Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
 Therefore, the output of this block is also a path but with a timescale, i.e., sampling period.
 This path is often referred as a reference trajectory $r(t)$.
-$r(t)$ describes the position and orientation that needed to be reach over time by a machine system govern by a dynamic equation.
+$r(t)$ describes the position and orientation that need to be reach over time by a machine system governed by a dynamic equation.
 Then, Tracking Control block will track $r(t)$ to really do that behavior.
 Note that the path and trajectory are distinguished in some literature.
-Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has consider the time in physic world.
+Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
 The flowchart of Local Motion Planning block is shown in Fig.
@@
 }
-However, for these two behaviors, there all exists an inevitable kinematic constraint on curvature of local motion.
+However, for these two behaviors, there all exist an inevitable kinematic constraint on curvature of local motion.
 Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem.
 Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant.
-At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not causing collision.
+At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision.
 As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$.
@@
 $\phi_r[k]$ is set to zero since no need for spinning when flying.
-$\theta_r[k]$ and $\psi_r[k]$ cannot be set since UAV is an underactuated system, which will be discussed in the next section.
+$\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section.
 Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
@@
     \begin{remark}
-        A frame in $\mathbb{R}^3$ can be determined by given the "position" and "orientation" with respect to a reference frame.
+        A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
 That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK.
@@
 
-To obtain CoM postion path $(CP_n)$, ZMP path need to obtain first.
-ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path point out when a feet is stand on the ground.
+To obtain CoM postion path $(CP_n)$, ZMP path needs to be obtained first.
+ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground.
 Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution of ODE $x$ in (\ref{eq:LIPM}), i.e., the CoM position path we want is found.
-Unlike conventional methods, the problem is solved by optimal control.
+Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path we want is found.
+Unlike conventional methods, the problem is solved by the optimal control.
 The system is discretized first and the discrete LQ tracker is employed to achieve the output tracking.
@@
 Let $\pmb{e}(t)=\begin{bmatrix}
-    \int_{0}^{t}e(\tau)d\tau & e(t) & \dot{e}(t)
-\end{bmatrix}\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
+    \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
+\end{bmatrix}^T\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
 \begin{equation} \label{eq:linear f1}
@@
 
-Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the stable control problem of the linear system (\ref{eq:linear f1}) with fault signal.
+Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the stable control problem of the linear system (\ref{eq:linear f1}) with fault signal by the feedforward linearization.
 The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
@@
 At the same time, the external disturbances on sensor also need to be considered as mentioned before.
-Since the sensor information (\ref{eq:agent output}) will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are concerned.
+Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are concerned.
 Suppose the total effect can be equivalent to an unknown sensor fault signal $f_2(t)\in \mathbb{R}^{n}$ with same size as $f_1(t)$, the measurement output equation can be described as:
@@
 \end{equation}
-where $y(t)\in\mathbb{R}^l$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, and $B_2\in\mathbb{R}^{l\times n}$ is the input matrix of $f_2(t)$.
+where $y(t)\in\mathbb{R}^{ln}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, and $B_2\in\mathbb{R}^{l\times n}$ is the input matrix of $f_2(t)$.
 By putting (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have the following system:
@@
 where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
-\begin{equation} \label{eq:7}
+\begin{equation} \label{eq:smooth model}
     \dot{F}_i(t)=A_iF_i(t)+v_i(t)
@@
     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
-\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:7})
+\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:smooth model})
 \begin{equation} \label{eq:8}
@@
     1 & 0 & \dots & 0
-\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:7}) and (\ref{eq:8}) into (\ref{eq:error}), we get:
+\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:smooth model}) and (\ref{eq:8}) into (\ref{eq:error}), we get:
 \begin{equation} \label{eq:9}
@@
 \end{equation}
-where $t_f$ is the final time, $Q \leq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
+where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
 \begin{theorem} \label{theorem1}
-    If there exists matrices $P=P^T>0, K$ and a scalar $\rho>0$ such that the following matrix inequality hold:
+    If there exists matrices $P=P^T>0, K,L$ such that the following matrix inequality hold:
     \begin{equation} \label{BMI1}
@@
         K & -K
-    \end{bmatrix}$, then the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) holds.
+    \end{bmatrix}$, then the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) can be achieved.
 \end{theorem}
@@
 
-Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:aug}).
-
-For the optimal $H_\infty$ observer-based stablized control specification for (\ref{eq:aug}), we need to solve the following LMIs-constrained optimization problem:
-\begin{equation}
-    \begin{split}
-        & \rho^*=\min \rho \\
-        & s.t.
-    \end{split}
-\end{equation}
-...
-
-% The design procedure of the $H_\infty$ observer-based stablized control scheme for the augmented system (\ref{eq:aug}) is organized as follows.
-% \begin{enumerate}
-%     \item ...
-% \end{enumerate}
+% Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:aug}).
+
+If we want to find the optimal $H_\infty$ observer-based stablized control specification for the system (\ref{eq:aug}), we need to solve the following LMIs-constrained optimization problem:
+\begin{equation} \label{LMI constraint}
+    \begin{split}
+        & \rho^*=\mathop{\min}_{P,K,L} \rho \\
+        & s.t. (\refeq{eq:step1}),(\refeq{eq:step2}) 
+    \end{split}
+\end{equation}
+
+The design procedure of the optimal $H_\infty$ observer-based feedforward-linearized PID FTC scheme for the agent (\ref{eq:agent d1}) is organized as follows.
+\begin{enumerate}
+    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized system (\ref{eq:error})
+    \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$.
+Embed into the linearized system (\ref{eq:error}) to get the augment system (\ref{eq:aug}).
+    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$.
+\end{enumerate}
+
 % \begin{theorem} \label{theorem2}
@@
 % \end{proof}
-Although the control gain and observer gain that satisfy with the specification can already be found through the previous steps, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{BMI1}).
-Observing the matrices $A,B,C,B_2$ in linear system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ have the same form to $A,B$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l\times 3},B_{2,0}\in\mathbb{R}^{l\times 1}$.
+Although the control gain and observer gain can already be found through the previous steps, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{BMI1}).
+First, let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$ and the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $y_i(t)\in\mathbb{R}^l$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$.
+Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l\times 3},B_{2,0}\in\mathbb{R}^{l\times 1}$.
+This means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
+In actual systems, this is usually done.
 Due to the fact that $f_1(t)\in\mathbb{R}^n, f_2(t)\in\mathbb{R}^{n}$, the n subsystems are obtained from (\ref{eq:error}):
@@
         & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fb,i}(t)+f_{1,i}(t)) \\
-        & \pmb{y}_i(t)=C_0\pmb{e}_i(t)+B_{2,0}f_{2,i}(t)   
-    \end{split}
-\end{equation}
-where subscript $i = 1, 2, ..., n$ denote the element in the corresponding vector.
+        & {y}_i(t)=C_0\pmb{e}_i(t)+B_{2,0}f_{2,i}(t)   
+    \end{split}
+\end{equation}
+where $u_{fb,i}(t),f_{1,i}(t),f_{2,i}(t)\in \mathbb{R}$ denote the element in the corresponding vector.
 By Theorem \ref{theorem1} again, the form shows that the subsystems (\ref{eq:linear subsys}) can achieve the $H_\infty$ observer-based stablized control performance.
@@
     \mathit{v}_1 & \mathit{v}_2 & ... & \mathit{v}_n
-\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$ where $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$.
+\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$.
 The origin observer gain $L$ can be obtained in the same way.

### 2022-08-25 paper/paper.tex
UAV simulation Fa,Fs

@@
 
-\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
+\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage}
 % \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
@@
 \begin{abstract}
-In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue usage.
+In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue (S\&R) usage.
 The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them.
@@
 \begin{keywords}
-biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, search and rescue, smoothing signal model, UAV, UAVs-UGVs team system
+biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, UAVs-UGVs team system
 \end{keywords}
@@
 It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans.
-Due to these benefits, it has been widely used in many scenarios, such as search and rescue, battlefield, logistics and transportation, and surveillance, etc (cite:UV).
+Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, and surveillance, etc (cite:UV).
 Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
@@
 For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
-To discuss more concretely, we consider an UAVs-UGVs team system for search and rescue.
+To discuss more concretely, we consider an UAVs-UGVs team system for S\&R.
 For the need for search mobility, we choose quadrotor aircraft as UAV.
-In order to deal with the complex terrain of the search and rescue environment, we choose biped robot as UGV.
-Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.
-
-To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent search and rescue system, such as task allocation problem, path planning problem or control problem.
+In order to deal with the complex terrain of the S\&R environment, we choose biped robot as UGV.
+Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.
+
+To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem.
 Additionally, few literatures illustrate the relationship between these problems.
-This leads us to propose an system architecture of UAVs-robots team system (URTS) for search and rescue usage.
+This leads us to propose an system architecture of UAVs-robots team system (URTS) for S\&R usage.
 The flowchart of decision-making and control process of URTS is also given.
@@
 The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
-In order to deal with the complex terrain of the search and rescue environment, biped robot was chosen as the UGV.
-Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a search and rescue system.
+In order to deal with the complex terrain of the S\&R environment, biped robot was chosen as the UGV.
+Although other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.
 However, to let the biped robot moving, not only the control problem (cite: robot control) but also the local motion planning problem need to be solved.
@@
 
-\section{PRELIMINARIES OF search and rescue URTS}
-The URTS will start with a given search and rescue area, and end with mission completed.
+\section{PRELIMINARIES OF S\&R URTS}
+The URTS will start with a given S\&R area, and end with mission completed.
 The URTS is composed of $N_T$ teams and a ground station.
 Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots.
-Hence, the $i$th agent in the $j$th team is denoted as $agent_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
-The UAVs are chosed as the first agents in each team, i.e., $agent_{1,j}$.
+Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
+The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$.
 Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making.
@@
 
-To complete search tasks, each team is designed to be responsible for a small area of the overall search area, and each agent will be assigned an appropriate path to cover the area.
+To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area.
 To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target.
@@
 The agents overall have the same system architecture in URTS except for some subprocess differences.
-Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in search and rescue is proposed as shown in Fig.
+Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in S\&R is proposed as shown in Fig.
 \ref{fig:sys}.
@@
 The 2 blocks on left side are used to convert low-level sensor information into high-level information, such as map, start point and object information.
-The 5 blocks on right side are the flow of an agent performing a search and rescue mission.
+The 5 blocks on right side are the flow of an agent performing a S\&R mission.
 From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control}%
@@
         This block is like a commander since it is used to assign task for agents.
-Thus, if the real search and rescue system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
+Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
     \end{remark}
@@
 % where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
-$m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust.
+$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust.
 This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction.
@@
 
-Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $(\beta_n)=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
+Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n={flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
 The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
-$(\sigma_n')$ is the position reference path $\begin{bmatrix}
+Then, $(\sigma_n')$ will be the position reference path $\begin{bmatrix}
     x_r[k] & y_r[k] & z_r[k]
@@
 In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}).
-Therefore, through appropriate conversion, the above disturbances can be equivalent to an disturbance force $d_1(t)$.
+Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $d_1(t)$.
 The nominal system (\ref{eq:agent}) then be rewrited as the following real system:
@@
 \end{equation}
-where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))$ is the unknown actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
+where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
 % \textit{
@@
 The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
-In a real system, the feedback information is measured by sensor, i.e, the state $\pmb{e}(t)$ in (\ref{eq:linear f1}) is unavailable.
+In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
 At the same time, the external disturbances on sensor also need to be considered as mentioned before.
 Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are concerned.
-Suppose the total effect can be equivalent to an unknown sensor fault signal $f_2(t)\in \mathbb{R}^{n}$ with same size as $f_1(t)$, the measurement output equation can be described as:
+Let $\pmb{x}(t)=\begin{bmatrix}
+    \int_{0}^{t}x^T(\tau)d\tau & x^T(t) & \dot{x}^T(t)
+\end{bmatrix}^T$
+% Suppose the total effect can be equivalent to an unknown sensor fault signal $f_2(t)\in \mathbb{R}^{n}$ with same size as $f_1(t)$, 
+, the measurement output equation can be described as:
 \begin{equation} \label{eq:agent output}
-    y(t) = C\pmb{e}(t) + B_2f_2(t)
-\end{equation}
-where $y(t)\in\mathbb{R}^{ln}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, and $B_2\in\mathbb{R}^{l\times n}$ is the input matrix of $f_2(t)$.
-By putting (\ref{eq:linear f1}) and (\ref{eq:agent output}) together, we have the following system:
+    y(t) = C\pmb{x}(t) + B_2f_2(t)
+\end{equation}
+where $y(t)\in\mathbb{R}^{l}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, $B_2\in\mathbb{R}^{l\times o}$ is the input matrix of $f_2(t)$, and $f_2(t)\in\mathbb{R}^o$ is the actuator fault signal .
+Let $\pmb{r}(t)=\begin{bmatrix}
+    \int_{0}^{t}r^T(\tau)d\tau & r^T(t) & \dot{r}^T(t)
+\end{bmatrix}^T$ to modify the output equation (\ref{eq:agent output}) and putting it and (\ref{eq:linear f1}) together, we have the following system:
 \begin{equation} \label{eq:error}
@@
         & \dot{\pmb{e}}(t)=A\pmb{e}(t)+B(u_{fb}(t)+f_1(t)) \\
-        & y(t) = C\pmb{e}(t) + B_2f_2(t)   
+        & y(t) = C\pmb{e}(t) + C\pmb{r}(t) + B_2f_2(t)   
     \end{split}  
@@
 
-To deal with the fault signals, an active fault-tolerant control (FTC) is introduced \cite{9306757}.
-First, we need a model of the fault signal.
-In general, constructing a model for an unknown signal is impossible since there is no information about it.
-Hence, the following assumption is maded:
-\begin{assumption} \label{asm:smooth}
-    The first $p-1$ derivatives of the fault signals $f_i(t), i=1,2$ all exist and are continuous, i.e., $f_i(t)\in C^{p-1}$.
-\end{assumption}
-Under the assumption, now we can construct a smoothing signal model by finite difference method.
+To deal with the fault signals $f_i(t),i=1,2$, a smoothing signal model is introduced \cite{9306757}:
+%% teacher say the following assumption too strong
+% First, we need a model of the fault signal. In general, constructing a model for an unknown signal is impossible since there is no information about it. Hence, the following assumption is maded:
+% \begin{assumption} \label{asm:smooth}
+%     The first $p-1$ derivatives of the fault signals $f_i(t), i=1,2$ all exist and are continuous, i.e., $f_i(t)\in C^{p-1}$.
+% \end{assumption}
+% Under the assumption, now we can construct a smoothing signal model by finite difference method.
 To obtain a state-space representation, the derivative of the fault signals $\dot{f}_i(t)$ with uniform grid $h$ are needed, which can be expressed as:
-\begin{equation} \label{eq:df}
-    \dot{f}_i(t)=\sum_{k\in{Z_0}}\frac{a_k f_i(t-kh)}{h} + R_{p-1}(t), Z_0\subset\mathbb{Z}
-\end{equation}
-where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference.
+% \begin{equation} \label{eq:df}
+%     \dot{f}_i(t)=\sum_{k\in{Z_0}}\frac{a_k f_i(t-kh)}{h} + R_{p-1}(t), Z_0\subset\mathbb{Z}
+% \end{equation}
+% where $R_{p-1}(t)\in O(h^{p-1})$ denotes the remainder term, and $p=\vert{Z_0}\vert > 1$ is the accuracy of difference.
 The derivative of $f_i(t-kh),k\in{Z_0}$ in (\ref{eq:df}) is also needed.
@@
 By changing index $k$ to $j$, the derivative of $f_i(t-jh),j\in{Z_0}$ can be obtained by (\ref{eq:df}):
-\begin{equation} \label{eq:df1}
-    \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t)
-\end{equation}
-where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
+% \begin{equation} \label{eq:df1}
+%     \dot{f}_i(t-jh)=\sum_{k=0}^{p-1}\frac{a_{j,k} f_i(t-kh)}{h}+\epsilon_j(t)
+% \end{equation}
+% where $\epsilon_j(t)\in O(h^{p-1})$. By arranging $\dot{f}_i(t-jh)$ into a state-space representation, we have:
+%
+% where $F_i(t)=\begin{bmatrix}
+%     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-kh)
+% \end{bmatrix}^T$, $v_i(t)=\begin{bmatrix}
+%     \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
+% \end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. 
+% Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:smooth model})
+% \begin{equation} \label{eq:8}
+%     f_i(t)=C_iF_i(t)
+% \end{equation}
+% where $C_i=\begin{bmatrix}
+%     1 & 0 & \dots & 0
+% \end{bmatrix}\otimes I_{n}$.
 \begin{equation} \label{eq:smooth model}
-    \dot{F}_i(t)=A_iF_i(t)+v_i(t)
-\end{equation}
-where $v_i(t)=\begin{bmatrix}
-    \epsilon_0^T(t) & \epsilon_1^T(t) & \dots & \epsilon_{p-1}^T(t)
-\end{bmatrix}^T$, $F_i(t)=\begin{bmatrix}
-    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-(p-1)h)
-\end{bmatrix}^T$, and $A_i=[a_{j,k}]\otimes I_{n}$. Then, the fault signals $f_i(t), i=1,2$ are the output of the system in (\ref{eq:smooth model})
-\begin{equation} \label{eq:8}
-    f_i(t)=C_iF_i(t)
-\end{equation}
-where $C_i=\begin{bmatrix}
+    \begin{split}
+        & \dot{F}_i(t)=A_iF_i(t)+v_i(t) \\
+        & f_i(t)=C_iF_i(t)        
+    \end{split}
+\end{equation}
+where $F_i(t)=\begin{bmatrix}
+    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-kh)
+\end{bmatrix}^T\in\mathbb{R}^{(k+1)n}$, $A_i\in\mathbb{R}^{{(k+1)n}\times{(k+1)n}}$, $v_i(t)$ is the model error, and $C_i=\begin{bmatrix}
         1 & 0 & \dots & 0
-\end{bmatrix}\otimes I_{n}$. Sub. (\ref{eq:smooth model}) and (\ref{eq:8}) into (\ref{eq:error}), we get:
-\begin{equation} \label{eq:9}
+    \end{bmatrix}\otimes I_{n_i}$ with $n_1=n$ and $n_2 = o$. Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get:
+\begin{equation} \label{eq:e_bar}
     \begin{split}
         & \dot{\bar{e}}(t) = \bar{A}\bar{e}(t)+\bar{B}u_{fb}(t)+\bar{v}(t) \\
-        & y(t)=\bar{C}\bar{e}(t)
+        & y(t)=\bar{C}\bar{e}(t) + C\pmb{r}(t)
     \end{split}
@@
 \end{bmatrix}$.
-\textit{
-    \begin{remark}
-        The equation (\ref{eq:df}) is derived by Taylor expansion, so Assumption \ref{asm:smooth} is nessasry.
+% \textit{
+%     \begin{remark}
+%         The equation (\ref{eq:df}) is derived by Taylor expansion, so Assumption \ref{asm:smooth} is nessasry.
 Unlike previous work, a finite-difference-method-based modeling method is proposed, which reduce the approximation error between origin fault signal and its smooth model.
 Besides, the fault signals $f_i(t)$ are assumed to be of differentiability class $C^{p-1}$ rather than bounded, which will make the proposed method more general for practical scenario.
-    \end{remark}
-}
-Since the fault signals become a state variable of the augment system in (\ref{eq:9}), a Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC:
-\begin{equation} \label{eq:10}
+%     \end{remark}
+% }
+Since the fault signals become a state variable of the augment system in (\ref{eq:e_bar}), a Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC:
+\begin{equation} \label{eq:e_hat}
     \begin{split}
         & \dot{\hat{\bar{e}}}(t)=\bar{A}\hat{\bar{e}}(t)+\bar{B}u_{fb}(t)-{L}(y(t)-\hat{y}(t)) \\
-        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t)  
+        & \hat{y}(t)=\bar{C}\hat{\bar{e}}(t) + C\pmb{r}(t)
     \end{split}
@@
 \begin{assumption}
-    The augmented system (\ref{eq:9}) is observable.
+    The augmented system (\ref{eq:e_bar}) is observable.
 \end{assumption}
@@
 \end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
-Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, then an new augmented system can be obtained from (\ref{eq:9}), (\ref{eq:10}) and (\ref{eq:Kx}):
+Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, by the two subsystems (\ref{eq:e_bar}) and (\ref{eq:e_hat}), we get:
+\begin{equation} \label{eq:e_tilde}
+    \dot{\tilde{e}}(t) = \bar{A}\tilde{e}(t) +L\bar{C}\tilde{e}(t)
+\end{equation}
+Combining (\ref{eq:e_bar}), (\ref{eq:e_hat}) and (\ref{eq:Kx}), we have the following augmented system:
 \begin{equation} \label{eq:aug}
@@
 \begin{equation} \label{Hinf}
-    \begin{split}     
-        & H_{\infty}(K, L) \\
-        & = \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u_{fb}^T(t)Ru_{fb}(t))dt - V(\tilde{x}(0))}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
-    \end{split}
-\end{equation}
-where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of state and estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
-If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on tracking and estimation error $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
+    % \begin{split}     
+        % & H_{\infty}(K, L) \\
+        % & = 
+        \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u_{fb}^T(t)Ru_{fb}(t))dt - V(\tilde{x}(0))}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
+    % \end{split}
+\end{equation}
+where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of augmented state, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
+If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented state $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
 Before analyzing the $H_\infty$ observer-based stablized control problem in (\ref{Hinf}), the following lemmas are given:
@@
         \end{split}
-    \end{equation}. By (\ref{eq:aug}) and Lemma \ref{lemma1}, we have:
+    \end{equation}
+    By (\ref{eq:aug}) and Lemma \ref{lemma1}, we have:
     \begin{equation} \label{pf:2}
@@
         \end{split}
-    \end{equation}. Substituting (\ref{pf:2}) and (\ref{eq:Kx}) into (\ref{pf:1}), we get:
+    \end{equation}
+    Substituting (\ref{pf:2}) and (\ref{eq:Kx}) into (\ref{pf:1}), we get:
     \begin{equation*} \label{pf:3}
@@
         \end{split}
-    \end{equation*}. Thus, if (\ref{BMI1}) holds then (\ref{Hinf}) holds
+    \end{equation*}
+    Thus, if (\ref{BMI1}) holds then (\ref{Hinf}) holds
 \end{proof}
@@
 
-\textit{Step 1:} First, let $P=\begin{bmatrix}
+\textit{Step 1:} First, let the Lyapunov function of augmented system (\ref{eq:aug}) be the sum of two Lyapunov function of subsystems (\ref{eq:e_bar}) and (\ref{eq:e_tilde}), i.e., $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)=\bar{e}^T(t)P_1\bar{e}(t)+\tilde{e}^T(t)P_2\tilde{e}(t)$.
+Second, let the augmented state energy be the sum of tracking error energy and estimated error energy, i.e., $\tilde{x}^T(t)Q\tilde{x}(t)=\bar{e}^T(t)Q_1\bar{e}(t)+\tilde{e}^T(t)Q_2\tilde{e}(t)$.
+Substituting $P=\begin{bmatrix}
     P_1 & 0 \\ 0 & P_2
-\end{bmatrix}, Q=\begin{bmatrix}
+\end{bmatrix}$ and $Q=\begin{bmatrix}
     Q_1 & 0 \\ 0 & Q_2
-\end{bmatrix}$ where $P_1,Q_1$ are for stablized control error and $P_2,Q_2$ are for estimated error. Substituting it into (\ref{BMI1}), we get:
+\end{bmatrix}$ into (\ref{BMI1}), we get:
 \begin{equation} \label{eq:M}
@@
     \begin{bmatrix}
-        Sym(\bar{A}W_1+\bar{B}Y_1) & W_1\sqrt[1/2]{Q_1} & Y_1^T & I \\
-        * & -I & 0 & 0 \\
-        * & * & -R^{-1} & 0 \\
-        * & * & * & -\rho^2I\\
+        Sym(\bar{A}W_1+\bar{B}Y_1) + \frac{1}{\rho^2} & W_1\sqrt[1/2]{Q_1} & Y_1^T \\
+        * & -I & 0\\
+        * & * & -R^{-1}\\
     \end{bmatrix} < 0
@@
 % \end{proof}
-Although the control gain and observer gain can already be found through the previous steps, the calculation speed can be further improved by reducing the dimensionality of the LMI (\ref{BMI1}).
-First, let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$ and the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $y_i(t)\in\mathbb{R}^l$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$.
-Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l\times 3},B_{2,0}\in\mathbb{R}^{l\times 1}$.
-This means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
-In actual systems, this is usually done.
-Due to the fact that $f_1(t)\in\mathbb{R}^n, f_2(t)\in\mathbb{R}^{n}$, the n subsystems are obtained from (\ref{eq:error}):
+Although the control gain and observer gain can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
+Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
+Let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^l_0$, $f_{2,i}(t)\in\mathbb{R}^o_0$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
 \begin{equation} \label{eq:linear subsys}
@@
     \end{split}
-\end{equation}
-where $u_{fb,i}(t),f_{1,i}(t),f_{2,i}(t)\in \mathbb{R}$ denote the element in the corresponding vector.
-By Theorem \ref{theorem1} again, the form shows that the subsystems (\ref{eq:linear subsys}) can achieve the $H_\infty$ observer-based stablized control performance.
-Let $K_i$ be the control gain of the $i$th subsystems, the origin control gain $K$ of the origin agent system can be obtained by $K = \begin{bmatrix}
+\end{equation}.
+\begin{remark}
+    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
+In actual systems, this is usually done.
+\end{remark}
+
+By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based stablized control performance with prescribed attenuation level $\rho_i$, where $s=3+(k-1)+(k-1)o_0$.
+The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
     \mathit{v}_1 & \mathit{v}_2 & ... & \mathit{v}_n
-\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$.
-The origin observer gain $L$ can be obtained in the same way.
-In this case, the calculate speed can be improved since the dimensionality is decrease.
-\textit{
-    \begin{remark}
-        This method can regard as designing the control and observer gain to each state variable, which is a common control method in practice.
+\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$. The origin observer gain $L$ can be reconstructed in the same way.
+
+In this case, the calculation speed of finding gains $K,L$ can be improved since the dimensionality is decrease.
+Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness.
+More clearly, the number of elements in matrix $K$, the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)n$.
+For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)n$.
+% \textit{
+%     \begin{remark}
+%         This method can regard as designing the control and observer gain to each state variable, which is a common control method in practice.
 However, the gains are not directly adjusted but indirectly designed through prescribed specifications (\ref{Hinf}).
@@
 Dependent on the actual system situation, the appropriate $L_i$ and $K_i$ can be designed for each state variable by adjusting the weighting matrix $Q_i,R_i$ and attenuation level $\rho_i$ for each subsystem.
-    \end{remark}
-}
+%     \end{remark}
+% }
 
@@
 
-The overall flowchart of Tracking Control is shown in Fig.
+The overall flowchart of tracking control is shown in Fig.
 \ref{fig:tracking}.
@@
 The reference generator for robot is an identity function since it is a fully actuated system.
-Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)=\begin{bmatrix}
-    \int_{0}^{t}r(\tau)d\tau & r(t) & \dot{r}(t)
-\end{bmatrix}$.
+Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
 $\pmb{r}(t)$ then pass to sensor to calculate the PID tracking error $\pmb{e}(t)$.
@@
 \section{simulation results}
+In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy.
+First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig.
+\ref{fig:SR_area}.
+To simplify the description, we will focus on the UAV and robot in $1$st team.
+Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$.
+At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$.
+The search task is obtained by dividing the unsearched region as shown in Fig.
+\ref{fig:S_task}.
+Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper task-agent pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$.
+Suppose a target is found after a while as shown in Fig.
+\ref{fig:S_task}, at this point, we have a rescue task $T_6$.
+The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one.
+If the ground station assigns $\alpha_{1,2}$ and $\alpha_{1,3}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,2},T_2),(\alpha_{1,3},T_3) \})\cup\{ \alpha_{1,2},T_6),(\alpha_{1,3},T_6) \}$.
+Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
+    \label{fig:SR_area}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining.
+The search tasks $T_j,j=1,2,...,5$ are to reach a destinition $q_{goal}$ as shown in figure.
+For robots, $q_{goal}$ will be passed to path planning algorithm to find a collision path.
+For UAV, the path is directly assigned due to the no-collision assumption as shown in figure.}%
+    \label{fig:S_task}
+\end{figure}
+
+To explain the path planning block and behavior layer block, we choose the pair $(\alpha_{1,2},T_6)$ as an example, i.e., the robot $\alpha_{1,2}$ performing the task $T_6$.
+From $T_6$, we have the goal configuration $q_{goal}$.
+With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n)$ can be found as shown in Fig.
+\ref{fig:R_task}.
+The behavior sequence $(\beta_n)$ is set as shown in Fig.
+\ref{fig:R_task}.
+We choose the first walking behavior to illustrate the local motion planning block of robots.
+For the the UAV $\alpha_{1,1}$, the path $(\sigma_n)$ is directly set to $([ 0,0,0 ]^T, [0,0,0]^T, ...)$ without going through path planning.
+The behavior sequence $(\beta_n)$ of the UAV $\alpha_{1,1}$ is set to flying behavior from start to finish, i.e., $\beta_n={flying}, n\in\mathbb{Z}\cap[1,k_f]$.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
+    \label{fig:R_task}
+\end{figure}
+
+Following the procedure in Fig. \ref{fig:FandW}, the resuls of local motion planning of UAV flying and robot walking are shown in Fig. \ref{fig:sim:FandW}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The resuls of local motion planning of flying and walking.}%
+    \label{fig:sim:FandW}
+\end{figure}
+
+Through the previous steps, the reference trajectory $r(t)$ of flying and walking has been designed. The remaining parameter setting is given as follow.
+
+\textit{UAV:}\begin{enumerate}
+    \item system parameters: $g = 9.81, m = 2,
+    J_x = J_y = 1.25, Jz = 2.2,
+    K_x = K_y = K_z = 0.01,
+    K_\phi = K_\theta = K_\psi = 0.012$
+    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
+\end{enumerate}
+
+\textit{robot:} \begin{enumerate}
+    \item system parameters: Appendix E in \cite{ourrobot}
+    \item designed parameters:
+\end{enumerate}
+
+The tracking error and fault signal estimation of UAV $\alpha_{1,1}$ are shown in Fig.
+\ref{fig:UAV, error, estimation}, where the external disturbances is set to...
+.
+The tracking error and error signal estimation of the robot $\alpha_{1,2}$ are shown in Fig.
+\ref{fig:robot, error, estimation}, where the external disturbances is set to...
+.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:UAV, error, estimation}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
+    \label{fig:robot, error, estimation}
+\end{figure}
+
+description of fig...
 
 \section{conclusion}
-% \subsection{tracking control of UAV-robot team}
-% Since the dynamical system of UAV (\ref{eq:uav}) and robot (\ref{eq:robot}) are nonlinear, it is not easy to design the controller relative to the linear system
-% Use feedback linearization, dynamic of UAV and robot become the form (\ref{eq:4})...
-
-% \subsection{reference trajectories design of UAV-robot team}
-% \textit{Assumption :} The behavior of uavs and robots is always at "fly" and "walk" respectively during the whole process. 
-% \textit{Assumption :} Robots always walking on a flat ground.
-% \subsection{path planning of UAV-robot team}
-% In order to facilitate the verification of the feasibility of URTS, the following assumptions are given
+In this study, a system architecture of URTS for R\&S usage is given.
+This gives a holistic view of the operational framework for UTRS.
+Next, we focus on part of the system architecture of UTRS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot.
+The procedure of reference trajectory design method is given.
+An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agent in URTS.
+After analysis, this control problem is transformed into a LMI-constrained optimization problem.
+Through two-step design procedure, the problem is effectively solved by MATLAB LMI Toolbox.
+Finally, the effectiveness of the designed controller and observer is also verified by the simulation results.
+In the future, we will...
 

### 2022-08-25 src/Hinf_Theorem/K_L/solveLMI13.m

@@ -1,0 +1,122 @@
+function [K, L] = solveLMI13(A, B, C, E, Q1, Q2, R, rho)
+%solution of "Qb + Pb*Ab + Ab'*Pb + Kb'RKb + Pb*Pb/rho^2 < 0, Pb > 0" (Method in my paper)
+%
+% This function is used to solve a control problem defined below:
+% (1) system
+%       dxb/dt = Ab*xb + vb
+%       where xb = [x; x-xh], Ab = [A+B*K -B*K; 0 A+L*C]
+% (4) control law
+%       u = Kb*xb, Kb = [K -K];
+% (5) H infinity performance
+%       xb'Qbxb + u'Ru/ vb'*vb < rho^2
+%       Qb = [Q1 0; 0 Q2]
+% (6) Lyapunov function
+%       V(x) = xb'Pb*xb
+%       where Pb = [P1 0; 0 P2]
+%
+% This method is currently not feasible. The term Kb'RKb cause the matrix inequality coupling and need two-step method.
+% The version without Kb'RKb, solveLMI10(), is feasible.
+
+%% solve
+[DIM_X, DIM_U]  = size(B);
+[DIM_Y, ~]      = size(C);
+O               = zeros(DIM_X);
+I               = eye(DIM_X);
+options = sdpsettings('solver', 'mosek');
+options = sdpsettings(options,'verbose', 0);
+
+%% step 1
+eqn = [];
+W1 = sdpvar(DIM_X, DIM_X);
+Y1 = sdpvar(DIM_U, DIM_X);
+
+eqn = [eqn, W1 >= 0];
+
+M11 = addSym(A*W1 + B*Y1) + rho^(-2)*I; % E for LMI solvable
+
+M12 = W1*sqrt(Q1);
+M22 = -I;
+
+M13 = Y1';
+M23 = zeros(DIM_X, DIM_U);
+M33 = -eye(DIM_U)/R;
+
+% LMI = [
+%     M11  M12  M13  M14  M15
+%     M12' M22  M23  M24  M25
+%     M13' M23' M33  M34  M35
+%     M14' M24' M34' M44  M45
+%     M15' M25' M35' M45' M55
+% ];
+
+LMI = [
+    M11  M12  M13
+    M12' M22  M23
+    M13' M23' M33
+];
+
+eqn = [eqn, LMI <= 0];  
[…]

### 2022-08-25 src/System/UAV/@UAV_AGENTmodel/Save.m

@@ -1,0 +1,24 @@
+function Save(uav, whichVar)
+%Save a property into classname.mat
+% whichVar  : which property be saved
+
+switch whichVar
+    case 'tr'
+        tr = uav.tr;
+    case 'qr'
+        qr = uav.qr;
+    case 'K'
+        K = uav.K;
+    case 'KL'
+        KL = uav.KL;
+    otherwise
+        disp(['No such property in uav'])
+end
+
+if isfile([uav.PATH '.mat'])
+    save(uav.PATH, whichVar, '-append');
+else
+    save(uav.PATH, whichVar);
+end
+    
+end

### 2022-08-25 src/URTS main script/UAV/function/AugmentSystem.m

@@ -1,0 +1,21 @@
+function [Ab, Bb, Cb] = AugmentSystem(A, B, C, Aa, Ba, Ca, As, Bs, Cs)
+%construct augment system, Fa + Fs
+% Ab = [A Ba*Ca 0; 0 Aa 0; 0 0 As]
+% Bb = [B; 0; 0]
+% Cb = [C 0 Bs*Cs]
+
+[DIM_X, DIM_U] = size(B);
+[DIM_Y, ~] = size(C);
+DIM_Xa = size(Aa, 1);
+DIM_Xs = size(As, 1);
+
+Ab3_2 = zeros(DIM_Xs, DIM_Xa);
+Ab = [
+    A                        Ba*Ca  zeros(DIM_X, DIM_Xs)
+    zeros(DIM_Xa, DIM_X)     Aa     zeros(DIM_Xa, DIM_Xs)
+    zeros(DIM_Xs, DIM_X)     Ab3_2  As
+];
+Bb = [B; zeros(DIM_Xa, DIM_U); zeros(DIM_Xs, DIM_U)];
+Cb = [C zeros(DIM_Y, DIM_Xa) Bs*Cs];
+end
+

### 2022-08-25 src/URTS main script/UAV/function/Plot.m

@@ -1,0 +1,20 @@
+function Plot(t, x, xh, j, DIM, TITLE)
+figure
+% obtain a suitable size
+div = divisors(DIM);
+i = ceil((length(div))/2);
+Layout = tiledlayout(DIM/div(i), div(i));
+for i = 1 : DIM
+    nexttile
+    hold on
+    index = j + i;
+    plot(t, x(index, :), 'Displayname', 'state', 'LineWidth', 3)
+    plot(t, xh(index, :), 'DisplayName', 'estimated', 'LineWidth', 3)
+%     plot(t, x(index, :)-xh(index, :), 'Displayname', 'error', 'LineWidth', 3)
+    grid on
+    legend
+    % ylim([-1 1])
+    title(['v' TITLE '_' num2str(i)])
+end
+title(Layout, ['F' TITLE])
+end

### 2022-08-25 test/Robot/oneRobot/oneRobot_FaFs.m

@@ -5,12 +5,12 @@ addpath(genpath('../../../src'))
 addpath(genpath('function'))
 
 rb = Robot();
+dt = rb.dt;
 
-dt = .001;
 %% sys
 DIM_F = rb.DIM_F; % Dimension of e
 DIM_SOLVE_K = 1; 
-A1 = [0 1 0; 0 0 1; 0 0 0]; B1 = [0; 0; 1]; C1 = eye(3); % Intergral{e}, e, de
+A1 = [0 1 0; 0 0 1; 0 0 0]; B1 = [0; 0; 1]; C1 = [1 0 0; 0 1 0; 0 0 1]; % Intergral{e}, e, de
 A = kron(A1, eye(DIM_F));
 B = kron(B1, eye(DIM_F));
 C = kron(C1, eye(DIM_F));
@@ -30,7 +30,7 @@ WINDOW = 3; dt_ = 1*dt; METHOD = '2';
 sys_a1 = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
 sys_a = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
 sys_a1.B = sys1.B;
-sys_a.B = sys.B;
+sys_a.B = kron(sys_a1.B, eye(DIM_F));
 
 Q1 = 0*(.1.^(0 : WINDOW-1)); % Can't stablilze unknown signal
 sys_a1.Q1 = diag(Q1);
@@ -41,7 +41,7 @@ sys_a1.Q2 = diag(Q2);
 WINDOW = 3; dt_ = 1*dt; METHOD = '1-3';
 sys_s1 = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
 sys_s = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
-sys_s1.B = [0; .1; 1];
+sys_s1.B = [0; .1; .2];
 sys_s.B = kron(sys_s1.B, eye(DIM_F));
 
 Q1 = 0*(.1.^(0 : WINDOW-1)); % Can't stablilze unknown signal
@@ -58,7 +58,7 @@ sys_aug1 = LinearModel(A, B, C);
 sys_aug1.Q1 = 10^(-2)*blkdiag(sys1.Q1, sys_a1.Q1, sys_s1.Q1); % weight of integral{e}, e, de, f1, f2
[…]

### 2022-08-29 test/Robot/oneRobot/@Robot/GRF.m
add GRF

@@ -1,0 +1,35 @@
+function rb = GRF(rb)
+% left foot
+% x = [1/6 3/6 5/6 1 7/6 8/6 9/6 10/6 11/6 2];
+% y = [1 .9 1.2 .09 .01 0 0 0 .01 .09];
+x = linspace(0, 1, 12);
+y = [1 .95 .9 .95 1.1 .09 .01 0 0 0 .01 .09];
+r = [
+    x
+    y*10
+];
+r0 = cat(2, [0; 0], r);
+num_of_step_period = ceil((rb.tr.LEN-1)/(rb.INTERP_DENSITY*2)); % How many step
+for i = 1 : num_of_step_period - 1
+    r(1, :) = r(1, :) + i;
+    r0 = cat(2, r0, r);
+end
+
+% plot(r0(1,:), r0(2,:))
+r2 = fit_linear_spline(r0, [2 3]);
+
+t = linspace(0, 1, length(r2));
+fx = fit(t', r2(1,:)', 'SmoothingSpline');
+fy = fit(t', r2(2,:)', 'SmoothingSpline');
+t3 = linspace(0, 1, rb.tr.LEN);
+r3 = [
+    feval(fx, t3)';
+    feval(fy, t3)';
+];
+r3 = r3(:, 1:rb.tr.LEN); % cut to fit the simulation trajectories
+figure
+plot(r3(1,:), r3(2,:))
+axis equal
+rb.tr.GRF{1} = r3(2,:); % left foot
+
+end

### 2022-08-29 test/Robot/oneRobot/@Robot/Robot.m

@@ -28,17 +28,16 @@ classdef Robot
             10^(-5)*[22 99 91 0 -.1 0]
         ] % inertia of CoM1~12
 
-        dt = .001
         DIM_F = 12 % dimension of state (pos)
         INTERP_DENSITY = 2500 % interp density of zmp
         PATH = ['data/' mfilename] %  path of saved data
 
         %% flow control of code
-        EXE_LMI = 0
-        EXE_Z2C = 0 % ZMP to CoM converter
-        EXE_IK = 0 % inverse dynamic
-        EXE_TRAJ = 1 % trajectory
-        EXE_PLOT = 1 % plot results
+        EXE_LMI     = 0
+        EXE_Z2C     = 0 % ZMP to CoM converter
+        EXE_IK      = 0 % inverse dynamic
+        EXE_TRAJ    = 1 % trajectory
+        EXE_PLOT    = 1 % plot results
     end
     properties
         %% rigidbodytree
@@ -109,6 +108,7 @@ classdef Robot
             rb.height_CoM0_stand = sum(rb.L(2:6));
             rb.height_CoM0_walk  = rb.height_CoM0_stand - rb.OFFSER_COM_STAND_WALK;
             rb = get_rbtree(rb); % Construct robot rbtree
+            rb = GRF(rb); % Ground Reaction Force
         end
         
         function y = M(rb, x)
@@ -139,7 +139,8 @@ classdef Robot
 
         rb = get_rbtree(rb) % rigidBodyTree setting
         y = m(rb, i) % Just a mapping between m and MASS
-        rb = Ref2Config(rb) % Task space ref to joint space configuration ref
+        rb = Ref2Config(rb, r) % Task space ref to joint space configuration ref
+        y = GRF(rb)
         rb = trajectory(rb)
         Save(rb, filename, whichVar) % Save property
         rb = Load(rb, filename) % Load property

### 2022-08-29 test/Robot/oneRobot/oneRobot_FaFs.m

@@ -5,9 +5,10 @@ addpath(genpath('../../../src'))
 addpath(genpath('function'))
 
 rb = Robot();
-dt = rb.dt;
+rb.tr.dt    = .001; % Time step
+rb.tr.T     = 2; % Final time
 
-%% sys
+%% system
 DIM_F = rb.DIM_F; % Dimension of e
 DIM_SOLVE_K = 1; 
 A1 = [0 1 0; 0 0 1; 0 0 0]; B1 = [0; 0; 1]; C1 = [1 0 0; 0 1 0; 0 0 1]; % Intergral{e}, e, de
@@ -20,46 +21,46 @@ B = kron(B1, eye(DIM_SOLVE_K));
 C = kron(C1, eye(DIM_SOLVE_K));
 sys1 = LinearModel(A, B, C);
 % Error weighting. Tracking:1, Estimation:2
-Q1 = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
+Q1      = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
 sys1.Q1 = diag(Q1);
-Q2 = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
+Q2      = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
 sys1.Q2 = diag(Q2);
 
 %% smooth model (acuator)
-WINDOW = 3; dt_ = 1*dt; METHOD = '2';
-sys_a1 = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
-sys_a = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
-sys_a1.B = sys1.B;
-sys_a.B = kron(sys_a1.B, eye(DIM_F));
+WINDOW = 3; dt_ = 1*rb.tr.dt; METHOD = '2';
+sys_a1      = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
+sys_a       = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
+sys_a1.B    = sys1.B;
+sys_a.B     = kron(sys_a1.B, eye(DIM_F));
 
-Q1 = zeros(1,WINDOW); % Can't stablilze unknown signal
-sys_a1.Q1 = diag(Q1);
-Q2 = 10^(1)*(.1.^(0 : WINDOW-1));
-sys_a1.Q2 = diag(Q2);
[…]

### 2022-08-31 paper/paper.tex
add GRF
add Agent class to be the superclass of class UAV_AGENTmodel.m and Robot.m. oneUAV traj stable. Change the structure of setting sys, sys_a, sys_s.

@@
 
-The external disturbances during tracking control must also be considered. The agent ...
+In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied.
+According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}.
+The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it.
+In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller.
+Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
 % the control problem of robot
-
-Fault-tolerant contrl (FTC) ...
 
@@
     \item system parameters: Appendix E in \cite{ourrobot}
-    \item designed parameters:
+    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
 \end{enumerate}
 
+For convenience, the distubance $d_1(t)$ in actuator fault is set as $d_1(t)=0.2\cos(t)$ and the sensor fault is set as $f_2(t)=\sin(t)$.
 The tracking error and fault signal estimation of UAV $\alpha_{1,1}$ are shown in Fig.
-\ref{fig:UAV, error, estimation}, where the external disturbances is set to...
-.
+\ref{fig:UAV, error, estimation}.
 The tracking error and error signal estimation of the robot $\alpha_{1,2}$ are shown in Fig.
-\ref{fig:robot, error, estimation}, where the external disturbances is set to...
-.
+\ref{fig:robot, error, estimation}.
 \begin{figure}[htbp]

### 2022-08-31 src/System/@AGENT/Save.m

@@ -1,0 +1,22 @@
+function is_saved = Save(ag, whichVar)
+%Save a property into classname.mat
+% whichVar  : which property be saved
+is_saved = true;
+switch whichVar
+    case 'tr'
+        tr = ag.tr;
+    case 'K'
+        K = ag.K;
+    case 'KL'
+        KL = ag.KL;
+    otherwise
+        is_saved = false;
+end
+
+if isfile([ag.PATH '.mat'])
+    save(ag.PATH, whichVar, '-append');
+else
+    save(ag.PATH, whichVar);
+end
+    
+end

### 2022-08-31 src/System/UAV/@UAV_AGENTmodel/UAV_AGENTmodel.m

@@ -1,4 +1,4 @@
-classdef UAV_AGENTmodel  
+classdef UAV_AGENTmodel < Agent 
 % agent model
   
     properties (Constant)
@@ -10,38 +10,23 @@ classdef UAV_AGENTmodel
         Kph = 0.012, Kth = 0.012, Kps = 0.012
         dt = .001
 
-        DIM_F = 6 % dimension of state (pos)
-        PATH = ['data/' mfilename] % path of saved data
-
         %% flow control of code
-        EXE_LMI = 0
-        EXE_TRAJ = 0 % trajectory
-        EXE_PLOT = 1 % plot results
     end
 
     properties
         Dt % torque drag coefficient matrix
         Df % force drag coefficient matrix
 
-        %% Control design
-        sys
-        sys_a
-        sys_s
-        sys_aug
-
-        K  % Control gain matrix
-        KL  % Observer gain matrix
-        DIM
-
-        %% trajectories
         qr
-        tr
     end
   
     methods
         function uav = UAV_AGENTmodel()
-            %% Load old data
+            uav@Agent();
+            uav.PATH  = ['data/' mfilename]; % path of saved data
             uav = uav.Load(); % load old data
+            uav.DIM_F = 6;
+            
             uav.Dt = diag([uav.Kph, uav.Kth, uav.Kps]);
             uav.Df = diag([uav.Kx, uav.Ky, uav.Kz]);                 
         end
@@ -88,8 +73,6 @@ classdef UAV_AGENTmodel
             phi = atan(-c(2)*cos(theta)/c(3));
         end
 
-        uav = trajectory(uav) % get trajectory (x, u, ...)
-
         function y = f_aug(uav, t, xb)
             DIM_X3 = uav.sys_aug.DIM_X;
             x = xb(1 : DIM_X3);
@@ -100,9 +83,6 @@ classdef UAV_AGENTmodel
                 uav.sys_aug.A*xh + uav.sys_aug.B*u - uav.KL*uav.sys_aug.C*(x-xh)
             ];
         end
-
-        Save(uav, filename, whichVar) % save property
-        uav = load(uav, filename)
     end
 
     methods (Access = private)

### 2022-08-31 src/System/UAV/@UAV_AGENTmodel/trajectory.m

@@ -50,6 +50,8 @@ end
 %% trajectory
 disp(['Calculating trajectory ..., t = 0 ~ ' num2str(dt*(LEN-1))])
 xb = [x; xh];
+uav.tr.r = cell(1,3);
+uav.tr.u = zeros(uav.sys.DIM_U, LEN);
 for i = startTime : LEN - 1
     %% debug message
     if mod(i, 1/dt) == 0
@@ -114,8 +116,8 @@ for i = startTime : LEN - 1
 
     % Show norm of error terms
     if mod(i, 100) == 0 
-        disp(['norm of M-Mh: ' num2str(norm(M-Mh))])
-        disp(['norm of H-Hh: ' num2str(norm(H-Hh))])
+        % disp(['norm of M-Mh: ' num2str(norm(M-Mh))])
+        % disp(['norm of H-Hh: ' num2str(norm(H-Hh))])
     end
     uav.tr.f1(:, i) = f;
     

### 2022-08-31 test/Inheritance/test1.m

@@ -3,5 +3,4 @@ addpath(genpath('../src'))
 % Combvec([2 3])
 c1 = Class1(1);
 c2 = Class2(1);
-c1
-c2
+c2.Print()

### 2022-08-31 test/Robot/oneRobot/oneRobot_FaFs.m

@@ -1,71 +1,88 @@
 %main script
-% one Robot, CTM, reference model tracking control, Fa + Fs, K solved by DIM = 1
+% one Robot, observer-based tracking control, feedfoward linearization, FTC (smoothed model, actuator and sensor fault), K solved by DIM = 1 method, path planning
 clc; clear; close all; tic;
 addpath(genpath('../../../src'))
 addpath(genpath('function'))
 
 rb = Robot();
+% flow control of code
+rb.EXE_LMI     = 1;
+rb.EXE_Z2C     = 0; % ZMP to CoM converter
+rb.EXE_IK      = 0; % inverse dynamic
+rb.EXE_TRAJ    = 1; % trajectory
+rb.EXE_PLOT    = 1; % plot results
+
+% time
 rb.tr.dt    = .001; % Time step
 rb.tr.T     = 2; % Final time
 
+% global variable
+DIM_F       = rb.DIM_F; % Dimension of e
+DIM_SOLVE_K = 1;
+I           = eye(DIM_F);
+
 %% system
-DIM_F = rb.DIM_F; % Dimension of e
-DIM_SOLVE_K = 1; 
-A1 = [0 1 0; 0 0 1; 0 0 0]; B1 = [0; 0; 1]; C1 = [1 0 0; 0 1 0; 0 0 1]; % Intergral{e}, e, de
-A = kron(A1, eye(DIM_F));
-B = kron(B1, eye(DIM_F));
-C = kron(C1, eye(DIM_F));
-sys = LinearModel(A, B, C);
-A = kron(A1, eye(DIM_SOLVE_K));
-B = kron(B1, eye(DIM_SOLVE_K));
-C = kron(C1, eye(DIM_SOLVE_K));
-sys1 = LinearModel(A, B, C);
 % Error weighting. Tracking:1, Estimation:2
-Q1      = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
-sys1.Q1 = diag(Q1);
-Q2      = 10^(2)*[1 100 10]; % corresponding to [Intergral{e}, e, de]
-sys1.Q2 = diag(Q2);
+A0          = [0 1 0; 0 0 1; 0 0 0];
+B0          = [0; 0; 1];
[…]

### 2022-09-01 paper/paper.tex
UAV and robor ok, fa=sin(), fs=square wavw, problem of scale of system solved: UAV ~= 10*robot. add smoothModel.set_real_signal(), simplified code.

@@
 % where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
-Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(r(t))\ddot{x}(t)$ from the left and right sides, we have:
+Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
 \begin{equation} \label{eq:agent1}
     \begin{split}
-        & (M(x(t))-M(r(t)))\ddot{x}(t) + H(x(t),\dot{x}(t)) \\
-        & =(M(r(t))(\ddot{r}(t)-\ddot{x}(t)) + M(r(t))u_{fb}(t) \\
+        & M(x(t))(\ddot{x}(t)-\ddot{r}(t)) + H(x(t),\dot{x}(t)) \\
+        & =(M(r(t))-M(x(t)))\ddot{r}(t) + M(r(t))u_{fb}(t) \\
         & + H(r(t),\dot{r}(t)) + d_1(t)
@@
 \end{equation}
-By Multipling $M(r(t))^{-1}$ from the left and right sides and with some arrangments, we have:
+By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have:
 \begin{equation} \label{eq:error, state eq}
@@
 \end{equation}
-where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
+where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
 % \textit{

### 2022-09-01 src/System/UAV/@UAV_AGENTmodel/trajectory.m

@@ -1,7 +1,6 @@
 function uav = trajectory(uav)
 %calculate trajectory
 
-sys         = uav.sys;
 sys_a       = uav.sys_a;
 sys_s       = uav.sys_s;
 dt          = uav.tr.dt;
@@ -11,6 +10,28 @@ DIM_F       = uav.DIM_F;
 DIM_X       = uav.sys.DIM_X;
 DIM_X3      = uav.sys_aug.DIM_X;
 startTime   = 5; % For calculate ddr(t), start at 3-rd step (k = 3)
+
+%% set disturbance
+%-1 actuator fault
+d1 = repmat(100*sin(3*t), sys_a.DIM, 1);
+sys_a.fault = zeros(sys_a.DIM, LEN);
+
+%-2 sensor fault
+% square wave
+% uav.tr.f2    = 0.1*ones(sys_s.DIM, uav.tr.LEN);
+% b = [0.1 -0.05 0.05]; n = length(b)+1;
+% a = round(linspace(1,uav.tr.LEN,n));
+% for i = 1 : n-1
+%     uav.tr.f2(:, a(i):a(i+1)) = b(i);
+% end
+
+% smoothed square wave
+t_ = linspace(0, uav.tr.T, 100);
+x_ = 1*square(t_, 60);
+fx = fit(t_', x_', 'SmoothingSpline');
+x3 = feval(fx, uav.tr.t)';
+% plot(uav.tr.t, x3)
+sys_s.fault = repmat(x3, sys_s.DIM, 1);
 
 % r = uav.qr;
 % dr = diff(r, 1, 2)/dt;
@@ -76,7 +97,7 @@ for i = startTime : LEN - 1
     Xh      = xh(DIM_F + (1:DIM_F));
     dXh     = xh(2*DIM_F + (1:DIM_F));
 
-     %% reference
+    %% reference
     [phi, theta, F] = uav.pos_controller(xh, r4(1:3, i-2:i), dt);
     r = [
         r4(1, i)
@@ -110,42 +131,28 @@ for i = startTime : LEN - 1
     % Hh = uav.H(X+r, dXh+dr);
     % Hh = 0;
     
-    f = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + H-Hh + uav.tr.f1(:, i));
-    % f = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + uav.tr.f1(:, i));
-    % f = -eye(DIM_F)/M*(uav.tr.f1(:, i));
[…]

### 2022-09-01 src/URTS main script/UAV/oneUAV_FaFs.m

@@ -44,7 +44,7 @@ METHOD  = '2';
 sys_a1      = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
 sys_a1.B    = sys1.B;
 sys_a1.Q1   = diag(zeros(1,WINDOW)); % Can't stablilze unknown signal
-sys_a1.Q2   = 10^(1)*diag((.1.^(0 : WINDOW-1)));
+sys_a1.Q2   = 10^(2)*diag((.1.^(0 : WINDOW-1)));
 
 % for plot trajectories
 sys_a       = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
@@ -73,16 +73,18 @@ sys_aug1.Q1     = 10^(0)/2*blkdiag(sys1.Q1, sys_a1.Q1, sys_s1.Q1); % weight of i
 sys_aug1.Q2     = 10^(-1)/2*blkdiag(sys1.Q2, sys_a1.Q2, sys_s1.Q2); % weight of integral{e}, e, de, f1, f2
 sys_aug1.E      = 1*eye(sys_aug1.DIM_X);
 sys_aug1.R      = 2*10^(-3)*eye(sys_aug1.DIM_U);
-sys_aug1.rho    = 25;
+sys_aug1.rho    = 30;
 
 % for plot trajectories
 [A, B, C]   = AugmentSystem(sys.A, sys.B, sys.C, sys_a.A, sys_a.B, sys_a.C, sys_s.A, sys_s.B, sys_s.C);
 sys_aug     = LinearModel(A, B, C);
 
 %% some mapping
-uav.sys      = sys;
-uav.sys_a    = sys_a;
-uav.sys_s    = sys_s;
+sys_a.begin = sys.DIM_X;
+sys_s.begin = sys.DIM_X + sys_a.DIM_X;
+uav.sys     = sys;
+uav.sys_a   = sys_a;
+uav.sys_s   = sys_s;
 uav.sys_aug = sys_aug;
 
 %% solve LMI
@@ -129,27 +131,6 @@ if uav.EXE_TRAJ
     uav.tr.x0    = [x0_pos zeros(1, sys_a.DIM_X) zeros(1, sys_s.DIM_X)]';
     uav.tr.xh0   = zeros(uav.sys_aug.DIM_X, 1);
 
-    %% set distuuavance
-    %-1 actuator fault
-    uav.tr.f1    = repmat(.2*sin(1*uav.tr.t), sys_a.DIM, 1);
-
-    %-2 sensor fault
[…]

### 2022-09-01 test/Robot/oneRobot/oneRobot_FaFs.m

@@ -14,7 +14,7 @@ rb.EXE_PLOT    = 1; % plot results
 
 % time
 rb.tr.dt    = .001; % Time step
-rb.tr.T     = 2; % Final time
+rb.tr.T     = 9; % Final time
 
 % global variable
 DIM_F       = rb.DIM_F; % Dimension of e
@@ -44,14 +44,14 @@ METHOD  = '2';
 sys_a1      = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
 sys_a1.B    = sys1.B;
 sys_a1.Q1   = diag(zeros(1,WINDOW)); % Can't stablilze unknown signal
-sys_a1.Q2   = 10^(1)*diag((.1.^(0 : WINDOW-1)));
+sys_a1.Q2   = 10^(2)*diag((.1.^(0 : WINDOW-1)));
 
 % for plot trajectories
 sys_a       = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
 sys_a.B     = kron(sys_a1.B, I);
 
 %% smooth model (sensor)
-WINDOW  = 5;
+WINDOW  = 4;
 dt_     = 1000*rb.tr.dt; % multiply 1000 is better by testing
 METHOD = '2';
 
@@ -73,13 +73,15 @@ sys_aug1.Q1     = 10^(0)/2*blkdiag(sys1.Q1, sys_a1.Q1, sys_s1.Q1); % weight of i
 sys_aug1.Q2     = 10^(-1)/2*blkdiag(sys1.Q2, sys_a1.Q2, sys_s1.Q2); % weight of integral{e}, e, de, f1, f2
 sys_aug1.E      = 1*eye(sys_aug1.DIM_X);
 sys_aug1.R      = 2*10^(-3)*eye(sys_aug1.DIM_U);
-sys_aug1.rho    = 25;
+sys_aug1.rho    = 30;
 
 % for plot trajectories
 [A, B, C]   = AugmentSystem(sys.A, sys.B, sys.C, sys_a.A, sys_a.B, sys_a.C, sys_s.A, sys_s.B, sys_s.C);
 sys_aug     = LinearModel(A, B, C);
 
 %% some mapping
+sys_a.begin = sys.DIM_X;
+sys_s.begin = sys.DIM_X + sys_a.DIM_X;
 rb.sys      = sys;
 rb.sys_a    = sys_a;
[…]

### 2022-09-12 paper/paper.tex
uav path planning trajectory ok

@@
 Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
+Based on the foregoing, a robust $H_\infty$ decentralized fault-tolerant tracking control strategy is proposed to deal with the control problem in URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
 % the control problem of robot
-
-Based on the foregoing, a robust $H_\infty$ decentralized fault-tolerant tracking control strategy is proposed to deal with the control problem in URTS.
-
-% Based on the foregoing, an UAV-robot team system (URTS) is discussed in this paper.
 
@@
 \textbf{Notation 1:} 
-% $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
+$diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
 $A^T$: transpose of A.
@@
     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-kh)
-\end{bmatrix}^T\in\mathbb{R}^{(k+1)n}$, $A_i\in\mathbb{R}^{{(k+1)n}\times{(k+1)n}}$, $v_i(t)$ is the model error, and $C_i=\begin{bmatrix}
+\end{bmatrix}^T\in\mathbb{R}^{(k+1)n}$, $A_i\in\mathbb{R}^{{(k+1)n}\times{(k+1)n}}$, $v_i(t)$ is the model error, $C_i=\begin{bmatrix}
         1 & 0 & \dots & 0
-    \end{bmatrix}\otimes I_{n_i}$ with $n_1=n$ and $n_2 = o$. Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get:
+    \end{bmatrix}\otimes I_{n_i}$, and $k$ is the smoothing signal model window size with $n_1=n$ and $n_2 = o$. Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get:
 \begin{equation} \label{eq:e_bar}
@@
     \end{split}
-\end{equation}.
+\end{equation}
 \begin{remark}
@@
 Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness.
-More clearly, the number of elements in matrix $K$, the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)n$.
+More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)n$.
 For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)n$.
@@
 
-Through the previous steps, the reference trajectory $r(t)$ of flying and walking has been designed. The remaining parameter setting is given as follow.
+Through the previous steps, the reference trajectory $r(t)$ of flying and walking has been designed. The remaining parameters are set as follow.
+
+\textit{agent:}\begin{enumerate}
+    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$;
+    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$.
+Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
+\end{enumerate}
 
@@
     K_\phi = K_\theta = K_\psi = 0.012$
-    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
+    % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
 \end{enumerate}
@@
 
-For convenience, the distubance $d_1(t)$ in actuator fault is set as $d_1(t)=0.2\cos(t)$ and the sensor fault is set as $f_2(t)=\sin(t)$.
-The tracking error and fault signal estimation of UAV $\alpha_{1,1}$ are shown in Fig.
-\ref{fig:UAV, error, estimation}.
-The tracking error and error signal estimation of the robot $\alpha_{1,2}$ are shown in Fig.
-\ref{fig:robot, error, estimation}.
+The simulation results of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.
+
+\textit{UAV:}
+The reference, state and estimated state are shown in Fig.
+\ref{fig:UAV, state}.
+The estimation of actuator fault $f_1(t)$ is shown in Fig.
+\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=10\sin(3t)$.
+The estimation of sensor fault $f_2(t)$ is shown in Fig.
+\ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure.
+The control effort is shown in Fig.
+\ref{fig:UAV, control}.
 \begin{figure}[htbp]
@@
     \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
-    \label{fig:UAV, error, estimation}
+    \label{fig:UAV, state}
 \end{figure}
@@
     \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:UAV, fa}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:UAV, fs}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:UAV, control}
+\end{figure}
+
+\textit{robot:}
+The reference, state and estimated state are shown in Fig.
+\ref{fig:robot, state}.
+The estimation of actuator fault $f_1(t)$ is shown in Fig.
+\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$.
+The estimation of sensor fault $f_2(t)$ is shown in Fig.
+\ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure.
+The control effort is shown in Fig.
+\ref{fig:robot, control}
+\begin{figure}[htbp]
+    \centering
     \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
-    \label{fig:robot, error, estimation}
+    \label{fig:robot, state}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:robot, fa}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:robot, fs}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \label{fig:robot, control}
 \end{figure}
@@
 Next, we focus on part of the system architecture of UTRS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot.
-The procedure of reference trajectory design method is given.
-An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agent in URTS.
+The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail.
+An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agent in URTS under the external disturbances.
 After analysis, this control problem is transformed into a LMI-constrained optimization problem.

### 2022-09-12 src/Hinf_Theorem/K_L/solveLMI13.m

@@ -1,5 +1,5 @@
 function [K, L] = solveLMI13(A, B, C, E, Q1, Q2, R, rho)
-%solution of "Qb + Pb*Ab + Ab'*Pb + Kb'RKb + Pb*Pb/rho^2 < 0, Pb > 0" (Method in my paper)
+%solution of "Qb + Pb*Ab + Ab'*Pb + Kb'RKb + Pb*Pb/rho^2 < 0, Pb > 0"
 %
 % This function is used to solve a control problem defined below:
 % (1) system
@@ -13,10 +13,7 @@ function [K, L] = solveLMI13(A, B, C, E, Q1, Q2, R, rho)
 % (6) Lyapunov function
 %       V(x) = xb'Pb*xb
 %       where Pb = [P1 0; 0 P2]
-%
-% This method is currently not feasible. The term Kb'RKb cause the matrix inequality coupling and need two-step method.
-% The version without Kb'RKb, solveLMI10(), is feasible.
-
+% Infeasible, Kb'RKb couple, need two-step method
 %% solve
 [DIM_X, DIM_U]  = size(B);
 [DIM_Y, ~]      = size(C);
@@ -24,39 +21,52 @@ O               = zeros(DIM_X);
 I               = eye(DIM_X);
 options = sdpsettings('solver', 'mosek');
 options = sdpsettings(options,'verbose', 0);
-
-%% step 1
 eqn = [];
+
 W1 = sdpvar(DIM_X, DIM_X);
+P2 = sdpvar(DIM_X, DIM_X);
 Y1 = sdpvar(DIM_U, DIM_X);
+Y2 = sdpvar(DIM_X, DIM_Y);
+Z  = sdpvar(DIM_U, DIM_U);
 
-eqn = [eqn, W1 >= 0];
+eqn = [eqn, W1 >= 0, P2 >= 0];
 
-M11 = addSym(A*W1 + B*Y1) + rho^(-2)*I; % E for LMI solvable
+M11 = addSym(A*W1 + B*Y1) + rho^(-2)*E*E';
 
-M12 = W1*sqrt(Q1);
-M22 = -I;
+M12 = -B*Y1;
+M22 = addSym(P2*A + Y2*C) + Q2 + 2*Z;
 
-M13 = Y1';
-M23 = zeros(DIM_X, DIM_U);
[…]

### 2022-09-12 src/System/@AGENT/AGENT.m

@@ -35,8 +35,10 @@ classdef Agent
     methods
         function ag = AGENT()
         end
+        
         y = M(ag, x) % inertial matrix
         y = H(ag, x, dx) % non-inertial matrix
+        ag = get_K_L(ag, sys_aug1) % solve LMI to obtain control gain K and observer gain L
         ag = trajectory(ag) % get trajectory (x, u, ...)
         is_saved = Save(ag, whichVar) % save properties
         ag = Load(ag) % load properties

### 2022-09-12 test/Robot/oneRobot/@PathPlanning/PathPlanning.m

@@ -40,13 +40,12 @@ classdef PathPlanning
             goal = [map.XWorldLimits(2) map.YWorldLimits(2) 0];
             rng(1); % repeatable result
             [pthObj, solnInfo] = planner.plan(start,goal);
-            r3 = pp.Post_processing(pthObj.States(:, 1:2)'); % Interpolate path, make it more smooth and increase density
 
+            pp.r = fit_linear_spline(pthObj.States(:, 1:2)', pp.INTERP_DENSITY); % Interpolate path, make it more smooth and increase density
+            pp.tree = solnInfo.TreeData;
+            pp.map = map;
             pp.start = start;
             pp.goal = goal;
-            pp.r = r3;
-            pp.map = map;
-            pp.tree = solnInfo.TreeData;
         end 
 
         function Plot(pp)

### 2022-09-15 paper/paper.tex
paper, sim result description.

@@
 where $\bar{e}(t) = \begin{bmatrix}
-    \pmb{e}(t) \\ F_1 \\ F_2
+    \pmb{e}(t) \\ F_1(t) \\ F_2(t)
 \end{bmatrix}$, $\bar{A}=\begin{bmatrix}
@@
 
-\textit{agent:}\begin{enumerate}
-    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$;
+\textit{agents:}\begin{enumerate}
+    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
     \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$.
@@
 
-\textit{UAV:}\begin{enumerate}
+\textit{UAVs:}\begin{enumerate}
     \item system parameters: $g = 9.81, m = 2,
@@
     K_x = K_y = K_z = 0.01,
-    K_\phi = K_\theta = K_\psi = 0.012$
+    K_\phi = K_\theta = K_\psi = 0.012$. Initial values $\bar{x}_0=$.
     % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
@@
 
-\textit{robot:} \begin{enumerate}
-    \item system parameters: Appendix E in \cite{ourrobot}
-    \item designed parameters: $Q_1=,Q_2=,R=,rho=$ % correspond to x - xr, R=, \rho=$
+\textit{robots:} \begin{enumerate}
+    \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
+    \item designed parameters: $Q_1=,Q_2=,R=,rho=20$.
 \end{enumerate}
 
-The simulation results of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.
+The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.
 
 \textit{UAV:}
-The reference, state and estimated state are shown in Fig.
+The trajectories of reference, state and estimated state are shown in Fig.
 \ref{fig:UAV, state}.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, control}
@@
 \textit{robot:}
-The reference, state and estimated state are shown in Fig.
+The trajectories of reference, state and estimated state are shown in Fig.
 \ref{fig:robot, state}.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of robot walking.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
     \label{fig:robot, state}
@@
 
-description of fig...
+In Fig.
+\ref{fig:UAV, state} and Fig.
+\ref{fig:robot, state}, the tracking and estimation errors have reached a steady state at x seconds.
+The transient responses that occur later are caused from fault signals, especially the sensor fault.
+This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the error over time $\dot{e}$ not only from $\bar{A}$ but also from $L\bar{C}$.
+In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbance and feedforward errors, can be effectively estimated.
+In Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds.
+In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
 
@@
 The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail.
-An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agent in URTS under the external disturbances.
-After analysis, this control problem is transformed into a LMI-constrained optimization problem.
+An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agents in URTS under the external disturbances.
+The control problem of UAV and robot are solved together via a transformation from a general agent model.
+After analysis, the control problem is further transformed into a LMI-constrained optimization problem.
 Through two-step design procedure, the problem is effectively solved by MATLAB LMI Toolbox.
+The simulation results give an example of the proposed URTS architecture to more concretely illustrate its operational flow.
 Finally, the effectiveness of the designed controller and observer is also verified by the simulation results.

### 2022-09-22 paper/paper.tex
move folder oneRobot to src/UTRSmainScript/Robot, add content in simulation in paper.tex, adjust the format of fig in rb.EXE_PLOT in oneRobot_FaFs.m

@@
 \usepackage{amsmath,amssymb,amsfonts}
+\usepackage{breqn}
 \usepackage{mathtools}
@@
 \usepackage[inline]{enumitem}
+
 % \usepackage{amsmath}
@@
 % \setmainfont{TeX Gyre Termes}
+
 \setcounter{MaxMatrixCols}{30}
@@
 \subsection{Task Allocation}
-In the URTS, it can be expected that each agent will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
+In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
 However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g.
@@
 A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}.
-Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of task-agent pairs to achieve a specific cost function.
-In this paper, we assume that the tasks have been properly assigned and therefore do not further discuss this issue.
-In other words, every agent knows a destinition $q_{goal}$ it needs to go at every moment.
+Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
+In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
 }
+\textit{
+    \begin{remark}
+        Although each agent has its own team, agents can also work across teams.
+For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{4,1},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{4,1}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together.
+    \end{remark}
+}
 
 \subsection{Path Planning}
-After a target point is assigned for each agent, next step is to find a collision-free path from current position to it.
+After a destinition $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
 There must exist multiple feasible paths to go.
@@
 There are several path planning algorithm to handle this problem.
-Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper uses it as the path planning method of UTRS.
+Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of UTRS.
 This method attempts to discretize the search space into interconnected roads and find the path on it.
@@
 For a simpler explanation of how the URTS works, the following assumption is made.
+
 \begin{assumption}
@@
 \end{assumption}
+
 From above assumptions, a path of agent can be expressed as a sequence
@@
 Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario.
-These behaviors with changing position are called "moving" in this paper.
+These behaviors with changing position are classified as "moving" behavior in this paper.
 Besides, the agents do not always moving.
 Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
-These behaviors without changing position are called an "action" in this paper.
+These behaviors without changing position are classified as "action" behavior in this paper.
 More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control.
@@
 
-Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n={flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
+Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
 The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
@@
 
-\textit{Step 2:} Substituting $P_1=W^{-1}$ and $K=Y_1W_1^{-1}$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
+\textit{Step 2:} Substituting $P_1=W_1^{-1}$ and $K=Y_1W_1^{-1}$ found in \textit{Step 1} into (\ref{eq:M}) and applying Lemma \ref{lemma2}, we obtain:
 \begin{equation} \label{eq:step2}
@@
 Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness.
-More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)n$.
-For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)n$.
+More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)\times n$.
+For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)\times n$.
 % \textit{
@@
 Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$.
-At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$.
-The search task is obtained by dividing the unsearched region as shown in Fig.
+At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets.
+The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
 \ref{fig:S_task}.
-Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper task-agent pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$.
+Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$.
 Suppose a target is found after a while as shown in Fig.
@@
 From $T_6$, we have the goal configuration $q_{goal}$.
-With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n)$ can be found as shown in Fig.
+With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
 \ref{fig:R_task}.
-The behavior sequence $(\beta_n)$ is set as shown in Fig.
-\ref{fig:R_task}.
+The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking},n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing},n\in\mathbb{Z}\cap[6,15]$, $\beta_n=\mathit{running},n\in\mathbb{Z}\cap[16,27]$.
 We choose the first walking behavior to illustrate the local motion planning block of robots.
-For the the UAV $\alpha_{1,1}$, the path $(\sigma_n)$ is directly set to $([ 0,0,0 ]^T, [0,0,0]^T, ...)$ without going through path planning.
-The behavior sequence $(\beta_n)$ of the UAV $\alpha_{1,1}$ is set to flying behavior from start to finish, i.e., $\beta_n={flying}, n\in\mathbb{Z}\cap[1,k_f]$.
+
+For the the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
+The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
 \begin{figure}[htbp]
@@
 
-Following the procedure in Fig. \ref{fig:FandW}, the resuls of local motion planning of UAV flying and robot walking are shown in Fig. \ref{fig:sim:FandW}.
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The resuls of local motion planning of flying and walking.}%
-    \label{fig:sim:FandW}
+Following the procedure in Fig. \ref{fig:FandW}, the results of local motion planning of UAV flying and robot walking are shown in Fig. \ref{sim:flying} and \ref{sim:walking}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The top view of result of local motion planning of flying.}%
+    \label{sim:flying}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/untitled.png}\caption{The top view of result of local motion planning of walking.}%
+    \label{sim:walking}
 \end{figure}
@@
     \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
-    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),$\\$ 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,$\\$0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$.
+    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),\allowbreak 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,\allowbreak 0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$.
 Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{1,2}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{1,2}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The tracking error of UAV flying.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{1,2}$}%
     \label{fig:robot, control}
@@
 The transient responses that occur later are caused from fault signals, especially the sensor fault.
-This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the error over time $\dot{e}$ not only from $\bar{A}$ but also from $L\bar{C}$.
+This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{e}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.
 In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbance and feedforward errors, can be effectively estimated.

### 2022-09-22 src/System/@AGENT/AGENT.m

@@ -38,7 +38,7 @@ classdef Agent
         
         y = M(ag, x) % inertial matrix
         y = H(ag, x, dx) % non-inertial matrix
-        ag = get_K_L(ag, sys_aug1) % solve LMI to obtain control gain K and observer gain L
+        ag = get_K_L(ag, sys1, sys_aug1) % solve LMI to obtain control gain K and observer gain L
         ag = trajectory(ag) % get trajectory (x, u, ...)
         is_saved = Save(ag, whichVar) % save properties
         ag = Load(ag) % load properties

### 2022-09-22 src/System/@AGENT/get_K_L.m

@@ -1,4 +1,4 @@
-function ag = get_K_L(ag, sys_aug1)
+function ag = get_K_L(ag, sys1, sys_aug1)
 I = eye(ag.DIM_F);
 
 if ag.EXE_LMI
@@ -12,8 +12,10 @@ if ag.EXE_LMI
 end
 
 %% Fine tune of gain
-% gain = [-1 zeros(1, sys_a.WINDOW-1)];
-% ag.K(:, sys1.DIM_X + (1:sys_a.WINDOW)) = gain;
+% feedback control law u_fb = K*x_b, where K = [Kp Ki Kd Ka Ks]
+
+gain = [-1 zeros(1, ag.sys_a.WINDOW-1)]; % since the optimal actuator fault gain Ka is -I so that it can offset the estimation of actuator fault f_a.
+ag.K(:, sys1.DIM_X + (1:ag.sys_a.WINDOW)) = gain;
 % ag.KL(4:6, :) = [1000 0 0; 0 100 0; 0 0 10];
 % ag.KL(7:9,:) = [1000 0 0; 0 100 0; 0 0 10];
 % ag.K(:, sys1.DIM_X + sys_a.WINDOW + (1:sys_s.WINDOW)) = zeros(1, sys_s.WINDOW);

### 2022-09-22 src/URTS main script/Robot/@Robot/Ref2Config.m

@@ -71,8 +71,7 @@ CoM0(3, :) = rb.height_CoM0_walk;
 
 %% Inverse Kinemic, [x y z phi theta psi] -> config
 if rb.EXE_IK
-    simTime = rb.tr.T;
-    n = simTime/dt;
+    n = rb.tr.LEN;
     qr = zeros(12, n);
     newSubtree = subtree(robot, 'body_f1');
     qr(1:2:11, :) = IK_leg(newSubtree, CoM0(:, 1:n), r_lh(:, 1:n));

### 2022-09-22 src/URTS main script/Robot/function/Plot.m

@@ -1,0 +1,18 @@
+function Plot(t, x, xh, j, DIM, TITLE)
+figure
+% obtain a suitable size
+Layout = tiledlayout(DIM/2, 2);
+for i = 1 : DIM
+    nexttile
+    hold on
+    index = j + i;
+    plot(t, x(index, :), 'Displayname', 'state', 'LineWidth', 1)
+    plot(t, xh(index, :), 'DisplayName', 'estimated state', 'LineWidth', 1)
+%     plot(t, x(index, :)-xh(index, :), 'Displayname', 'error', 'LineWidth', 3)
+    grid on
+    ylabel(['$f_{' TITLE ',' num2str(i) '} (rad)$'], 'Interpreter','latex')      
+    legend('Interpreter','latex','Location','southeast')
+% ylim([-2 2])
+end
+xlabel(Layout,'t (sec)')
+end

### 2022-09-22 src/URTS main script/UAV/oneUAV_FaFs.m

@@ -86,7 +86,7 @@ uav.sys_s       = sys_s;
 uav.sys_aug     = sys_aug;
 
 %% solve LMI
-uav = uav.get_K_L(sys_aug1);
+uav = uav.get_K_L(sys1, sys_aug1);
 
 %% trajectory
 % Construct reference r(t) = [xd, yd, zd, phid]^T
@@ -111,30 +111,24 @@ uav.tr.LEN  = length(uav.tr.t);
 r1 = [
     0 0 1 1 2 2 2 1 0
     0 1 1 0 0 1 2 2 2
+    0 .5 1 .5 0 -.5 -1 -.5 0
 ]*5;
-a = 20;
 
 len1 = length(r1);
 t1 = linspace(0,1,len1);
-
-len2 = (len1-1)*a+1;
+density = 5;
+len2 = (len1-1)*density+1;
 t2 = linspace(0,1,len2);
-r2 = zeros(2, len2);
-r2 = [
-    interp1(t1, r1(1, :), t2);
-    interp1(t1, r1(2, :), t2);
-];
-
-fx = fit(t2', r2(1,:)', 'SmoothingSpline');
-fy = fit(t2', r2(2,:)', 'SmoothingSpline');
+r2 = zeros(3, len2);
 len3 = uav.tr.LEN;
 t3 = linspace(0,1,len3);
-r3 = [
-    feval(fx, t3)';
-    feval(fy, t3)';
-];
-r4 = cat(1, r3, 1*sin(uav.tr.t));
-uav.qr = cat(1, r4, zeros(1, length(r4)));
+r3 = zeros(3, len3);
+for i = 1 : 3
+    r2(i, :) = interp1(t1, r1(i, :), t2);
+    f2{i} = fit(t2', r2(i, :)', 'SmoothingSpline');
+    r3(i, :) = feval(f2{i}, t3)';
+end
+uav.qr = cat(1, r3, zeros(1, length(r3)));
 
 if uav.EXE_TRAJ
     %% set initial
@@ -149,9 +143,16 @@ end
 if uav.EXE_PLOT
     disp('Ploting trajectory ...')
     %% r(t)
-    figure; hold on;    
-    plot(r2(1, :), r2(2, :));
-    plot(uav.qr(1, :), uav.qr(2, :), '-o', 'DisplayName', 'r(t)')
+    figure
[…]

### 2022-09-22 test/Robot/oneRobot/test.m

@@ -1,20 +1,0 @@
-clc; clear; close all;
-t = linspace(0, 10, 100);
-x = square(t);
-plot(t,x,'o');
-hold on
-
-fx = fit(t', x', 'SmoothingSpline');
-len3 = 200;
-t3 = linspace(0,10,len3);
-x3 = feval(fx, t3)';
-plot(t3, x3)
-
-% fx = fit(t', t', 'SmoothingSpline');
-% fy = fit(t', x', 'SmoothingSpline');
-% t3 = linspace(0, 10, 200);
-% r3 = [
-%     feval(fx, t3)';
-%     feval(fy, t3)';
-% ];
-% plot(r3(1,:),r3(2,:))

### 2022-10-19 paper/paper.tex
Make UAV and robot animation

@@
 
-\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage}
+\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
 % \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
@@
 Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots.
-Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
+Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{j,i}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
 The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$.
@@
         Although each agent has its own team, agents can also work across teams.
-For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{4,1},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{4,1}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together.
+For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together.
     \end{remark}
@@
 
-Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to Local Motion Planning block to deal with.
+\begin{remark}
+    To avoid agents colliding with each other, the concept of multi-agent path planning is proposed \cite{yu2013multi}.
+However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate.
+Therefore, when the paths collide, the mechanism of waiting for the other side to pass can be used to avoid the collision problem.
+\end{remark}
+
+Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
 The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary.
@@
 In this case, a unified planner will become overly complex and impracticable.
-For this reason, we divide path planning into three subprocesses, i.e., Path Planning, Behavior Layer and Local Motion Planning.
-Then, the global planner, Path Planning block, will regard an agent as a point without kinodynamic constraints.
-The local planners, Local Motion Planning block, will consider the motion planning of a specific behavior.
+For this reason, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning.
+Then, the global planner, path planning block, will regard an agent as a point without kinodynamic constraints.
+The local planners, local motion planning block, will consider the motion planning of a specific behavior.
 % In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
@@
 \begin{assumption} \label{asm:collision} % UAV do not consider obstacle collisions a little wierd.
-    UAVs do not consider obstacle collisions because there are few obstacles in the air.
-Hence, the path of UAVs can be directly assigned rather than found by planner.
-Robots do not consider obstacle collisions in the direction perpendicular to the ground.
+    UAVs do not consider obstacle collision, so the path of UAVs can be directly assigned rather than found by planner.
+Robots do not consider obstacle collision in the direction perpendicular to the ground.
 \end{assumption}
@@
 Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$.
-For agents, the replanning decision can be a goal changing that is made by human or Task Allocation.
+For agents, the replanning decision can be a goal changing that is made by human or task allocation block.
 For robot, it can be a collision detecting by a dynamic roadmap-based planner.
@@
 The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one.
-If the ground station assigns $\alpha_{1,2}$ and $\alpha_{1,3}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,2},T_2),(\alpha_{1,3},T_3) \})\cup\{ \alpha_{1,2},T_6),(\alpha_{1,3},T_6) \}$.
+If the ground station assigns $\alpha_{1,5}$ and $\alpha_{2,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,5},T_2),(\alpha_{2,2},T_3) \})\cup\{ (\alpha_{1,5},T_6),(\alpha_{2,2},T_6) \}$.
 Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
@@
     \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining.
-The search tasks $T_j,j=1,2,...,5$ are to reach a destinition $q_{goal}$ as shown in figure.
-For robots, $q_{goal}$ will be passed to path planning algorithm to find a collision path.
-For UAV, the path is directly assigned due to the no-collision assumption as shown in figure.}%
+The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure).
+For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths.
+For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
     \label{fig:S_task}
@@
 
-To explain the path planning block and behavior layer block, we choose the pair $(\alpha_{1,2},T_6)$ as an example, i.e., the robot $\alpha_{1,2}$ performing the task $T_6$.
-From $T_6$, we have the goal configuration $q_{goal}$.
-With the current configuration $q_{start}$ and configuration space obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
+To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{1,5},T_6)$ and $(\alpha_{1,1}, T_1)$ as example.
+For the robot $\alpha_{1,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$.
+With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
 \ref{fig:R_task}.
-The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking},n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing},n\in\mathbb{Z}\cap[6,15]$, $\beta_n=\mathit{running},n\in\mathbb{Z}\cap[16,27]$.
-We choose the first walking behavior to illustrate the local motion planning block of robots.
-
-For the the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
+The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking}$ for $n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing}$ for $n\in\mathbb{Z}\cap[6,15]$ and $\beta_n=\mathit{running}$ for $n\in\mathbb{Z}\cap[16,27]$.
+We choose the walking behavior to illustrate the local motion planning block of robots.
+
+For the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.

### 2022-10-19 src/Hinf_Theorem/K/tracking/solveLMI.m

@@ -1,101 +1,0 @@
-function K = solveLMI(A, B, E, Ar, Br, Q1, Q2, rho)
-%solution of "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-%
-% This function is used to solve a control problem defined below :
-% (1) system
-%       dx/dt = Ax + Bu + Ev
-% (2) reference model
-%       dxr/dt = Arx + Bru
-% (3) augment system
-%       dxb/dt = Abxb + Bbu + Ebvb
-%       where xb = [x; x-xr], vb = [v; r]
-%             Ab = [A 0; A-Ar Ar], Bb = [B; B], Eb = [E 0; E -Br]
-% (4) control law
-%       u = K(x-xr) = Kbxb
-%       where Kb = [0 K]
-% (5) H infinity performance
-%       xb'Qbxb / vb'vb < rho^2
-%       where Qb = [Q1 0; 0 Q2]
-% (6) Lyapunov function
-%       V(x) = xb'Pbxb
-%       where Pb = [P1 0; 0 P2]
-%
-% Given (1) ~ (6), form H infinity theorem, if
-%       "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-% hold then (3) achieve (5).
-
-%% tunable parameter
-d1 = 0*10^(-4); % LMI <= d1*I. if problem infeasible, try increasing d1
-
-%% solve
-[DIM_X, DIM_U] = size(B);
-
-options = sdpsettings('solver','sdpt3');
-options = sdpsettings(options,'verbose', 0);
-
-W1 = sdpvar(DIM_X, DIM_X); % symmetric
-W2 = sdpvar(DIM_X, DIM_X);
-Y2 = sdpvar(DIM_U, DIM_X); % full
-    
-M11 = addSym(A*W1) + rho^(-2)*E*E';
-
-M12 = B*Y2 + W1*(A-Ar)' + rho^(-2)*E*E';
-M22 = addSym(Ar*W2 + B*Y2) + rho^(-2)*(E*E' + Br*Br');
-
-M13 = zeros(DIM_X);
-M23 = W2;
-M33 = -inv(Q2);
-
-if Q1 == 0
-    LMI = [
-        M11  M12  M13
-        M12' M22  M23
-        M13' M23' M33
-    ];
-
[…]

### 2022-10-19 src/Hinf_Theorem/K/tracking/solveLMI2.m

@@ -1,80 +1,0 @@
-function K = solveLMI1(A, B, E, Ar, Br, Q, rho)
-%solution of "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-%
-% This function is used to solve a control problem defined below :
-% (1) system
-%       dx/dt = Ax + Bu + Ev
-% (2) reference model
-%       dxr/dt = Arx + Bru
-% (3) augment system
-%       dxb/dt = Abxb + Bbu + Ebvb
-%       where xb = [x; xr], vb = [v; r]
-%             Ab = [A 0; 0 Ar], Bb = [B; 0], Eb = [E 0; 0 Br]
-% (4) control law
-%       u = K(x-xr) = Kbxb
-%       where Kb = [K -K]
-% (5) H infinity performance
-%       xb'Qbxb / vb'vb < rho^2
-%       where Qb = [Q -Q; -Q Q]
-% (6) Lyapunov function
-%       V(x) = xb'Pbxb
-%       where Pb = [P1 0; 0 P2]
-%
-% Given (1) ~ (6), form H infinity theorem, if
-%       "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-% hold then (3) achieve (5).
-
-%% tunable parameter
-d1 = 0*10^(-4); % LMI <= d1*I. if problem infeasible, try increasing d1
-
-%% solve
-[DIM_X, DIM_U]  = size(B);
-O               = zeros(DIM_X);
-
-options = sdpsettings('solver', 'sdpt3');
-options = sdpsettings(options,'verbose', 0);
-eqn = [];
-
-W1 = sdpvar(DIM_X, DIM_X); % symmetric
-Y1 = sdpvar(DIM_U, DIM_X); % full
-eqn = [eqn, W1 >= 0];
-
-M11 = addSym(A*W1 + B*Y1) + rho^(-2)*E*E';
-
-M12 = W1*sqrtm(Q);
-M22 = -eye(DIM_X);
-
-LMI = [
-    M11  M12
-    M12' M22
-];
-eqn = [eqn, LMI <= d1*eye(2*DIM_X)];
-% eq1 = M11 <= 0;
-    
-% If you want to limit size of K
-% LMI2 = [
-%     -10^(4)*eye(DIM_U)   Y2
[…]

### 2022-10-19 src/Hinf_Theorem/K/tracking/solveLMI3.m

@@ -1,97 +1,0 @@
-function K = solveLMI1(A, B, E, Ar, Br, Q, rho)
-%solution of "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-%
-% This function is used to solve a control problem defined below :
-% (1) system
-%       dx/dt = Ax + Bu + Ev
-% (2) reference model
-%       dxr/dt = Arx + Bru
-% (3) augment system
-%       dxb/dt = Abxb + Bbu + Ebvb
-%       where xb = [x; xr], vb = [v; r]
-%             Ab = [A 0; 0 Ar], Bb = [B; 0], Eb = [E 0; 0 Br]
-% (4) control law
-%       u = K(x-xr) = Kbxb
-%       where Kb = [K -K]
-% (5) H infinity performance
-%       xb'Qbxb / vb'vb < rho^2
-%       where Qb = [Q -Q; -Q Q]
-% (6) Lyapunov function
-%       V(x) = xb'Pbxb
-%       where Pb = [P -P; -P P]
-%
-% Given (1) ~ (6), form H infinity theorem, if
-%       "Qb + Pb(Ab+BbKb) + (Ab+BbKb)'Pb + PbEbEb'Pb/rho^2 < 0, Pb > 0"
-% hold then (3) achieve (5).
-
-%% tunable parameter
-d1 = 0*10^(-4); % LMI <= d1*I. if problem infeasible, try increasing d1
-
-%% solve
-[DIM_X, DIM_U]  = size(B);
-O               = zeros(DIM_X);
-EEBB            = E*E'+ Br*Br';
-
-options = sdpsettings('solver', 'mosek');
-options = sdpsettings(options,'verbose', 0);
-eqn = [];
-
-W = sdpvar(DIM_X, DIM_X); % symmetric
-Y = sdpvar(DIM_U, DIM_X); % full
-
-eqn = [eqn, W >= 0];
-    
-M11 = addSym(A*W + B*Y) + rho^(-2)*EEBB;
-
-M12 = -addSym(B*Y) - Ar*W - W*A' - rho^(-2)*EEBB;
-M22 = addSym(Ar*W + B*Y) + rho^(-2)*EEBB;
-
-M13 = W*sqrtm(Q);
-M23 = O;
-M33 = -eye(DIM_X);
-
-M14 = O;
-M24 = W*sqrtm(Q);
-M34 = O;
-M44 = -eye(DIM_X);
-
[…]

### 2022-10-19 src/Hinf_Theorem/K_L/solveLMI12.m

@@ -1,190 +1,0 @@
-function [K, L] = solveLMI12(sys, sys1, sys2)
-%solution of "Qb + Pb*Ab + Ab'*Pb + Pb*Eb*Eb'*Pb/rho^2 < 0, Pb > 0"
-%
-% This function is used to solve a control problem defined below :
-% (1) system
-%       dxb/dt = Ab*xb + Eb*vb
-%       xb = [x; x-xh], Ab = [A+B*K -B*K; 0 A+L*C]
-%       Eb = [Ebs 0; 0 Ebe]
-%       Ebs = blkdiag(0, Es1, Es2), Ebe = blkdiag(0, Ee1, Ee2)
-% (4) control law
-%       u = K*xh
-%       K = [K1 Ka Ks], Ka = [-I 0 ... 0]
-% (5) H infinity performance
-%       (x-xh)'*Q2*(x-xh) + x*Q1*x / vb'*vb < rho^2
-%       Qb = [Qbs 0; 0 Qbe]
-%       Qbs = blkdiag(Qs, Qs1, Qs2), Qbe = blkdiag(Qe, Qe1, Qe2)
-% (6) Lyapunov function
-%       V(x) = xb'Pb*xb
-%       Pb = [Pbs 0; 0 Pbe]
-%       Pbs = blkdiag(Ps, Ps1, Ps2), Qbe = blkdiag(Pe, Pe1, Pe2)
-%
-% Since actuator fault state is always stable (corresponding terms in LMI do not affect the positive definiteness of LMI),
-% it can be remove from LMI. That is, NO Ka, Qs1, Ps1, and 6*6 block matrix will become 5*5 block matrix.
-%
-% By testing, this method will let LMI more difficult to solve. The reason could be the increasing of conservative in Pbs, Pbe
-% due to let Pbs = blkdiag(Ps, Ps1, Ps2) rather origin Pbs.
-
-%% solve
-I = eye(sys.DIM_X);
-I1 = eye(sys1.DIM_X);
-I2 = eye(sys2.DIM_X);
-A = sys.A;
-A1 = sys1.A;
-A2 = sys2.A;
[…]

### 2022-10-19 src/Hinf_Theorem/L/solveLMI7.m

@@ -1,83 +1,0 @@
-function L = solveLMI7(A, C, Q, rho)
-%solution of "Q + Pb*Ab + Ab*Pb + PbPb/rho^2 < 0, Pb > 0"
-%
-% This function is used to solve a control problem defined below :
-% (1) system
-%       dx/dt = Ax + v
-% (2) observer
-%       dxh/dt = Ax + L*C*(x - xh)
-% (3) augment sys
-%       dxb/dt = Ab*xb + vb
-%       where xb = [x; x-xh], Ab = [A 0; 0 A-L*C], vb = [v; 0]
-% (5) H infinity performance
-%       x'Qbx / vb'vb < rho^2
-% (6) Lyapunov function
-%       V(x) = x'Pbx
-%       where Pb = [P1 0; 0 P2]
-
-%% solve
-[DIM_U, DIM_X]  = size(C);
-O               = zeros(DIM_X);
-I               = eye(DIM_X);
-options = sdpsettings('solver', 'mosek');
-options = sdpsettings(options,'verbose', 0);
-eqn = [];
-
-P1 = sdpvar(DIM_X, DIM_X);
-P2 = sdpvar(DIM_X, DIM_X);
-Y2 = sdpvar(DIM_X, DIM_U);
-
-eqn = [eqn, P1 >= 0, P2 >= 0];
-
-M11 = addSym(P1*A);
-
-M12 = O;
-M22 = Q + addSym(P2*A - Y2*C);
-
-M13 = P1;
-M23 = O;
-M33 = -rho^(2)*eye(DIM_X);
-
-M14 = O;
-M24 = P2;
-M34 = O;
-M44 = -rho^(2)*eye(DIM_X);
-
-LMI = [
-    M11  M12
-    M12' M22
-];
-% LMI = [
-%     M11  M12  M13 M14
-%     M12' M22  M23 M24
-%     M13' M23' M33 M34
-%     M14' M24' M34 M44
-% ];
-eqn = [eqn, LMI <= 0];  
-
-% If you want to limit size of L, i.e., Y'*weight*Y <= Ub
-% weight = eye(DIM_X); % weight of Y
-% Ub = 10^(3)*eye(DIM_U); % upper bound
-% LMI2 = [
-%     -Ub  Y2'
-%     Y2  -P2
-% ];
-% eqn = [eqn, LMI2 <= 0];
-
-sol = optimize(eqn, [], options);
-
-% If you want to see solution information
[…]

### 2022-10-19 src/ODE_solver.m

@@ -1,62 +1,0 @@
-function y = ODE_solver(f, h, x, t, method)
-%Runge-Kutta-Fehlberg method
-% dx(t)/dt = f(t, x)
-%
-% input:
-% f     - dx(t)/dt
-% h     - time step
-%
-% output:
-% y     - x(t+h)
-
-switch method
-case 'Euler'
-k = h*f(t, x);
-y = x + k;
-
-case 'RK4'
-CH = [1/6 2/6 2/6 1/6];
-k = zeros(length(x), 4);
-k(:, 1) = h*f(t, x);
-k(:, 2) = h*f(t, x+k(:, 1)/2);
-k(:, 3) = h*f(t, x+k(:, 2)/2);
-k(:, 4) = h*f(t, x+k(:, 3));
-y = x + k*CH';
-
-case 'RKF'
-% table 1
-A = [0 2/9 1/3 3/4 1 5/6];
-B = [
-    0 0 0 0 0
-    2/9 0 0 0 0
-    1/12 1/4 0 0 0
-    69/128 -243/128 135/64 0 0
-    -17/12 27/4 -27/5 16/15 0
-    65/432 -5/16 13/16 4/27 5/144
-];
-CH = [47/450 0 12/25 32/225 1/30 6/25];
-CT = [-1/150 0 3/100 -16/75 -1/20 6/25];
-
-% % table 2
-% A = [0 1/2 1/2 1 2/3 1/5];
-% B = [
-%     0 0 0 0 0
-%     1/2 0 0 0 0
-%     1/4 1/4 0 0 0
-%     0 -1 2 0 0
-%     7/27 10/27 0 1/27 0
-%     1/5 28/625 -1/5 546/625 54/625 -378/625
-% ];
-% CH = [1/24 0 0 5/48 27/56 125/336]
-
-k = zeros(length(x), 6);
-k(:, 1) = h*f(t+A(1)*h, x);
-for i = 2 : 6
-    k(:, i) = h*f(t+A(i)*h, x+k(:, 1:i-1)*B(i,1:i-1)');
-end
-y = x + k*CH';
-% TE = norm(k*CT')
-end
-
-end
-

### 2022-10-19 src/System/@SmoothModel/SmoothModel.m

@@ -1,64 +1,0 @@
-classdef SmoothModel
-    %Smooth model
-    % dx/dt = Ax + Ev
-    % 
-
-    properties
-        METHOD % method for construct A
-        WINDOW % window size  
-        dt % smapling time
-
-        A % system matrix
-        B % input matrix
-        C % mapping matrix
-        E % disturbance matrix
-
-        Q1 % tracking weighting matrix of state in H infinity performance index
-        Q2 % estimation weighting matrix of state in H infinity performance index
-        rho
-
-        DIM % dimension of fault signal
-        DIM_X % dimension of A
-
-        begin % begining index in the augment system
-        fault % the fault signal of this model
-    end
-    
-    methods
-        function obj = SmoothModel(WINDOW, DIM, dt, method)
-            obj.WINDOW = WINDOW;
-            obj.DIM = DIM;
-            obj.DIM_X = DIM*WINDOW;
-            obj.METHOD = method;
-
-            % A
-            if isempty(dt) % DT
-                obj = obj.getA_DT();
-            else          
-                obj.dt = dt;
-                obj = obj.getA_CT();
-            end
-            % C
-            C = [1 zeros(1, WINDOW-1)];
-            obj.C = kron(C, eye(obj.DIM));
-
-            obj.E = eye(obj.DIM_X);
-        end
-
-        function xb = set_real_signal(obj, xb, i)
-            %assign real fault signal
-            % Since the real fault signal is not produced from smooth model, we need reassign it.
-            j0 = obj.begin;
-            range = 1 : obj.DIM;
-            for j = 1 : obj.WINDOW-1
-                j1 = j0 + j*obj.DIM;
-                xb(j1+range, i+1) = xb(j1+range-obj.DIM, i); % Since Fa(i) = [fa(i), fa(i-1), fa(i-2), ...], so Fa(i+1) = ["new fa", fa(i), f(i-1)]
-            end
-            xb(j0+range, i+1) = obj.fault(:, i); % assign "new fa"
-        end
-
-        obj = getA_CT(obj); % construct continuos time smoothing model
-        obj = getA_DT(obj); % construct discrete time smoothing mode
-    end
-end
-

### 2022-10-19 src/System/@SmoothModel/getA_CT.m

@@ -1,64 +1,0 @@
-function obj = getA_CT(obj)
-%CONSTRUCT SMooth Model's A matrix
-% method 1-1    - [FDC; 1- 1 0 ... 0; 0 1 -1 0 ... 0; ...]
-% method 1-2    - [1 -1 0 ... 0; 1- 1 0 ... 0; 0 1 -1 0 ... 0; ...]
-% method 1-3    - [a1-1 a2 ... an; 1- 1 0 ... 0; 0 1 -1 0 ... 0; ...], sum of "a1" to "an" = 1
-% method 2      - [FDC]
-% method 3      - zeros
-% method 4      - with second order differential term
-% method 5      - with integral term
-WINDOW  = obj.WINDOW;
-h      = obj.dt;
-method  = obj.METHOD;
-A       = zeros(WINDOW); % init
-
-switch method
-case '1-1' % finite differenciation
-    point = 0 : -1 : -WINDOW+1;
-    A(1, 1:WINDOW) = FindFDC(point, 1)'/h;
-case '1-2' % 1 -1
-    point = zeros(WINDOW, 1); point(1:2) = [1 -1];
-    A(1, 1:WINDOW) = point/h;
-case '1-3' % origin smooth coefficient
-    coeff2 = 0.3.^(0:WINDOW-1);
-    coeff2 = coeff2/sum(coeff2); % sum of coeff must be 1
-    A(1, 1:WINDOW) = [-1 zeros(1, WINDOW-1)];
-    A(1, 1:WINDOW) = (A(1, 1:WINDOW) + coeff2)/h;
-end
-
-switch method
-case {'1-1', '1-2', '1-3'} % different in first column
-    for i = 2 : WINDOW
-        point = [1 0];
-        A(i, i-1:i) = FindFDC(point, 1)'/h; % obtain coefficient
-    end
-case '2' % finite differenciation
-    for i = 1 : WINDOW
-        point = i-1 : -1 : -WINDOW+i;
-        A(i, :) = FindFDC(point, 1)'/h;
-    end
-case '3' % zero    
-case '4'
-    A = [
-        0 0 1 0
-        0 0 0 1
-        -6/h^2 6/h^2 6/h 2/h
-        6/h^2 -6/h^2 -2/h -6/h
-    ]; % test for WINDOW = 4 (trajectory there need to change manually too)
-case '5'
-    A = [
-        1 -1 0 0
-        1 -1 0 0
[…]

### 2022-10-19 src/System/@Trajectory/Trajectory.m

@@ -1,70 +1,0 @@
-classdef Trajectory 
-%trajectory for a system
-
-    properties (Constant)
-
-    end   
-    
-    properties
-        dt  = 0.001 % time step
-        t % time
-        T   = 10 % final time
-        LEN
-        
-        % initial value
-        x0
-        xr0
-        xh0
-
-        IS_LINEAR = 1 % run fuzzy linear system or origin nonlinear system
-        IS_RK4 = 0 % run RK4 or Euler
-
-        % trajectory
-        x % system state
-        x2 % system state 2
-        r % reference trajectory
-        xr % reference model state
-        xh % estimated state
-
-        e % x - r
-        er % x - xr
-        eh % x - xh
-
-        u % control
-        v % distrubance
-
-        f % unknown signal
-    end
-    
-    methods
-        function o = Trajectory()
-            o.t = 0 : o.dt : o.T;
-        end
-        
-        function plot(o)
-            % figure('units','normalized','outerposition',[0 0 1 1])
-            % x(t), xr(t)
-            SIZE_X = size(o.x, 1);
-            for i = 1 : SIZE_X
-                figure
-                plot(o.t, o.x(i, :), o.t, o.xr(i, :))
-                title(['x_{' num2str(i) '}'])
-                legend("x", "x_r")
-                xlabel("t")
-                % ylim([-2 2])
-            end 
-            
-            % u(t)
-            % for j = 1 : o.SIZE_U
-            %     figure(i+j)
-            %     plot(o.t, o.u(j, :));
-            %     title(['u_{' num2str(j) '}'])
-            % end
-        end
-    end
-
-    methods (Access = private)
-        
-    end
-end
-

### 2022-10-19 src/System/UAV/@UAV_FZmodel/UAV_FZmodel.m

@@ -1,42 +1,0 @@
-classdef UAV_FZmodel < UAV_RM_L
-%UAV fuzzy model
-% - System form
-%       - dx/dt = Ai*x + Bi*u + Ev
-% - Control law
-%       - u = Ki*x;
-%
-    properties (Constant)
-        % system parameters
-    end   
-    
-    properties
-        % fz may be moved to here
-    end
-    
-    properties (Access = private)
-
-    end
-
-    % system functions
-    methods
-        function uav = UAV_FZmodel(fz)
-            uav@UAV();
-            uav.PATH = [uav.DATA_FOLDER_PATH mfilename]; % Path of data
-            uav = uav.load(); % load old data
-        end
-        
-        uav = getAB(uav, fz)
-        uav = getKL(uav, fz)
-        uav = trajectory(uav, fz) % get trajectory (x, xr, u, ...)
-        
-        % function Save(uav, whichVar) % pass "mfilename" to save@UAV()
-        %     Save@UAV(uav, whichVar);
-        % end
-    end
-
-    methods (Access = private)
-
-    end
-end
-%#ok<*PROPLC>
-%#ok<*NASGU>

### 2022-10-19 src/System/UAV/@UAV_FZmodel/getAB.m

@@ -1,50 +1,0 @@
-function obj = getAB(obj, fz)
-%Find fuzzy local matrix
-% This algorithm is for "primary term" only.
-%
-% Im trying to write a general algorithm for finding fuzzy local matrix.
-% Given a system sys with sys.f(), sys.g(), sys.A, sys.B, the algorithm will
-%       sys.f() -> sys.A, sys.g() -> sys.B
-% 
-% In this version, let f(x) = [f1(x) ... fn(x)],
-% the alogorithm is corrected if fi(x) is composed of a1x1 + a2x2 + ... after substitude the fuzzy operation point.
-% When fi(x) has constant term or high-order term, the algorithm will go wrong.
-%
-% For safety, construct fuzzy matrix manually but you must revise sys.A when sys.f() change.
-
-s = sym('s', [obj.DIM_X, 1]);
-
-% find A
-obj.A = cell(1, fz.num);
-disp('Construct A, B matrix...');
-for k = 1 : fz.num
-    disp(['A' num2str(k) ' constructed'])
-                
-    y = subs(obj.f(s), s(fz.PV), fz.set(:, k)); % Sub fuzzy operation point into nonlinear function f()
-    
-    % We want f(x) = [f1 ... fn]' = A*x = [A1 ... An]'*[x1 ... xn]', where A1 is row 1 of A
-    obj.A{k} = zeros(obj.DIM_X);
-    for i = 1 : obj.DIM_X % i-th row of A               
-        [cf, u] = coeffs(y(i)); % ex. f1 = s2 + 2*s3 -> cf = [1 2], u = [s2, s3]
-        u = subs(u, s, (1:obj.DIM_X)'); % u = [s2, s3] -> u = [2, 3]
-        obj.A{k}(i, u) = cf; % A1 = [0 1 1 0 ... 0]
-    end
-
-    % Remove constant term
-    % x6_FZ_SET = [0 1 2];
-    % obj.A{k}(6, 6) = obj.A{k}(6, 6) + obj.A{k}(6, 1)/x6_FZ_SET(2);
-    obj.A{k}(6, 1) = 0;
-end
-
-% find B
-obj.B = cell(1, fz.num);
-for k = 1 : fz.num
-    disp(['B' num2str(k) ' constructed'])
-                
-    y = subs(obj.g(s), s(fz.PV), fz.set(:, k));
-
[…]

### 2022-10-19 src/System/UAV/@UAV_TPmodel/trajectory.m

@@ -1,100 +1,0 @@
-function uav = trajectory(uav)
-%calculate trajectory
-
-dt          = uav.tr.dt;
-t           = 0 : dt : uav.tr.T;
-LEN         = length(t);
-
-xb          = zeros(2*uav.DIM_X, LEN);
-xb(:, 1)    = [uav.tr.x0; uav.tr.xr0];
-u           = zeros(uav.DIM_U, LEN);
-
-disp('Ploting trajectory ...')
-for i = 1 : LEN - 1       
-    if mod(i, 1/dt) == 0
-        disp(['t = ' num2str(i*dt)])
-    end
-    
-    k1 = RK4(uav, xb(:, i), i*dt);
-    if uav.tr.IS_RK4
-        k2 = RK4(uav, xb(:, i)+k1*dt/2, i*dt + dt/2);
-        k3 = RK4(uav, xb(:, i)+k2*dt/2, i*dt + dt/2);
-        k4 = RK4(uav, xb(:, i)+k3*dt, i*dt + dt); 
-
-        xb(:, i+1)  = xb(:, i)  + (k1 + 2*k2 + 2*k3 + k4)*dt/6;
-    end
-    xb(:, i+1)  = xb(:, i) +  k1*dt;
-
-    uav.tr.x(:, i+1) = xb(1 : uav.DIM_X, i+1);
-    uav.tr.xr(:, i+1) = xb(uav.DIM_X+1 : 2*uav.DIM_X, i+1);
-
-    % total_K = zeros(o.DIM_U, o.DIM_X);
-    % for j = 1 : fz.num
-    %     total_K = total_K + fz.mbfun(j, o.x(:, i+1))*uav.K{j};
-    % end
-    % o.u(:, i+1) = total_K*(o.x(:, i+1) - o.xr(:, i+1));
-end
-uav.tr.t = t;
-end
-
-%% Local function
-function k = RK4(uav, xb, t)
-    DIM_X   = uav.DIM_X;
-    DIM_U   = uav.DIM_U;
-    O       = zeros(DIM_X);
-    v       = @(t) 0.01*randn(DIM_X, 1) + 0; % disterbance
-    x       = xb(1 : DIM_X);
-    xr      = xb(DIM_X+1 : DIM_X*2);
-    [r, F]  = uav.r_F(x, t);
-    feed    = uav.g(x)*[F; 0; 0; 0]; % feedforward
[…]

### 2022-10-19 src/URTS main script/Robot/function/Plot.m

@@ -1,4 +1,4 @@
-function Plot(t, x, xh, j, DIM, TITLE)
+function Plot(t, x, xh, j, DIM, TITLE, unit)
 figure
 % obtain a suitable size
 Layout = tiledlayout(DIM/2, 2);
@@ -10,7 +10,7 @@ for i = 1 : DIM
     plot(t, xh(index, :), 'DisplayName', 'estimated state', 'LineWidth', 1)
 %     plot(t, x(index, :)-xh(index, :), 'Displayname', 'error', 'LineWidth', 3)
     grid on
-    ylabel(['$f_{' TITLE ',' num2str(i) '} (rad)$'], 'Interpreter','latex')      
+    ylabel(['$f_{' TITLE ',' num2str(i) '} (' unit ')$'], 'Interpreter','latex')      
     legend('Interpreter','latex','Location','southeast')
 % ylim([-2 2])
 end

### 2022-10-19 src/URTS main script/Robot/oneRobot_FaFs.m

@@ -4,8 +4,7 @@
 %   - calculating the inverse dynamic (line 20 in IK_leg.m)
 %   - calculating the nonlinear terms M(x) and H(x, dx) in rb.trajectory()
 clc; clear; close all; tic;
-addpath(genpath('./././src'))
-addpath(genpath('function'))
+addpath(genpath('../../../src'))
 
 rb = Robot();
 % flow control of code
@@ -13,7 +12,7 @@ rb.EXE_LMI     = 0;
 rb.EXE_Z2C     = 0; % ZMP to CoM converter
 rb.EXE_IK      = 0; % inverse dynamic
 rb.EXE_TRAJ    = 0; % trajectory
-rb.EXE_PLOT    = 0; % plot results
+rb.EXE_PLOT    = 1; % plot results
 
 % time
 rb.tr.dt    = .001; % Time step
@@ -56,7 +55,7 @@ sys_a       = SmoothModel(WINDOW, DIM_F, dt_, METHOD);
 sys_a.B     = kron(sys_a1.B, I);
 
 %% smooth model (sensor)
-WINDOW  = 4;
+WINDOW  = 3;
 dt_     = 1000*rb.tr.dt; % multiply 1000 is better by testing
 METHOD = '2';
 
@@ -193,33 +192,29 @@ if rb.EXE_PLOT
         grid on
         ylabel(['$q_{' num2str(i) '} (rad)$'], 'Interpreter','latex')      
         legend('Interpreter','latex','Location','southeast')
-        % ylim([-2 2])
     end
     xlabel(Layout,'t (sec)')
     
-    % save_fig(fig)
-    
     %% Fa and Fs
-    Plot(rb.tr.t, rb.tr.x, rb.tr.xh, rb.sys_a.begin, sys_a.DIM, '1')
-    Plot(rb.tr.t, rb.tr.x, rb.tr.xh, rb.sys_s.begin, sys_s.DIM, '2')
+    Plot(rb.tr.t, rb.tr.x, rb.tr.xh, rb.sys_a.begin, sys_a.DIM, '1', 'm/s^2')
+    Plot(rb.tr.t, rb.tr.x, rb.tr.xh, rb.sys_s.begin, sys_s.DIM, '2', 'm')
 
     %% control u(t)
     fig = figure;
     DIM = size(rb.tr.u, 1);
-    div = divisors(DIM);
-    i = ceil((length(div))/2);
[…]

### 2022-10-19 src/URTS main script/Robot/robot_simulink.m

@@ -1,0 +1,81 @@
+% robot joint tracking, simulink, use the result of oneRobot_FaFs.m
+
+clc; clear; close all
+addpath(genpath('../../../src'))
+addpath(genpath('function'))
+rb = Robot();
+dt = rb.tr.dt;
+t = 0 : dt : rb.tr.T;
+%% use reference
+% qr = rb.tr.qr;
+
+%% use state
+qr = rb.tr.x(rb.DIM_F + (1:rb.DIM_F), :) + rb.tr.r{1}(1:rb.DIM_F, :);
+
+%% Control
+% robot = rb.rbtree;
+% massMatrix(robot)
+% robot.massMatrix()
+% bodyname = 'body12';
+% J = geometricJacobian(robot, qr(:, 1)', bodyname);
+% wrench = 1:6;
+% robot.homeConfiguration
+% fext = externalForce(robot,bodyname,wrench,robot.homeConfiguration)
+
+%% simulink
+
+%% joint ref
+qr_L = cat(1, t, qr(1:2:11, :))';
+qr_R = cat(1, t, qr(2:2:12, :))';
+
+%% Plot robot joint traj
+% n = length(rb.qr);
+% figure; hold on
+% for i = 1 : 12
+%     plot(t, rb.qr(i, :)/pi*180, 'DisplayName', ['theta' num2str(i)])
+% end
+% movegui('center')
+% legend
+
+%% Contact and friction parameters
+contact_stiffness = 40/.001;          % Approximated at weight (N) / desired displacement (m)
+contact_damping = contact_stiffness/10; % Tuned based on contact stiffness value
+mu_s = 0.9*1;     % Static friction coefficient: Around that of rubber-asphalt
+mu_k = 0.8*1;     % Kinetic friction coefficient: Lower than the static coefficient
+mu_vth = 0.1;   % Friction velocity threshold (m/s)
+
+plane_x = 50;
+plane_y = 3;
+plane_z = 0.025; 
+
+%% Robot mechanical Parameters (m)
+% density = 1000;
+
+leg_width = 0.08;
+lower_leg_length = 0.38; 
+upper_leg_length = 0.40;
+
+foot_x = 0.08;
+foot_y = 0.04;
+foot_z = 0.005;
+
+torso_width = 0.24; 
+torso_length = 0.20; 
+torso_height = 0.35; 
+
+torso_offset_height = 0; 
+torso_offset_length = 0; 
+
[…]

### 2022-10-19 src/URTS main script/UAV/UAV_animation.m

@@ -1,0 +1,17 @@
+clc; clear; close all
+
+addpath(genpath('../../../src'))
+uav = UAV_AGENTmodel();
+DIM_F = uav.DIM_F;
+dt = uav.tr.dt;
+fps = 1/dt;
+N = 100;
+fps = fps/N;
+r = uav.tr.r{1};
+r = r(:, 1:N:length(r));
+e = uav.tr.x(DIM_F+(1:DIM_F), :);
+e = e(:, 1:N:length(e));
+x = e + r;
+x(4:6, :) = x(4:6, :)*180/2/pi;
+% drone_Animation(r(1,:),r(2,:),r(3,:),r(4,:),r(5,:),r(6,:))
+drone_Animation(x(1,:),x(2,:),x(3,:),x(4,:),x(5,:),x(6,:), r, fps)

### 2022-10-19 src/functions/FindFDC.m

@@ -1,0 +1,32 @@
+function coeff = FindFDC(point, order)
+%Find Coefficient of Finite Difference Method
+%
+% Input:
+%   point
+%   order
+%
+% Output:
+%   coeff
+%
+% Ex:
+%   Find the first-order derivative of a function f(x) constructed by f(x-2), f(x), f(x + 1) and their coefficient c_(-2), c_0, c_1
+%   f'(x) = c_(-2)*f(x-2) + c_0*f(x) + c_1*f(x + 1)
+%   then
+%       point = [-2 0 1]
+%       order = 1
+
+n = length(point);
+if order >= n
+    error('Order of the derivative needs less than number of points')
+end
+
+A = zeros(n);
+for i = 1 : n
+    for j = 1 : n
+        A(j, i) = point(i)^(j-1)/factorial(j-1);
+    end
+end
+b = zeros(n, 1); b(order + 1) = 1;
+
+coeff = A\b;
+end

### 2022-10-19 src/functions/Hinf_Theorem/K_L/solveLMI10.m

@@ -1,0 +1,116 @@
+function [K, L] = solveLMI10(A, B, C, E, Q1, Q2, R, rho)
+%solution of "Qb + Pb*Ab + Ab'*Pb + Pb*E*E'*Pb/rho^2 < 0, Pb > 0"
+%
+% This function is used to solve a control problem defined below :
+% (1) system
+%       dxb/dt = Ab*xb + vb
+%       where xb = [x; x-xh], Ab = [A+B*K -B*K; 0 A+L*C]
+% (4) control law
+%       u = K*xh
+% (5) H infinity performance
+%       (x-xh)'*Q2*(x-xh) + x*Q1*x/ vb'*vb < rho^2
+%       Qb = [Q1 0; 0 Q2]
+% (6) Lyapunov function
+%       V(x) = xb'Pb*xb
+%       where Pb = [P1 0; 0 P2]
+
+%% solve
+[DIM_X, DIM_U]  = size(B);
+[DIM_Y, ~]      = size(C);
+O               = zeros(DIM_X);
+I               = eye(DIM_X);
+options = sdpsettings('solver', 'mosek');
+options = sdpsettings(options,'verbose', 0);
+eqn = [];
+
+W1 = sdpvar(DIM_X, DIM_X);
+P2 = sdpvar(DIM_X, DIM_X);
+Y1 = sdpvar(DIM_U, DIM_X);
+Y2 = sdpvar(DIM_X, DIM_Y);
+
+eqn = [eqn, W1 >= 0, P2 >= 0];
+
+M11 = addSym(A*W1 + B*Y1) + rho^(-2)*E*E';
+
+M12 = -B*Y1;
+M22 = addSym(P2*A + Y2*C) + Q2;
+
+M13 = W1*sqrt(Q1);
+M23 = O;
+M33 = -I;
+
+M14 = O;
+M24 = P2*E*rho^(-1);
+M34 = O;
+M44 = -I;
+
+if isempty(R)
+    LMI = [
+        M11  M12  M13  M14
+        M12' M22  M23  M24
+        M13' M23' M33  M34
+        M14' M24' M34' M44
+    ];
+else
+    M15 = Y1'*sqrt(R);
+    M25 = zeros(DIM_X, DIM_U);
+    M35 = zeros(DIM_X, DIM_U);
+    M45 = zeros(DIM_X, DIM_U);
+    M55 = -eye(DIM_U);
+    LMI = [
+        M11  M12  M13  M14  M15
+        M12' M22  M23  M24  M25
[…]

### 2022-10-19 src/functions/Hinf_Theorem/K_L/solveLMI12.m

@@ -1,0 +1,190 @@
+function [K, L] = solveLMI12(sys, sys1, sys2)
+%solution of "Qb + Pb*Ab + Ab'*Pb + Pb*Eb*Eb'*Pb/rho^2 < 0, Pb > 0"
+%
+% This function is used to solve a control problem defined below :
+% (1) system
+%       dxb/dt = Ab*xb + Eb*vb
+%       xb = [x; x-xh], Ab = [A+B*K -B*K; 0 A+L*C]
+%       Eb = [Ebs 0; 0 Ebe]
+%       Ebs = blkdiag(0, Es1, Es2), Ebe = blkdiag(0, Ee1, Ee2)
+% (4) control law
+%       u = K*xh
+%       K = [K1 Ka Ks], Ka = [-I 0 ... 0]
+% (5) H infinity performance
+%       (x-xh)'*Q2*(x-xh) + x*Q1*x / vb'*vb < rho^2
+%       Qb = [Qbs 0; 0 Qbe]
+%       Qbs = blkdiag(Qs, Qs1, Qs2), Qbe = blkdiag(Qe, Qe1, Qe2)
+% (6) Lyapunov function
+%       V(x) = xb'Pb*xb
+%       Pb = [Pbs 0; 0 Pbe]
+%       Pbs = blkdiag(Ps, Ps1, Ps2), Qbe = blkdiag(Pe, Pe1, Pe2)
+%
+% Since actuator fault state is always stable (corresponding terms in LMI do not affect the positive definiteness of LMI),
+% it can be remove from LMI. That is, NO Ka, Qs1, Ps1, and 6*6 block matrix will become 5*5 block matrix.
+%
+% By testing, this method will let LMI more difficult to solve. The reason could be the increasing of conservative in Pbs, Pbe
+% due to let Pbs = blkdiag(Ps, Ps1, Ps2) rather origin Pbs.
+
+%% solve
+I = eye(sys.DIM_X);
+I1 = eye(sys1.DIM_X);
+I2 = eye(sys2.DIM_X);
+A = sys.A;
+A1 = sys1.A;
+A2 = sys2.A;
[…]

### 2022-10-19 src/functions/Hinf_Theorem/K_L/solveLMI9.m

@@ -1,0 +1,86 @@
+function [K, L] = solveLMI9(A, B, C, Q1, Q2, rho)
+%solution of "Qb + Pb*Ab + Ab'*Pb + Pb*Pb/rho^2 < 0, Pb > 0"
+%
+% This function is used to solve a control problem defined below :
+% (1) system
+%       dxb/dt = Ab*xb + vb
+%       where xb = [x; xh], Ab = [A BK; -LC A+LC]
+% (4) control law
+%       u = K*xh
+% (5) H infinity performance
+%       (x-xh)'*Q2*(x-xh) + x*Q1*x/ vb'*vb < rho^2
+%       Qb = [Q1+Q2 -Q2; -Q2 Q2]
+% (6) Lyapunov function
+%       V(x) = xb'Pb*xb
+%       where Pb = [P1 0; 0 P2]
+
+%% solve
+[DIM_X, DIM_U]  = size(B);
+[DIM_Y, ~]      = size(C);
+O               = zeros(DIM_X);
+I               = eye(DIM_X);
+options = sdpsettings('solver', 'mosek');
+options = sdpsettings(options,'verbose', 0);
+eqn = [];
+
+W1 = sdpvar(DIM_X, DIM_X);
+P2 = sdpvar(DIM_X, DIM_X);
+Y1 = sdpvar(DIM_U, DIM_X);
+Y2 = sdpvar(DIM_X, DIM_Y);
+
+eqn = [eqn, W1 >= 0, P2 >= 0];
+
+M11 = addSym(A*W1) + rho^(-2)*I;
+
+M12 = B*Y1 - C'*Y2' - W1*Q2;
+M22 = addSym(P2*A + Y2*C) + Q2;
+
+M13 = W1*sqrtm(Q1+Q2);
+M23 = O;
+M33 = -I;
+
+M14 = O;
+M24 = P2;
+M34 = O;
+M44 = -rho^2*I;
+
+LMI = [
+    M11  M12  M13  M14
+    M12' M22  M23  M24
+    M13' M23' M33  M34
+    M14' M24' M34' M44
+];
+
+eqn = [eqn, LMI <= 0];  
+% eqn = [eqn, LMI <= d1*eye(4*DIM_X)];  
+
+% If you want to limit size of K, i.e., Y*weight*Y' <= Ub
+% weight = -eye(DIM_X); % weight of Y
+% Ub = -1000*eye(DIM_U); % upper bound
+% LMI2 = [
+%     Ub  Y
+%     Y'  weight
+% ];
[…]

### 2022-10-19 src/functions/Linearlization/@TPmodel/TPmodel.m

@@ -1,0 +1,23 @@
+classdef TPmodel
+    %TP type polytopic LPV model (transformed from LPV model)
+    
+    properties (Access = public)
+        val         % Core tensor (or "linear matrice")
+        len         % number of Core tensor (length(val))
+        index       % for indexing "mf_discrete"
+        mf_discrete % Discrete (because it's composed by "points") membership function (or "weighting functions") of Core tensor
+    end
+
+    properties (Access = private)
+        sizeO       % Origin size in hosvd result, just for indexing M.mf(). ex: size(S) = [9, 2, 9, 2, 4, 4] -> A.sizeO = size(S, 1 : 4)
+    end
+    
+    methods
+        function o = TPmodel()
+        end
+        
+        y = mf(o, x, ind) % membership function
+        o = getTPmodel(o, para) % Execute TPmodel transformation
+    end
+end
+

### 2022-10-19 src/functions/System/@Agent/Load.m

@@ -1,0 +1,17 @@
+function ag = Load(ag)
+%load old data
+
+if isfile([ag.PATH '.mat'])
+    data = load(ag.PATH);
+    if isfield(data, 'tr')
+        ag.tr = data.tr;
+    end
+    if isfield(data, 'K')
+        ag.K = data.K;
+    end
+    if isfield(data, 'KL')
+        ag.KL = data.KL;
+    end
+end
+
+end

### 2022-10-19 src/functions/System/@Agent/get_K_L.m

@@ -1,0 +1,28 @@
+function ag = get_K_L(ag, sys1, sys_aug1)
+I = eye(ag.DIM_F);
+
+if ag.EXE_LMI
+    disp('solving LMI ...')
+    [ag.K, ag.KL] = solveLMI10(sys_aug1.A, sys_aug1.B, sys_aug1.C, sys_aug1.E, sys_aug1.Q1, sys_aug1.Q2, sys_aug1.R, sys_aug1.rho);
+    
+%     norm(ag.KL)
+
+    ag.Save('K') 
+    ag.Save('KL') 
+end
+
+%% Fine tune of gain
+% feedback control law u_fb = K*x_b, where K = [Kp Ki Kd Ka Ks]
+
+gain = [-1 zeros(1, ag.sys_a.WINDOW-1)]; % since the optimal actuator fault gain Ka is -I so that it can offset the estimation of actuator fault f_a.
+ag.K(:, sys1.DIM_X + (1:ag.sys_a.WINDOW)) = gain;
+% ag.KL(4:6, :) = [1000 0 0; 0 100 0; 0 0 10];
+% ag.KL(7:9,:) = [1000 0 0; 0 100 0; 0 0 10];
+% ag.K(:, sys1.DIM_X + sys_a.WINDOW + (1:sys_s.WINDOW)) = zeros(1, sys_s.WINDOW);
+% I0 = diag(1.1.^(0:ag.DIM_F-1));
+% ...
+
+%% construt origin gain
+ag.K = kron(ag.K, I);
+ag.KL = kron(ag.KL, I);
+end

### 2022-10-19 src/functions/System/@SmoothModel/SmoothModel.m

@@ -1,0 +1,64 @@
+classdef SmoothModel
+    %Smooth model
+    % dx/dt = Ax + Ev
+    % 
+
+    properties
+        METHOD % method for construct A
+        WINDOW % window size  
+        dt % smapling time
+
+        A % system matrix
+        B % input matrix
+        C % mapping matrix
+        E % disturbance matrix
+
+        Q1 % tracking weighting matrix of state in H infinity performance index
+        Q2 % estimation weighting matrix of state in H infinity performance index
+        rho
+
+        DIM % dimension of fault signal
+        DIM_X % dimension of A
+
+        begin % begining index in the augment system
+        fault % the fault signal of this model
+    end
+    
+    methods
+        function obj = SmoothModel(WINDOW, DIM, dt, method)
+            obj.WINDOW = WINDOW;
+            obj.DIM = DIM;
+            obj.DIM_X = DIM*WINDOW;
+            obj.METHOD = method;
+
+            % A
+            if isempty(dt) % DT
+                obj = obj.getA_DT();
+            else          
+                obj.dt = dt;
+                obj = obj.getA_CT();
+            end
+            % C
+            C = [1 zeros(1, WINDOW-1)];
+            obj.C = kron(C, eye(obj.DIM));
+
+            obj.E = eye(obj.DIM_X);
+        end
+
+        function xb = set_real_signal(obj, xb, i)
+            %assign real fault signal
+            % Since the real fault signal is not produced from smooth model, we need reassign it.
+            j0 = obj.begin;
+            range = 1 : obj.DIM;
+            for j = 1 : obj.WINDOW-1
+                j1 = j0 + j*obj.DIM;
+                xb(j1+range, i+1) = xb(j1+range-obj.DIM, i); % Since Fa(i) = [fa(i), fa(i-1), fa(i-2), ...], so Fa(i+1) = ["new fa", fa(i), f(i-1)]
+            end
+            xb(j0+range, i+1) = obj.fault(:, i); % assign "new fa"
+        end
+
+        obj = getA_CT(obj); % construct continuos time smoothing model
+        obj = getA_DT(obj); % construct discrete time smoothing mode
+    end
+end
+

### 2022-10-19 src/functions/System/@Trajectory/Trajectory.m

@@ -1,0 +1,70 @@
+classdef Trajectory 
+%trajectory for a system
+
+    properties (Constant)
+
+    end   
+    
+    properties
+        dt  = 0.001 % time step
+        t % time
+        T   = 10 % final time
+        LEN
+        
+        % initial value
+        x0
+        xr0
+        xh0
+
+        IS_LINEAR = 1 % run fuzzy linear system or origin nonlinear system
+        IS_RK4 = 0 % run RK4 or Euler
+
+        % trajectory
+        x % system state
+        x2 % system state 2
+        r % reference trajectory
+        xr % reference model state
+        xh % estimated state
+
+        e % x - r
+        er % x - xr
+        eh % x - xh
+
+        u % control
+        v % distrubance
+
+        f % unknown signal
+    end
+    
+    methods
+        function o = Trajectory()
+            o.t = 0 : o.dt : o.T;
+        end
+        
+        function plot(o)
+            % figure('units','normalized','outerposition',[0 0 1 1])
+            % x(t), xr(t)
+            SIZE_X = size(o.x, 1);
+            for i = 1 : SIZE_X
+                figure
+                plot(o.t, o.x(i, :), o.t, o.xr(i, :))
+                title(['x_{' num2str(i) '}'])
+                legend("x", "x_r")
+                xlabel("t")
+                % ylim([-2 2])
+            end 
+            
+            % u(t)
+            % for j = 1 : o.SIZE_U
+            %     figure(i+j)
+            %     plot(o.t, o.u(j, :));
+            %     title(['u_{' num2str(j) '}'])
+            % end
+        end
+    end
+
+    methods (Access = private)
+        
+    end
+end
+

### 2022-10-19 src/functions/System/UAV/@UAV_CTMmodel/ref.m

@@ -1,0 +1,91 @@
+function r = ref(obj, i)
+%Generate reference and feedforward force
+% x     | vector | system state
+% t     | scalar | current time
+% r     | vector | tracking reference
+% F     | scalar | feedforward force
+
+amp_z   = 1; % 0.8
+
+amp     = 1; % 1
+freg    = 0.5;
+
+xd      = amp*sin(freg*t);
+dxd     = freg*amp*cos(freg*t);
+d2xd    = -freg^2*amp*sin(freg*t);
+d3xd    = -freg^3*amp*cos(freg*t);
+yd      = amp*cos(freg*t);
+dyd     = -freg*amp*sin(freg*t);
+d2yd    = -freg^2*amp*cos(freg*t);
+d3yd    = freg^3*amp*sin(freg*t);
+zd      = amp_z*t;
+dzd     = amp_z;
+d2zd    = 0;
+d3zd    = 0;
+psid    = 0;
+
+r = [
+    xd
+    dxd
+    yd
+    dyd
+    zd
+    dzd
+    0
+    0
+    0
+    0
+    psid
+    psid
+];
+
+%% method 1, 1.pdf, r = r(x, t)
+% ux = obj.c(1)*(x(1) - y(1)) + obj.c(2)*(x(2) - y(2));
+% uy = obj.c(3)*(x(3) - y(3)) + obj.c(4)*(x(4) - y(4));
+% uz = obj.c(5)*(x(5) - y(5)) + obj.c(6)*(x(6) - y(6));
+
+% method 1-1     
+% a = 1/(uz + obj.G);
+% phi_d = x(11);
+% r(7) = asin(obj.m/F*(ux*sin(x(11)) - uy*cos(x(11))));
+% r(7) = atan(a*(ux*sin(phi_d) - uy*cos(phi_d)));
+% r(9) = atan(a*(ux*cos(phi_d) + uy*sin(phi_d))/cos(x(7)));
+
+% method 1-3
+% y(7) = 0.4*atan(obj.m*(-uy)/(ux + uy + uz));
+% y(9) = 0.4*atan(ux/(uz + obj.G));
+
+% method 1-4 (李博's method)         
+% y(7) = atan(ux*sin(y(11))-1*uy*cos(y(11))); % roll
+% % y(8) = (y(7)-f1(7))/h;
[…]

### 2022-10-19 src/functions/System/UAV/@UAV_RM_L/UAV_RM_L.m

@@ -1,0 +1,115 @@
+classdef UAV_RM_L  
+% UAV model, Reference Model, Linearized (e.g., fuzzy, global linearized, tensor product, ...)
+% - System form
+%       - dx/dt = f(x) + g(x)*u + Ev
+% - The model is refered to 1.pdf
+%       - Euler angle (intrinsic rotation)
+%           - x(7)  : phi, x-axis, roll
+%           - x(9)  : theta, y-axis, pitch
+%           - x(11) : psi, z-axis, yaw
+%       - Typo in 1.pdf.
+%           - Coriolis term in dx(7)dt
+%               ((uav.Jy - uav.Jz)*x(9)*x(11) - uav.Kph*x(8))/uav.Jx
+%             need to be corrected to
+%               ((uav.Jy - uav.Jz)*x(10)*x(12) - uav.Kph*x(8))/uav.Jx
+%             dx(9)/dt, dx(11)/dt as well.
+%               - More detail
+%                   Quadrotor control: modeling, nonlinear control design, and simulation (2.19)
+%                   [https://www.diva-portal.org/smash/get/diva2:860649/FULLTEXT01.pdf]
+% - Reference model
+%       - dxr/dt = Ar*x + Br*r
+
+    properties (Constant)  
+        DIM_X = 12  % dimension of state
+        DIM_U = 4 % dimension of control
+    end   
+    
+    properties
+        % Designed parameters
+        rho = 10^(1);
+        Q   = 10^(-1)*diag([1, 0.001, 1.5, 0.002, 1, 0.001, 0.1, 0, 0.1, 0, 1, 0.001]); % correspond to x - xr
+        E   = 10^(-1)*diag([0 1 0 1 0 1 0 1 0 1 0 1]); % disturbance matrix
+
+        % Linearized system
+        A  % System matrix
+        B  % Input matrix
+        C  % output matrix
+        K  % Control gain matrix
+        L  % Observer gain matrix
+
+        % Reference model
+        Ar
+        Br
+        TIMES_AR = 10;
+
+        % trajectories (x, xr, t, dt, ...)
+        tr 
+
+        tau
+        
+        debug
+    end
+
+    properties (Access = protected)
+        % system parameters
+        m = 2, G = 9.81 %, l = 0.2, b = 2, d = 5, 
[…]

### 2022-10-19 src/functions/System/UAV/@UAV_TPmodel/trajectory.m

@@ -1,0 +1,100 @@
+function uav = trajectory(uav)
+%calculate trajectory
+
+dt          = uav.tr.dt;
+t           = 0 : dt : uav.tr.T;
+LEN         = length(t);
+
+xb          = zeros(2*uav.DIM_X, LEN);
+xb(:, 1)    = [uav.tr.x0; uav.tr.xr0];
+u           = zeros(uav.DIM_U, LEN);
+
+disp('Ploting trajectory ...')
+for i = 1 : LEN - 1       
+    if mod(i, 1/dt) == 0
+        disp(['t = ' num2str(i*dt)])
+    end
+    
+    k1 = RK4(uav, xb(:, i), i*dt);
+    if uav.tr.IS_RK4
+        k2 = RK4(uav, xb(:, i)+k1*dt/2, i*dt + dt/2);
+        k3 = RK4(uav, xb(:, i)+k2*dt/2, i*dt + dt/2);
+        k4 = RK4(uav, xb(:, i)+k3*dt, i*dt + dt); 
+
+        xb(:, i+1)  = xb(:, i)  + (k1 + 2*k2 + 2*k3 + k4)*dt/6;
+    end
+    xb(:, i+1)  = xb(:, i) +  k1*dt;
+
+    uav.tr.x(:, i+1) = xb(1 : uav.DIM_X, i+1);
+    uav.tr.xr(:, i+1) = xb(uav.DIM_X+1 : 2*uav.DIM_X, i+1);
+
+    % total_K = zeros(o.DIM_U, o.DIM_X);
+    % for j = 1 : fz.num
+    %     total_K = total_K + fz.mbfun(j, o.x(:, i+1))*uav.K{j};
+    % end
+    % o.u(:, i+1) = total_K*(o.x(:, i+1) - o.xr(:, i+1));
+end
+uav.tr.t = t;
+end
+
+%% Local function
+function k = RK4(uav, xb, t)
+    DIM_X   = uav.DIM_X;
+    DIM_U   = uav.DIM_U;
+    O       = zeros(DIM_X);
+    v       = @(t) 0.01*randn(DIM_X, 1) + 0; % disterbance
+    x       = xb(1 : DIM_X);
+    xr      = xb(DIM_X+1 : DIM_X*2);
+    [r, F]  = uav.r_F(x, t);
+    feed    = uav.g(x)*[F; 0; 0; 0]; % feedforward
[…]

### 2022-10-20 paper/paper.tex
Add +Show folder. Can Plot URTS Senario.

@@
 \ref{fig:sys}.
-The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$.
+The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$.
 The visual object recognition block provides distance information and object information through the analysis of sensor information.
@@
 Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$.
-At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets.
+At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupancy map and find targets.
 The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.

### 2022-10-20 src/URTS main script/Robot/@Robot/Load.m

@@ -6,13 +6,14 @@ if isfile([rb.PATH '.mat'])
     data = load(rb.PATH);
     
     if isfield(data, 'r_lr')
-        r_lr = rb.r_lr;
-    if isfield(data, 'INTERP_DENSITY')
-        INTERP_DENSITY = rb.INTERP_DENSITY;
+        rb.r_lr = data.r_lr;
     end
-    if isfield(data, 'rbtree')
-        rb.rbtree = data.rbtree;
-    end
+    % if isfield(data, 'INTERP_DENSITY')
+    %     INTERP_DENSITY = rb.INTERP_DENSITY;
+    % end
+    % if isfield(data, 'rbtree')
+    %     rb.rbtree = data.rbtree;
+    % end
     if isfield(data, 'qr')
         rb.qr = data.qr;
     end

### 2022-10-20 src/URTS main script/Robot/@Robot/Save.m

@@ -8,10 +8,10 @@ end
 switch whichVar
     case 'r_lr'
         r_lr = rb.r_lr;
-    case 'INTERP_DENSITY'
-        INTERP_DENSITY = rb.INTERP_DENSITY;
-    case 'rbtree'
-        rbtree = rb.rbtree;
+    % case 'INTERP_DENSITY'
+    %     INTERP_DENSITY = rb.INTERP_DENSITY;
+    % case 'rbtree'
+    %     rbtree = rb.rbtree;
     case 'qr'
         qr = rb.qr;
     case 'CoM'

### 2022-10-20 src/URTS main script/Robot/@Robot/trajectory.m

@@ -130,8 +130,7 @@ for i = startTime : LEN - 1
 
     % fext1 = externalForce(rb.rbtree, 'body11', [0 0 0 0 0 rb.tr.GRF{1}(i)], X');
     % tau = inverseDynamics(rb.rbtree, X', [], [], fext1);
-
-    d1(:, i) = d1(:, i) + 0.12*x.*x
+    d1(:, i) = d1(:, i) + 0.12*x(DIM_F + (1:DIM_F)).*x(DIM_F + (1:DIM_F));
     sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + H-Hh - d1(:, i));
     % sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) - d1(:, i));
     % sys_a.fault(:, i) = -eye(DIM_F)/M*(-d1(:, i));

### 2022-10-20 src/URTS main script/Robot/function/+Show/Map.m

@@ -1,0 +1,8 @@
+function Map()
+    % Show the occupy map of URTS
+    img = imread('data/map.png');     % Load a sample image
+    xImage = [6.5 6.5;-.5 -.5]; % The x data for the image corners
+    yImage = [-3 6; -3 6 ];   
+    zImage = [ 0 0; 0 0 ];
+    surf(xImage,yImage,zImage, 'CData', img, FaceColor='texturemap', EdgeColor='none');
+end

### 2022-10-20 src/functions/External/drone animation/drone_Animation.m

@@ -27,15 +27,13 @@ zp = zeros(1,length(to));
  fig1 = figure('pos', [0 50 800 600]);
  hg   = gca;
 
- 
- 
-
 plot3(r(1, :),r(2, :),r(3, :),'DisplayName', 'reference r(t)', 'LineWidth',1.5); % plot ref
 axis equal;
 grid on;
 %  view(68,50);
-view(150,20);
-xlim([-.5 10.5]); ylim([-.5 10.5]); zlim([-1.5 1.5]);
+view(-30,20);
+axisRange = [-.5 6.5; -4 6.5; 0 4];
+xlim(axisRange(1, :)); ylim(axisRange(2, :)); zlim(axisRange(3, :));
 xlabel('X(m)');
 ylabel('Y(m)');
 zlabel('Z(m)');
@@ -87,8 +85,8 @@ plotState = plot3(x(1:1),y(1:1),z(1:1), 'b:','DisplayName', 'state x(t)','LineWi
      translation = makehgtform('translate',...
                                [x(i) y(i) z(i)]);
      %set(combinedobject, 'matrix',translation);
-     rotation1 = makehgtform('xrotate',(pi/180)*(roll(i)));
-     rotation2 = makehgtform('yrotate',(pi/180)*(pitch(i)));
+     rotation1 = makehgtform('xrotate',roll(i));
+     rotation2 = makehgtform('yrotate',pitch(i));
      rotation3 = makehgtform('zrotate',yaw(i));
      %scaling = makehgtform('scale',1-i/20);
      set(combinedobject,'matrix',...
@@ -104,7 +102,7 @@ plotState = plot3(x(1:1),y(1:1),z(1:1), 'b:','DisplayName', 'state x(t)','LineWi
  
  disp('making .avi ...')
 %% save frame to .avi
-writerObj = VideoWriter('myVideo.avi');
+writerObj = VideoWriter('data/myVideo.avi');
 writerObj.FrameRate = fps;
 open(writerObj);
  for i = 1 : length(F)

### 2022-10-20 src/functions/System/@Agent/Load.m

@@ -1,6 +1,5 @@
 function ag = Load(ag)
 %load old data
-
 if isfile([ag.PATH '.mat'])
     data = load(ag.PATH);
     if isfield(data, 'tr')

### 2022-10-26 paper/paper.tex
team1 -> teami

@@
 \ref{fig:SR_area}.
-To simplify the description, we will focus on the UAV and robot in $1$st team.
-Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$.
-At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupancy map and find targets.
+To simplify the description, we will focus on the UAV and robot in $i$th team.
+Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | j=1,2,...,5 \}$.
+At the beginning, the agents in $team_i$ are assigned the search tasks of $area_i$ to build the occupancy map and find targets.
 The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
 \ref{fig:S_task}.
-Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$.
+Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}$.
 Suppose a target is found after a while as shown in Fig.
@@
 The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one.
-If the ground station assigns $\alpha_{1,5}$ and $\alpha_{2,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,5},T_2),(\alpha_{2,2},T_3) \})\cup\{ (\alpha_{1,5},T_6),(\alpha_{2,2},T_6) \}$.
+If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_2),(\alpha_{i+1,2},T_3) \})\cup\{ (\alpha_{i,5},T_6),(\alpha_{i+1,2},T_6) \}$.
 Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining.
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $i$th team at the begining.
 The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure).
@@
 
-To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{1,5},T_6)$ and $(\alpha_{1,1}, T_1)$ as example.
-For the robot $\alpha_{1,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$.
+To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_6)$ and $(\alpha_{i,1}, T_1)$ as example.
+For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$.
 With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
@@
 
-For the UAV $\alpha_{1,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
+For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
@@
 
-The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ are given as follow.
+The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{i,1}$ and the robot $\alpha_{i,2}$ are given as follow.
 
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$}
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, control}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{1,2}$.}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{i,2}$}%
     \label{fig:robot, control}

### 2022-10-27 paper/paper.tex
Add couple term to paper. Finish the uav+robots animation.

@@
 Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots.
-Hence, the $i$th agent in the $j$th team is denoted as $\alpha_{j,i}$, where $i=1,2,...,N_A$ and $j=1,2,...,N_T$.
-The UAVs are chosed as the first agents in each team, i.e., $\alpha_{1,j}$.
+Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$.
+The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1}$.
 Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making.
@@
 \begin{enumerate}
-    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9448458}.
+    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
     \item For agent, there exists cyber-attack on communication network between agents and ground station.
@@
 \end{enumerate}
+Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
+    \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
+\end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
+    \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
+\end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
+
 Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
@@
 
-\textit{agents:}\begin{enumerate}
+\textit{Agents:}\begin{enumerate}
     \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
@@
 
-\textit{robots:} \begin{enumerate}
+\textit{Robots:} \begin{enumerate}
     \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
@@
 \ref{fig:UAV, state}.
-The estimation of actuator fault $f_1(t)$ is shown in Fig.
-\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=10\sin(3t)$.
+The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig.
+\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
+Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = 0.1diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
 The estimation of sensor fault $f_2(t)$ is shown in Fig.
@@
 
-\textit{robot:}
-The trajectories of reference, state and estimated state are shown in Fig.
-\ref{fig:robot, state}.
+\textit{Robot:}
+The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}.
+The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig.
+\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [\sin(3t),...,\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
+Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = 0.01diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
+
 The estimation of actuator fault $f_1(t)$ is shown in Fig.

### 2022-10-27 src/URTS main script/Robot/RobotSimulation.m

@@ -1,3 +1,8 @@
+% Search task simuation
+%
+% Definition
+% - transformation : homogeneous transformation
+%  
 clc; clear; close all
 
 rb = Robot();
@@ -20,42 +25,8 @@ fps = fps/factor;
 config = r(1:factor:length(x), :); % For simulatiom speed, compress the array by a factor
 config = cat(2, config(:, 1:2:11), config(:, 2:2:12)); % To match the rigidbodytree config format, 1,2,...,12 -> 1,3,...11,2,4,...,12
 
-%% Animation
-% for i = 1 : length(config)
-%     disp(i)
-%     show(robot, config(i, :));
-%     F{i} = getframe(gcf);
-%     drawnow
-% end
-
 %% State
-isLeftFoot = true;
-index = 1;
-supportFeetTransform = eul2tform([0 0 0]);
-% supportFeetTransform = eul2tform([-pi/2 0 0]);
-numberOfFrameInHalf = rb.INTERP_DENSITY/factor; % The number of "animation frame" in a half walking cycle
-supportFeetChanged = 1 + numberOfFrameInHalf/2; 
-transform{index} = supportFeetTransform;
-for i = 2 : size(config, 1)
-    if i == supportFeetChanged + 1      
-        if isLeftFoot
-            tf = getTransform(robot, config(i, :), 'body12', 'body11'); % Left foot is the supporting foot
-        else
-            tf = getTransform(robot, config(i, :), 'body11', 'body12'); % Right foot is the supporting foot
-        end
-
-        % Update
-        supportFeetChanged = supportFeetChanged + numberOfFrameInHalf;
-        supportFeetTransform = supportFeetTransform*eul2tform([0 -pi/2 -pi/2])*tf/eul2tform([0 -pi/2 -pi/2]);
-        index = index + 1;
-        isLeftFoot = ~isLeftFoot;
-
-        transform{index} = supportFeetTransform*eul2tform([0 -pi/2 -pi/2]);
-
-        % show(robot, config(i, :));
-        % F{index-1} = getframe(gcf);
-    end
-end
+transform = Config2LRSupportFeetTransform(robot, config, rb.INTERP_DENSITY/factor);
 
 %% Reference
 len = length(rb.r_lr);
@@ -68,9 +39,17 @@ for i = 1 : len
 end
 
 %% Plot
+% Animation
[…]

### 2022-10-27 src/URTS main script/Robot/function/+Show/Map.m

@@ -6,5 +6,5 @@ function Map(xLimit, yLimit)
     % xImage = [6.5 6.5;-.5 -.5]; % The x data for the image corners
     % yImage = [-3 6; -3 6 ];   
     zImage = [ 0 0; 0 0 ];
-    surf(xImage,yImage,zImage, 'CData', img, FaceColor='texturemap', EdgeColor='none');
+    surf(xImage, yImage, zImage, 'CData', img, FaceColor='texturemap', EdgeColor='k', DisplayName='map', MarkerEdgeColor='k');
 end

### 2022-10-27 src/URTS main script/Robot/function/Config2LRSupportFeetTransform.m

@@ -1,0 +1,38 @@
+function transform = Config2LRSupportFeetTransform (robot, config, numberOfFrameInHalf)
+    % Config to left and right support feet homogeneous tansformation
+    %
+    % Input
+    %   - robot | rigidbodytree         : A N-DOF biped robot
+    %   - config | M-by-N matrix        : Configuration path of the robot
+    %   - numberOfFrameInHalf | int     : The number of "animation frame" in a half walking cycle
+    % Output
+    %   - transform | cell array        : Left and right support feet homogeneous tansformation
+
+    isLeftFoot = true; % Left foot is support feet at begining
+    index = 1;
+    supportFeetChanged = 1 + numberOfFrameInHalf/2; % The moment of support feet changed
+    supportFeetTransform = trvec2tform([6.75 .75 0])*eul2tform([0 0 0]); % Initial transformation of support feet
+    initFrame2SupportFrame = eul2tform([pi/2 0 0])*eul2tform([0 -pi/2 -pi/2]);
+    % initFrame2SupportFrame = eul2tform([0 -pi/2 -pi/2])
+    transform{index} = supportFeetTransform; % Set first transformation
+    for i = 2 : size(config, 1)
+        if i == supportFeetChanged + 1 % Calculate support feet transformation only   
+            if isLeftFoot % Left foot is the supporting foot
+                tf = getTransform(robot, config(i, :), 'body12', 'body11'); % Find right feet transformation
+            else
+                tf = getTransform(robot, config(i, :), 'body11', 'body12');
+            end
+
+            % Update
+            supportFeetChanged = supportFeetChanged + numberOfFrameInHalf; % Swap left and right feet
+            supportFeetTransform = supportFeetTransform*initFrame2SupportFrame*tf/initFrame2SupportFrame;
+            index = index + 1;
+            isLeftFoot = ~isLeftFoot;
+
+            transform{index} = supportFeetTransform*initFrame2SupportFrame;
+
+            % show(robot, config(i, :));
+            % F{index-1} = getframe(gcf);
+        end
+    end
+end

### 2022-11-01 src/URTS main script/Robot/@Robot/trajectory.m
Auto export figures as .png

@@ -85,7 +85,6 @@ for i = startTime : LEN - 1
     end
     if isnan(xb(:, i))
         disp(['traj has NaN, t = ' num2str(i*dt)])
-        % rb.tr.LEN = i;
         break
     end
     if norm(xb(:, i)) == Inf
@@ -130,8 +129,8 @@ for i = startTime : LEN - 1
 
     % fext1 = externalForce(rb.rbtree, 'body11', [0 0 0 0 0 rb.tr.GRF{1}(i)], X');
     % tau = inverseDynamics(rb.rbtree, X', [], [], fext1);
-    % d1(:, i) = d1(:, i) + 0.12*x(DIM_F + (1:DIM_F)).*x(DIM_F + (1:DIM_F));
-    sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + H-Hh - d1(:, i));
+    d1(:, i) = d1(:, i) + 1*x(DIM_F + (1:DIM_F)).*x(DIM_F + (1:DIM_F)); % Couple terms
+    sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + H-Hh - d1(:, i)); % Total fault
     % sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) - d1(:, i));
     % sys_a.fault(:, i) = -eye(DIM_F)/M*(-d1(:, i));
     % f = tau;

### 2022-11-01 src/URTS main script/Robot/function/+Show/PlotTC.m

@@ -1,7 +1,7 @@
 function PlotTC(rb)
     % Plot tracking control result
     %
-    % There are three figures:
+    % There are 4 figures:
     %   - Trajectory of state, estimated state, reference
     %   - Estimation of actuator and sensor fault
     %   - Control effort
@@ -9,76 +9,81 @@ function PlotTC(rb)
     %% state, estimated state, reference
     fig = figure;
     DIM = rb.DIM_F;
-    % div = divisors(DIM);
-    % i = ceil((length(div))/2);
-    % Layout = tiledlayout(DIM/div(i), div(i));
-    Layout = tiledlayout(DIM/2, 2);
-    Layout.TileSpacing = 'tight';
-    Layout.Padding = 'tight';
-    % r = rb.tr.r{1};
-    r = rb.qr;
+    
+    Layout = GetTiledlayout(DIM);
+    r = rb.tr.r{1};
     for i = 1 : DIM % position
-        ax = nexttile;
+        nexttile
         hold on
+
         index = DIM + i;
-        % plot(rb.tr.t, rb.tr.x(index, :)+r(i, :), 'DisplayName', 'state', 'LineWidth', 2)
-        % plot(rb.tr.t, rb.tr.xh(index, :)+r(i, :), 'DisplayName', 'estimated', 'LineWidth', 2)
-        % plot(rb.tr.t, r(i, :), 'DisplayName', 'reference', 'LineWidth', 2)
         plot(rb.tr.t, rb.tr.x(index, :)+r(i, :))
         plot(rb.tr.t, rb.tr.xh(index, :)+r(i, :))
         plot(rb.tr.t, r(i, :))
 
         grid on
         ylabel(['$q_{' num2str(i) '} (rad)$'], 'Interpreter','latex')      
-        legend('Interpreter','latex','Location','southeast')
     end
     xlabel(Layout,'t (sec)')
-    lg  = legend('state', 'estimated', 'reference', NumColumns=3); 
+    lg  = legend('state', 'estimated state', 'reference', NumColumns=3); 
     lg.Layout.Tile = 'north';
     % ylabel(Layout, 'rad')
-%     legend(Layout, 'Interpreter','latex','Location','southeast')
 
-    
+    SaveFig(fig)
+
     %% Fa and Fs
[…]

### 2022-11-01 paper/paper.tex
Auto export figures as .png
robot and uav simulation figures ok. rewrite Abstract in paper. Move some functions to become agent's method

@@
 The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them.
-Then we focus on two issues, local motion planning and tracking control.
-We discuss the methods of local motion planning for UAV flying behavior and robot walking behavior, and then give the control methods for UAV and robot.
-The relationship between the two issues, the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics model of UAV and robot into a unified agent model, a design method for a $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agent in URTS.
+The task allocation and path planning problems are first investigated and stated.
+Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and the tracking control problem for UAV and robot.
+The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail.
+By converting the dynamics model of UAV and robot into a unified agent model, a design method for an $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation.
-The design of this $H_\infty$ observer-based FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
-Finally, with the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved.
-Simulations are given ...
+Then, the design of the $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
+With the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved.
+Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed tracking control method.
 \end{abstract}
@@
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig.
-\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
-Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = 0.1diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
+\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
+Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
 The estimation of sensor fault $f_2(t)$ is shown in Fig.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.42]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
+    \includegraphics[scale=.42]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of snesor fault of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.42]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.42]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, control}
@@
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig.
-\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [\sin(3t),...,\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
-Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = 0.01diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
+\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
+Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
 
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.42]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
+    \includegraphics[scale=.42]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.42]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The control effort of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.42]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{i,2}$}%
     \label{fig:robot, control}

### 2022-11-01 src/URTS main script/Robot/@Robot/Robot.m

@@ -28,6 +28,7 @@ classdef Robot < Agent
         ] % inertia of CoM1~12
 
         INTERP_DENSITY = 1500 % interp density of zmp
+        UNIT = {'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad', 'rad'}
     end
     properties
         %% rigidbodytree
@@ -101,23 +102,6 @@ classdef Robot < Agent
         function y = H(rb, x, dx)
             CG = rb.rbtree.velocityProduct(x', dx') + rb.rbtree.gravityTorque(x');
             y = CG';
-        end
-
-        function y = f_aug(rb, t, xb)
-            DIM_X3 = rb.sys_aug.DIM_X;
-            x = xb(1 : DIM_X3);
-            xh = xb(DIM_X3 + (1:DIM_X3));
-            u = rb.u_PID(xh);
-            y = [
-                rb.sys_aug.A*x + rb.sys_aug.B*u
-                rb.sys_aug.A*xh + rb.sys_aug.B*u - rb.KL*rb.sys_aug.C*(x-xh)
-            ];
-        end
-
-        function y = u_PID(rb, xh)
-            % range = 1 : rb.DIM_F*3; 
-            % y = rb.K(:, range)*xh(range); % without unknown sigal info
-            y = rb.K*xh; 
         end
 
         rb = get_rbtree(rb) % rigidBodyTree setting

### 2022-11-01 src/URTS main script/Robot/@Robot/trajectory.m

@@ -1,8 +1,6 @@
 function rb = trajectory(rb)
 %calculate trajectory
 
-sys_a       = rb.sys_a;
-sys_s       = rb.sys_s;
 dt          = rb.tr.dt;
 t           = rb.tr.t;
 LEN         = rb.tr.LEN;
@@ -13,16 +11,16 @@ startTime   = 3; % For calculate ddr(t), start at 3-rd step (k = 3)
 
 %% set disturbance
 %-1 actuator fault
-d1 = 1*repmat(10*sin(3*t), sys_a.DIM, 1);
-sys_a.fault = zeros(sys_a.DIM, LEN);
+d1 = 1*repmat(10*sin(3*t), rb.sys_a.DIM, 1);
+rb.sys_a.fault = zeros(rb.sys_a.DIM, LEN);
 
 %-2 sensor fault
 % square wave
-% sys_s.fault = 0.1*ones(sys_s.DIM, rb.tr.LEN);
+% rb.sys_s.fault = 0.1*ones(rb.sys_s.DIM, rb.tr.LEN);
 % b = [0.1 -0.05 0.05]; n = length(b)+1;
 % a = round(linspace(1,rb.tr.LEN,n));
 % for i = 1 : n-1
-%     sys_s.fault(:, a(i):a(i+1)) = b(i);
+%     rb.sys_s.fault(:, a(i):a(i+1)) = b(i);
 % end
 
 % smoothed square wave
@@ -30,15 +28,15 @@ t_ = linspace(0, rb.tr.T, 100);
 x_ = .1*square(.5*t_, 60);
 fx = fit(t_', x_', 'SmoothingSpline');
 x3 = feval(fx, rb.tr.t)';
-sys_s.fault = repmat(x3, sys_s.DIM, 1);
+rb.sys_s.fault = repmat(x3, rb.sys_s.DIM, 1);
 
 % sin wave
 % x = 1*sin(1*rb.tr.t);
 % x = x + sqrt(.01)*randn(1, rb.tr.LEN);
-% sys_s.fault    = repmat(x, sys_s.DIM, 1);
+% rb.sys_s.fault    = repmat(x, rb.sys_s.DIM, 1);
 
 % constant 
-% rb.tr.f2    = 0.5*ones(sys_s.DIM, rb.tr.LEN);
+% rb.tr.f2    = 0.5*ones(rb.sys_s.DIM, rb.tr.LEN);
 
 %% Construct r(t)
 % Method 1
[…]

### 2022-11-01 src/functions/System/@Agent/Agent.m

@@ -35,13 +35,34 @@ classdef Agent
     methods
         function ag = AGENT()
         end
-        
+
+        function y = u_PID(ag, xh)
+            % range = 1 : rb.DIM_F*3; 
+            % y = rb.K(:, range)*xh(range); % without unknown sigal info
+            y = ag.K*xh; 
+        end
+
+        function y = f_aug(rb, t, xb)
+            DIM_X3 = rb.sys_aug.DIM_X;
+            x = xb(1 : DIM_X3);
+            xh = xb(DIM_X3 + (1:DIM_X3));
+            u = rb.u_PID(xh);
+            y = [
+                rb.sys_aug.A*x + rb.sys_aug.B*u
+                rb.sys_aug.A*xh + rb.sys_aug.B*u - rb.KL*rb.sys_aug.C*(x-xh)
+            ];
+        end
+
         y = M(ag, x) % inertial matrix
         y = H(ag, x, dx) % non-inertial matrix
         ag = get_K_L(ag, sys1, sys_aug1) % solve LMI to obtain control gain K and observer gain L
         ag = trajectory(ag) % get trajectory (x, u, ...)
         is_saved = Save(ag, whichVar) % save properties
         ag = Load(ag) % load properties
+        PlotTC(ag) % Plot the results of tracking control
+        [ag, xb] = CalculateNextState(ag, xb, d1, r, dr, ddr, i)
+        PlotFault(ag, TITLE)
+
     end
 end
 %#ok<*PROPLC>

### 2022-11-01 src/functions/System/@Agent/CalculateNextState.m

@@ -1,0 +1,61 @@
+%
+% input:
+%   - xb    | matrix    : augment state
+%   - d1    | matrix    : disturbance on acuator
+%   - r     | scaler    : reference
+%   - dr    | scaler    : first difference of reference
+%   - ddr   | scaler    : second difference of  reference
+%   - i     | scaler    : time step
+
+function [ag, xb] = CalculateNextState(ag, xb, d1, r, dr, ddr, i)
+    DIM_X3 = ag.sys_aug.DIM_X;
+    DIM_F = ag.DIM_F;
+
+    %% extract x, xh, X, dX form xb
+    x       = xb(1 : DIM_X3, i);
+    xh      = xb(DIM_X3 + (1:DIM_X3), i);
+    X       = x(DIM_F + (1:DIM_F)); % position
+    dX      = x(2*DIM_F + (1:DIM_F)); % velocity
+    Xh      = xh(DIM_F + (1:DIM_F));
+    dXh     = xh(2*DIM_F + (1:DIM_F));
+
+    %% fault signal
+    % feedback linearized term: Mh(), Hh(). By testing, using feedforward only ( Mh(r(t)) ) is more stable then feedback + feedforward ( Mh(xh(t)+r(t)) ).
+    u = ag.u_PID(xh); % PID control
+
+    M = ag.M(X+r); 
+    Mh = ag.M(r); % feedforward compensation
+    % Mh = ag.M(Xh+r); 
+    % Mh = 0;
+    
+    H = ag.H(X+r, dX+dr);
+    Hh = ag.H(r, dr); % feedforward compensation
+    % Hh = ag.H(Xh+r, dXh+dr); % feedback compensation
+    % Hh = 0;
+
+    d1(:, i) = d1(:, i) + 1*x(DIM_F + (1:DIM_F)).*x(DIM_F + (1:DIM_F)); % Couple terms
+    % fext1 = externalForce(ag.rbtree, 'body11', [0 0 0 0 0 ag.tr.GRF{1}(i)], X');
+    % tau = inverseDynamics(ag.rbtree, X', [], [], fext1);
+    ag.sys_a.fault(:, i) = -eye(DIM_F)/M*((M-Mh)*(ddr + u) + H-Hh - d1(:, i)); % Total fault
[…]

### 2022-11-01 src/functions/System/@Agent/PlotTC.m

@@ -1,0 +1,53 @@
+function PlotTC(ag)
+    % Plot tracking control result
+    %
+    % There are 4 figures:
+    %   - Trajectory of state, estimated state, reference
+    %   - Estimation of actuator and sensor fault
+    %   - Control effort
+
+    %% state, estimated state, reference
+    fig = figure;
+    DIM = ag.DIM_F;
+    
+    Layout = GetTiledlayout(DIM);
+    r = ag.tr.r{1};
+    for i = 1 : DIM % position
+        nexttile
+        hold on
+        grid on
+
+        index = DIM + i;
+        plot(ag.tr.t, ag.tr.x(index, :)+r(i, :))
+        plot(ag.tr.t, ag.tr.xh(index, :)+r(i, :))
+        plot(ag.tr.t, r(i, :))
+
+        ylabel(['$x_{' num2str(i) '} (' ag.UNIT{i} ')$'], 'Interpreter','latex')      
+    end
+    xlabel(Layout,'t (sec)')
+    lg  = legend('state', 'estimated state', 'reference', NumColumns=3); 
+    lg.Layout.Tile = 'north';
+    % ylabel(Layout, 'rad')
+
+    SaveFig(fig)
+
+    %% Fa and Fs
+    ag.PlotFault('1')
+    ag.PlotFault('2')
+    
+    %% control u(t)
+    fig = figure;
+    DIM = size(ag.tr.u, 1);
+    
+    hold on
+    grid on
+    for i = 1 : DIM
+        index = i;
+        plot(ag.tr.t, ag.tr.u(index, :), 'DisplayName', ['$u_{' num2str(i) '}$'], 'LineWidth', 1)    
+    end
+    xlabel('t (sec)')
+    ylabel('$u (N\cdot m)$', 'Interpreter','latex')
+    legend('Interpreter','latex','Location','southeast')
+
+    SaveFig(fig)
+end

### 2022-11-02 paper/paper.tex
Refactor. Add sim result and some description of figures to paper

@@
 In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy.
-First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig.
+First, a S\&R area divided into $N_T$ areas, $area_i,i=1,2,...,N_T$, is given as shown in Fig.
 \ref{fig:SR_area}.
 To simplify the description, we will focus on the UAV and robot in $i$th team.
-Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | j=1,2,...,5 \}$.
+Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,5 \}$.
 At the beginning, the agents in $team_i$ are assigned the search tasks of $area_i$ to build the occupancy map and find targets.
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
+    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$}%
     \label{fig:SR_area}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $i$th team at the begining.
+    \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in $i$th team at the begining.
 The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure).
-For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths.
+For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The path planning tasks.}%
+    \includegraphics[scale=.6]{fig/robot_PP.png}\caption{The path planning result of robot using RRT algorithm. The block polygons represent the obstacle space $\mathcal{C}_{obs}$.}%
     \label{fig:R_task}
@@
     \centering
-    \includegraphics[scale=.42]{fig/1.pdf}\caption{The top view of result of local motion planning of flying.}%
+    \includegraphics[scale=.57]{fig/uav_LMP.png}\caption{The result of local motion planning of UAV flying.}%
     \label{sim:flying}
@@
     \centering
-    \includegraphics[scale=.42]{fig/untitled.png}\caption{The top view of result of local motion planning of walking.}%
+    \includegraphics[scale=.57]{fig/robot_LMP.png}\caption{The top view of result of local motion planning of robot walking.
+The joint path, i.e., reference path $r[k]$ will be obtained by solving IK with CoM, left foothold and right foothold path.}
     \label{sim:walking}
@@
     \centering
-    \includegraphics[scale=.42]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
+    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
     \label{fig:UAV, control}
@@
     \centering
-    \includegraphics[scale=.42]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.42]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
+    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.42]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.42]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{i,2}$}%
     \label{fig:robot, control}
@@
 In Fig.
-\ref{fig:UAV, state} and Fig.
-\ref{fig:robot, state}, the tracking and estimation errors have reached a steady state at x seconds.
-The transient responses that occur later are caused from fault signals, especially the sensor fault.
+\ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $1$ second.
+There is a brief jitter when the UAV turns, but it returns quickly to steady state.
+In Fig.
+\ref{fig:robot, state} , the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the fault signals.
+In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbances and feedforward errors, can be effectively estimated.
+However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds.
+In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
+% The transient responses that occur later are caused from fault signals, especially the sensor fault.
 This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{e}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.
-In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbance and feedforward errors, can be effectively estimated.
-In Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds.
-In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
 

### 2022-11-02 src/URTS main script/UAV/@UAV_AGENTmodel/SetPath.m

@@ -1,0 +1,47 @@
+%Construct path and smoothed path
+%
+% path          : Some waypoints
+% smoothed path : The reference r(t) = [xd, yd, zd, phid]^T
+
+function uav = SetPath(uav)
+    %-1 circle up
+    % uav.qr  = zeros(4, uav.tr.LEN);
+    % amp_z   = 0.9;
+    % amp     = 0.8;
+    % freg    = 1;
+    % for i = 1 : uav.tr.LEN - 1
+    %     uav.qr(:, i) = [
+    %         amp*sin(freg*uav.tr.t(i))
+    %         amp*cos(freg*uav.tr.t(i))
+    %         amp_z*uav.tr.t(i) + 1
+    %         0
+    %     ];
+    % end
+
+    %-2 search task
+    r1 = [
+        0 0 0 0 .5          .5 .5 1 1 1        1.5 1.5 1.5 2 2     2
+        0 .5 1 2 2          1 0 0 1 2          2 1 0 0 1           2 
+        0 .025 .05 .05 .1   .1 .1 .2 .2 .2     .3 .3 .3 .3 .3      .3
+    ]*5;
+    r1(1:2, :) = r1(1:2, :)/2;
+    r1(3, :) = r1(3, :) + 2;
+
+    len1 = length(r1);
+    t1 = linspace(0,1,len1);
+    density = 5;
+    len2 = (len1-1)*density+1;
+    t2 = linspace(0,1,len2);
+    r2 = zeros(3, len2);
+    len3 = uav.tr.LEN;
+    t3 = linspace(0,1,len3);
+    r3 = zeros(3, len3);
+    for i = 1 : 3
+        r2(i, :) = interp1(t1, r1(i, :), t2);
+        f2{i} = fit(t2', r2(i, :)', 'SmoothingSpline');
+        r3(i, :) = feval(f2{i}, t3)';
+    end
+    uav.sigma = r1;
+    uav.qr = cat(1, r3, zeros(1, length(r3))); % phi = 0
+    uav.Save('qr');
+end

### 2022-11-02 src/functions/System/@Agent/PlotTC.m

@@ -47,7 +47,7 @@ function PlotTC(ag)
     end
     xlabel('t (sec)')
     ylabel('$u (N\cdot m)$', 'Interpreter','latex')
-    legend('Interpreter','latex','Location','southeast')
+    legend(Interpreter='latex',Location='southeast')
 
     SaveFig(fig)
 end

### 2022-11-02 paper/paper.tex
UAV simulation, parameter adjustment. Add actual control input figure

@@
         \begin{bmatrix}
-            f \\ \tau
+            F \\ \tau
         \end{bmatrix}&=\begin{bmatrix}
@@
     0 & 0 & K_{\tau_z}
-\end{bmatrix}$, $f =\begin{bmatrix}
+\end{bmatrix}$, $F =\begin{bmatrix}
     f_x \\ f_y \\ f_z
@@
 % where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
-$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $f$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame, and $F$ is the total thrust.
+$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $F$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
 This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction.

### 2022-11-02 src/URTS main script/UAV/@UAV_AGENTmodel/UAV_AGENTmodel.m

@@ -26,6 +26,7 @@ classdef UAV_AGENTmodel < Agent
     methods
         function uav = UAV_AGENTmodel()
             uav@Agent();
+            uav.FILE_NAME = mfilename;
             uav.PATH  = ['data/' mfilename]; % path of saved data
             uav = uav.Load(); % load old data
             uav.DIM_F = 6;
@@ -52,7 +53,7 @@ classdef UAV_AGENTmodel < Agent
             % In practice, r([1 2 3], i) get from path planning algorithm.
             % UAV no spin, r(6, i) is zeros. r([4 5], i) is obtain from r([1 2 3 6], i)
 
-            ddr = r4*[1 -2 1]'/dt^2;
+            ddr = 0*r4*[1 -2 1]'/dt^2; % This term may have numerical differential error
             u = uav.u_PID(xh);
             c = uav.m*eye(3)*ddr + [0; 0; -uav.m*uav.G] + uav.Df*xh(2*uav.DIM_F + (1:3));%+u(1:3);
             % c = u(1:3);

### 2022-11-02 src/URTS main script/UAV/function/Plot.m

@@ -1,20 +1,0 @@
-function Plot(t, x, xh, j, DIM, TITLE)
-figure
-% obtain a suitable size
-div = divisors(DIM);
-i = ceil((length(div))/2);
-Layout = tiledlayout(DIM/div(i), div(i));
-for i = 1 : DIM
-    nexttile
-    hold on
-    index = j + i;
-    plot(t, x(index, :), 'Displayname', 'state', 'LineWidth', 3)
-    plot(t, xh(index, :), 'DisplayName', 'estimated', 'LineWidth', 3)
-%     plot(t, x(index, :)-xh(index, :), 'Displayname', 'error', 'LineWidth', 3)
-    grid on
-    legend
-    % ylim([-1 1])
-    title(['v' TITLE '_' num2str(i)])
-end
-title(Layout, ['F' TITLE])
-end

### 2022-11-02 src/functions/System/@Agent/Agent.m

@@ -7,6 +7,7 @@ classdef Agent
 
     properties (Access = protected)
         PATH % path of saved data
+        FILE_NAME % file name of class
     end
 
     properties
@@ -14,10 +15,10 @@ classdef Agent
         % INTERP_DENSITY = 2500 % interp density of zmp
 
         %% Control design
-        sys
-        sys_a
-        sys_s
-        sys_aug
+        sys % agent system
+        sys_a % actuator smoothed model
+        sys_s % sensor smoothed model
+        sys_aug % augment system
 
         K  % Control gain matrix
         KL  % Observer gain matrix
@@ -42,7 +43,7 @@ classdef Agent
             y = ag.K*xh; 
         end
 
-        function y = f_aug(rb, t, xb)
+        function y = f_aug(rb, t, xb) % A_bar*x_bar
             DIM_X3 = rb.sys_aug.DIM_X;
             x = xb(1 : DIM_X3);
             xh = xb(DIM_X3 + (1:DIM_X3));
@@ -60,8 +61,8 @@ classdef Agent
         is_saved = Save(ag, whichVar) % save properties
         ag = Load(ag) % load properties
         PlotTC(ag) % Plot the results of tracking control
-        [ag, xb] = CalculateNextState(ag, xb, d1, r, dr, ddr, i)
-        PlotFault(ag, TITLE)
+        [ag, xb] = CalculateNextState(ag, xb, d1, r, dr, ddr, i) % Calculate xb(i+1). Temporary method, the coupling between subclass (UAV_AGENTmodel and Robot) must be reduced
+        PlotFault(ag, TITLE) % Plot fault estimation
 
     end
 end

### 2022-11-02 paper/paper.tex
paper, figure descriptions.

@@
 Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
-    \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
+    \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
 \end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
-    \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
+    \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
 \end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
@@
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig.
-\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}f_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
-Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $f_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
+\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
+Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $h_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
 The estimation of sensor fault $f_2(t)$ is shown in Fig.
@@
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig.
-\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}f_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
-Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $f_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
+\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
+Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $h_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
 
@@
 In Fig.
-\ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $1$ second.
-There is a brief jitter when the UAV turns, but it returns quickly to steady state.
+\ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $2$ second.
+There is a brief jitter when the sensor fault signal changes drastically, but it returns quickly to steady state.
 In Fig.
-\ref{fig:robot, state} , the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the fault signals.
+\ref{fig:robot, state}, the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the influence of fault signals.
 In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbances and feedforward errors, can be effectively estimated.
-However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change, but returns to a steady state after about $3$ seconds.
-In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control effort has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control, and then maintains the sine wave shape to offset the estimated actuator fault value.
+However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change and returns to a steady state after about $3$ seconds.
+In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control efforts has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control.
+After that, they maintain the sine wave shape to offset the estimated actuator fault value.
+Besides, it can be seen that the total force $F$ remains constant against gravity in Fig \ref{fig:UAV, control}.
 % The transient responses that occur later are caused from fault signals, especially the sensor fault.
-This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{e}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.
+This can be inferred from the dynamic of the estimation error (\ref{eq:e_tilde}) because the value of the sensor fault affects the value of the estimation error over time $\dot{\tilde{e}}$ not only from the term $\bar{A}$ but also from the term $L\bar{C}$.
 

### 2022-11-02 paper/paper.tex
Add citations. Article organization in introduction. Add online resource simulation description.

@@
 The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics model of UAV and robot into a unified agent model, a design method for an $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
+By converting the dynamics model of UAV and robot into a unified agent model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation.
-Then, the design of the $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
 With the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved.
@@
 It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans.
-Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, and surveillance, etc (cite:UV).
+Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, and surveillance, etc \cite{9700861}.
 Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
-However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents.
-In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued (cite:HMAS).
+However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents \cite{chen2019control}.
+In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued \cite{9371292}.
 Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.
@@
 To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control.
-Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision-making content through the actuator.
-To limit the scope of this paper, we focus on decision-making and control only.
+Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision through the actuator.
+To limit the scope of this paper, we focus on decision-making and control problem only.
 The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
-Task allocation is to optimally assign tasks to each agent, subject to constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}.
-Path planning is to optimally plan paths to each agent, subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc (cite: path planning).
+Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}.
+Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc \cite{zhang2018path}.
 Collision avoidance is to avoid collision with obstacles.
@@
 
-Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability (cite:UAV-UGV).
-Additionally, the complementarity between them also makes such a system more potential.
+Although there are many types of UVs to make up an unmanned HMAS, Unmanned Aerial Vehicle (UAV) and Unmanned Ground Vehicle (UGV) have been the subject of major recent research because of their availability and applicability.
+Additionally, the complementarity between them also makes such a system more potential \cite{arbanas2018decentralized}.
 In other words, UAV is widely used in reconnaissance due to the high mobility.
@@
 To make agent move on the path, a behavior corresponding to the environment is required to determine.
-Then, a local motion corresponding to the behavior of the agent needs to be planned.
+Then, a local motion corresponding to the behavior of the agent needs to be designed.
 Finally, a controller must be designed to track the trajectory of the motion.
@@
 The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter.
-The local motion planning of walking of biped robot, i.e., stable walking pattern generation, is a popular research topic due to its challenge(cite: walking pattern).
+The local motion planning of walking of biped robot, i.e., stable walking pattern generation, is a popular research topic due to its challenge \cite{olcay2017design}.
 
@@
 
-Besides, the formation control is also a topic in MAS (cite:formation control).
+Besides, the formation control is also a topic in MAS \cite{wang2022consensus}.
 Its purpose is to keep a MAS in a formation while moving.
@@
 Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
-Based on the foregoing, a robust $H_\infty$ decentralized fault-tolerant tracking control strategy is proposed to deal with the control problem in URTS.
+Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed to deal with the control problem in URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
@@
 
-The remainder of the paper is organized as follows. In Section II, ...
+The remainder of the paper is organized as follows.
+In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship of its components, i,e, task allocation, path planning, behavior layer and local motion planning are described.
+In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed for the agents in URTS with the help of a general agent model.
+In Section V, an simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed control method.
+In Section VI, a conclusion is maded.
 
@@
 
-\section{PRELIMINARIES OF S\&R URTS}
+\section{PRELIMINARIES OF URTS in S\&R usage}
 The URTS will start with a given S\&R area, and end with mission completed.
@@
 After a specific behavior is determined, the next step is to design a motion to achieve that behavior.
-Local Motion Planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher.
+local motion planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher.
 Collision checking is needed since we consider agent as a point in Path Planning block and it is a real body here.
@@
 $r(t)$ describes the position and orientation that need to be reach over time by a machine system governed by a dynamic equation.
-Then, Tracking Control block will track $r(t)$ to really do that behavior.
+Then, tracking control block will track $r(t)$ to really do that behavior.
 Note that the path and trajectory are distinguished in some literature.
 Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
-The flowchart of Local Motion Planning block is shown in Fig.
+The flowchart of local motion planning block is shown in Fig.
 \ref{fig:LocalMotionPlanning}
@@
 
-\section{system description of UAV-Robot Team System}
+\section{system description of UAVs and biped robots in URTS}
 In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first.
@@
 
+For further verification, we visualized the simulation of a team in URTS and the configuration trajectory of biped robot on the online resource (cite:online source).
+The results again demonstrate the effectiveness of the proposed method.
+
 \section{conclusion}
@@
 The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail.
-An $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) strategy is proposed to control the agents in URTS under the external disturbances.
+A robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC strategy is proposed to control the agents in URTS under the external disturbances.
 The control problem of UAV and robot are solved together via a transformation from a general agent model.

### 2022-11-03 paper/paper.tex
Go through paper once. Add parameter setting. Revise system flow.

@@
 \begin{enumerate}
-    \item contribution 1 ...
+    \item A system architecture and system flow of URTS for S\&R usage are proposed so that the issues involved in URTS and their relationships can be defined and resolved.
+    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the tracking control of agents in URTS.
+    \item A general agent model is proposed so that the tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
 \end{enumerate}
@@
 The 5 blocks on right side are the flow of an agent performing a S\&R mission.
-From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control}%
+From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
 \label{fig:sys}
@@
 Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques.
-Goal configuration is obtained by the previous block, Task Allocation.
+Goal configuration is obtained by the previous block, task allocation block.
 Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
@@
 After a specific behavior is determined, the next step is to design a motion to achieve that behavior.
-local motion planning block is like Path Planning block but its scale is smaller and its resolution and precision must be higher.
-Collision checking is needed since we consider agent as a point in Path Planning block and it is a real body here.
+Local motion planning block is like path planning block but its scale is smaller and its resolution and precision must be higher.
+Collision checking is needed since we consider agent as a point in path planning block and it is a real body here.
 Furthermore, the kinodynamic constraint is handled in this block.
@@
 Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
+We also distinguish in this way in this article.
 The flowchart of local motion planning block is shown in Fig.
@@
 where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness.
+
 To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
@@
 \end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
-
 Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
@@
 \end{equation}
-Combining (\ref{eq:e_bar}), (\ref{eq:e_hat}) and (\ref{eq:Kx}), we have the following augmented system:
+Combining (\ref{eq:e_bar}), (\ref{eq:Kx}), and (\ref{eq:e_tilde}), we have the following augmented system:
 \begin{equation} \label{eq:aug}
@@
 \end{equation}
-where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of augmented state, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}_0)$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
+where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of augmented state, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented state $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
 Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
-Let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^l_0$, $f_{2,i}(t)\in\mathbb{R}^o_0$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
+Let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
 \begin{equation} \label{eq:linear subsys}
@@
 Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness.
-More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times(sn)$ to $(1\times s)\times n$.
-For $L$, it changes from $(sn)\times(l_0n)$ to $(s\times l_0)\times n$.
+More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times sn$ to $n(1\times s)$.
+For $L$, it changes from $sn\times l_0n$ to $n(s\times l_0)$.
+The number of scalar gains to be designed between them is $n$ times different.
 % \textit{
@@
 \ref{fig:tracking}.
-The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u(t)$ according to the result of Local Motion Planning $r'(t)$ and Theorem \ref{theorem1} $u'(t)$.
+The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u(t)$ according to the output of local motion planning block $r'(t)$ and Theorem \ref{theorem1} $u'(t)$.
 The reference generator for robot is an identity function since it is a fully actuated system.
 Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
-$\pmb{r}(t)$ then pass to sensor to calculate the PID tracking error $\pmb{e}(t)$.
-The sensor measure not only the agent's own information (e.g., position, velocity or $\pmb{e}(t)$) but environmental information.
-The environmental information is passed back to the high-level block for positioning, mapping and object recognition.
-The measurement output $y(t)$ is input to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
-The differentiation of $\pmb{r}(t)$, $\pmb{\dot{r}}(t)$, is input to controller for feedforward control.
+$\pmb{r}(t)$ then pass to observer to calculate the PID tracking error $\pmb{e}(t)$.
+Its differential, $\dot{\pmb{r}}(t)$, then input to controller for feedforward control.
+The sensor measure not only the agent's own information (e.g., position or velocity) but environmental information.
+The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
+The letter is passed back to the high-level block for positioning, mapping and object recognition.
 
@@
     \centering
-    \includegraphics[scale=.42]{fig/tracking.pdf}\caption{The flowchart of tracking control.
+    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control.
 The control scheme of UAV and robot is only different from the block, reference generator.
@@
 
-For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly set to $([0,0,0]^T\mathbin{,} [0,5,2.5]^T\mathbin{,} [5,5,5]^T\mathbin{,} [5,0,2.5]^T\mathbin{,} [10,0,0]^T\mathbin{,} [10,5,-2.5]^T\mathbin{,} [10,10,-5]^T\mathbin{,} [5,10,-2.5]^T\mathbin{,} [0,10,0]^T)$ without going through path planning by \textit{Assumption \ref{asm:collision}}.
+For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly assigned as shown in Fig.
+\ref{sim:flying} without going through path planning by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
@@
 \textit{Agents:}\begin{enumerate}
-    \item system parameters: $C_0 = I_3$, $B_{2,0} = [0, 0.1, 1]^T$.
-    \item designed parameters: $Q_1 = 50*diag(diag(1,100,10),\allowbreak 0, 0), Q_2 = 5*diag(diag([1,100,10]), diag(1,0.1,\allowbreak 0.01), diag(1,0.1,0.01 ,0.001)), R=0.002, \rho=30$.
-Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
+    \item system parameters:
+    Initial value $\tilde{x}(0) = [\pmb{e}(0)^T, F_1(0)^T\mathbin{,} F_2(0)^T, \tilde{e}(0)]^T = [[0.1X, ..., 0.1X]^T, 0, 0, 0]^T$ where $X \sim \mathcal{N}(0, 1)$. $C_0 = I_3$.
+    \item designed parameters: $\rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
 \end{enumerate}
@@
 \textit{UAVs:}\begin{enumerate}
-    \item system parameters: $g = 9.81, m = 2,
+    \item system parameters:
+    $B_{2,0} = [0, 0.1, 1]^T$,
+    $g = 9.81, m = 2,
     J_x = J_y = 1.25, Jz = 2.2,
     K_x = K_y = K_z = 0.01,
-    K_\phi = K_\theta = K_\psi = 0.012$. Initial values $\bar{x}_0=$.
+    K_\phi = K_\theta = K_\psi = 0.012$.
+    \item designed parameters: 
+    $Q_1 = 10diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
+    $Q_2 = diag(0.1diag([1\mathbin{,} 100\mathbin{,} 10]), diag(1,0.1\mathbin{,} 0.01), 20diag(1,0.1,0.01 ,0.001))$, 
+    $R = 0.02$.
     % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
@@
 \textit{Robots:} \begin{enumerate}
-    \item system parameters: Appendix E in \cite{ourrobot}. Initial values $\bar{x}_0=$.
-    \item designed parameters: $Q_1=,Q_2=,R=,rho=20$.
+    \item system parameters: Appendix E in \cite{ourrobot}. $B_{2,0} = [0, 0, 1]^T$.
+    \item designed parameters:
+    $Q_1 = 50diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
+    $Q_2 = 5diag(diag([1\mathbin{,} 100\mathbin{,} 10]), diag(1,0.1\mathbin{,}0.01)\mathbin{,} diag(1,0.1,0.01,0.001))$, 
+    $R = 0.002$.
 \end{enumerate}

### 2022-11-03 src/URTS main script/Robot/function/+Show/PlotLMP.m

@@ -6,9 +6,9 @@ function PlotLMP(pp, rb)
 
     % Path and smoothed path
     len = 4;
-    plot(pp.sigma(1, 1:len), pp.sigma(2, 1:len), '^', 'DisplayName', '$\sigma(t)$','MarkerSize', 7)
+    plot(pp.sigma(1, 1:len), pp.sigma(2, 1:len), '^', 'DisplayName', '$(\sigma_n)$','MarkerSize', 7)
     len = 20;
-    plot(pp.r(1, 1:len), pp.r(2, 1:len), 'LineWidth', 1, 'DisplayName', '$\sigma''(t)$')
+    plot(pp.r(1, 1:len), pp.r(2, 1:len), 'LineWidth', 1, 'DisplayName', '$(\sigma''_n)$')
 
     % Start and goal configuration
     % len = length(pp.sigma);

### 2022-11-03 src/URTS main script/Robot/oneRobot_FaFs.m

@@ -113,9 +113,9 @@ end
 
 if rb.EXE_PLOT
     disp('Ploting trajectory ...')
-%     Show.PlotPP(pp); % path planning
+    Show.PlotPP(pp); % path planning
     % Show.PlotLMP(pp, rb); % local motion planning
-    rb.PlotTC() % tracking control
+    % rb.PlotTC() % tracking control
 end
     
 %% Execution time

### 2022-11-06 examples/solveLMI1Test.m
Remove redundent files

@@ -1,16 +1,23 @@
-%A simple linear system to test solveLMI()
+%Using a simple linear system to test solveLMI1()
 clc; clear; close all;
-addpath(genpath('../../src'))
+addpath(genpath('../src'))
 
-I = eye(2); O = zeros(2);
-A = [0 1; 1 2]; B = [0; 1]; E = 1*[1 0; 0 1]; Ar = -10*I; Br = -Ar;
-Q1 = 0; Q2 = 10^(-1)*[1 0; 0 0.001]; rho = 3;
-dt = 0.002; T = 10; x0 = [0.1; 0.2]; xr0 = [1; 0];
+I = eye(2);
+O = zeros(2);
+A = [0 1; 1 2];
+B = [0; 1];
+E = 1*[1 0; 0 1];
+Ar = -10*I;
+Br = -Ar;
+Q1 = 1;
+Q2 = 10^(-1)*[1 0; 0 0.001];
+rho = 3;
+dt = 0.002; T = 10;
+x0 = [0.1; 0.2]; xr0 = [1; 0];
 freq = 1; amp = 1;
 v = @(t)[0.5*randn + 0; 0.5*randn + 0];
 r = @(t)[amp*sin(freq*t); amp*freq*cos(freq*t)];
 
-% K1 = solveLMI(A, B, E, Ar, Br, Q1, Q2, rho);
 K2 = solveLMI1(A, B, E, Ar, Br, Q2, rho);
 K = K2*1;
 

### 2022-11-06 test/Inheritance/@Class2/Class2.m

@@ -1,29 +1,0 @@
-classdef Class2 < Class1
-    %CLASS1 Summary of this class goes here
-    %   Detailed explanation goes here
-    
-    properties
-        % A1
-        C1
-    end
-    
-    methods
-        function obj = Class2(c1)
-            %CLASS1 Construct an instance of this class
-            %   Detailed explanation goes here
-            obj = obj@Class1(3);
-            obj.C1 = 2;
-        end
-        
-        function obj = setC(obj, a1)
-            %METHOD1 Summary of this method goes here
-            %   Detailed explanation goes here
-            obj.C1 = a1;
-        end
-        function Print(obj)
-            obj.Print@Class1();
-            2
-        end
-    end
-end
-

### 2022-11-06 test/SimpleLinearSys/main.m

@@ -1,40 +1,0 @@
-%A simple linear system to test solveLMI()
-clc; clear; close all;
-addpath(genpath('../../src'))
-
-I = eye(2); O = zeros(2);
-A = [2 0; 1 1]; B = [1.5; 1]; E = 1*[1 0; 0 1]; Ar = -10*I; Br = -Ar;
-[DIM_X, DIM_U] = size(B);
-Q1 = 0; Q2 = 10^(0)*[1 0; 0 0.001]; rho = 10; R = 0;
-dt = 0.001; T = 10; x0 = [0.1; 0.2]; xr0 = [1; 0];
-freq = 1; amp = 1;
-r = @(t)[amp*sin(freq*t); amp*freq*cos(freq*t)];
-
-K2 = solveLMI1(A, B, E, Ar, Br, Q2, rho);
-% K2 = solveLMI6(A, B, R, Q2, rho);
-K = K2;
-norm(K)
-
-t = 0 : dt : T;
-x = zeros(DIM_X, length(t)); 
-xr = x;
-x(:, 1) = x0; xr(:, 1) = xr0;
-for i = 1 : length(t) - 1
-    k = A*x(:, i) + B*K*(x(:, i) - xr(:, i));
-    x(:, i+1) = x(:, i) + dt*k;
-    k = Ar*xr(:, i+1) + Br*r(i*dt);
-%     xr(:, i+1) = xr(:, i) + dt*k;
-    xr(:, i+1) = r(i*dt);
-end
-
-plot(t, x, t, xr)
-legend('x1', 'x2', 'xr1', 'xr2')
-
-if rank(ctrb(A, B)) == size(A, 1)
-    disp('controllable')
-else
-    disp('rank of system:')
-    disp(rank(ctrb(A, B)))
-end
-
-rmpath(genpath('../../src'))

### 2022-11-06 test/indexNDarray.m

@@ -1,16 +1,0 @@
-clc; clear
-len = 5*4*3*2;
-S = zeros(5, 4, 3, 2);
-for i = 1 : len
-    S(i) = i;
-end
-
-len2 = 5*4;
-A = cell(1, len2);
-for i = 1 : len2
-    A{i} = zeros(3, 2);
-    for j = 1 : 3*2
-        A{i}(j) = S(i + len2*(j-1));
-    end
-end
-A{1}

### 2022-11-14 paper/paper.tex
Remove redundent files
Revise paper, INTRODUCTION, done.

@@
 
-\title{Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage}
+\title{Motion Planning and Robust Fault-Tolerant Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}
 % \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
@@
 \begin{abstract}
-In this study, we investigate a UAVs and biped robots team system (URTS) for search and rescue (S\&R) usage.
-The system architecture of URTS is proposed to illustrate the issues need to be addressed in URTS and the relationships between them.
+In this study, we investigate a motion planning and robust fault-tolerant control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
+The system architecture of URTS is proposed at first to illustrate the issues to be addressed in URTS and the relationships between them.
 The task allocation and path planning problems are first investigated and stated.
-Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and the tracking control problem for UAV and robot.
+Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAV and robot.
 The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail.
 By converting the dynamics model of UAV and robot into a unified agent model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
-A novel smoothing signal model of fault signal is embedded into the linearized system to active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is transformed into a linear matrix inequality (LMI) -constrained optimization problem by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the tracking problem of UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed tracking control method.
+A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem which can be solved by a two-step design procedure.
+With the help of MATLAB LMI Toolbox, the tracking problem of each UAV and robot in URTS is effectively solved.
+Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed tracking control method under the external disturbance and the actuator and sensor fault.
 \end{abstract}
@@
 \begin{keywords}
-biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, UAVs-UGVs team system
+biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, hybrid UAVs-UGVs team system
 \end{keywords}
@@
 It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans.
-Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, and surveillance, etc \cite{9700861}.
+Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc \cite{9700861}.
 Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
@@
 To limit the scope of this paper, we focus on decision-making and control problem only.
-The three main problem of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
+Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
 Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}.
@@
 Collision avoidance is to avoid collision with obstacles.
-Although collision avoidance is often concerned in path planning part, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.
+Although collision avoidance is often concerned in path planning, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.
 
@@
 For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
-To discuss more concretely, we consider an UAVs-UGVs team system for S\&R.
+To discuss more concretely, we consider a hybrid UAVs-UGVs team system for S\&R.
 For the need for search mobility, we choose quadrotor aircraft as UAV.
@@
 Additionally, few literatures illustrate the relationship between these problems.
-This leads us to propose an system architecture of UAVs-robots team system (URTS) for S\&R usage.
+This leads us to propose a system architecture of hyibrid UAVs and biped robots team system (URTS) for S\&R usage.
 The flowchart of decision-making and control process of URTS is also given.
-We divide it into five main hierarchical processes, i.e., tack allocation, path planning, behavior layer, local motion planning and tracking control.
+We divide it into five main hierarchical processes, i.e., taskallocation, path planning, behavior layer, local motion planning and tracking control.
 It is because the UTRS needs to be able to assign different tasks to agents to perform first.
@@
 This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
-Although there are some literatures directly tackle the kinodynamic constraints path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
+Although some literatures directly tackle the kinodynamic constraints path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
 Through this decomposition, we can focus on the local motion planning of specific behaviors.
-The motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter.
-The local motion planning of walking of biped robot, i.e., stable walking pattern generation, is a popular research topic due to its challenge \cite{olcay2017design}.
+The local motion planning of flying behavior for UAV and walking behavior for robot is studied in this paper, especially the latter.
+The local motion planning of biped robot walking, i.e., stable walking pattern generation, is a popular research topic due to its challenge \cite{olcay2017design}.
 
@@
 According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}.
-Centralized control means there exist a powerful central controller in MAS to gather the state information and send the control command back to each agent to reach a global goal.
+Centralized control means there exists a powerful central controller in MAS to gather the state information of MAS and send the control command back to each agent to reach a global goal.
 Due to the powerful nature of the central controller, control commands can be determined well and quickly.
@@
 In contrast, decentralized control means that each agent has its own controller to collect and control the agent's own state information.
-Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller is avoided.
+Under this architecture, although the global goal cannot be achieved, the possibility of paralyzing the entire system due to the failure of the controller can be avoided.
 
@@
 It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
-In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for the agent to follow.
+In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for each agent to follow.
 
@@
 \begin{enumerate}
-    \item A system architecture and system flow of URTS for S\&R usage are proposed so that the issues involved in URTS and their relationships can be defined and resolved.
+    \item A system architecture and system flow of URTS for the purpose of S\&R are proposed so that the issues involved in URTS and their relationships can be defined and resolved.
     \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the tracking control of agents in URTS.
-    \item A general agent model is proposed so that the tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
+    \item A general agent model is proposed so that the robust $H_\infty$ decentralized observer-based tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
 \end{enumerate}
@@
 The remainder of the paper is organized as follows.
-In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship of its components, i,e, task allocation, path planning, behavior layer and local motion planning are described.
+In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship of its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described.
 In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
 In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed for the agents in URTS with the help of a general agent model.
-In Section V, an simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed control method.
+In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method.
 In Section VI, a conclusion is maded.
@@
 $diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
-$A^T$: transpose of A.
+$A^T$: transpose of $A$.
 $A > 0$: a positive definite matrix.
@@
 The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it).
-The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.
+The detailed functions of remaining 5 blocks, i.e., Task Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.
 

### 2022-11-15 paper/paper.tex
Revise paper. I-C, done

@@
 It is because the UTRS needs to be able to assign different tasks to agents to perform first.
-After a task is assigned, if the task is to reach a target location, a path to reach it needs to be planned.
+After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned.
 To make agent move on the path, a behavior corresponding to the environment is required to determine.
@@
 To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area.
-To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target.
+To complete rescue tasks, whenever a goal (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of goal.
 % It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents.
@@
 
-In order to make a behavior, we must design a corresponding motion which is handled by local motion planning.
-The motion is a desired reference trajectory for an actual mechanical system to follow.
-Finally, a tracking controller is designed to follow this desired reference trajectory.
+In order to make a behavior, we must design a corresponding motion by local motion planning.
+The motion is a prescribed reference trajectory for an actual mechanical system to follow.
+Finally, a tracking controller is designed for each agent to follow this desired reference trajectory.
 
 The agents overall have the same system architecture in URTS except for some subprocess differences.
-Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in S\&R is proposed as shown in Fig.
+Followed by the concept in \cite{paden2016survey}, a system architecture for an agent employed for S\&R is proposed as shown in Fig.
 \ref{fig:sys}.
@@
 The visual object recognition block provides distance information and object information through the analysis of sensor information.
-The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it).
-The detailed functions of remaining 5 blocks, i.e., Task Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.
+The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decides to climb through it).
+The detailed functions of remaining 5 blocks, i.e., Task Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following subsections.
 
@@
 \includegraphics[scale=.5]{fig/sys.pdf}\caption{The system architecture of agent in URTS.
-The 2 blocks on left side are used to convert low-level sensor information into high-level information, such as map, start point and object information.
-The 5 blocks on right side are the flow of an agent performing a S\&R mission.
-From top to bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
+The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map, start point and object information.
+The 5 blocks on right hand side are the flow of an agent performing a S\&R mission.
+From the top to the bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
 \label{fig:sys}
@@
 In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
-However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g.
-moving speed or load capacity) and status (e.g.
-their own position or the amount of supplies carried), and each task has different characteristics (e.g.
-Urgency, position, amout of supplies needed).
-Therefore, the results of task allocation can be "good or bad", which leads us want to find the optimal allocation.
-This problem is refered as a task allocation problem or multi-robot task allocation problem.
+However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
+Therefore, the results of task allocation can be "good or bad", which leads us to find the optimal allocation.
+This problem is referred to a task allocation problem or multi-robot task allocation problem.
 A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}.
-Although there are many different formulations and models to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
+Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
 In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
@@
 According to the way of pathfinding, it can be divided into multi-query planner and single-query planner \cite{elbanhawi2014sampling}.
-Multi-query planner will first construct a roadmap and then use the graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
+Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
 Single-query planner will complete the pathfinding by constructing and querying simultaneously,
@@
 However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner.
-Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such like PRM with D* search algorithm, dynamic RRT, and extended RRT.
+Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT.
 All of the above common roadmap-based planners can be applied to the URTS.
@@
 Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
-The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and the constraints on these behaviors will vary.
-(e.g., curvature constraints of two behavior: running and walking are expected to be different for robot).
+The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robot).
 In this case, a unified planner will become overly complex and impracticable.
-For this reason, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning.
-Then, the global planner, path planning block, will regard an agent as a point without kinodynamic constraints.
-The local planners, local motion planning block, will consider the motion planning of a specific behavior.
+Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning.
+The path planning block becomes a global planner and regard an agent as a point without kinodynamic constraints.
+The local motion planning block becomes a local planner and consider the motion planning of a specific behavior.
 % In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
@@
 Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
-$\mathcal{C}$ is a space contain all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
-For a simpler explanation of how the URTS works, the following assumption is made.
+$\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
+For a simpler explanation of how the URTS works, the following assumptions are made.
 
@@
 Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$.
-For agents, the replanning decision can be a goal changing that is made by human or task allocation block.
-For robot, it can be a collision detecting by a dynamic roadmap-based planner.
-The results path $(\sigma_n)$ is passed to the next block, Behavior Layer.
+For agents, the replanning decision can be due to a goal changing that is made by human or task allocation block.
+For robot, it can be a collision detected by a dynamic roadmap-based planner.
+The resulting path $(\sigma_n)$ is passed to the next block, Behavior Layer.
 
@@
 % Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
-Path Planning tells agents where to go but not how.
-Take robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario.
+Path planning tells agents where to go but not how since we regard the agent as a point.
+Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario.
 These behaviors with changing position are classified as "moving" behavior in this paper.
-Besides, the agents do not always moving.
+Besides, the agents in the hybrid URTS do not always moving.
 Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
@@
 More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control.
-The sequence of these behaviors be expressed as:
+The sequence of these behaviors can be expressed as:
 \begin{equation}
@@
 \end{equation}
-It is to say that the path $(\sigma_n)$ is divided into many segments and each corresponding to a specific behavior.
+where $\mathcal{B}$ is the set of behaviors.
+It is to say that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
 Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set.
-The set of behavior $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig.
+The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig.
 \ref{fig:behavior}.
@@
 Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,5 \}$.
-At the beginning, the agents in $team_i$ are assigned the search tasks of $area_i$ to build the occupancy map and find targets.
+At the beginning, the agents in $team_i$ are assigned the search tasks of $area_i$ to build the occupancy map and find goals.
 The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
@@
 Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}$.
-Suppose a target is found after a while as shown in Fig.
+Suppose a goal is found after a while as shown in Fig.
 \ref{fig:S_task}, at this point, we have a rescue task $T_6$.

### 2022-11-15 paper/paper.tex
Revise paper, I-E, done

@@
 \centering
-\includegraphics[scale=.5]{fig/sys.pdf}\caption{The system architecture of agent in URTS.
+\includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS.
 The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map, start point and object information.
@@
 It is to say that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
-Judging an appropriate behavior according to the current environment will be a rather complicated project, so this article only gives the structure of the behavior set.
+By the object information in Fig.
+\ref{fig:sys}, an appropriate behavior can be judged.
+However, it will be a rather complicated project, so this article only gives the structure of the behavior set.
 The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig.
@@
     \centering
-    \includegraphics[scale=.5]{fig/behavior.pdf}\caption{The structure of behavior layer.
-The leaf of the tree structure are the possible behaviors an agent can take.
-The behavior to be take at every moment will be decided in this block.}%
+    \includegraphics[scale=.15]{fig/behavior.png}\caption{The structure of behavior layer.
+The leaves of the tree structure are the possible behaviors an agent can take.
+The behavior to be took at every moment will be decided in this block.}%
     \label{fig:behavior}
@@
 Local motion planning block is like path planning block but its scale is smaller and its resolution and precision must be higher.
-Collision checking is needed since we consider agent as a point in path planning block and it is a real body here.
+Collision checking is needed since we consider agent as a point in path planning block and it is a real mechanical body here.
 Furthermore, the kinodynamic constraint is handled in this block.
@@
 Therefore, the output of this block is also a path but with a timescale, i.e., sampling period.
-This path is often referred as a reference trajectory $r(t)$.
-$r(t)$ describes the position and orientation that need to be reach over time by a machine system governed by a dynamic equation.
-Then, tracking control block will track $r(t)$ to really do that behavior.
+This path is often referred as a desired reference trajectory $r(t)$.
+$r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation.
 Note that the path and trajectory are distinguished in some literature.
-Different from path $(\sigma_n)$ (or say $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
+Different from path $(\sigma_n)$, a trajectory $r(t)$ has considered the time in physic world.
 We also distinguish in this way in this article.
@@
 The corresponding motion planning will be executed according to the behavior determined by the behavior layer.
-The terminator, exception, represents an exceptional condition that performs unconsidered behaviors.
+The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
 The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
-$r[k]$ will convert to reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
+$r[k]$ will be converted to the desired reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
     \label{fig:LocalMotionPlanning}
@@
 \ref{fig:LocalMotionPlanning}.
+A more detailed description will be given in the next section.
+
+\subsection{Tracking Control}
+If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect.
+This is because the previous blocks have already completed all planning for the trajectory $r(t)$.
+All that remains is to track $r(t)$, to do so, a control method need to be design.
+It will be discussed detailly in Section IV.
+In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper layer as shown in Fig.
+\ref{fig:sys}.
 

### 2022-11-16 paper/paper.tex
Revise paper, III, done

@@
     \centering
-    \includegraphics[scale=.4]{fig/FandW.pdf}\caption{The flowchart of Flying and Walking.
-In both two blocks, a smoothed path is obtained by post-processing first.
+    \includegraphics[scale=.4]{fig/FandW.png}\caption{The flowchart of Flying and Walking.
+In both blocks, a smoothed path is obtained by post-processing first.
 Then the respective motion of behavior is designed.
-The final outputs of Flying and Walking are all reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
+The final outputs of Flying and Walking are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
     \label{fig:FandW}
 \end{figure*}
-Before the discussion of the motion planning of these two behavior, the following assumption is maded.
+Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
 \textit{
@@
 }
-However, for these two behaviors, there all exist an inevitable kinematic constraint on curvature of local motion.
+However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion.
 Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem.
-Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking curvature constraint is relatively insignificant.
+Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant.
 At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision.
@@
 % where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
-$g$ is the gravity acceleration, $m$ and $J$ is the mass and inertia matrix of UAV, respectively, $\tau$ and $F$ are the total touque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
-This model treats the UAV as a mass point and can control the force in the $z$ direction and the touque in the $x$, $y$ and $z$ direction.
-Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denote the reference.
-
-Now, suppose the UAV flying is occured between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
+$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
+This model treats the UAV as a mass point and can control the force in the $z$ direction and the torque in the $x$, $y$ and $z$ direction.
+Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denotes the reference.
+
+Now, suppose the UAV flying occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
 The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
-Then, $(\sigma_n')$ will be the position reference path $\begin{bmatrix}
-    x_r[k] & y_r[k] & z_r[k]
-\end{bmatrix}^T$.
-Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are considered.
+Then, $(\sigma_n')$ will be the position reference path $[
+    x_r[k], y_r[k], z_r[k]
+]^T$.
+Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are all considered.
 $\phi_r[k]$ is set to zero since no need for spinning when flying.
 $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section.
-Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = \begin{bmatrix}
-    x_r[k] & y_r[k] & z_r[k] & \psi_r[k]
-\end{bmatrix}^T$. The flowchart is shown in Fig. \ref{fig:FandW}.
+Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
+    x_r[k], y_r[k], z_r[k], \psi_r[k]
+]^T$. The flowchart is shown in Fig. \ref{fig:FandW}.
 
@@
 For robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space.
-Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern prevent robot from falling.
+Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern to prevent robot from falling.
 These make the design of walking motion more difficult.
@@
 
+With 3D-LIPM, we can significantly reduce the amount of computation.
 Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}.
@@
 More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
-The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} ($\widehat{Y_b}$ direction as same form):
+The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
 \begin{equation}
@@
 \end{equation}
-It can be seen that ZMP is related to 12 link masses, moment of inertia, positions, accelerations, and angular velocities.
-This makes the analytical solution of reference $q_r(t)$ impossible.
-However, an approximate solution can be derived through 3D-LIPM.
-It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinemic (IK) given step size, step height, step period and CoM height.
+where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$.
+However, it is difficult to directly calculate the analytical solution of $q_r$ through (6).
+Since there is a complex coordinate transformation between $q_r$ and $x_i, z_i, \ddot{\Omega}_{iy}$.
+At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r$.
+To simplify this complex problem, an approximate solution can be derived through 3D-LIPM.
+It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height.
 Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model.
-Although the actual dynamic model is different from 3D-LIPM so there is an error between them, the design process will be more simple.
+Although there exist a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple.
 The overall process is shown in Fig.
@@
 Following the same step in UAV, the smoothed path $(\sigma_n')$ for robot can be obtained at first.
-For ease of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$.
+For the convenience of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$.
 Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance.
@@
 After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed.
-Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component are given by step height.
+Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by step height.
 By using cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
-The ankle orientation path is found by gradient of ground.
+The ankle orientation path is found by the gradient of ground.
 Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together.
@@
     \begin{split}
-        & \ddot{x} = \frac{g}{z_c}(x - p_x) \\
-        & \ddot{y} = \frac{g}{z_c}(y - p_y)
-    \end{split}
-\end{equation}
-where $(x,y)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP.
-Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x,y)$ can be solved.
-To solve the ODE in (\ref{eq:LIPM}), a method is proposed to convert it to a servo problem \cite{1241826}:
+        & \ddot{x}_c = \frac{g}{z_c}(x_c - p_x) \\
+        & \ddot{y}_c = \frac{g}{z_c}(y_c - p_y)
+    \end{split}
+\end{equation}
+where $(x_c, y_c, z_c)$ is the position of CoM of the inverted pendulum, $g$ is the gravity acceleration, and $(p_x,p_y)$ is the position of ZMP on the $x$-$y$ plane.
+Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x_c, y_c)$ can be solved.
+Observing the dynamic equations in the $x$ and $y$ directions in (\ref{eq:LIPM}), it can be found that they are decoupled and thus can be calculated separately.
+Therefore, only the solution in the $x$ direction is given below (the $y$ direction as the same).
+To solve it, a method is proposed to convert it to a servo problem \cite{1241826}:
 \begin{equation} \label{eq:output tracking}
     \begin{split}
-        & \dot{\bar{x}} = A\bar{x} + Bu \\
-        & p_x = C\bar{x}
-    \end{split}
-\end{equation}
-where $\bar{x} = \begin{bmatrix}
-    x \\ \dot{x} \\ \ddot{x}
+        & \dot{\bar{x}}_c = A\bar{x}_c + Bu \\
+        & p_x = C\bar{x}_c
+    \end{split}
+\end{equation}
+where $\bar{x}_c = \begin{bmatrix}
+    x_c \\ \dot{x}_c \\ \ddot{x}_c
 \end{bmatrix}$, $A = \begin{bmatrix}
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path we want is found.
+Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x_c$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path is found.
 Unlike conventional methods, the problem is solved by the optimal control.
@@
 The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}.
-The $y$-direction can be found by same procedure since the dynamic of 3D-LIPM in the $x$-direction and $y$-direction is decoupled with same form.
-The CoM position path $(CP_n)$ then be obtained by combining $x$, $y$ and $z_c$.
-% $\bar{x}$ in (\ref{eq:output tracking}),
-
-By combining the CoM orientation $(CO_n)$ and position $(CP_n)$ path, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot is found by solving IK.
+The CoM position path $(CP_n)$ then be obtained by combining $x_c$ and $y_c$ with $z_c$.
+
+By combining the CoM orientation path $(CO_n)$ and position path $(CP_n)$, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot can be found by solving IK.
 

### 2022-11-16 paper/paper.tex
Revise IV-eq.(23), done except adding remark

@@
 The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics model of UAV and robot into a unified agent model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
+By converting the dynamics model of UAV and robot into a unified agent dynamics model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
@@
 We divide it into five main hierarchical processes, i.e., taskallocation, path planning, behavior layer, local motion planning and tracking control.
-It is because the UTRS needs to be able to assign different tasks to agents to perform first.
+It is because the URTS needs to be able to assign different tasks to agents to perform first.
 After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned.
@@
     \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the tracking control of agents in URTS.
-    \item A general agent model is proposed so that the robust $H_\infty$ decentralized observer-based tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
+    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
 \end{enumerate}
@@
 In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
-In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed for the agents in URTS with the help of a general agent model.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
 In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method.
@@
 There are several path planning algorithm to handle this problem.
-Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of UTRS.
+Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS.
 This method attempts to discretize the search space into interconnected roads and find the path on it.
@@
     \centering
-    \includegraphics[scale=.15]{fig/behavior.png}\caption{The structure of behavior layer.
+    \includegraphics[scale=.13]{fig/behavior.png}\caption{The structure of behavior layer.
 The leaves of the tree structure are the possible behaviors an agent can take.
@@
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
-The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
-$r[k]$ will be converted to the desired reference trajectory $r(t)$, an analog signal, by an A to D convertor.}
+The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.}
     \label{fig:LocalMotionPlanning}
@@
 If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect.
-This is because the previous blocks have already completed all planning for the trajectory $r(t)$.
-All that remains is to track $r(t)$, to do so, a control method need to be design.
+To this end, a control method need to be design.
 It will be discussed detailly in Section IV.
@@
     \centering
-    \includegraphics[scale=.4]{fig/FandW.png}\caption{The flowchart of Flying and Walking.
+    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of Flying and Walking.
 In both blocks, a smoothed path is obtained by post-processing first.
@@
         \begin{bmatrix}
-            F \\ \tau
+            f_u \\ \tau_u
         \end{bmatrix}&=\begin{bmatrix}
@@
     0 & 0 & K_{\tau_z}
-\end{bmatrix}$, $F =\begin{bmatrix}
+\end{bmatrix}$, $f_u =\begin{bmatrix}
     f_x \\ f_y \\ f_z
@@
     0 \\ 0 \\ F
-\end{bmatrix}$, $\tau=\begin{bmatrix}
+\end{bmatrix}$, $\tau_u=\begin{bmatrix}
     \tau_x \\ \tau_y \\ \tau_z
@@
 % where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
-$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
+$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
 This model treats the UAV as a mass point and can control the force in the $z$ direction and the torque in the $x$, $y$ and $z$ direction.
@@
     x_r[k], y_r[k], z_r[k], \psi_r[k]
-]^T$. The flowchart is shown in Fig. \ref{fig:FandW}.
+]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.
 
@@
     \begin{split}
-        & \tau = M(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
-    \end{split}
-\end{equation}
-where $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector.
+        & \tau_R = M_R(q)\ddot{q} + C(q,\dot{q})\dot{q} + G(q)    
+    \end{split}
+\end{equation}
+where $\tau_R$ is the total torque on revolute joints, $q,\dot{q},\ddot{q}\in\mathbb{R}^{12}$  are angular position, angular velocity, and angular acceleration vector of revolute joints, $M_R(q)\in\mathbb{R}^{12\times 12}$ is the inertia matrix, $C(q,\dot{q})\in\mathbb{R}^{12}$ is the Coriolis and centripetal force vector and $G(q)\in\mathbb{R}^{12}$ is the gravitational force vector.
 The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}.
@@
 
-By combining the CoM orientation path $(CO_n)$ and position path $(CP_n)$, CoM path can be obtained. Finally, the joint path, i.e., reference path $r[k]$ of robot can be found by solving IK.
-
-\section{Reference Tracking control}
-After the reference trajectory $r(t)$ is set, the last step is to design a controller for an agent to track it.
-To analyze the tracking control problem of UAV model in (\ref{eq:uav}) and robot model in (\ref{eq:robot}) together, we represent them by the same form called agent model through some appropriate variable transformations:
+By combining the CoM orientation path $(CO_n)$ and position path $(CP_n)$, CoM path can be obtained.
+Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK.
+
+\section{Tracking control of each agent in hybrid URTS}
+To analyze the tracking control problem of UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) together, we represent them by the same form called agent dynamics model through some appropriate variable transformations:
 \begin{equation} \label{eq:agent} 
@@
 \end{equation}
-where $u(t)\in\mathbb{R}^n$ is control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(\cdot)\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(\cdot, \cdot)\in\mathbb{R}^n$ is non-inertial force vector.
+where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is non-inertial force vector.
 The control law is given as:
@@
 \end{equation}
-where $M(r(t)),\ddot{r}(t),H(r(t),\dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law for improving system robustness.
+where $r(t)\in\mathbb{R}^n$ is the reference trajectory, $M(r(t)), \ddot{r}(t)\mathbin{,} H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
+For UAVs, we have $u(t)=\begin{bmatrix}
+    f_u \\ \tau_u
+\end{bmatrix}$, $x(t)=\begin{bmatrix}
+    X \\ \Theta
+\end{bmatrix}$, $M(x(t))=\begin{bmatrix}
+    mI & 0 \\ 0 & J
+\end{bmatrix}$, $H(x(t),\dot{x}(t))=\begin{bmatrix}
+    0 \\ \dot{\Theta}\times(J\dot{\Theta})
+\end{bmatrix}+\begin{bmatrix}
+    f_g \\ 0
+\end{bmatrix}+\begin{bmatrix}
+    K_F & 0 \\
+    0 & K_\tau
+\end{bmatrix}\begin{bmatrix}
+    \dot{X} \\ \dot{\Theta}
+\end{bmatrix}$, and $n=6$. For robots, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$.
+
+To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to tranfer the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig.
+\ref{fig:tracking}.
+For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
+Besides, it can be seen that the control input $u(t)=[f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design of UAV (\ref{eq:control}) is different from the actual control input for actuator $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ of UAV since UAV is an underactuated system.
+The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem.
+By substituting $\Theta=\begin{bmatrix}
+    \phi_r \\ \theta_r \\ \psi_r
+\end{bmatrix}$ into $\begin{bmatrix}
+        f_x \\ f_y \\ f_z
+\end{bmatrix} = R(\Theta)\begin{bmatrix}
+        0 \\ 0 \\ F
+\end{bmatrix} $ from UAV dynacmis (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
+Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]$.
+For robot, we get $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since robot is a fully actuated system.
+So far, the design of reference trajectory $r(t)$ of each agent is done.
+The flowchart can be found in the reference generator block in Fig.
+\ref{fig:tracking}.
 
@@
 \begin{enumerate}
-    \item For agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
-    \item For agent, there exists cyber-attack on communication network between agents and ground station.
-    \item For agent, there exists sensor noise.
-    \item For UAV, there exists wind disturbance \cite{9075385}.
-    \item For robot, there exists ground reaction force \cite{chen2013human}. 
+    \item For each agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
+    \item For each agent, there exists cyber-attack on communication network between agents and ground station.
+    \item For each agent, there exists sensor noise.
+    \item For each UAV, there exists wind disturbance \cite{9075385}.
+    \item For each robot, there exists ground reaction force \cite{chen2013human}. 
 \end{enumerate}
-Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.The coupling term can be represented as \begin{equation} \label{eq:UAV couple}
-    \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
-\end{equation} for UAVs $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
-    \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
-\end{equation} for robots $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
-Since the ground station is responsible for the calculation, the calculated control command (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
+Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$. The coupling disturbance $c(t)$ can be represented as \begin{equation} \label{eq:UAV couple}
+    c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
+\end{equation} for UAV $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
+    c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
+\end{equation} for robot $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
+Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
 Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command.
-In addition, the wind disturbance and the ground reaction force will apply extra force on an agent (\ref{eq:agent}).
-Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $d_1(t)$.
-The nominal system (\ref{eq:agent}) then be rewrited as the following real system:
+In addition, the wind disturbance and the ground reaction force will apply extra force on an agent in (\ref{eq:agent}).
+Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance.
+The nominal system in (\ref{eq:agent}) of an agent then be rewrited as the following real system:
 % The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
 \begin{equation} \label{eq:agent d1} 
-    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + d_1(t)
+    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + c(t) + d_1(t)
 \end{equation}
@@
 % where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
+
 Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
@@
         & =(M(r(t))-M(x(t)))\ddot{r}(t) + M(r(t))u_{fb}(t) \\
-        & + H(r(t),\dot{r}(t)) + d_1(t)
+        & + H(r(t),\dot{r}(t)) + c(t) + d_1(t)
     \end{split}
@@
 \end{equation}
-where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
+where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + c(t) + d_1(t))\in\mathbb{R}^n$ is considered as the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t))$ and $ \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
 % \textit{
@@
     \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
-\end{bmatrix}^T\in\mathbb{R}^{3n}$ be the PID tracking error, (\ref{eq:error, state eq}) can be rewrited as:
+\end{bmatrix}^T\in\mathbb{R}^{3n}$, (\ref{eq:error, state eq}) can be rewrited as:
 \begin{equation} \label{eq:linear f1}
@@
 In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
-At the same time, the external disturbances on sensor also need to be considered as mentioned before.
-Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the coupling effect due to co-channel interference and the cyber-attack signal are concerned.
+At the same time, the sensor fault on sensor also need to be considered as mentioned before.
+Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but the cyber-attack signal are concerned.
 Let $\pmb{x}(t)=\begin{bmatrix}
@@
 \end{equation}
-where $y(t)\in\mathbb{R}^{l}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, $B_2\in\mathbb{R}^{l\times o}$ is the input matrix of $f_2(t)$, and $f_2(t)\in\mathbb{R}^o$ is the actuator fault signal .
-Let $\pmb{r}(t)=\begin{bmatrix}
+where $y(t)\in\mathbb{R}^{l}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, $B_2\in\mathbb{R}^{l\times o}$ is the input matrix of sensor fault signal $f_2(t)\in\mathbb{R}^o$.
+Let us define $\pmb{r}(t)=\begin{bmatrix}
     \int_{0}^{t}r^T(\tau)d\tau & r^T(t) & \dot{r}^T(t)
-\end{bmatrix}^T$ to modify the output equation (\ref{eq:agent output}) and putting it and (\ref{eq:linear f1}) together, we have the following system:
+\end{bmatrix}^T$ to modify the output equation (\ref{eq:agent output}) and combine it with (\ref{eq:linear f1}), we have the following tracking error dynamic system of an agent in the hybrid URTS:
 \begin{equation} \label{eq:error}
@@
 where $F_i(t)=\begin{bmatrix}
-    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-kh)
-\end{bmatrix}^T\in\mathbb{R}^{(k+1)n}$, $A_i\in\mathbb{R}^{{(k+1)n}\times{(k+1)n}}$, $v_i(t)$ is the model error, $C_i=\begin{bmatrix}
+    f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-wh)
+\end{bmatrix}^T\in\mathbb{R}^{(w+1)n}$, $A_i\in\mathbb{R}^{{(w+1)n}\times{(w+1)n}}$, $v_i(t)$ is the model error, $C_i=\begin{bmatrix}
         1 & 0 & \dots & 0
-    \end{bmatrix}\otimes I_{n_i}$, and $k$ is the smoothing signal model window size with $n_1=n$ and $n_2 = o$. Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get:
+    \end{bmatrix}\otimes I_{n_i}$, and $w$ is the window size of smoothing signal model with $n_1=n$ and $n_2 = o$.
+Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get the following augmented tracking error system of an agent:
 \begin{equation} \label{eq:e_bar}
@@
 % }
-Since the fault signals become a state variable of the augment system in (\ref{eq:e_bar}), a Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC:
+Since the fault signals become a state variable of the augmented tracking error system of an agent in (\ref{eq:e_bar}), their corruption on the tracking error dynamic system in (\ref{eq:error}) can be avoided.
+A Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC by the following estimation system:
 \begin{equation} \label{eq:e_hat}
@@
 \begin{assumption}
-    The augmented system (\ref{eq:e_bar}) is observable.
+    The augmented tracking error system (\ref{eq:e_bar}) of an agent is observable, i.e., $rank\begin{bmatrix}
+        zI-\bar{A} \\ \bar{C}
+    \end{bmatrix} = 3n + (w-1)n + (w-1)o, \forall z \in eig(\bar{A})$.
 \end{assumption}
-The PID FTC law is given as:
+The robust PID FTC law of each agent is given as:
 \begin{equation} \label{eq:Kx}
@@
 \end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
-Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, by the two subsystems (\ref{eq:e_bar}) and (\ref{eq:e_hat}), we get:
+Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, by the augmented tracking error system (\ref{eq:e_bar}) and the estimation system (\ref{eq:e_hat}), we get:
 \begin{equation} \label{eq:e_tilde}
@@
 \end{equation}
-Combining (\ref{eq:e_bar}), (\ref{eq:Kx}), and (\ref{eq:e_tilde}), we have the following augmented system:
+Combining (\ref{eq:e_bar}), (\ref{eq:Kx}), and (\ref{eq:e_tilde}), we have the following augmented tracking and estimation error system of each agent in the hybrid URTS:
 \begin{equation} \label{eq:aug}
@@
     \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$.
-Embed into the linearized system (\ref{eq:error}) to get the augment system (\ref{eq:aug}).
+Embed into the linearized system (\ref{eq:error}) to get the augmented system (\ref{eq:aug}).
     \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$.
@@
 Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
-Let us decompose the PID tracking error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
+Let us decompose the error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
 \begin{equation} \label{eq:linear subsys}
@@
 
-By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based stablized control performance with prescribed attenuation level $\rho_i$, where $s=3+(k-1)+(k-1)o_0$.
+By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based stablized control performance with prescribed attenuation level $\rho_i$, where $s=3+(w-1)+(w-1)o_0$.
 The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
@@
 
-Even though the design of the agent controller and observer has been completed, the trajectory design of UAV is not done yet.
-Since the UAV is an underactuated system, the "virtual" control input for UAV $u(t)=\begin{bmatrix}
-    f_x & f_y & f_z & \tau_x & \tau_y & \tau_z 
-\end{bmatrix}^T\in\mathbb{R}^6$ obtained from Theorem \ref{theorem1} needs to convert to actual control input $u'(t)=\begin{bmatrix}
-    F & \tau_x & \tau_y & \tau_z 
-\end{bmatrix}^T\in\mathbb{R}^4$.
-At the same time, the extra two degrees of freedom are used to find the remaining two reference trajectories $\phi_r$ and $\theta_r$ through inverse dynamics.
-That is to say, we want to find a total force $F$ and its angles $\phi_r$, $\theta_r$ and $\psi_r$ from the three component forces $f_x$, $f_y$ and $f_z$.
-By substituting $\Theta=\begin{bmatrix}
-    \phi_r \\ \theta_r \\ \psi_r
-\end{bmatrix}$ into $\begin{bmatrix}
-        f_x \\ f_y \\ f_z
-    \end{bmatrix} = R(\Theta)\begin{bmatrix}
-        0 \\ 0 \\ F
-\end{bmatrix} $ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
-
 The overall flowchart of tracking control is shown in Fig.
@@
 Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
-$\pmb{r}(t)$ then pass to observer to calculate the PID tracking error $\pmb{e}(t)$.
+$\pmb{r}(t)$ then pass to observer to calculate the error $\pmb{e}(t)$.
 Its differential, $\dot{\pmb{r}}(t)$, then input to controller for feedforward control.
@@
 \section{simulation results}
-In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy.
+In this section, a specific S\&R procedure for URTS is given to illustrate the proposed URTS system architecture and demonstrate the effectiveness of motion planning and control strategy.
 First, a S\&R area divided into $N_T$ areas, $area_i,i=1,2,...,N_T$, is given as shown in Fig.
@@
     K_\phi = K_\theta = K_\psi = 0.012$.
+
     \item designed parameters: 
@@
     $R = 0.02$.
-    % \item external disturbances: $d_1(t) = [ 10\sin(3t), \dots,$\\$ 10\sin(3t)] \in\mathbb{R}^6$, $f_2(t)=$
+
+    \item actuator coupling disturbance in \ref{eq:UAV couple}:
+    \\$c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$ where $D_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$ with $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$.
+    \item actuator non-coupling disturbance: $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T$.
+    \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:UAV, fa}.
 \end{enumerate}
@@
     $R = 0.002$.
+    \item actuator coupling disturbance in \ref{eq:UAV couple}:
+    \\ $c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, where $D_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$ with $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$.
+    \item actuator non-coupling disturbance: $d_1(t) = [10\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T$.
+    \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:robot, fa}.
 \end{enumerate}
@@
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig.
-\ref{fig:UAV, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [100\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq i}^{N_T}h_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:UAV couple}).
-Let $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$, then $h_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$.
+\ref{fig:UAV, fa}.
 The estimation of sensor fault $f_2(t)$ is shown in Fig.
-\ref{fig:UAV, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure.
+\ref{fig:UAV, fs}.
 The control effort is shown in Fig.
@@
 \textit{Robot:}
-The trajectories of reference, state and estimated state are shown in Fig. \ref{fig:robot, state}.
+The trajectories of reference, state and estimated state are shown in Fig.
+\ref{fig:robot, state}.
 The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig.
-\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t) = [10\sin(3t),...,10\sin(3t)]^T + \sum_{k = 1, k \neq j'}^{N_A}h_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, i.e., the non-couple term and the couple term in (\ref{eq:robot couple}).
-Let $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$, then $h_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$.
-
-The estimation of actuator fault $f_1(t)$ is shown in Fig.
-\ref{fig:robot, fa} where the distubance $d_1(t)$ in $f_1(t)$ is set as $d_1(t)=\sin(3t)$.
+\ref{fig:robot, fa}.
 The estimation of sensor fault $f_2(t)$ is shown in Fig.
-\ref{fig:robot, fs} where $f_2(t)$ is set as a smoothed square wave as shown in figure.
+\ref{fig:robot, fs}.
 The control effort is shown in Fig.
-\ref{fig:robot, control}
+\ref{fig:robot, control}.
 \begin{figure}[htbp]
@@
 In this study, a system architecture of URTS for R\&S usage is given.
-This gives a holistic view of the operational framework for UTRS.
-Next, we focus on part of the system architecture of UTRS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot.
+This gives a holistic view of the operational framework for URTS.
+Next, we focus on part of the system architecture of URTS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot.
 The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail.
 A robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC strategy is proposed to control the agents in URTS under the external disturbances.
-The control problem of UAV and robot are solved together via a transformation from a general agent model.
+The control problem of UAV and robot are solved together via a transformation from a general agent dynamics model.
 After analysis, the control problem is further transformed into a LMI-constrained optimization problem.

### 2022-11-17 paper/paper.tex
Revise paper V-agent. Add CalculateHinfPerformance()

@@
 Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
-In this paper, we assume that the tasks have been properly assigned so that every agent knows a destinition $q_{goal}$ it needs to go at every moment.
+In this paper, we assume that the tasks have been properly assigned so that every agent knows a destination $q_{goal}$ it needs to go at every moment.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
 \subsection{Path Planning}
-After a destinition $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
+After a destination $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
 There must exist multiple feasible paths to go.
@@
     \pmb{e}(t) \\ F_1(t) \\ F_2(t)
-\end{bmatrix}$, $\bar{A}=\begin{bmatrix}
+\end{bmatrix}$ is the augmented tracking error, $\bar{A}=\begin{bmatrix}
     A & BC_1 & 0 \\
@@
 The robust PID FTC law of each agent is given as:
-\begin{equation} \label{eq:Kx}
+\begin{equation} \label{eq:u_fb}
     u_{fb}(t)=K\hat{\bar{e}}(t)
@@
 \end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
-Let us define the estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, by the augmented tracking error system (\ref{eq:e_bar}) and the estimation system (\ref{eq:e_hat}), we get:
+Let us define the augmented estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, the augmented estimation error system can be obtained by (\ref{eq:e_bar}) and (\ref{eq:e_hat}):
 \begin{equation} \label{eq:e_tilde}
@@
 \end{equation}
-Combining (\ref{eq:e_bar}), (\ref{eq:Kx}), and (\ref{eq:e_tilde}), we have the following augmented tracking and estimation error system of each agent in the hybrid URTS:
-\begin{equation} \label{eq:aug}
+Combining (\ref{eq:e_bar}), (\ref{eq:u_fb}), and (\ref{eq:e_tilde}), we have the following augmented tracking and estimation error system of each agent in the hybrid URTS:
+\begin{equation} \label{eq:x_tilde}
     \dot{\tilde{x}}(t) = \tilde{A}\tilde{x}(t)+\tilde{v}(t)
@@
 
-In order to enable the designed control gain $K$ and observer gain $L$ to achieve a specific stablized performance for the system (\ref{eq:aug}) under the disturbance $\bar{v}(t)$, the $H_\infty$ observer-based stablized control performance below a prescribed disturbance attenuation level $\rho^2$ is given as:
+In order to enable the designed control gain $K$ in (\ref{eq:u_fb}) and observer gain $L$ in (\ref{eq:e_hat}) to achieve a specific performance for the augmented system in (\ref{eq:x_tilde}) under the disturbance $\bar{v}(t)$, the robust $H_\infty$ decentralized observer-based tracking control strategy below a prescribed disturbance attenuation level $\rho^2$ for each agent in hybrid URTS is given as:
 \begin{equation} \label{Hinf}
     % \begin{split}
+    \resizebox{1\hsize}{!}{    
         % & H_{\infty}(K, L) \\
         % & = 
-        \frac{\int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t) + u_{fb}^T(t)Ru_{fb}(t))dt - V(\tilde{x}(0))}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2
+        $\frac{\int_{0}^{t_f}(\bar{e}^T(t)Q_1\bar{e}(t) + \tilde{e}^T(t)Q_2\tilde{e}(t) + u_{fb}^T(t)Ru_{fb}(t))dt - V(\tilde{x}(0))}{\int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt}\leq \rho^2$
+    }
     % \end{split}
 \end{equation}
-where $t_f$ is the final time, $Q \geq 0$ is the weighting matrix of augmented state, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on augmented system(\ref{eq:aug}), and $\tilde{v}(t)$ is the total disturbance needs to be attenuated.
-If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented state $\tilde{x}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
-Before analyzing the $H_\infty$ observer-based stablized control problem in (\ref{Hinf}), the following lemmas are given:
+where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented system in (\ref{eq:x_tilde}), and $\tilde{v}(t)$ is the total disturbance needed to be attenuated.
+If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented tracking error $\bar{e}(t)$ and augmented estimation error $\tilde{e}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
+Before analyzing the robust $H_\infty$ decentralized observer-based tracking control problem of each agent in (\ref{Hinf}), the following lemmas are given:
 \begin{lemma}[\cite{boyd1994linear}] \label{lemma1}
@@
         K & -K
-    \end{bmatrix}$, then the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) can be achieved.
+    \end{bmatrix}$, $Q=\begin{bmatrix}
+        Q_1 & 0 \\ 0 & Q_2
+    \end{bmatrix}$, then the $H_\infty$ decentralized observer-based tracking control strategy in (\ref{Hinf}) can be achieved.
 \end{theorem}
 \begin{proof}
-    Choose the Lyapunov function $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)$ for the augmented system (\ref{eq:aug}) with $P=P^T>0$, we have:
+    Choose the Lyapunov function $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)$ for the augmented system (\ref{eq:x_tilde}) with $P=P^T>0$, we have:
     \begin{equation} \label{pf:1}
@@
     \end{equation}
-    By (\ref{eq:aug}) and Lemma \ref{lemma1}, we have:
+    By (\ref{eq:x_tilde}) and Lemma \ref{lemma1}, we have:
     \begin{equation} \label{pf:2}
@@
     \end{equation}
-    Substituting (\ref{pf:2}) and (\ref{eq:Kx}) into (\ref{pf:1}), we get:
+    Substituting (\ref{eq:u_fb}), (\ref{pf:2}) and $\tilde{x}^T(t)Q\tilde{x}(t)=\bar{e}^T(t)Q_1\bar{e}(t)+\tilde{e}^T(t)Q_2\tilde{e}(t)$ into (\ref{pf:1}), we get:
     \begin{equation*} \label{pf:3}
         \begin{split}
-            & \int_{0}^{t_f}(\tilde{x}^T(t)Q\tilde{x}(t))dt + u_{fb}^T(t)Ru_{fb}(t))dt \\
+            & \int_{0}^{t_f}(\bar{e}^T(t)Q_1\bar{e}(t)+\tilde{e}^T(t)Q_2\tilde{e}(t))dt + u_{fb}^T(t)Ru_{fb}(t))dt \\
             & \leq V(\tilde{x}(0)) + \int_{0}^{t_f}(\tilde{x}^T(t)(Q + P\tilde{A} + \tilde{A}^T P +\tilde{K}^TR\tilde{K}\\
@@
 
-Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ observer-based stablized control specification (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the variables.
-To solve the issue, a two-step design is exploit.
-
-\textit{Step 1:} First, let the Lyapunov function of augmented system (\ref{eq:aug}) be the sum of two Lyapunov function of subsystems (\ref{eq:e_bar}) and (\ref{eq:e_tilde}), i.e., $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)=\bar{e}^T(t)P_1\bar{e}(t)+\tilde{e}^T(t)P_2\tilde{e}(t)$.
-Second, let the augmented state energy be the sum of tracking error energy and estimated error energy, i.e., $\tilde{x}^T(t)Q\tilde{x}(t)=\bar{e}^T(t)Q_1\bar{e}(t)+\tilde{e}^T(t)Q_2\tilde{e}(t)$.
+Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the variables.
+To solve the issue, a two-step design is exploited.
+
+\textit{Step 1:} First, let the Lyapunov function of augmented system (\ref{eq:x_tilde}) be the sum of two Lyapunov function of subsystems (\ref{eq:e_bar}) and (\ref{eq:e_tilde}), i.e., $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)=\bar{e}^T(t)P_1\bar{e}(t)+\tilde{e}^T(t)P_2\tilde{e}(t)$.
 Substituting $P=\begin{bmatrix}
@@
 
-% Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:aug}).
-
-If we want to find the optimal $H_\infty$ observer-based stablized control specification for the system (\ref{eq:aug}), we need to solve the following LMIs-constrained optimization problem:
+% Finally, we can find the gains $K$ and $L=P_2^{-1}Y_2$ that achieve the $H_\infty$ observer-based stablized control performance in (\ref{Hinf}) of the augmented system (\ref{eq:x_tilde}).
+
+If we want to find the optimal $H_\infty$ decentralized observer-based tracking control strategy for the augmented system of each agent in (\ref{eq:x_tilde}), we need to solve the following LMIs-constrained optimization problem:
 \begin{equation} \label{LMI constraint}
     \begin{split}
-        & \rho^*=\mathop{\min}_{P,K,L} \rho \\
+        & \rho^{*2}=\mathop{\min}_{P,K,L} \rho^2 \\
         & s.t. (\refeq{eq:step1}),(\refeq{eq:step2}) 
@@
 
-The design procedure of the optimal $H_\infty$ observer-based feedforward-linearized PID FTC scheme for the agent (\ref{eq:agent d1}) is organized as follows.
+The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward-linearized PID FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
 \begin{enumerate}
-    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized system (\ref{eq:error})
+    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized tracking error dynamic system (\ref{eq:error})
     \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$.
-Embed into the linearized system (\ref{eq:error}) to get the augmented system (\ref{eq:aug}).
-    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$.
+Embed into the linearized system (\ref{eq:error}) to get the augmented tracking error system (\ref{eq:e_bar}).
+    \item Construct the robust PID FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
+    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
 \end{enumerate}
@@
 % \begin{proof}
-%     Let $W_1=P_1^{-1}$. By $\tilde{A}$ in (\ref{eq:aug}) and (\ref{eq:PQ}), and multiplying (\ref{BMI1}) left and right by $\begin{bmatrix}
+%     Let $W_1=P_1^{-1}$. By $\tilde{A}$ in (\ref{eq:x_tilde}) and (\ref{eq:PQ}), and multiplying (\ref{BMI1}) left and right by $\begin{bmatrix}
 %         W_1 & 0 \\ 0 & I
@@
 % \end{proof}
-Although the control gain and observer gain can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
-Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
+Although the control gain in (\ref{eq:u_fb}) and observer gain in (\ref{eq:e_bar}) for each agent in URTS can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
+Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems for each agent if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
 Let us decompose the error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
@@
 \begin{remark}
-    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
+    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
 In actual systems, this is usually done.
@@
 
-By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based stablized control performance with prescribed attenuation level $\rho_i$, where $s=3+(w-1)+(w-1)o_0$.
+By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based tracking control performance with a prescribed attenuation level $\rho_i$, where $s=3+(w-1)+(w-1)o_0$.
 The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
-    \mathit{v}_1 & \mathit{v}_2 & ... & \mathit{v}_n
-\end{bmatrix}^T, \mathit{v}_i=K_i^T\otimes\mathbf{e}_i$. The origin observer gain $L$ can be reconstructed in the same way.
+    \mathit{k}_1 & \mathit{k}_2 & ... & \mathit{k}_n
+\end{bmatrix}^T, \mathit{k}_i=K_i^T\otimes\mathbf{e}_i$. The origin observer gain $L$ can be reconstructed in the same way.
 
@@
 \ref{fig:tracking}.
-The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u(t)$ according to the output of local motion planning block $r'(t)$ and Theorem \ref{theorem1} $u'(t)$.
-The reference generator for robot is an identity function since it is a fully actuated system.
+The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u'(t)$ for each agent according to the output $r'(t)$ of local motion planning block and the control law $u(t)$ we design in (\ref{eq:control}).
 Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
 $\pmb{r}(t)$ then pass to observer to calculate the error $\pmb{e}(t)$.
-Its differential, $\dot{\pmb{r}}(t)$, then input to controller for feedforward control.
-The sensor measure not only the agent's own information (e.g., position or velocity) but environmental information.
+Its differential, $\dot{\pmb{r}}(t)$, then inputs to controller for feedforward control.
+The sensor measure not only the agent's own information (e.g., position or velocity) but also environmental information.
 The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
@@
     \centering
-    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control.
-The control scheme of UAV and robot is only different from the block, reference generator.
+    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
+The control scheme of UAV and robot in URTS is only different from the reference generator block.
 The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
-By introducing this block, a general feedforward-linearized PID FTC for an agent in URTS is proposed.}%
+By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}%
     \label{fig:tracking}
@@
 \section{simulation results}
-In this section, a specific S\&R procedure for URTS is given to illustrate the proposed URTS system architecture and demonstrate the effectiveness of motion planning and control strategy.
+In this section, a specific S\&R procedure for URTS is given to illustrate the proposed URTS system architecture and demonstrate the effectiveness of motion planning and control strategy of a hybrid UAVs and biped robots team system.
 First, a S\&R area divided into $N_T$ areas, $area_i,i=1,2,...,N_T$, is given as shown in Fig.
@@
 Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,5 \}$.
-At the beginning, the agents in $team_i$ are assigned the search tasks of $area_i$ to build the occupancy map and find goals.
+
+At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find goals.
 The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
 \ref{fig:S_task}.
-Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}$.
+Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}$.
 Suppose a goal is found after a while as shown in Fig.
-\ref{fig:S_task}, at this point, we have a rescue task $T_6$.
+\ref{fig:S_task}.
+At this point, we have a rescue task $T_6$.
 The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one.
@@
     \centering
-    \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in $i$th team at the begining.
-The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure).
+    \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in the $i$th team at the begining.
+The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinations $q_{goal}$ (black dots in figure).
 For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.
@@
 
-Following the procedure in Fig. \ref{fig:FandW}, the results of local motion planning of UAV flying and robot walking are shown in Fig. \ref{sim:flying} and \ref{sim:walking}.
+After $(\beta_n)$ is set, we can find the reference path $r[k]$ by local motion planning block.
+Following the procedure in Fig.
+\ref{fig:FandW}, the results of local motion planning of UAV flying and robot walking are shown in Fig.
+\ref{sim:flying} and \ref{sim:walking}, respectively.
 \begin{figure}[htbp]
@@
 
-Through the previous steps, the reference trajectory $r(t)$ of flying and walking has been designed. The remaining parameters are set as follow.
+Through the previous steps and the help of reference generator block, the reference trajectory $r(t)$ of flying behavior for each UAV and walking behavior for each biped robot has been designed in URTS.
+The remaining parameters are set as follows:
 
@@
     \item system parameters:
-    Initial value $\tilde{x}(0) = [\pmb{e}(0)^T, F_1(0)^T\mathbin{,} F_2(0)^T, \tilde{e}(0)]^T = [[0.1X, ..., 0.1X]^T, 0, 0, 0]^T$ where $X \sim \mathcal{N}(0, 1)$. $C_0 = I_3$.
-    \item designed parameters: $\rho=30$. Actuator and sensor smoothing signal model window sizes are $3$ and $4$, respectively.
+    Initial value $\tilde{x}(0) = [\pmb{e}(0)^T, F_1(0)^T\mathbin{,} F_2(0)^T, \tilde{e}(0)]^T = [[0.1X, ..., 0.1X]^T, 0, 0, 0]^T$ where $X \sim \mathcal{N}(0, 1)$.
+$C = C_0 \otimes I_n$ where $C_0 = I_3$.
+    \item designed parameters: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $3$ and $4$, respectively.
 \end{enumerate}

### 2022-11-17 src/functions/System/@Agent/Agent.m

@@ -63,6 +63,7 @@ classdef Agent
         PlotTC(ag) % Plot the results of tracking control
         [ag, xb] = CalculateNextState(ag, xb, d1, r, dr, ddr, i) % Calculate xb(i+1). Temporary method, the coupling between subclass (UAV_AGENTmodel and Robot) must be reduced
         PlotFault(ag, TITLE) % Plot fault estimation
+        y = GetHinfPerformance(ag)
 
     end
 end

### 2022-11-17 src/functions/System/@Agent/get_K_L.m

@@ -3,8 +3,9 @@ I = eye(ag.DIM_F);
 
 if ag.EXE_LMI
     disp('solving LMI ...')
-    [ag.K, ag.KL] = solveLMI10(sys_aug1.A, sys_aug1.B, sys_aug1.C, sys_aug1.E, sys_aug1.Q1, sys_aug1.Q2, sys_aug1.R, sys_aug1.rho);
-    
+    [ag.K, ag.KL, P1, P2] = solveLMI10(sys_aug1.A, sys_aug1.B, sys_aug1.C, sys_aug1.E, sys_aug1.Q1, sys_aug1.Q2, sys_aug1.R, sys_aug1.rho);
+    ag.sys_aug.P1 = kron(P1, I);
+    ag.sys_aug.P2 = kron(P2, I);
 %     norm(ag.KL)
 
     ag.Save('K') 

### 2022-11-17 test/Robot/oneRobot/oneRobot1.m

@@ -71,7 +71,7 @@ rho = sys_aug.rho;
 if EXE.LMI
     disp('solving LMI ...')
     % method 1
-    [rb.K, rb.KL] = solveLMI10(rb.sys_aug.A, rb.sys_aug.B, rb.sys_aug.C, sys_aug.E, Q1, Q2, R, rho);
+    [rb.K, rb.KL, P1, P2] = solveLMI10(rb.sys_aug.A, rb.sys_aug.B, rb.sys_aug.C, sys_aug.E, Q1, Q2, R, rho);
     % method 2
     % gain = zeros(1, WINDOW); gain(1) = -1;
     % [rb.K, rb.L] = solveLMI11(Ab, Cb, Eb, Q11, Q2, R, rho, kron(Ca, eye(DIM_F)), kron(A, eye(DIM_F)), kron(B, eye(DIM_F)));

### 2022-11-17 test/signalEstimation/smoothModel_Fa copy.m

@@ -73,7 +73,7 @@ for WINDOW = 2 : MAX_WINDOW
     
     gain = zeros(1, WINDOW); gain(1) = -1;
     % method 1
-    [K, L] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
+    [K, L, P2, P2] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
 %     K(1:DIM_U*DIM_F, DIM_F*DIM_X + (1:DIM_X2)) = kron(gain, eye(DIM_F));
     % method 2, remove unknown siganl state in augment state
 %     [K, L] = solveLMI11(Ab, Cb, Eb, Q11, Q2, R, rho, kron(Ca, eye(DIM_F)), kron(A, eye(DIM_F)), kron(B, eye(DIM_F)));

### 2022-11-17 test/signalEstimation/smoothModel_FaFs.m

@@ -71,7 +71,7 @@ for WINDOW = MIN_WINDOW : MAX_WINDOW
    
     gain = zeros(1, WINDOW); gain(1) = -1;
     % method 1
-    [K, L] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
+    [K, L, P1, P2] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
 %     L(1:2) = [-100; -200]*10;
 %     L(7:8) = [500; 1000];
 %     K(1:DIM_U*DIM_F, DIM_F*DIM_X + (1:DIM_X2)) = kron(gain, eye(DIM_F));

### 2022-11-17 test/signalEstimation/smoothModel_FaFs_v1.m

@@ -54,7 +54,7 @@ sys_aug.R = [];
 sys_aug.rho = 100;
 
 %% L, K
-[K, L] = solveLMI10(sys_aug.A, sys_aug.B, sys_aug.C, sys_aug.E, sys_aug.Q1, sys_aug.Q2, sys_aug.R, sys_aug.rho);
+[K, L, P1, P2] = solveLMI10(sys_aug.A, sys_aug.B, sys_aug.C, sys_aug.E, sys_aug.Q1, sys_aug.Q2, sys_aug.R, sys_aug.rho);
 % gain = zeros(1, sys_a.WINDOW); gain(1) = -1;
 % K(:, sys.DIM_X + (1:sys_a.DIM_X)) = kron(gain, eye(DIM_F));
 % L(sys.DIM_X+(1:sys_a.DIM_X), :) = -diag([100,200,700]);

### 2022-11-17 test/signalEstimation/smothModel_Fs.m

@@ -76,7 +76,7 @@ for WINDOW = 2 : MAX_WINDOW
     R = [];
     rho = 10;
 
-    [K, L] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
+    [K, L, P1, P2] = solveLMI10(Ab, Bb, Cb, Eb, Q1, Q2, R, rho);
 %     eig([Ab+Bb*K -Bb*K; zeros(5) Ab+L*Cb])
     %% trajectory
     x = zeros(DIM_X3, length(t));

### 2022-11-17 paper/paper.tex
Revise done, remain remark

@@
 The flowchart of decision-making and control process of URTS is also given.
-We divide it into five main hierarchical processes, i.e., taskallocation, path planning, behavior layer, local motion planning and tracking control.
+We divide it into five main hierarchical processes, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control.
 It is because the URTS needs to be able to assign different tasks to agents to perform first.
@@
     \centering
-    \includegraphics[scale=.13]{fig/behavior.png}\caption{The structure of behavior layer.
+    \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer.
 The leaves of the tree structure are the possible behaviors an agent can take.
@@
     \centering
-    \includegraphics[scale=.4]{fig/LMP.pdf}\caption{The flowchart of local motion planning.
+    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning.
 The corresponding motion planning will be executed according to the behavior determined by the behavior layer.
@@
 
-To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to tranfer the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig.
+To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig.
 \ref{fig:tracking}.
@@
 \ref{fig:tracking}.
+\begin{figure*}[htbp]
+    \centering
+    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
+The control scheme of UAV and robot in URTS is only different from the reference generator block.
+The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
+By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}%
+    \label{fig:tracking}
+\end{figure*}
 
@@
 
-Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the stable control problem of the linear system (\ref{eq:linear f1}) with fault signal by the feedforward linearization.
+Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the regulation problem of the linear system (\ref{eq:linear f1}) with fault signal by the feedforward linearization.
 The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
@@
 
+The overall flowchart of tracking control is shown in Fig.
+\ref{fig:tracking}.
+The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u'(t)$ for each agent according to the output $r'(t)$ of local motion planning block and the control law $u(t)$ we design in (\ref{eq:control}).
+Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
+$\pmb{r}(t)$ then pass to observer to calculate the error $\pmb{e}(t)$.
+Its differential, $\dot{\pmb{r}}(t)$, then inputs to controller for feedforward control.
+The sensor measure not only the agent's own information (e.g., position or velocity) but also environmental information.
+The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
+The letter is passed back to the high-level block for positioning, mapping and object recognition.
+
+\textit{
+    \begin{remark}
+        By the proposed agent dynamics model in (\ref{eq:agent}) and the introduction of reference generator block in Fig.
+\ref{fig:tracking}, the tracking control block of each agent $\alpha_{i,j}$ in the hybrid URTS can be designed by a general method.
+The decentralized architecture also ensures the scalability of URTS scale.
+More specifically, each agent $\alpha_{i,j},i=1,2,...,N_T,j=1,2,...,N_A$ will have its own state $x_{i,j}(t)$, reference trajectory $r_{i,j}(t)$, control gain $K_{i,j}$, etc.
+by introducing subscripts $i$ and $j$ to the corresponding variables.
+And the number of teams $N_T>0$ and number of agents in a team $N_A>0$ are scalable.
+    \end{remark}
+}
 % \begin{theorem} \label{theorem2}
@@
 % \end{proof}
+
 Although the control gain in (\ref{eq:u_fb}) and observer gain in (\ref{eq:e_bar}) for each agent in URTS can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
@@
 
-The overall flowchart of tracking control is shown in Fig.
-\ref{fig:tracking}.
-The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u'(t)$ for each agent according to the output $r'(t)$ of local motion planning block and the control law $u(t)$ we design in (\ref{eq:control}).
-Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
-$\pmb{r}(t)$ then pass to observer to calculate the error $\pmb{e}(t)$.
-Its differential, $\dot{\pmb{r}}(t)$, then inputs to controller for feedforward control.
-The sensor measure not only the agent's own information (e.g., position or velocity) but also environmental information.
-The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
-The letter is passed back to the high-level block for positioning, mapping and object recognition.
-
-\begin{figure*}[htbp]
-    \centering
-    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
-The control scheme of UAV and robot in URTS is only different from the reference generator block.
-The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
-By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}%
-    \label{fig:tracking}
-\end{figure*}
-
 \section{simulation results}
@@
     \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in the $i$th team at the begining.
-The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinations $q_{goal}$ (black dots in figure).
+The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinations $q_{goal}$ (black dots in figure) obtained from task allocation block.
 For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.
-For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
+For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.}
     \label{fig:S_task}
@@
 To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_6)$ and $(\alpha_{i,1}, T_1)$ as example.
+For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly assigned as shown in Fig.
+\ref{sim:flying} without going through path planning by \textit{Assumption \ref{asm:collision}}.
+The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
 For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$.
@@
 We choose the walking behavior to illustrate the local motion planning block of robots.
-
-For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly assigned as shown in Fig.
-\ref{sim:flying} without going through path planning by \textit{Assumption \ref{asm:collision}}.
-The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
 \begin{figure}[htbp]
@@
     \item system parameters:
-    $B_{2,0} = [0, 0.1, 1]^T$,
+    $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0.1, 1]^T$.
     $g = 9.81, m = 2,
@@
 
-    \item actuator coupling disturbance in \ref{eq:UAV couple}:
-    \\$c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)$ where $D_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$ with $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$.
-    \item actuator non-coupling disturbance: $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T$.
+    \item actuator coupling disturbance in (\ref{eq:UAV couple}):
+    \\$c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)\in\mathbb{R}^6$ where $D_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$ with $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$.
+    \item actuator non-coupling disturbance:
+    \\ $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T\in\mathbb{R}^6$.
     \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:UAV, fa}.
@@
 \textit{Robots:} \begin{enumerate}
-    \item system parameters: Appendix E in \cite{ourrobot}. $B_{2,0} = [0, 0, 1]^T$.
+    \item system parameters: $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0, 1]^T$. Remaining parameters can be found in Appendix E in \cite{ourrobot}. 
     \item designed parameters:
@@
     $R = 0.002$.
-    \item actuator coupling disturbance in \ref{eq:UAV couple}:
-    \\ $c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)$, where $D_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$ with $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$.
-    \item actuator non-coupling disturbance: $d_1(t) = [10\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T$.
+    \item actuator coupling disturbance in (\ref{eq:robot couple}):
+    \\ $c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)\in\mathbb{R}^{12}$ where $D_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$ with $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$.
+    \item actuator non-coupling disturbance:
+    \\ $d_1(t) = [10\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T\in\mathbb{R}^{12}$.
     \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:robot, fa}.
@@
 
-The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{i,1}$ and the robot $\alpha_{i,2}$ are given as follow.
-
-\textit{UAV:}
+The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ in $team_1$ are given as follows:
+
+\textit{UAV $\alpha_{1,1}$:}
 The trajectories of reference, state and estimated state are shown in Fig.
 \ref{fig:UAV, state}.
-The estimation of actuator fault $f_1(t)\in\mathbb{R}^6$ is shown in Fig.
+The estimation of actuator fault $f_1(t)$ is shown in Fig.
 \ref{fig:UAV, fa}.
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{i,1}$}
+    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{i,1}$}%
+    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{1,1}$}%
     \label{fig:UAV, control}
@@
 
-\textit{Robot:}
+\textit{Robot $\alpha_{1,2}$:}
 The trajectories of reference, state and estimated state are shown in Fig.
 \ref{fig:robot, state}.
-The estimation of actuator fault $f_1(t)\in\mathbb{R}^{12}$ is shown in Fig.
+The estimation of actuator fault $f_1(t)$ is shown in Fig.
 \ref{fig:robot, fa}.
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{i,2}$.}%
+    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{1,2}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,2}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{i,2}$}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,2}$}%
     \label{fig:robot, control}
@@
 In Fig.
-\ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach steady state wihtin $2$ second.
-There is a brief jitter when the sensor fault signal changes drastically, but it returns quickly to steady state.
+\ref{fig:UAV, state}, the tracking and estimation errors of UAV position and attitude reach the steady state all within $2$ seconds.
+There is a brief jitter when the sensor fault signal changes drastically, but it returns quickly to the steady state.
 In Fig.
-\ref{fig:robot, state}, the tracking and estimation errors of robot joint angles immediately reach and maintain steady under the influence of fault signals.
-In Fig \ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., disturbances and feedforward errors, can be effectively estimated.
-However, in Fig \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change and returns to a steady state after about $3$ seconds.
-In Fig \ref{fig:UAV, control} and \ref{fig:robot, control}, the control efforts has high frequency and high amplitude performance at the initial instance due to the high gain characteristic of the robust control.
+\ref{fig:robot, state}, the tracking and estimation errors of robot joint angles immediately reach and maintain steady state under the influence of fault signals.
+In Figs.
+\ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., feedforward control errors and disturbances, can be effectively estimated.
+However, in Figs.
+\ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change and returns to a steady state after about $2$ seconds.
+In Figs.
+\ref{fig:UAV, control} and \ref{fig:robot, control}, the control efforts have high frequency and high amplitude at the initial instance due to the high gain characteristic of the robust control.
 After that, they maintain the sine wave shape to offset the estimated actuator fault value.
-Besides, it can be seen that the total force $F$ remains constant against gravity in Fig \ref{fig:UAV, control}.
+Besides, it can be seen that the total force $F$ of UAV remains constant against gravity in Fig.
+\ref{fig:UAV, control}.
 % The transient responses that occur later are caused from fault signals, especially the sensor fault.
@@
 
-For further verification, we visualized the simulation of a team in URTS and the configuration trajectory of biped robot on the online resource (cite:online source).
-The results again demonstrate the effectiveness of the proposed method.
+For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource (cite:online source).
+The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized PID FTC method for agents in URTS.
 
 \section{conclusion}
-In this study, a system architecture of URTS for R\&S usage is given.
+In this study, a system architecture of URTS is given for S\&R usage.
 This gives a holistic view of the operational framework for URTS.
-Next, we focus on part of the system architecture of URTS, i.e., the reference trajectory design of UAV flying and robot walking and controller design of UAV and robot.
-The procedure of reference trajectory design method of UAV flying and robot walking is also given in detail.
-A robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC strategy is proposed to control the agents in URTS under the external disturbances.
-The control problem of UAV and robot are solved together via a transformation from a general agent dynamics model.
-After analysis, the control problem is further transformed into a LMI-constrained optimization problem.
-Through two-step design procedure, the problem is effectively solved by MATLAB LMI Toolbox.
-The simulation results give an example of the proposed URTS architecture to more concretely illustrate its operational flow.
-Finally, the effectiveness of the designed controller and observer is also verified by the simulation results.
+By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common path planning algorithm can be applied in URTS.
+Next, we focus on the local motion planning of UAV flying and robot walking behavior.
+Besides, the bridging method between the reference path designed by local motion planning and the tracking control design is also given.
+By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analysis together.
+Through a feedforward-linearized strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
+Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system.
+After that, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC strategy is proposed for each agent in the hybrid URTS.
+To solve the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
+A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works.
+Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC method is also verified by the simulation results.
 In the future, we will...

### 2022-11-17 paper/paper.tex
Revise paper, add remark

@@
 \newtheorem{assumption}{Assumption}[section]
-\newtheorem{ramark}{Remark}[section]
+% \newtheorem{remark}{Remark}[section]
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
@@
     \dot{X} \\ \dot{\Theta}
-\end{bmatrix}$, and $n=6$. For robots, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$.
+\end{bmatrix}$, and $n=6$ by (\ref{eq:uav}). For robots, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by (\ref{eq:robot}).
 
@@
 The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
-By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}%
+By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}
     \label{fig:tracking}
 \end{figure*}
+
+\textit{
+    \begin{remark}
+        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r[k]_{i,j}$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the URTS works as we expect since the previous blocks have completed their respective responsibilities and found the corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r[k]_{i,j}$.
+That is, $r_{i,j}(t)$ is the reference trajectory that can complete specific task, follow specific path and perform specific behavior.
+    \end{remark}
+}
 

### 2022-11-23 paper/paper.tex
Revise paper, citation ok. Add author.

@@
 \usepackage[inline]{enumitem}
-
-% \usepackage{amsmath}
-% \usepackage{amsfonts}
-% \usepackage{amssymb}
-% \usepackage{fontspec}
-% \setmainfont{TeX Gyre Termes}
-
-\setcounter{MaxMatrixCols}{30}
-\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
+\usepackage[hyphens]{url}
+
+% \setcounter{MaxMatrixCols}{30}
+% \providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
 \newtheorem{theorem}{Theorem}
-\newtheorem{acknowledgement}[theorem]{Acknowledgement}
-\newtheorem{algorithm}[theorem]{Algorithm}
-% \newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-% \newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-% \newtheorem{condition}[theorem]{Condition}
-% \newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}[theorem]{Corollary}
-% \newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}[theorem]{Definition}
-% \newtheorem{example}[theorem]{Example}
-% \newtheorem{exercise}[theorem]{Exercise}
+% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
+% \newtheorem{algorithm}[theorem]{Algorithm}
+% \newtheorem{case}[theorem]{Case}
+% \newtheorem{conclusion}[theorem]{Conclusion}
+% \newtheorem{corollary}[theorem]{Corollary}
+% \newtheorem{definition}[theorem]{Definition}
 \newtheorem{lemma}{Lemma}
-\newtheorem{notation}{Notation}
-\newtheorem{problem}[theorem]{Problem}
-% \newtheorem{proposition}[theorem]{Proposition}
+% \newtheorem{notation}{Notation}
+% \newtheorem{problem}[theorem]{Problem}
 \newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-% \newtheorem{summary}[theorem]{Summary}
+% \newtheorem{solution}[theorem]{Solution}
 \newtheorem{assumption}{Assumption}[section]
-% \newtheorem{remark}{Remark}[section]
 \newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
@@
 \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
+
 \doi{10.1109/ACCESS.2017.DOI}
@@
 \title{Motion Planning and Robust Fault-Tolerant Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}
-% \author{\uppercase{First A. Author}\authorrefmark{1}, \IEEEmembership{Fellow, IEEE},
-% \uppercase{Second B. Author\authorrefmark{2}, and Third C. Author,
-% Jr}.\authorrefmark{3},
-% \IEEEmembership{Member, IEEE}}
+
+\author{\uppercase{Bor-Sen Chen}\authorrefmark{1,2}, \IEEEmembership{Life
+Fellow, IEEE}, \uppercase{Ting-Wei Hung\authorrefmark{1}}}
+
+\address[1]{Department of Electrical Engineering, National Tsing Hua
+University, Hsinchu 30013, Taiwan} \address[2]{Department of Electrical
+Engineering, Yuan Ze University, Taoyuan 32003, Taiwan}
+
+\tfootnote{This work was supported by the Ministry of Science and Technology
+of Taiwan under Grant MOST 108-2221-E-007-099-MY3.}
+
+\markboth
+{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
+{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
+
+\corresp{Corresponding author: Bor-Sen Chen (bschen@ee.nthu.edu.tw)}
 % \address[1]{National Institute of Standards and 
@@
 Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
-Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{9476736}.
+Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{skaltsis2021survey}.
 Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc \cite{zhang2018path}.
@@
 This problem is referred to a task allocation problem or multi-robot task allocation problem.
-A problem formulation and a mathematical model of problem can be found in \cite{Khamis2015}.
+A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}.
 Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
@@
 
-For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource (cite:online source).
+For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
 The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized PID FTC method for agents in URTS.
@@
 % \nocite{*}
-\bibliographystyle{unsrt}
+\bibliographystyle{ieeetr}
 \bibliography{citation}
+% \begin{thebibliography}{00}
+%     \bibitem{9700861} L. Kloeker, T. Moers, L. Vater, A. Zlocki, and L. Eckstein, “Utilization
+%     and potentials of unmanned aerial vehicles (uavs) in the field of automated
+%     driving: A survey,” in 2021 5th International Conference on Vision, Image
+%     and Signal Processing (ICVISP), pp. 9–17, 2021
+% \end{thebibliography}
 

### 2022-11-24 paper/paper.tex
Revise whole paper again, 2nd

@@
 Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
-Therefore, the output of this block is also a path but with a timescale, i.e., sampling period.
-This path is often referred as a desired reference trajectory $r(t)$.
-$r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation.
-Note that the path and trajectory are distinguished in some literature.
-Different from path $(\sigma_n)$, a trajectory $r(t)$ has considered the time in physic world.
-We also distinguish in this way in this article.
+Therefore, the output of this block is also a path $r[k]$.
 The flowchart of local motion planning block is shown in Fig.
@@
 \subsection{Tracking Control}
+To analysis the control problem in the continuous time domain, $r[k]$ will first convert to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
+By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is designed.
+$r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation.
+Note that the path and trajectory are distinguished in some literature.
+Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
+We also distinguish in this way in this article.
+
 If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect.
@@
 \section{Tracking control of each agent in hybrid URTS}
-To analyze the tracking control problem of UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) together, we represent them by the same form called agent dynamics model through some appropriate variable transformations:
+Before converting $r[k]$ to $r(t)$, we first convert the UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) into a form called agent dynamic model to analyze their tracking control problems together.
+Through some appropriate variable transformations, we have:
 \begin{equation} \label{eq:agent} 
@@
 \end{equation}
-where $r(t)\in\mathbb{R}^n$ is the reference trajectory, $M(r(t)), \ddot{r}(t)\mathbin{,} H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
+where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t)), \ddot{r}(t)\mathbin{,} H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
 For UAVs, we have $u(t)=\begin{bmatrix}
@@
     \begin{remark}
-        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r[k]_{i,j}$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the URTS works as we expect since the previous blocks have completed their respective responsibilities and found the corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r[k]_{i,j}$.
+        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r_{i,j}[k]$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the URTS works as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found the corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
 That is, $r_{i,j}(t)$ is the reference trajectory that can complete specific task, follow specific path and perform specific behavior.
@@
 The decentralized architecture also ensures the scalability of URTS scale.
-More specifically, each agent $\alpha_{i,j},i=1,2,...,N_T,j=1,2,...,N_A$ will have its own state $x_{i,j}(t)$, reference trajectory $r_{i,j}(t)$, control gain $K_{i,j}$, etc.
-by introducing subscripts $i$ and $j$ to the corresponding variables.
-And the number of teams $N_T>0$ and number of agents in a team $N_A>0$ are scalable.
+More specifically, let us introduce subscripts $i$ and $j$ to the corresponding variables of each agent $\alpha_{i,j},i=1,2,...,N_T,j=1,2,...,N_A$ (e.g., the state $x_{i,j}(t)$, the reference trajectory $r_{i,j}(t)$, the control gain $K_{i,j}$, etc.).
+It can be seen that the number of teams $N_T>0$ and the number of agents in a team $N_A>0$ are scalable.
     \end{remark}

### 2022-11-24 src/URTS main script/UAV/oneUAV_FaFs.m

@@ -7,7 +7,7 @@ uav = UAV_AGENTmodel();
 % flow control of code
 uav.EXE_LMI     = 0; % solving LMI
 uav.EXE_TRAJ    = 0; % trajectory
-uav.EXE_PLOT    = 0; % plot results
+uav.EXE_PLOT    = 1; % plot results
 
 % time
 uav.tr.dt   = .001; % Time step
@@ -122,8 +122,8 @@ if uav.EXE_PLOT
     r = uav.tr.r{1};
     
     %% Tracking control results
-%     PlotLMP(uav)
-    uav.PlotTC(); 
+    PlotLMP(uav)
+%     uav.PlotTC(); 
     % PlotActualControl(uav) % Actual control input
     
     %% 3D, r(t), state

### 2022-11-24 paper/paper.tex
small revise paper

@@
         \end{bmatrix}
-        % form 2
+        % Form 2 of rotation matrix R(\Theta)
         % &R(\Theta)=\begin{bmatrix*}[l]
@@
     f_i^T(t) & f_i^T(t-h) & \dots & f_i^T(t-wh)
-\end{bmatrix}^T\in\mathbb{R}^{(w+1)n}$, $A_i\in\mathbb{R}^{{(w+1)n}\times{(w+1)n}}$, $v_i(t)$ is the model error, $C_i=\begin{bmatrix}
+\end{bmatrix}^T\in\mathbb{R}^{(w_i+1)n_i}$, $A_i\in\mathbb{R}^{{(w_i+1)n_i}\times{(w_i+1)n_i}}$, $v_i(t)$ is the model error, $C_i=\begin{bmatrix}
         1 & 0 & \dots & 0
-    \end{bmatrix}\otimes I_{n_i}$, and $w$ is the window size of smoothing signal model with $n_1=n$ and $n_2 = o$.
+    \end{bmatrix}\otimes I_{n_i}$, and $w_i$ is the window size of smoothing signal model with $n_1=n$ and $n_2 = o$.
 Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get the following augmented tracking error system of an agent:
@@
         zI-\bar{A} \\ \bar{C}
-    \end{bmatrix} = 3n + (w-1)n + (w-1)o, \forall z \in eig(\bar{A})$.
+    \end{bmatrix} = 3n + (w_1+1)n + (w_2+1)o, \forall z \in eig(\bar{A})$.
 \end{assumption}
@@
 Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems for each agent if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
-Let us decompose the error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}^1$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
+Let us decompose
+the error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, 
+the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, 
+the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, 
+the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, 
+and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ 
+where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
 \begin{equation} \label{eq:linear subsys}
@@
 
-By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based tracking control performance with a prescribed attenuation level $\rho_i$, where $s=3+(w-1)+(w-1)o_0$.
+By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based tracking control performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
 The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
@@
 $C = C_0 \otimes I_n$ where $C_0 = I_3$.
-    \item designed parameters: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $3$ and $4$, respectively.
+    \item designed parameters: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $w_1=3$ and $w_2=4$, respectively.
 \end{enumerate}
@@
     \item actuator non-coupling disturbance:
-    \\ $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T\in\mathbb{R}^6$.
+    \\ $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 100\sin(3t)]^T\in\mathbb{R}^6$.
     \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:UAV, fa}.

### 2022-11-25 paper/paper.tex
ieeetr->IEEEtran, change http://

@@
 The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
-\begin{equation}
+\begin{equation} \label{eq:x_zmp}
     x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
@@
 where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$.
-However, it is difficult to directly calculate the analytical solution of $q_r$ through (6).
-Since there is a complex coordinate transformation between $q_r$ and $x_i, z_i, \ddot{\Omega}_{iy}$.
-At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r$.
+However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}).
+Since there is a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$.
+At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r(t)$.
 To simplify this complex problem, an approximate solution can be derived through 3D-LIPM.
@@
 % \nocite{*}
-\bibliographystyle{ieeetr}
+\bibliographystyle{IEEEtran}
 \bibliography{citation}

### 2022-12-02 paper/paper.tex
Description of tracking control flowchart. UAV model remark.

@@
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem which can be solved by a two-step design procedure.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized FTC of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem which can be solved by a two-step design procedure.
 With the help of MATLAB LMI Toolbox, the tracking problem of each UAV and robot in URTS is effectively solved.
@@
 Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
-Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed to deal with the control problem in URTS.
+Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed to deal with the control problem in URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
@@
 In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
-In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
 In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method.
@@
 $g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
-This model treats the UAV as a mass point and can control the force in the $z$ direction and the torque in the $x$, $y$ and $z$ direction.
-Hence, the reference trajectory of UAV $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$, where the subscript $r$ denotes the reference.
+This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$.
+For UAV, the reference trajectory $r(t)=[x_r(t),y_r(t),z_r(t),\phi_r(t),\theta_r(t),\psi_r(t)]^T\in\mathbb{R}^{6}$ is in the task space, where the subscript $r$ denotes the reference.
+
+\textit{
+    \begin{remark}
+        Since the quadrotor has four rotors, we only have four control input.
+To simplify the model, the UAV (quadrotor) dynamic model in (\ref{eq:uav}) considers $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors.
+Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system.
+    \end{remark}
+}
 
@@
 For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
-Besides, it can be seen that the control input $u(t)=[f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design of UAV (\ref{eq:control}) is different from the actual control input for actuator $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ of UAV since UAV is an underactuated system.
+Besides, for UAV, it can be seen that the control input $u(t)=[f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actual control input for actuator $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ since UAV is an underactuated system.
 The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem.
@@
     \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
-The control scheme of UAV and robot in URTS is only different from the reference generator block.
-The reason is that the underactuated nature of the UAV imposes the limitation on the control input and reference trajectory.
-By introducing this block, a general $H_\infty$ decentralized observer-based feedforward-linearized PID FTC for an agent in URTS is proposed.}
+(a) The tracking control block of each agent in hybrid URTS.
+The reference generator block and control block are predefined processes defined in (b) and (c).
+The control block (the proposed general $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
+It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actual control input $u'(t)\in\mathbb{R}^4$ different for UAV.
+The reference generator block is introduced to deal with this problem.
+(b) The reference generator blocks for UAV and robot are different since UAV is an underactuated system.
+For UAV, we need to calculate $u'(t)$ and $r(t)$ from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}).
+For robot, $u'(t)=u(t)$ and $r(t)=r'(t)$ since the system is fully actuated.
+(c) The proposed general $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme for each agent in hybrid URTS.}
     \label{fig:tracking}
@@
 \end{assumption}
-The robust PID FTC law of each agent is given as:
+The robust FTC law of each agent is given as:
 \begin{equation} \label{eq:u_fb}
@@
 
-The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward-linearized PID FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
+The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
 \begin{enumerate}
@@
 Embed into the linearized system (\ref{eq:error}) to get the augmented tracking error system (\ref{eq:e_bar}).
-    \item Construct the robust PID FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
+    \item Construct the robust FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
     \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
@@
 For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
-The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized PID FTC method for agents in URTS.
+The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized FTC method for agents in URTS.
 
@@
 Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system.
-After that, a robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC strategy is proposed for each agent in the hybrid URTS.
-To solve the robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
+After that, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC strategy is proposed for each agent in the hybrid URTS.
+To solve the robust $H_\infty$ decentralized observer-based feedforward-linearized FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
 A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works.
-Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward-linearized PID FTC method is also verified by the simulation results.
+Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward-linearized FTC method is also verified by the simulation results.
 In the future, we will...

### 2022-12-06 paper/paper.tex
Revise paper Section II, done

@@
 
-\title{Motion Planning and Robust Fault-Tolerant Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}
+\title{Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}
 
@@
 The system architecture of URTS is proposed at first to illustrate the issues to be addressed in URTS and the relationships between them.
-The task allocation and path planning problems are first investigated and stated.
-Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAV and robot.
-The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics model of UAV and robot into a unified agent dynamics model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS.
+The task allocation and path planning problems are first investigated.
+Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAVs and robots in the hybrid team system.
+The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
+By converting the dynamics models of UAV and robot into a unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward fault-tolerant control (FTC) strategy is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized FTC of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem which can be solved by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the tracking problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed tracking control method under the external disturbance and the actuator and sensor fault.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
+With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking problem of each UAV and robot in URTS is effectively solved.
+Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed $H_\infty$ decentralized fault-tolerant tracking control method of hybrid URTS under the external disturbance and the actuator and sensor fault.
 \end{abstract}
@@
 It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans.
-Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc \cite{9700861}.
+Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc.
+\cite{9700861}.
 Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}.
@@
 Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
-Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{skaltsis2021survey}.
-Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc \cite{zhang2018path}.
+Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc.
+\cite{skaltsis2021survey}.
+Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc.
+\cite{zhang2018path}.
 Collision avoidance is to avoid collision with obstacles.
@@
 The flowchart of decision-making and control process of URTS is also given.
-We divide it into five main hierarchical processes, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control.
+We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) tracking control.
 It is because the URTS needs to be able to assign different tasks to agents to perform first.
 After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned.
-To make agent move on the path, a behavior corresponding to the environment is required to determine.
+To make agent move on the path, a behavior corresponding to the environment is required to be determined.
 Then, a local motion corresponding to the behavior of the agent needs to be designed.
@@
 It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
-In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for each agent to follow.
+In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation
+and specify an independent trajectory for each agent to follow.
 
@@
 In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller.
-Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
-Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed to deal with the control problem in URTS.
+Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
+Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed to deal with the control problem in hybrid URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
@@
 \begin{enumerate}
-    \item A system architecture and system flow of URTS for the purpose of S\&R are proposed so that the issues involved in URTS and their relationships can be defined and resolved.
-    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the tracking control of agents in URTS.
-    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
+    \item A system architecture and system flow of hybrid URTS for the purpose of S\&R are proposed so that the issues involved in hybrid URTS and their relationships can be defined and resolved.
+    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the team formation tracking control of agents in hybrid URTS.
+    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based fault-tolerant tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
 \end{enumerate}
@@
 The remainder of the paper is organized as follows.
-In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship of its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described.
-In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
-In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
+In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship among its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described.
+In Section III, the dynamics models of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
 In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method.
@@
 Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$.
-The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1}$.
+The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$.
 Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making.
@@
 Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station.
-The ground station will combine this information with the goal location assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby.
+The ground station will combine this information with the goal location assigned by task allocation algorithm and then make a decision to avoid obstacles and other agents nearby.
 % That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
@@
 \subsection{Task Allocation}
-In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
+In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
 However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
-Therefore, the results of task allocation can be "good or bad", which leads us to find the optimal allocation.
+Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation.
 This problem is referred to a task allocation problem or multi-robot task allocation problem.
@@
 Similar to task allocation, we usually want to find an optimal path.
-There are several path planning algorithm to handle this problem.
+There are several path planning algorithms to handle this problem.
 Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS.
@@
 Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
-The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robot).
-In this case, a unified planner will become overly complex and impracticable.
+The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robots).
+In this case, an unified planner will become overly complex and impracticable.
 Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning.
-The path planning block becomes a global planner and regard an agent as a point without kinodynamic constraints.
-The local motion planning block becomes a local planner and consider the motion planning of a specific behavior.
+The path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints.
+The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
 % In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
@@
 Path planning tells agents where to go but not how since we regard the agent as a point.
-Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario.
+Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario.
 These behaviors with changing position are classified as "moving" behavior in this paper.
@@
 where $\mathcal{B}$ is the set of behaviors.
-It is to say that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
+It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
 By the object information in Fig.
@@
 \subsection{Local Motion Planning}
-After a specific behavior is determined, the next step is to design a motion to achieve that behavior.
-Local motion planning block is like path planning block but its scale is smaller and its resolution and precision must be higher.
-Collision checking is needed since we consider agent as a point in path planning block and it is a real mechanical body here.
+After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior.
+Local motion planning block is like path planning block but with smaller scale and higher resolution and precision.
+Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here.
 Furthermore, the kinodynamic constraint is handled in this block.
@@
 In Fig.
-\ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are added to illustrate the flow of this block.
+\ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block.
 To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
-They are belong to moving behavior in Fig.
+They are belong to the moving behavior in Fig.
 \ref{fig:LocalMotionPlanning}.
@@
 \subsection{Tracking Control}
-To analysis the control problem in the continuous time domain, $r[k]$ will first convert to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
+To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
 By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is designed.
@@
 Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world.
-We also distinguish in this way in this article.
+We also distinguish them in this way in this article.
 
 If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect.
-To this end, a control method need to be design.
+To this end, a control method needs to be designed.
 It will be discussed detailly in Section IV.
@@
 In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first.
-After the system description of UAV and robot, the motion planning of flying and walking as shown in Fig.
+After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig.
 \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
@@
 The reference generator block and control block are predefined processes defined in (b) and (c).
-The control block (the proposed general $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
+The control block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
 It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actual control input $u'(t)\in\mathbb{R}^4$ different for UAV.
@@
 For robot, $u'(t)=u(t)$ and $r(t)=r'(t)$ since the system is fully actuated.
-(c) The proposed general $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme for each agent in hybrid URTS.}
+(c) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
     \label{fig:tracking}
@@
 
-The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
+The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
 \begin{enumerate}
@@
 \begin{remark}
-    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that $\pmb{e}_i(t)$, the PID error of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
+    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that the error $\pmb{e}_i(t)$ of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
 In actual systems, this is usually done.
@@
 For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
-The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized FTC method for agents in URTS.
+The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method for agents in URTS.
 
@@
 By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analysis together.
-Through a feedforward-linearized strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
+Through a feedforward strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
 Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system.
-After that, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC strategy is proposed for each agent in the hybrid URTS.
-To solve the robust $H_\infty$ decentralized observer-based feedforward-linearized FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
+After that, a robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for each agent in the hybrid URTS.
+To solve the robust $H_\infty$ decentralized observer-based feedforward FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
 A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works.
-Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward-linearized FTC method is also verified by the simulation results.
+Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward FTC method is also verified by the simulation results.
 In the future, we will...

### 2022-12-06 paper/paper.tex
Recise paper, IV, done

@@
 Additionally, few literatures illustrate the relationship between these problems.
-This leads us to propose a system architecture of hyibrid UAVs and biped robots team system (URTS) for S\&R usage.
+This leads us to propose a system architecture of hybrid UAVs and biped robots team system (URTS) for S\&R usage.
 The flowchart of decision-making and control process of URTS is also given.
@@
     \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer.
+(a) The behavior set of each agent in URTS.
 The leaves of the tree structure are the possible behaviors an agent can take.
-The behavior to be took at every moment will be decided in this block.}%
+The behavior to be took at every moment by each agent will be decided in this block.
+For UAVs, the moving behavior set is predefined in (b).
+For robots, the moving behavior set is predefined in (c).
+(b) The moving behavior set of each UAV.
+(c) The moving behavior set of each robot.}%
     \label{fig:behavior}
@@
 The flowchart of local motion planning block is shown in Fig.
-\ref{fig:LocalMotionPlanning}
+\ref{fig:LMP}
 \begin{figure*}[htbp]
@@
     \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning.
-The corresponding motion planning will be executed according to the behavior determined by the behavior layer.
+(a) The local motion planning of each agent in URTS .
+The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer.
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
-The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.}
-    \label{fig:LocalMotionPlanning}
+The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
+For UAVs, the moving block is predefined in (b).
+For robots, the moving block is predefined in (c).
+(b) The moving block of each UAV where the flying block is predefined in \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in \ref{fig:FandW}}
+    \label{fig:LMP}
 \end{figure*}
@@
 In Fig.
-\ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block.
+\ref{fig:LMP}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block.
 To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
 They are belong to the moving behavior in Fig.
-\ref{fig:LocalMotionPlanning}.
+\ref{fig:LMP}.
 A more detailed description will be given in the next section.
@@
 \section{system description of UAVs and biped robots in URTS}
-In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first.
+In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first.
 After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig.
@@
     \centering
-    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of Flying and Walking.
+    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}.
 In both blocks, a smoothed path is obtained by post-processing first.
 Then the respective motion of behavior is designed.
-The final outputs of Flying and Walking are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
+    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
+    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
+    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
     \label{fig:FandW}
@@
 \subsection{motion planning of flying of UAV}
-A dynamic model about how the UAV moves in the physical world is given first. By Newton-Euler equation, the dynamic model of UAV can be formulated as \cite{sabatino2015quadrotor}:
+A dynamic model about how an UAV in URTS moves in the physical world is given first. By Newton-Euler equation, the dynamic model of each UAV in URTS can be formulated as \cite{sabatino2015quadrotor}:
 \begin{equation} \label{eq:uav} 
@@
     \begin{remark}
-        Since the quadrotor has four rotors, we only have four control input.
-To simplify the model, the UAV (quadrotor) dynamic model in (\ref{eq:uav}) considers $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors.
+        Since the UAV (quadrotor) has four rotors, we only have four control input.
+To simplify the model, the UAV dynamic model in (\ref{eq:uav}) considers the actuator control input $u'(t)=[F, \tau_u^T]^T=[F, \tau_x, \tau_y, \tau_z]^T$ as the equivalent control input for the four rotors.
 Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system.
+This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be reversed from the dynamic equation in (\ref{eq:uav}).
     \end{remark}
@@
 
-Now, suppose the UAV flying occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
+Now, suppose the UAV flying behavior occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
 The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
@@
 \subsection{motion of walking of robot}
-By Lagrange equation, the dynamic model of biped robot can be formulated as:
+By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
 \begin{equation} \label{eq:robot} 
@@
 The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}.
-For robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space.
+For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space.
 Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern to prevent robot from falling.
 These make the design of walking motion more difficult.
-In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion.
+In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion of each biped robot in URTS.
 
 With 3D-LIPM, we can significantly reduce the amount of computation.
-Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}.
-Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero.
-More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
-The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
+Let us define the body frame of biped robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}.
+Taking the forward direction of biped robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero.
+More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
+The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
 \begin{equation} \label{eq:x_zmp}
@@
 \end{equation}
-where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$.
+where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular acceleration component of link $i$.
 However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}).
-Since there is a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$.
-At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r(t)$.
+Since there exists a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$.
+At the same time, it is necessary to ensure that $x_{zmp}$ falls in the support polygon which also has a relationship with $q_r(t)$.
 To simplify this complex problem, an approximate solution can be derived through 3D-LIPM.
-It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height.
-Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model.
-Although there exist a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple.
+We find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height.
+Many researchers have used this method to avoid complex calculations for ZMP of the actual robot dynamic model.
+Although there exists a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple.
 The overall process is shown in Fig.
@@
 
-Following the same step in UAV, the smoothed path $(\sigma_n')$ for robot can be obtained at first.
+Following the same step in UAV, the smoothed path $(\sigma_n')$ for biped robot can be obtained at first.
 For the convenience of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$.
 Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance.
-Despite that, $(\sigma_n')$ tells the robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the robot will move forward (rather than sideways or backward).
+Despite of that, $(\sigma_n')$ tells the biped robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the biped robot will move forward (rather than sideways or backward).
 To keep torso upright, the $\widehat{Z_b}$ direction is equal to the $z$-axis in the inertial frame $\widehat{Z_g}$.
@@
         A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
-That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by IK.
+That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by \textnormal{IK}.
 Hence, we need to find the  position path and orientation path, which compose the desired path.
@@
 Let us denote the $x$ and $y$ component of $\sigma_n'$ in $(\sigma_n')$ as the sequence $(\sigma^{1}_{n}), \sigma^{1}_{n}\in\mathbb{R}^2$.
-The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation between $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is feet width (or shoulder width).
-Then the $x$ and $y$ component of left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
-Finally, left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding $z$ component which is given by ground height.
+The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation among $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is the feet width (or shoulder width).
+Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
+Finally, the left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding the $z$ component which is given by ground height.
 
 After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed.
-Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by step height.
-By using cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
+Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as the middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by the step height.
+By using the cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
 The ankle orientation path is found by the gradient of ground.
@@
 
-To obtain CoM postion path $(CP_n)$, ZMP path needs to be obtained first.
+To obtain the CoM postion path $(CP_n)$, ZMP path needs to be obtained first.
 ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground.
-Suppose the CoM height $z_c$ of robot is constant when walking, then the robot model can be regarded as an 3D-LIPM:
+Suppose the CoM height $z_c$ of biped robot is kept constant when walking, then the biped robot model can be regarded as an 3D-LIPM \cite{kajita2001real}:
 \begin{equation} \label{eq:LIPM}
@@
 Since $z_c$, $g$ and $(p_x,p_y)$ are given, $(x_c, y_c)$ can be solved.
-Observing the dynamic equations in the $x$ and $y$ directions in (\ref{eq:LIPM}), it can be found that they are decoupled and thus can be calculated separately.
+From the dynamic equations in the $x$ and $y$ directions in (\ref{eq:LIPM}), it can be found that they are decoupled and thus can be calculated separately.
 Therefore, only the solution in the $x$ direction is given below (the $y$ direction as the same).
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x_c$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path is found.
+Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x_c$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be found.
 Unlike conventional methods, the problem is solved by the optimal control.
-The system is discretized first and the discrete LQ tracker is employed to achieve the output tracking.
+The system is discretized first and the discrete LQ optimal tracker is employed to achieve the output tracking.
 The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}.
-The CoM position path $(CP_n)$ then be obtained by combining $x_c$ and $y_c$ with $z_c$.
-
-By combining the CoM orientation path $(CO_n)$ and position path $(CP_n)$, CoM path can be obtained.
+The CoM position path $(CP_n)$ can then be obtained by combining $x_c$ and $y_c$ with $z_c$.
+
+By combining the CoM orientation path $(CO_n)$ wtih the position path $(CP_n)$, the CoM path can be obtained.
 Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK.
@@
 \section{Tracking control of each agent in hybrid URTS}
-Before converting $r[k]$ to $r(t)$, we first convert the UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) into a form called agent dynamic model to analyze their tracking control problems together.
+Before converting $r[k]$ to $r(t)$, we first convert the UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
 Through some appropriate variable transformations, we have:
@@
 \end{equation}
-where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is non-inertial force vector.
-The control law is given as:
+where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is the state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is the inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is the non-inertial force vector.
+The control law for an agent in URTS is given as:
 \begin{equation} \label{eq:control}
@@
 \end{equation}
-where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t)), \ddot{r}(t)\mathbin{,} H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
-For UAVs, we have $u(t)=\begin{bmatrix}
+where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
+For each UAV in hybrid URTS, we have $u(t)=\begin{bmatrix}
     f_u \\ \tau_u
@@
     \dot{X} \\ \dot{\Theta}
-\end{bmatrix}$, and $n=6$ by (\ref{eq:uav}). For robots, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by (\ref{eq:robot}).
+\end{bmatrix}$, and $n=6$ by (\ref{eq:uav}).
+For each robot in hybrid URTS, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by (\ref{eq:robot}).
+
+\textit{
+    \begin{remark}
+        The difference between the control law $u(t)$ in \ref{eq:control} of this article and the traditional feedback linearization control is that we use the "feedward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
+This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$.
+    \end{remark}
+}
 
@@
 For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
-Besides, for UAV, it can be seen that the control input $u(t)=[f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actual control input for actuator $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ since UAV is an underactuated system.
+Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV actuator since UAV is an underactuated system.
 The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem.
@@
         0 \\ 0 \\ F
-\end{bmatrix} $ from UAV dynacmis (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
-Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]$.
-For robot, we get $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since robot is a fully actuated system.
-So far, the design of reference trajectory $r(t)$ of each agent is done.
-The flowchart can be found in the reference generator block in Fig.
+\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
+Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$.
+For biped robot, we get $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
+So far, the design of reference trajectory $r(t)$ of each agent in hybrid URTS is done.
+We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig.
 \ref{fig:tracking}.
@@
     (a) The tracking control block of each agent in hybrid URTS.
-The reference generator block and control block are predefined processes defined in (b) and (c).
-The control block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
-It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actual control input $u'(t)\in\mathbb{R}^4$ different for UAV.
+The controller block is predefined in (d).
+The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
+It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV.
 The reference generator block is introduced to deal with this problem.
-(b) The reference generator blocks for UAV and robot are different since UAV is an underactuated system.
-For UAV, we need to calculate $u'(t)$ and $r(t)$ from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}).
-For robot, $u'(t)=u(t)$ and $r(t)=r'(t)$ since the system is fully actuated.
-(c) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
+For UAVs, the reference generator block is predefined in (b).
+For robots, the reference generator block is predefined in (c).
+    (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}).
+    (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated.
+    (d) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
     \label{fig:tracking}
@@
         Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r_{i,j}[k]$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the URTS works as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found the corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
-That is, $r_{i,j}(t)$ is the reference trajectory that can complete specific task, follow specific path and perform specific behavior.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
+That is, $r_{i,j}(t)$ is the reference trajectory that can complete the specific task, follow the specific path and perform the specific behavior.
     \end{remark}
@@
 \end{enumerate}
-Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$. The coupling disturbance $c(t)$ can be represented as \begin{equation} \label{eq:UAV couple}
+Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.
+The coupling disturbance $c(t)$ on each agent in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
     c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
@@
     c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
-\end{equation} for robot $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
-Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in URTS.
+\end{equation} for biped robot $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
+Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in hybrid URTS.
 Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command.
@@
 Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance.
-The nominal system in (\ref{eq:agent}) of an agent then be rewrited as the following real system:
+The nominal system in (\ref{eq:agent}) of an agent in hybrid URTS then be rewrited as the following real system:
 % The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
@@
 
-Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
+Now, substituting the control law $u(t)$ in (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
 \begin{equation} \label{eq:agent1}
@@
 \end{equation}
-By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have:
+By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have the tracking error differential equation as follow:
 \begin{equation} \label{eq:error, state eq}
@@
 % }
-Let $\pmb{e}(t)=\begin{bmatrix}
+Let us denote $\pmb{e}(t)=\begin{bmatrix}
     \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
-\end{bmatrix}^T\in\mathbb{R}^{3n}$, (\ref{eq:error, state eq}) can be rewrited as:
+\end{bmatrix}^T\in\mathbb{R}^{3n}$, the tracking error differential equation in (\ref{eq:error, state eq}) can be rewrited as the following linear tracking error system:
 \begin{equation} \label{eq:linear f1}
@@
 
-Through above analysis, the tracking control problem of the nonlinear system with external disturbance (\ref{eq:agent d1}) is transformed into the regulation problem of the linear system (\ref{eq:linear f1}) with fault signal by the feedforward linearization.
-The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear system stable.
+Through the above analysis, the tracking control problem of the nonlinear system of each agent in hybrid URTS with external disturbance in (\ref{eq:agent d1}) is transformed into the regulation problem of the linear tracking error system in (\ref{eq:linear f1}) with actuator fault signal $f_1(t)$ by the feedforward linearization control law $u(t)$.
+The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear tracking error system stable.
 In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
-At the same time, the sensor fault on sensor also need to be considered as mentioned before.
+At the same time, the sensor fault on sensor also needs to be considered as mentioned before.
 Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but the cyber-attack signal are concerned.
@@
     \int_{0}^{t}r^T(\tau)d\tau & r^T(t) & \dot{r}^T(t)
-\end{bmatrix}^T$ to modify the output equation (\ref{eq:agent output}) and combine it with (\ref{eq:linear f1}), we have the following tracking error dynamic system of an agent in the hybrid URTS:
+\end{bmatrix}^T$ to modify the output equation in (\ref{eq:agent output}) and combine it with (\ref{eq:linear f1}), we have the following tracking error dynamic system of an agent in the hybrid URTS:
 \begin{equation} \label{eq:error}
@@
     \end{bmatrix}\otimes I_{n_i}$, and $w_i$ is the window size of smoothing signal model with $n_1=n$ and $n_2 = o$.
-Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get the following augmented tracking error system of an agent:
+Substituting (\ref{eq:smooth model}) into (\ref{eq:error}), we get the following augmented tracking error system of an agent in hybrid URTS:
 \begin{equation} \label{eq:e_bar}
@@
     \pmb{e}(t) \\ F_1(t) \\ F_2(t)
-\end{bmatrix}$ is the augmented tracking error, $\bar{A}=\begin{bmatrix}
+\end{bmatrix}$ is the augmented tracking error vector, $\bar{A}=\begin{bmatrix}
     A & BC_1 & 0 \\
@@
 Since the fault signals become a state variable of the augmented tracking error system of an agent in (\ref{eq:e_bar}), their corruption on the tracking error dynamic system in (\ref{eq:error}) can be avoided.
-A Luenberger observer is proposed to estimate them and origin state simutaniously to achieve active FTC by the following estimation system:
+A Luenberger observer is proposed to estimate them and origin state simutaniously to achieve an active FTC by the following estimation system:
 \begin{equation} \label{eq:e_hat}
@@
 \end{equation}
-\begin{assumption}
+\begin{assumption}[\cite{9306757}]
     The augmented tracking error system (\ref{eq:e_bar}) of an agent is observable, i.e., $rank\begin{bmatrix}
@@
 \end{assumption}
-The robust FTC law of each agent is given as:
+The feedback control law $u_{fb}(t)$ of each agent in hybrid URTS then be designed as follow:
 \begin{equation} \label{eq:u_fb}
@@
 \end{equation}
-where $K = \begin{bmatrix}
-    K_I & K_P & K_D & K_{F_1} & K_{F_2}
-\end{bmatrix}$ is the total control gain, $K_P,K_I,K_D$ are the PID control gain for position tracking error $e(t)$, and $K_{F_i}, i=1,2$ are the fault control gain.
+where $K$ is the control gain.
+\textit{
+    \begin{remark}
+        Let $u_{fb}(t) = K\hat{\bar{e}}(t) = [K_I\mathbin{,} K_P\mathbin{,} K_D\mathbin{,} K_{F_1}\mathbin{,} K_{F_2}][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t), F_1^T(t), F_2^T(t)]^T$, we can find that the control gain $K$ is composed of the PID control gains $K_I$, $K_P$ and $K_D$ for $\int_{0}^{t}\hat{e}(\tau)d\tau$, $\hat{e}(t)$ and $\dot{\hat{e}}(t)$, respectively, and the fault control gains $K_{F_i}$ for $F_i(t)$ with $i=1,2$.
+This show that $u_{fb}(t)$ is a fault-tolerant PID controller.
+    \end{remark}
+}
+
 Let us define the augmented estimation error $\tilde{e}(t)=\bar{e}(t)-\hat{\bar{e}}(t)$, the augmented estimation error system can be obtained by (\ref{eq:e_bar}) and (\ref{eq:e_hat}):
 \begin{equation} \label{eq:e_tilde}
-    \dot{\tilde{e}}(t) = \bar{A}\tilde{e}(t) +L\bar{C}\tilde{e}(t)
+    \dot{\tilde{e}}(t) = \bar{A}\tilde{e}(t) +L\bar{C}\tilde{e}(t) = (\bar{A} +L\bar{C})\tilde{e}(t)
 \end{equation}
@@
 \begin{theorem} \label{theorem1}
-    If there exists matrices $P=P^T>0, K,L$ such that the following matrix inequality hold:
+    If there exists matrices $P=P^T>0, K,L$ such that the following Riccati-like matrix inequality holds:
     \begin{equation} \label{BMI1}
@@
         Q_1 & 0 \\ 0 & Q_2
-    \end{bmatrix}$, then the $H_\infty$ decentralized observer-based tracking control strategy in (\ref{Hinf}) can be achieved.
+    \end{bmatrix}$, then the $H_\infty$ decentralized observer-based team formation tracking control strategy in (\ref{Hinf}) of each agent in the hybrid URTS can be achieved.
 \end{theorem}
+\textit{
+    \begin{remark}
+        Since Riccati-like inequality of each agent in URTS has not involved the system information of other agents, therefore, the robust decentralized team formation tracking control can be achieved.
+    \end{remark}
+}
 \begin{proof}
@@
 
-Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the variables.
-To solve the issue, a two-step design is exploited.
+Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the designed variables $K$ and $L$.
+To solve the issue, a two-step design procedure is exploited.
 
@@
 \end{equation}
-where $Y_1=KW_1$. By solving the LMI (\ref{eq:step1}), we can obtain $W_1,Y_1$.
+where $Y_1=KW_1$. By solving the LMI in (\ref{eq:step1}), we can obtain $W_1,Y_1$.
 
@@
 
-If we want to find the optimal $H_\infty$ decentralized observer-based tracking control strategy for the augmented system of each agent in (\ref{eq:x_tilde}), we need to solve the following LMIs-constrained optimization problem:
+If we want to find the optimal $H_\infty$ decentralized observer-based tracking control strategy for the augmented tracking and estimation error system in (\ref{eq:x_tilde}) of each agent in hybrid URTS , we need to solve the following LMIs-constrained optimization problem:
 \begin{equation} \label{LMI constraint}
@@
 
-The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
+The design procedure of the optimal decentralized $H_\infty$ observer-based feedforward FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
 \begin{enumerate}
-    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized tracking error dynamic system (\ref{eq:error})
+    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized tracking error dynamic system in (\ref{eq:error}) for each agent in hybrid URTS.
     \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$.
-Embed into the linearized system (\ref{eq:error}) to get the augmented tracking error system (\ref{eq:e_bar}).
-    \item Construct the robust FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
-    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
+Embed these smoothing signal models into the linearized system (\ref{eq:error}) to get the augmented tracking error system of each agent in (\ref{eq:e_bar}).
+    \item Construct the robust FTC law in (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system of each agent in (\ref{eq:x_tilde})
+    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design procedure to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
 \end{enumerate}
 
-The overall flowchart of tracking control is shown in Fig.
+The overall flowchart of tracking control of each agent in hybrid URTS is shown in Fig.
 \ref{fig:tracking}.
-The reference generator is used to compute the actual reference trajectory $r(t)$ and control input $u'(t)$ for each agent according to the output $r'(t)$ of local motion planning block and the control law $u(t)$ we design in (\ref{eq:control}).
+The reference generator is used to compute the desired reference trajectory $r(t)$ and actuator control input $u'(t)$ for each agent according to the continuous signal $r'(t)$ obtained by D/A and the control law $u(t)$ we design in (\ref{eq:control}).
 Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
-$\pmb{r}(t)$ then pass to observer to calculate the error $\pmb{e}(t)$.
-Its differential, $\dot{\pmb{r}}(t)$, then inputs to controller for feedforward control.
-The sensor measure not only the agent's own information (e.g., position or velocity) but also environmental information.
+$\pmb{r}(t)$ is then passed to observer to calculate the error $\pmb{e}(t)$.
+Its differential, $\dot{\pmb{r}}(t)$, is then inputted to controller for feedforward control.
+The sensor measures not only the agent's own information (e.g., position or velocity) but also environmental information.
 The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
@@
         By the proposed agent dynamics model in (\ref{eq:agent}) and the introduction of reference generator block in Fig.
-\ref{fig:tracking}, the tracking control block of each agent $\alpha_{i,j}$ in the hybrid URTS can be designed by a general method.
+\ref{fig:tracking} (b), a general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent $\alpha_{i,j}$ in hybrid URTS can be designed as shown in the controller block in Fig.
+\ref{fig:tracking} (c).
 The decentralized architecture also ensures the scalability of URTS scale.
@@
 Although the control gain in (\ref{eq:u_fb}) and observer gain in (\ref{eq:e_bar}) for each agent in URTS can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
-Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems for each agent if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
+Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems for each agent ($n=6$ for UAV and $n=12$ for robot) if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
 Let us decompose
@@
     \end{split}
-\end{equation}
+\end{equation} where $i=1,2,...,n$.
 \begin{remark}
@@
 
-By Theorem \ref{theorem1} again, the form shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ observer-based tracking control performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
+By Theorem \ref{theorem1} again, the form of subsystems in (\ref{eq:linear subsys}) shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the decentralized $H_\infty$ observer-based feedforward FTC performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
 The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
@@
 
-In this case, the calculation speed of finding gains $K,L$ can be improved since the dimensionality is decrease.
-Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining robustness.
+In this case, the calculation speed of finding gains $K,L$ of each agent can be improved since the dimensionality is decrease.
+Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining estimation and tracking robustness.
 More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times sn$ to $n(1\times s)$.

### 2022-12-08 paper/paper.tex
UAV noFTC simulation and describtion done

@@
 
+In order to show the effect of active FTC based on the proposed embed smoothing model method, a traditional PID computed torque controller without FTC is used for comparison \cite{7456706}.
+In order to only focus on the effect of FTC, the method in \cite{7456706} was revised to oberserver based, that is, the control law become $u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t))$ where $u_{fb}(t) = [K_I, K_P, K_D][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t)]^T$.
+The results are shown in Fig.
+\ref{fig:uav, state, noFTC} for UAV and Fig.
+\ref{fig:robot, state, noFTC} for robot.
+From Fig.
+\ref{fig:uav, state, noFTC} and Fig.
+\ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1$ on the tracking error is revealed.
+The value of sensor fault $f_2$ is relatively insignificant because it is much smaller than that of acuator fault by our simulation setting but $x_4,x_5,x_6$ can still see the ups and downs with a period of 10 seconds.
+Although still stable, its tracking performance has dropped significantly compared to Fig.
+\ref{fig:UAV, state}.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \label{fig:uav, state, noFTC}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \label{fig:robot, state, noFTC}
+\end{figure}
+
 For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.

### 2022-12-08 paper/paper.tex
- Robot, noFTC, simulation+paper, done - SearchTaskThreeTeam, robot reference ok

@@
 \ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1$ on the tracking error is revealed.
-The value of sensor fault $f_2$ is relatively insignificant because it is much smaller than that of acuator fault by our simulation setting but $x_4,x_5,x_6$ can still see the ups and downs with a period of 10 seconds.
-Although still stable, its tracking performance has dropped significantly compared to Fig.
-\ref{fig:UAV, state}.
+The influence of the sensor fault $f_2$ is relatively insignificant because its value is much smaller than $f_1$ by our simulation setting.
+However, the fluctuation of $f_2$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig.
+\ref{fig:uav, state, noFTC} and the robot joint state variables $x_5,x_6,x_{11},x_{12}$ in Fig.
+\ref{fig:robot, state, noFTC}.
+Although it still stable, the tracking performance has dropped significantly compared to Fig.
+\ref{fig:UAV, state} and \ref{fig:robot, state}, respectively.
 \begin{figure}[htbp]
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
     \label{fig:robot, state, noFTC}

### 2022-12-08 src/URTS main script/Robot/function/+Show/Area.m

@@ -1,15 +1,0 @@
-function Area(area1)
-    % Show the area1 in URTS
-    
-    % area1 = [0 6; 0 6; 0 4];
-    vertex = combvec(area1(1, :), area1(2, :), area1(3, :));
-    k = 1;
-    for i = 1 : size(area1, 1)
-        for j = 1 : size(area1, 2)
-            face(k, :) = find(vertex(i, :) == area1(i, j));
-            face(k, 3:4) = flip(face(k, 3:4));
-            k = k + 1;
-        end
-    end
-    patch('Faces',face,'Vertices',vertex','FaceColor','r', FaceAlpha=.1, EdgeColor=[.8 .8 .8], DisplayName='$area_1$');
-end

### 2022-12-08 src/URTS main script/Robot/function/+Show/Map.m

@@ -1,10 +1,0 @@
-function Map(xLimit, yLimit)
-    % Show the occupy map of URTS
-    img = imread('data/map.png');     % Load a sample image
-    xImage = [xLimit(2) xLimit(2);xLimit(1) xLimit(1)]; % The x data for the image corners
-    yImage = [yLimit(1) yLimit(2); yLimit(1) yLimit(2) ];   
-    % xImage = [6.5 6.5;-.5 -.5]; % The x data for the image corners
-    % yImage = [-3 6; -3 6 ];   
-    zImage = [ 0 0; 0 0 ];
-    surf(xImage, yImage, zImage, 'CData', img, FaceColor='texturemap', EdgeColor='k', DisplayName='map', MarkerEdgeColor='k');
-end

### 2022-12-08 src/URTS main script/Robot/oneRobot_noFTC.m

@@ -1,0 +1,119 @@
+%Compare control method
+% one robot, observer-based tracking control, feedfoward linearization, without FTC
+
+clc; clear; close all; tic;
+addpath(genpath('../../../src'))
+
+rb = Robot();
+rb.PATH  = ['./data/' mfilename]; % path of saved data
+rb = rb.Load(); % load old data
+
+% flow control of code
+rb.EXE_LMI     = 1;
+rb.EXE_Z2C     = 0; % ZMP to CoM converter
+rb.EXE_IK      = 0; % inverse dynamic
+rb.EXE_TRAJ    = 1; % trajectory
+rb.EXE_PLOT    = 1; % plot results
+
+% time
+rb.tr.dt    = .001; % Time step
+rb.tr.T     = 20; % Final time
+rb.tr.t    = 0 : rb.tr.dt : rb.tr.T;
+rb.tr.LEN  = length(rb.tr.t);
+
+% global variable
+DIM_F       = rb.DIM_F; % Dimension of e
+DIM_SOLVE_K = 1;
+I           = eye(DIM_F);
+
+%% Agent system model 
+% Error weighting. Tracking:1, Estimation:2
+A0          = [0 1 0; 0 0 1; 0 0 0];
+B0          = [0; 0; 1];
+C0          = [1 0 0; 0 1 0; 0 0 1]; % Intergral{e}, e, de
+
+% for solving control and observer gain
+sys1        = LinearModel(A0, B0, C0);
+sys1.Q1     = 10^(2)*diag([1 100 10]);
+sys1.Q2     = 10^(2)*diag([1 100 10]); % corresponding to [Intergral{e}, e, de]
+
+% for plot trajectories
+rb.sys = LinearModel(kron(A0, I), kron(B0, I), kron(C0, I));
+
+%% Smooth model (acuator)
+WINDOW  = 3;
+dt_     = 1*rb.tr.dt;
+METHOD  = '2';
+
+% for solving control and observer gain
+sys_a1      = SmoothModel(WINDOW, DIM_SOLVE_K, dt_, METHOD);
+sys_a1.B    = sys1.B;
+sys_a1.Q1   = diag(zeros(1,WINDOW)); % Can't stablilze unknown signal
[…]

### 2022-12-08 src/URTS main script/URTS/SearchTaskThreeTeam.m

@@ -1,0 +1,115 @@
+% Simulation of team 1~3 for all search task
+clc; clear; close all
+addpath(genpath('../../../src'))
+
+%% Path of UAV
+uav = UAV_AGENTmodel();
+uav.PATH  = ['../UAV/data/' uav.FILE_NAME]; % path of saved data
+uav = uav.Load(); % load old data
+
+factor = 250; % Sample rate, sample once for "factor" times. For speed up the simulation
+fps = 1/uav.tr.dt/factor; % fps for output video
+
+% Down sampling for state and reference state
+uav.tr.r{1} = uav.tr.r{1}(:, 1:factor:length(uav.tr.r{1})); 
+e = uav.tr.x(uav.DIM_F + (1:uav.DIM_F), :);
+e = e(:, 1:factor:length(e));
+xUAV = e + uav.tr.r{1};
+    
+%% Path of robots
+startPos = [
+    0.75 0 0    % Start postion
+    0.75 6.5 0  % Goal position
+]; % (x, y, z)
+Na = 5; % Number of agents in a team
+Nr = (Na-1)*3; % Number of robots
+
+rb = cell(1, Na-1);
+pp = cell(1, Na-1);
+for i = 1 : Nr
+    disp(['Path planning, ' num2str(i) '-th robot'])
+
+    rb{i} = Robot();
+    rb{i}.PATH  = ['../Robot/data/' rb{i}.FILE_NAME]; % path of saved data
+    rb{i} = rb{i}.Load(); % load old data
+
+    pp{i} = PathPlanning(startPos(1, :), startPos(2, :)); % Find task space ref in a map using RRT
+
+    % Since we want r_lr only, disable the Z2C and IK part
+    rb{i}.EXE_Z2C = 0; % Do not calculate Z2C (ZMP to CoM)
+    rb{i}.EXE_IK = 0; % Do not calculate IK
+    rb{i} = rb{i}.Ref2Config(pp{i}.r); % Calculate r_lr % Left and right footholds path
+
+    startPos(:, 1) = startPos(:, 1) + 2; % x += 1.5
+end
+
+% State
+r = rb{1}.tr.r{1}'; % reference
+x = rb{1}.tr.x(12 + (1:12), :);
+
+config = r(1:factor:length(r), :); % Down sampling
[…]

### 2022-12-08 src/URTS main script/URTS/functions/CoordConversion.m

@@ -1,0 +1,9 @@
+function newCoords = CoordConversion(coords)
+    rotZMinus90 = [0 1; -1 0];
+    for j = 1 : size(coords, 2)
+        coords(:, j) = rotZMinus90*coords(:, j); % Rotete Z-axis -90
+        coords(2, j) = coords(2, j) + 6; % Translate Y axis +6
+    end
+    newCoords = coords;
+end
+

### 2022-12-08 src/URTS main script/URTS/functions/PlotMap.m

@@ -1,0 +1,10 @@
+function PlotMap(xLimit, yLimit)
+    % Show the occupy map of URTS
+    img = imread('map.png');     % Load a sample image
+    xImage = [xLimit(2) xLimit(2);xLimit(1) xLimit(1)]; % The x data for the image corners
+    yImage = [yLimit(1) yLimit(2); yLimit(1) yLimit(2) ];   
+    % xImage = [6.5 6.5;-.5 -.5]; % The x data for the image corners
+    % yImage = [-3 6; -3 6 ];   
+    zImage = [ 0 0; 0 0 ];
+    surf(xImage, yImage, zImage, 'CData', img, FaceColor='texturemap', EdgeColor='k', DisplayName='map', MarkerEdgeColor='k');
+end

### 2022-12-08 src/functions/SaveFig.m

@@ -9,7 +9,7 @@ function SaveFig(fig, name_)
 
     % Save figure as .png
     folderName = 'data/png';
-    if ~exist(folderName, 'dir') % Create folder if not exist
+    if ~isfolder(folderName) % Create folder if not exist
         mkdir(folderName)
     end
     filePath = [folderName '/' name '.png']; % File path
@@ -19,7 +19,7 @@ function SaveFig(fig, name_)
 
     % Save figure as .fig
     folderName = 'data/fig';
-    if ~exist(folderName, 'dir') % Create folder if not exist
+    if ~isfolder(folderName) % Create folder if not exist
         mkdir(folderName)
     end
     filePath = [folderName '/' name '.fig']; % File path

### 2022-12-08 src/functions/System/@Agent/Agent.m

@@ -57,6 +57,7 @@ classdef Agent
 
         y = M(ag, x) % inertial matrix
         y = H(ag, x, dx) % non-inertial matrix
+        [A, B, C] = GetAugmentSystem(ag) % Get augmented system matrices
         ag = get_K_L(ag, sys1, sys_aug1) % solve LMI to obtain control gain K and observer gain L
         ag = trajectory(ag) % get trajectory (x, u, ...)
         is_saved = Save(ag, whichVar) % save properties

### 2022-12-10 src/URTS main script/UAV/oneUAV_FaFs.m
Simulation of 3team in URTS, done. - Make URTS 3 team figure.

@@ -8,8 +8,8 @@ uav.PATH  = ['./data/' mfilename]; % path of saved data
 uav = uav.Load(); % load old data
 
 % flow control of code
-uav.EXE_LMI     = 1; % solving LMI
-uav.EXE_TRAJ    = 1; % trajectory
+uav.EXE_LMI     = 0; % solving LMI
+uav.EXE_TRAJ    = 0; % trajectory
 uav.EXE_PLOT    = 1; % plot results
 
 % time
@@ -114,9 +114,9 @@ if uav.EXE_PLOT
   
     %% Tracking control results
     % PlotLMP(uav)
-    uav.PlotTC(); 
+    % uav.PlotTC(); 
     % PlotActualControl(uav) % Actual control input
-    % PlotStateAndRef3D(uav) % 3D, r(t), state
+    PlotStateAndRef3D(uav) % 3D, r(t), state
 
 end
 

### 2022-12-11 paper/paper.tex
Simulation of 3team in URTS, done. - Make URTS 3 team figure.
Revise paper, Section II and III.

@@
 For the need for search mobility, we choose quadrotor aircraft as UAV.
-In order to deal with the complex terrain of the S\&R environment, we choose biped robot as UGV.
+In order to deal with the complex terrain of the S\&R environment, we choose biped robot (referred to as "robot" in this article) as UGV.
 Even though other types of UGVs like wheeled robots and vehicles are easier to handle than biped robot, the high degree of freedom and the compatibility of the human environment still makes it a good candidate of UGV in a S\&R system.
@@
 \section{PRELIMINARIES OF URTS in S\&R usage}
-The URTS will start with a given S\&R area, and end with mission completed.
+The URTS will start with a given S\&R area, and end with the S\&R mission completed.
 The URTS is composed of $N_T$ teams and a ground station.
@@
 To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area.
-To complete rescue tasks, whenever a goal (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of goal.
+To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target.
 % It can be expected that there has multiple search or rescue tasks need to be performed at the same time but there has multiple agents.
@@
 Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station.
-The ground station will combine this information with the goal location assigned by task allocation algorithm and then make a decision to avoid obstacles and other agents nearby.
+The ground station will combine this information with the goal location determined by the task and then make a decision to avoid obstacles and other agents nearby through a path planning algorithm.
 % That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
 
-We need to determine specific behavior to follow the path found by path planning algorithm according to the situation of the environment especially for agents with complex mechanical systems like robots.
+We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots.
 Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path).
@@
 In order to make a behavior, we must design a corresponding motion by local motion planning.
-The motion is a prescribed reference trajectory for an actual mechanical system to follow.
-Finally, a tracking controller is designed for each agent to follow this desired reference trajectory.
+The motion is a prescribed reference path for an actual mechanical system to follow.
+Finally, a tracking controller is designed for each agent to follow this desired reference path.
 
@@
 \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS.
-The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map, start point and object information.
+The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information.
 The 5 blocks on right hand side are the flow of an agent performing a S\&R mission.
@@
 In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
-However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
+However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
 Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation.
@@
 Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
-In this paper, we assume that the tasks have been properly assigned so that every agent knows a destination $q_{goal}$ it needs to go at every moment.
+In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal $q_{goal}$ it needs to go at every moment.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
 \subsection{Path Planning}
-After a destination $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
+After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
 There must exist multiple feasible paths to go.
@@
 Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT.
-All of the above common roadmap-based planners can be applied to the URTS.
+All of the above common roadmap-based planners can be applied to the proposed URTS architecture.
 
@@
 However, URTS operates in a large environment so the probability of collision is small and the agents have the ability to communicate.
-Therefore, when the paths collide, the mechanism of waiting for the other side to pass can be used to avoid the collision problem.
+Therefore, an alternative solution is to use single-agent path planning together with the mechanism of waiting for the other agent to pass first in the event of a collision.
 \end{remark}
@@
 Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
-The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robots).
+The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for biped robot).
 In this case, an unified planner will become overly complex and impracticable.
@@
 
-By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or sayed waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space $\mathcal{C}$.
+By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or "waypoints"), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or "map") $\mathcal{C}$.
 Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques.
@@
 For robot, it can be a collision detected by a dynamic roadmap-based planner.
-The resulting path $(\sigma_n)$ is passed to the next block, Behavior Layer.
+The resulting path $(\sigma_n)$ is passed to the next block, behavior layer block.
 
@@
 Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
-Therefore, the output of this block is also a path $r[k]$.
+Therefore, the output of this block is also a path $r[k]$ (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
 The flowchart of local motion planning block is shown in Fig.
-\ref{fig:LMP}
+\ref{fig:LMP}.
 \begin{figure*}[htbp]
@@
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
-The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.
+The reference path $r[k]$ is a sequence (or discrete signal) designed by a specific behavior block.
 For UAVs, the moving block is predefined in (b).
 For robots, the moving block is predefined in (c).
-(b) The moving block of each UAV where the flying block is predefined in \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in \ref{fig:FandW}}
+(b) The moving block of each UAV where the flying block is predefined in Fig.
+\ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in Fig.
+\ref{fig:FandW}}
     \label{fig:LMP}
@@
 In Fig.
-\ref{fig:LMP}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block.
+\ref{fig:LMP}, some basic behaviors of UAV and robot mentioned in Fig.
+\ref{fig:behavior} are given to futher illustrate the flow of this block.
 To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
@@
     \begin{assumption} \label{asm:cc again}
-        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
+        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore the nonholonomic constraints (the velocity and acceleration constraints).
     \end{assumption}
 }
-However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion.
+However, for these two behaviors, there exists an inevitable holonomic constraint on the curvature of local motion.
 Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem.
 Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant.
-At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision.
+At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure this error will not cause collision.
 As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$.
@@
 % where $y'$ denotes the $y$ axis after rotating the $z$ axis and $x''$ denotes the $x$ axis after rotating the $y'$ axis
-$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
+$g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame as shown in Fig.
+2.8 in \cite{sabatino2015quadrotor}, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
 This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$.
@@
 Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system.
-This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be reversed from the dynamic equation in (\ref{eq:uav}).
+This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be inversely calculated through other degrees of freedom that can be assigned arbitrarily and the dynamic equation in (\ref{eq:uav}).
     \end{remark}
@@
 
-Now, suppose the UAV flying behavior occurs between time step $t_1$ and $t_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[t_1,t_2]$.
-The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[t_1,t_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[t_1,t_1+D(t_2-t_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}^+$ is the interpolation density.
+Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$.
+The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density.
 Then, $(\sigma_n')$ will be the position reference path $[
@@
 ]^T$.
-Subsequently, the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$ are all considered.
+Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$.
 $\phi_r[k]$ is set to zero since no need for spinning when flying.
@@
 
-\subsection{motion of walking of robot}
+\subsection{motion planning of walking of robot}
 By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
@@
 Given $\widehat{X_b}$ and $\widehat{Z_b}$, $\widehat{Y_b}$ can be obtained obviously through cross product.
-The sequence of body frame, i.e., CoM orientation path $(CO_n)$ can be obtained through the above steps.
+The sequence of body frame, i.e., CoM orientation path $(CO_n)$ then be obtained through the above steps.
 
@@
     \begin{remark}
-        A frame in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
-That is, given the position and orientation of two joints in a link with known kinematics, the position and orientation of joints between them can be found by \textnormal{IK}.
-Hence, we need to find the  position path and orientation path, which compose the desired path.
+        A frame (or homogenous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
+That is, given the frames of two joints in a link with known kinematics, the frames of joints between them can be found by \textnormal{IK}.
+Hence, we need to find the position paths and orientation paths, which compose the desired path.
     \end{remark}
@@
 The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation among $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is the feet width (or shoulder width).
-Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
+Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, respectively, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
 Finally, the left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding the $z$ component which is given by ground height.
@@
 After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed.
-Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as the middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,N-1]$, and the $z$ component is given by the step height.
+Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as the middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,M-1]$ with $k_1 = 1$ and $k_M = N$, and the $z$ component is given by the step height.
 By using the cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
-The ankle orientation path is found by the gradient of ground.
+To keep the soles of the feet on the ground, the ankle orientation path can be obtain by the gradient of ground.
 Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together.
@@
     \begin{split}
-        & \dot{\bar{x}}_c = A\bar{x}_c + Bu \\
-        & p_x = C\bar{x}_c
+        & \dot{\bar{x}}_c = A\bar{x}_c + Bu_s \\
+        & y_s = C\bar{x}_c
     \end{split}
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u$ in order that the output $p_x$ can track a ZMP reference trajectory so that the solution $x_c$ of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be found.
+Our goal is to find a control input $u_s$ in order that the output $y_s$ can track the ZMP reference trajectory $p_x$ so that the state $x_c$, i.e., the solution of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be found.
 Unlike conventional methods, the problem is solved by the optimal control.
@@
 By combining the CoM orientation path $(CO_n)$ wtih the position path $(CP_n)$, the CoM path can be obtained.
-Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK.
+Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK as shown in Fig.
+\ref{fig:FandW}.
 
@@
     \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in the $i$th team at the begining.
-The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinations $q_{goal}$ (black dots in figure) obtained from task allocation block.
+The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive goals $q_{goal}$ (black dots in figure) obtained from task allocation block.
 For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.
@@
 
+We use three teams $team_i, i=1, 2, 3$ to show the team tracking results of URTS as shown in Fig. \ref{fig:URTS}.
+\begin{figure*}[htbp]
+    \centering
+    \includegraphics[scale=.42]{fig/URTS.png}\caption{The simulation of team tracking of URTS when perform search tasks.
+As shown in Fig.
+\ref{fig:SR_area}, the UAV and robot in URTS will be released along the direction of the road ($Y$-axis) and each team is responsible for an area.
+First, the respective tasks of each agent are determined by the task allocation algorithm.
+According to the task content, the agent will be determined a goal $q_{goal}$.
+As in Fig.
+\ref{fig:S_task}, this simulation assumes that URTS are assigned search tasks.
+Subsequently, the path planning algorithm calculates the collision-free path $(\sigma_n)$ for each agent.
+Depending on the terrain environment, an appropriate behavior $(\beta_n)$ is determined to enable the agent to follow the path $(\sigma_n)$.
+A reference path $r[k]$ corresponding to a behavior is designed via local motion planning to enable an actual mechanical body to perform the behavior.
+Since this article only gives the motion planning method of flying (for UAV) or walking (for biped-robot), it is assumed that from $q_{start}$ to $q_{goal}$ are all flying or walking behaviors in this simulation.
+In this figure, we draw the smoothed path $\sigma'_n$ of each agent, which is the intermediate result of local motion planning as shown in Fig, \ref{fig:FandW}.
+It represents the path that the agent is going to reach in the task space.
+According to $r[k]$ and the dynamic model of UAV and robot, the reference trajectory $r(t)$ of each agent is obtained.
+Finally, through the decentralized $H_\infty$ observer-based feedforward FTC scheme proposed in this paper, the team tracking result of the agents in $team_i, i=1,2,3$ in URTS are shown.
+Note that the above process is dynamic.
+If a block in a higher layer in URTS architecture makes a new decision that produces a new output, the lower blocks must recalculate based on it.
+Rrelatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.}
+    \label{fig:URTS}
+\end{figure*}
+
 For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.

### 2022-12-11 paper/paper.tex
Revise paper, Section VI.

@@
 \section{Tracking control of each agent in hybrid URTS}
-Before converting $r[k]$ to $r(t)$, we first convert the UAV dynamic system in (\ref{eq:uav}) and robot dynamic system in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
+Before converting the reference path $r[k]$ to reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
 Through some appropriate variable transformations, we have:
@@
     \dot{X} \\ \dot{\Theta}
-\end{bmatrix}$, and $n=6$ by (\ref{eq:uav}).
-For each robot in hybrid URTS, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by (\ref{eq:robot}).
+\end{bmatrix}$, and $n=6$ by UAV dynamics in (\ref{eq:uav}).
+For each robot in hybrid URTS, we have $u(t)=\tau_R$, $x(t)=q$, $M(x(t))=M_R(q)$, $H(x(t),\dot{x}(t))=C(q,\dot{q})\dot{q} + G(q)$, and $n=12$ by robot dynamics in (\ref{eq:robot}).
 
@@
     \begin{remark}
-        The difference between the control law $u(t)$ in \ref{eq:control} of this article and the traditional feedback linearization control is that we use the "feedward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
+        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
 This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$.
@@
 For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
-Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV actuator since UAV is an underactuated system.
+Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system.
 The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem.
@@
 Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$.
-For biped robot, we get $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
+For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
 So far, the design of reference trajectory $r(t)$ of each agent in hybrid URTS is done.
@@
 \end{equation} for UAV $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
-    c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)
-\end{equation} for biped robot $\alpha_{i, j'}$ where $j'=2,3,...,N_A$ \cite{9834947}.
+    c(t) = \sum_{k = 1, k \neq j}^{N_A}D_{i, j, k}(x_{i, j}(t))x_{i, k}(t)
+\end{equation} for biped robot $\alpha_{i, j}$ where $i=1,2,\dots,N_T$ and $j=2,3,\dots,N_A$ \cite{9834947}.
 Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in hybrid URTS.
@@
 In addition, the wind disturbance and the ground reaction force will apply extra force on an agent in (\ref{eq:agent}).
-Therefore, through appropriate conversion, the above disturbances can be equivalent to a disturbance force $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance.
+Therefore, through appropriate conversion, the above disturbances can be equivalent to two disturbance forces $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance.
 The nominal system in (\ref{eq:agent}) of an agent in hybrid URTS then be rewrited as the following real system:
@@
 In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
-At the same time, the sensor fault on sensor also needs to be considered as mentioned before.
+At the same time, the sensor noise on sensor also needs to be considered as mentioned before.
 Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but the cyber-attack signal are concerned.
+We consider the effect of them as a sensor fault in this paper.
 Let $\pmb{x}(t)=\begin{bmatrix}
@@
         Let $u_{fb}(t) = K\hat{\bar{e}}(t) = [K_I\mathbin{,} K_P\mathbin{,} K_D\mathbin{,} K_{F_1}\mathbin{,} K_{F_2}][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t), F_1^T(t), F_2^T(t)]^T$, we can find that the control gain $K$ is composed of the PID control gains $K_I$, $K_P$ and $K_D$ for $\int_{0}^{t}\hat{e}(\tau)d\tau$, $\hat{e}(t)$ and $\dot{\hat{e}}(t)$, respectively, and the fault control gains $K_{F_i}$ for $F_i(t)$ with $i=1,2$.
-This show that $u_{fb}(t)$ is a fault-tolerant PID controller.
+This shows that the feedback control law $u_{fb}(t)$ has fault-tolerant capability and PID control characteristic.
     \end{remark}
@@
 
-In order to enable the designed control gain $K$ in (\ref{eq:u_fb}) and observer gain $L$ in (\ref{eq:e_hat}) to achieve a specific performance for the augmented system in (\ref{eq:x_tilde}) under the disturbance $\bar{v}(t)$, the robust $H_\infty$ decentralized observer-based tracking control strategy below a prescribed disturbance attenuation level $\rho^2$ for each agent in hybrid URTS is given as:
+In order to enable the designed control gain $K$ in (\ref{eq:u_fb}) and observer gain $L$ in (\ref{eq:e_hat}) to achieve a specific performance for the augmented system in (\ref{eq:x_tilde}) under the disturbance $\bar{v}(t)$, the robust $H_\infty$ decentralized observer-based tracking control strategy below a prescribed disturbance attenuation level $\rho^2$ for each agent in hybrid URTS is given as follow:
 \begin{equation} \label{Hinf}
@@
 \end{equation}
-where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented system in (\ref{eq:x_tilde}), and $\tilde{v}(t)$ is the total disturbance needed to be attenuated.
+where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented tracking and estimation error system in (\ref{eq:x_tilde}), and $\tilde{v}(t)$ is the total disturbance needed to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented tracking error $\bar{e}(t)$ and augmented estimation error $\tilde{e}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
     \begin{remark}
-        Since Riccati-like inequality of each agent in URTS has not involved the system information of other agents, therefore, the robust decentralized team formation tracking control can be achieved.
+        Since the Riccati-like inequality of each agent $\alpha_{i,j}$ in URTS has not involved the system information of other agents (e.g., the coupling term $c(t)$ in (\ref{eq:UAV couple}) and (\ref{eq:robot couple})), therefore, the robust decentralized team formation tracking control can be achieved.
     \end{remark}
@@
 and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ 
-where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}$, $f_{1,i}(t)\in\mathbb{R}^1$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems:
+where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}$, $f_{1,i}(t)\in\mathbb{R}$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems for each agent:
 \begin{equation} \label{eq:linear subsys}

### 2022-12-12 paper/paper.tex
Revise paper, All.

@@
 \begin{abstract}
-In this study, we investigate a motion planning and robust fault-tolerant control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
-The system architecture of URTS is proposed at first to illustrate the issues to be addressed in URTS and the relationships between them.
-The task allocation and path planning problems are first investigated.
+In this study, we investigate a motion planning and robust fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
+The system architecture of URTS is proposed at first to illustrate the problems to be addressed in URTS and the relationships between them.
+The task allocation problem and path planning problem are first investigated.
 Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAVs and robots in the hybrid team system.
 The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into a unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward fault-tolerant control (FTC) strategy is proposed for the agents in URTS.
+By converting the dynamics models of UAV and robot into a unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
@@
 With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed $H_\infty$ decentralized fault-tolerant tracking control method of hybrid URTS under the external disturbance and the actuator and sensor fault.
+Finally, the simulation results are used to demonstrate the operation of the proposed URTS architecture and to verify the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
 \end{abstract}
@@
 In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued \cite{9371292}.
-Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.
+Compared with homogeneous MAS, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.
 
@@
 For these reasons, a hybrid UAVs-UGVs team system will be more appealing.
-To discuss more concretely, we consider a hybrid UAVs-UGVs team system for S\&R.
+To discuss more concretely, we consider a hybrid UAVs-UGVs team system for S\&R usage.
 For the need for search mobility, we choose quadrotor aircraft as UAV.
@@
 It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
-In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation
-and specify an independent trajectory for each agent to follow.
+In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation.
 
@@
 Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
-Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed to deal with the control problem in hybrid URTS.
+Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward FTC scheme is proposed to deal with the control problem in hybrid URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
@@
 In this section, a specific S\&R procedure for URTS is given to illustrate the proposed URTS system architecture and demonstrate the effectiveness of motion planning and control strategy of a hybrid UAVs and biped robots team system.
-First, a S\&R area divided into $N_T$ areas, $area_i,i=1,2,...,N_T$, is given as shown in Fig.
+First, a S\&R area divided into $N_T$ areas $area_i,i=1,2,...,N_T$, is given as shown in Fig.
 \ref{fig:SR_area}.
-To simplify the description, we will focus on the UAV and robot in $i$th team.
-Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,5 \}$.
-
-At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find goals.
+To simplify the description, we will focus on the UAV and robot in $i$th team and $(i+1)$th team.
+Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,N_A \}$.
+
+At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find targets.
 The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
 \ref{fig:S_task}.
-Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}$.
+Representing the search tasks in Fig.
+\ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,N_A \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,N_A \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block.
 Suppose a goal is found after a while as shown in Fig.
 \ref{fig:S_task}.
-At this point, we have a rescue task $T_6$.
-The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one.
-If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_2),(\alpha_{i+1,2},T_3) \})\cup\{ (\alpha_{i,5},T_6),(\alpha_{i+1,2},T_6) \}$.
+At this point, we have a rescue task $T_7$.
+The new task list $task_2=task_1\cup\{ T_7 \}$ is obtained by updating the old one.
+If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_7$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_5),(\alpha_{i+1,2},T_6) \})\cup\{ (\alpha_{i,5},T_7),(\alpha_{i+1,2},T_7) \}$.
 Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
@@
     \centering
-    \includegraphics[scale=.4]{fig/S_task.pdf}\caption{The search tasks in the $i$th team at the begining.
+    \includegraphics[scale=.12]{fig/S_task.png}\caption{The search tasks in the $i$th team at the begining.
 The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive goals $q_{goal}$ (black dots in figure) obtained from task allocation block.
-For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.
-For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.}
+For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
+For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.}
     \label{fig:S_task}
@@
 
-To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_6)$ and $(\alpha_{i,1}, T_1)$ as example.
+To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
 For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly assigned as shown in Fig.
@@
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
-For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_6$.
+For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_7$.
 With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
@@
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking}$ for $n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing}$ for $n\in\mathbb{Z}\cap[6,15]$ and $\beta_n=\mathit{running}$ for $n\in\mathbb{Z}\cap[16,27]$.
-We choose the walking behavior to illustrate the local motion planning block of robots.
+We choose the walking behavior $\beta_n, n\in\mathbb{Z}\cap[1,5]$ to illustrate the local motion planning block of robots.
 \begin{figure}[htbp]
@@
 $C = C_0 \otimes I_n$ where $C_0 = I_3$.
-    \item designed parameters: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $w_1=3$ and $w_2=4$, respectively.
+    \item designed parameters of subsystems: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $w_1=3$ and $w_2=4$, respectively.
 \end{enumerate}
@@
 
-    \item designed parameters: 
-    $Q_1 = 10diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
-    $Q_2 = diag(0.1diag([1\mathbin{,} 100\mathbin{,} 10]), diag(1,0.1\mathbin{,} 0.01), 20diag(1,0.1,0.01 ,0.001))$, 
+    \item designed parameters of subsystems: 
+    $Q_1 = 10*diag(diag(1\mathbin{,} 100\mathbin{,} 10)\mathbin{,} 0\mathbin{,} 0)$, 
+    $Q_2 = diag(0.1diag([1\mathbin{,} 100\mathbin{,} 10])\mathbin{,} diag(1,0.1, 0.01)\mathbin{,} 20diag(1, 0.1, 0.01\mathbin{,} 0.001))$, 
     $R = 0.02$.
@@
     \item system parameters: $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0, 1]^T$. Remaining parameters can be found in Appendix E in \cite{ourrobot}. 
-    \item designed parameters:
-    $Q_1 = 50diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
-    $Q_2 = 5diag(diag([1\mathbin{,} 100\mathbin{,} 10]), diag(1,0.1\mathbin{,}0.01)\mathbin{,} diag(1,0.1,0.01,0.001))$, 
+    \item designed parameters of subsystems:
+    $Q_1 = 50*diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
+    $Q_2 = 5diag(diag([1\mathbin{,} 100\mathbin{,} 10])\mathbin{,} diag(1,0.1\mathbin{,}0.01)\mathbin{,} diag(1,0.1,0.01,0.001))$, 
     $R = 0.002$.
@@
 
-The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,2}$ in $team_1$ are given as follows:
+\textit{
+    \begin{remark}
+        Since we set $C = C_0\otimes I_n$ and $B_2 = B_{2,0}\otimes I_n$, the proposed method of decomposing each agent model into $n$ subsystems is used to find $K$ and $L$.
+For the convenience of solving, we set the same design parameters $Q_1$, $Q_2$, $R$ and $\rho^*$ for each subsystem as shown above.
+    \end{remark}
+}
+The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,5}$ in $team_1$ are given as follows:
 
@@
 
-\textit{Robot $\alpha_{1,2}$:}
+\textit{Robot $\alpha_{1,5}$:}
 The trajectories of reference, state and estimated state are shown in Fig.
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{1,2}$.}%
+    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,5}$}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,2}$}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,5}$}%
     \label{fig:robot, control}
@@
 In Figs.
-\ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault, i.e., feedforward control errors and disturbances, can be effectively estimated.
+\ref{fig:UAV, fa} and \ref{fig:robot, fa}, the results show that the actuator fault $f_1(t)$, i.e., feedforward control errors and disturbances, can be effectively estimated.
 However, in Figs.
-\ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault has an overshot phenomenon when there is a large change and returns to a steady state after about $2$ seconds.
+\ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault $f_2(t)$ has an overshot phenomenon when there is a large change and returns to a steady state after about $2$ seconds.
 In Figs.
@@
 \ref{fig:uav, state, noFTC} and Fig.
-\ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1$ on the tracking error is revealed.
-The influence of the sensor fault $f_2$ is relatively insignificant because its value is much smaller than $f_1$ by our simulation setting.
-However, the fluctuation of $f_2$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig.
+\ref{fig:robot, state, noFTC}, it can be clearly seen that the influence of the acuator fault $f_1(t)$ on the tracking error is revealed.
+The influence of the sensor fault $f_2(t)$ is relatively insignificant because its value is much smaller than $f_1(t)$ by our simulation setting.
+However, the fluctuation of $f_2(t)$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig.
 \ref{fig:uav, state, noFTC} and the robot joint state variables $x_5,x_6,x_{11},x_{12}$ in Fig.
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,2}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
     \label{fig:robot, state, noFTC}
@@
     \centering
-    \includegraphics[scale=.42]{fig/URTS.png}\caption{The simulation of team tracking of URTS when perform search tasks.
+    \includegraphics[scale=.42]{fig/URTS.png}\caption{The simulation of team tracking of URTS for $team_i,i=1,2,3$ when perform search tasks.
 As shown in Fig.
@@
 As in Fig.
-\ref{fig:S_task}, this simulation assumes that URTS are assigned search tasks.
-Subsequently, the path planning algorithm calculates the collision-free path $(\sigma_n)$ for each agent.
+\ref{fig:S_task}, this simulation assumes that $team_i,i=1,2,3$ are assigned search tasks.
+Subsequently, the path $(\sigma_n)$ for each UAV is assigned and the collision-free path $(\sigma_n)$ for each robot is calculated by the path planning algorithm.
 Depending on the terrain environment, an appropriate behavior $(\beta_n)$ is determined to enable the agent to follow the path $(\sigma_n)$.
 A reference path $r[k]$ corresponding to a behavior is designed via local motion planning to enable an actual mechanical body to perform the behavior.
-Since this article only gives the motion planning method of flying (for UAV) or walking (for biped-robot), it is assumed that from $q_{start}$ to $q_{goal}$ are all flying or walking behaviors in this simulation.
-In this figure, we draw the smoothed path $\sigma'_n$ of each agent, which is the intermediate result of local motion planning as shown in Fig, \ref{fig:FandW}.
+Since this article only gives the motion planning method of flying (for UAV) and walking (for biped-robot), it is assumed that from $q_{start}$ to $q_{goal}$ are all flying or walking behaviors in this simulation.
+In this figure, we draw the smoothed path $(\sigma'_n)$ of each agent, which is the intermediate result of local motion planning as shown in Fig, \ref{fig:FandW}.
 It represents the path that the agent is going to reach in the task space.
@@
 If a block in a higher layer in URTS architecture makes a new decision that produces a new output, the lower blocks must recalculate based on it.
-Rrelatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.}
+Relatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.}
     \label{fig:URTS}
@@
 This gives a holistic view of the operational framework for URTS.
-By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common path planning algorithm can be applied in URTS.
+By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common roadmap-based path planning algorithm can be applied in URTS.
 Next, we focus on the local motion planning of UAV flying and robot walking behavior.

### 2022-12-14 paper/paper.tex
Revise paper

@@
     \centering
-\includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS.
+    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of each agent in URTS.
 The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information.
 The 5 blocks on right hand side are the flow of an agent performing a S\&R mission.
-From the top to the bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
+From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$, the planning of the path $(\sigma_n)$, the decision of the behavior $(\beta_n)$, the planning of the local motion path $r[k]$, and the low-level tracking control.
+A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses.
+The Behavior Layer block is predefined in Fig.
+\ref{fig:behavior}.
+The Local Motion Planning block is predefined in Fig.
+\ref{fig:LMP}.
+The Tracking Control block is predefined in Fig.
+\ref{fig:tracking}.}
     \label{fig:sys}
@@
 In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
-However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
+However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
 Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation.
@@
 \ref{fig:sys}, an appropriate behavior can be judged.
-However, it will be a rather complicated project, so this article only gives the structure of the behavior set.
-The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig.
+However, it will be a rather complicated project, so this article will not discuss in detail.
+The behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig.
 \ref{fig:behavior}.
@@
     \centering
-    \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer.
-(a) The behavior set of each agent in URTS.
+    \includegraphics[scale=.12]{fig/behavior.png}\caption{
+        (a) The flowchart of Behavior Layer block in Fig. \ref{fig:sys} of each agent in URTS. The behavior to be took at every moment by each agent will be decided in this block. 
+        (b) The behavior set of each agent in URTS.
 The leaves of the tree structure are the possible behaviors an agent can take.
-The behavior to be took at every moment by each agent will be decided in this block.
-For UAVs, the moving behavior set is predefined in (b).
-For robots, the moving behavior set is predefined in (c).
-(b) The moving behavior set of each UAV.
-(c) The moving behavior set of each robot.}%
+For UAVs, the moving behavior set is predefined in (c).
+For robots, the moving behavior set is predefined in (d).
+        (c) The moving behavior set of each UAV. 
+        (d) The moving behavior set of each robot.}%
     \label{fig:behavior}
@@
     \centering
-    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning.
-(a) The local motion planning of each agent in URTS .
+    \includegraphics[scale=.12]{fig/LMP.png}\caption{
+        (a) The flowchart of Local Motion Planning block in Fig.
+\ref{fig:sys} of each agent in URTS.
 The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer.
@@
 For robots, the moving block is predefined in (c).
-(b) The moving block of each UAV where the flying block is predefined in Fig.
-\ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in Fig.
-\ref{fig:FandW}}
+        (b) The moving block of each UAV where the flying block is predefined in Fig. \ref{fig:FandW}. 
+        (c) The moving block of each robot where the walking block is predefined in Fig. \ref{fig:FandW}.}
     \label{fig:LMP}
@@
     \centering
-    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}.
+    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in Fig.
+\ref{fig:LMP}.
 In both blocks, a smoothed path is obtained by post-processing first.
@@
     %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
-    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
-    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
+    (a) The Flying block in Fig. \ref{fig:LMP} of each UAV . By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$. 
+    (b) The Walking block in Fig. \ref{fig:LMP}of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
     \label{fig:FandW}
@@
 Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
-    x_r[k], y_r[k], z_r[k], \psi_r[k]
+    x_r[k], y_r[k], z_r[k], \phi_r[k]
 ]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.
@@
 More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
-The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
+The ZMP in $\widehat{X_b}$ direction can be described as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
 \begin{equation} \label{eq:x_zmp}
@@
 \ref{fig:tracking}.
-For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
+For UAV, we get $r'(t) = [x_r, y_r, z_r, \phi_r]^T\in\mathbb{R}^{4}$.
 Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system.
@@
     \centering
-    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
-    (a) The tracking control block of each agent in hybrid URTS.
+    \includegraphics[scale=.12]{fig/tracking.png}\caption{
+    (a) The flowchart of Tracking Control block in Fig.
+\ref{fig:sys} of each agent in hybrid URTS.
 The controller block is predefined in (d).
@@
     \begin{remark}
-        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r_{i,j}[k]$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
+        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted.
+For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
+    \end{remark}
+}
+\textit{
+    \begin{remark}
+        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
 That is, $r_{i,j}(t)$ is the reference trajectory that can complete the specific task, follow the specific path and perform the specific behavior.
@@
 Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.
-The coupling disturbance $c(t)$ on each agent in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
-    c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
+The coupling disturbance $c_{i,j}(t)$ on each agent in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
+    c_{i,1}(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
 \end{equation} for UAV $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
-    c(t) = \sum_{k = 1, k \neq j}^{N_A}D_{i, j, k}(x_{i, j}(t))x_{i, k}(t)
+    c_{i,j}(t) = \sum_{k = 1, k \neq j}^{N_A}D_{i, j, k}(x_{i, j}(t))x_{i, k}(t)
 \end{equation} for biped robot $\alpha_{i, j}$ where $i=1,2,\dots,N_T$ and $j=2,3,\dots,N_A$ \cite{9834947}.
+For the convenience of reading, we use $c(t)$ to represent $c_{i,j}(t)$.
 Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in hybrid URTS.
@@
     \centering
-    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$}%
+    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$.}%
     \label{fig:SR_area}
@@
     \centering
-    \includegraphics[scale=.12]{fig/S_task.png}\caption{The search tasks in the $i$th team at the begining.
-The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive goals $q_{goal}$ (black dots in figure) obtained from task allocation block.
+    \includegraphics[scale=.12]{fig/S_task.png}\caption{The search tasks in the $i$th team and $(i+1)$th team at the begining.
+The search tasks $T_j,j=1,2,...,6$ are to reach some consecutive goals $q_{goal}$ (black dots in figure) obtained from task allocation block.
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
@@
 To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
-For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=9$ is directly assigned as shown in Fig.
+For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=16$ is directly assigned as shown in Fig.
 \ref{sim:flying} without going through path planning by \textit{Assumption \ref{asm:collision}}.
-The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,9]$.
+The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,k_f]$.
 For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_7$.
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$}
+    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$.}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{1,1}$}%
+    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, control}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$}%
+    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,5}$}%
+    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,5}$}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, control}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}.}%
     \label{fig:uav, state, noFTC}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$ by traditional PID computed torque controller without FTC \cite{7456706}}%
+    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$ by traditional PID computed torque controller without FTC \cite{7456706}.}%
     \label{fig:robot, state, noFTC}

### 2022-12-20 paper/paper.tex
Revise paper. Change legend of plots.

@@
 
-\title{Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}
+\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}
 
@@
 \begin{abstract}
-In this study, we investigate a motion planning and robust fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
-The system architecture of URTS is proposed at first to illustrate the problems to be addressed in URTS and the relationships between them.
-The task allocation problem and path planning problem are first investigated.
+In this study, we integrate a local motion planning and robust decentralized fault-tolerant tracking control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
+The system architecture of URTS is proposed at first to illustrate the task allocation problem, path planning problem and robust tracking control problem in URTS and the relationships among these problems.
+The task allocation problem and path planning problem are first investigated and unified.
+To deal with complex S\&R terrain, we break down the path planning problem into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning.
 Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAVs and robots in the hybrid team system.
 The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into a unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for the agents in URTS.
+By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for the agents in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
 Then, the design of the robust $H_\infty$ decentralized observer-based feedforward FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the operation of the proposed URTS architecture and to verify the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
+With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking control design problem of each UAV and robot in URTS is effectively solved.
+Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
 \end{abstract}
@@
 \PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power.
-It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans.
+It not only reduces labor costs and brings convenience to life, but also more importantly can replace some dangerous jobs for humans.
 Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc.
@@
 
-To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control.
+To construct an unmanned HMAS, three required key capabilities are perception, decision-making and control.
 Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision through the actuator.
 To limit the scope of this paper, we focus on decision-making and control problem only.
+
 Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance.
@@
 Additionally, few literatures illustrate the relationship between these problems.
-This leads us to propose a system architecture of hybrid UAVs and biped robots team system (URTS) for S\&R usage.
-The flowchart of decision-making and control process of URTS is also given.
-We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) tracking control.
+This leads us to propose a system architecture of hybrid UAVs and biped robots team system (URTS) for S\&R usage to illustrate these problems and the relationship between them.
+The flowchart of the system architecture is also given.
+We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) reference tracking control.
 It is because the URTS needs to be able to assign different tasks to agents to perform first.
@@
 To make agent move on the path, a behavior corresponding to the environment is required to be determined.
-Then, a local motion corresponding to the behavior of the agent needs to be designed.
+Then, a local motion corresponding to the behavior of the agent needs to be planned.
 Finally, a controller must be designed to track the trajectory of the motion.
 In order to further limit the scope of the study, we will focus on the latter two processes.
-But to illustrate how the whole system works, the first three problems are also briefly stated.
+But to illustrate how the whole system works, the first three steps are also briefly stated.
 
@@
 This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
-Although some literatures directly tackle the kinodynamic constraints path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning for clarity.
+Although some literatures directly tackle the kinodynamic constraints on path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning to deal with complex S\&R terrain.
 Through this decomposition, we can focus on the local motion planning of specific behaviors.
@@
 \begin{enumerate}
-    \item A system architecture and system flow of hybrid URTS for the purpose of S\&R are proposed so that the issues involved in hybrid URTS and their relationships can be defined and resolved.
-    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the team formation tracking control of agents in hybrid URTS.
-    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based fault-tolerant tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
+    \item A system architecture and system flow of hybrid URTS for the purpose of S\&R are proposed so that the motion planning and control issues involved in hybrid URTS and their systematic relationships can be defined and resolved.
+    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms to guide the team formation tracking control of agents in hybrid URTS.
+    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based fault-tolerant tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together to achieve search and rescue task under external disturbance and actuator and sensor fault.
 \end{enumerate}
@@
 In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship among its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described.
-In Section III, the dynamics models of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
+In Section III, the dynamics models of agents in URTS are given to plan the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
 In Section IV, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
@@
 
-To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the area.
+To complete search tasks, each team is designed to be responsible for a small area of the overall S\&R area, and each agent will be assigned an appropriate path to cover the unsearched area.
 To complete rescue tasks, whenever a target (e.g., victims or disaster area) is found by the machine vision of nearby agent, the ground station will assign some agents to the location of target.
@@
 
-We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots.
+We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots if the algorithm treat the agent as a point.
 Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path).
@@
 
-In order to make a behavior, we must design a corresponding motion by local motion planning.
+In order to make a behavior, we must plan a corresponding motion by local motion planning.
 The motion is a prescribed reference path for an actual mechanical system to follow.
@@
     \centering
-    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of each agent in URTS.
-The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information.
-The 5 blocks on right hand side are the flow of an agent performing a S\&R mission.
-From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$, the planning of the path $(\sigma_n)$, the decision of the behavior $(\beta_n)$, the planning of the local motion path $r[k]$, and the low-level tracking control.
+    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of the reference trajectory planning and tracking control of each agent in URTS.
+The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as occupancy map $\mathcal{C}$ of URTS, current configuration $q_{start}$ of agents and object information of environment.
+The 5 blocks on right hand side are the flowchart of an agent performing a S\&R mission.
+From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision and allocation of the behavior $(\beta_n)$ of agents, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents.
 A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses.
-The Behavior Layer block is predefined in Fig.
+The Behavior Layer block is described detailly in Fig.
 \ref{fig:behavior}.
-The Local Motion Planning block is predefined in Fig.
+The Local Motion Planning block to generate the desired reference is described detailly in Fig.
 \ref{fig:LMP}.
-The Tracking Control block is predefined in Fig.
+The Reference Tracking Control block is described detailly in Fig.
 \ref{fig:tracking}.}
@@
 \subsection{Task Allocation}
-In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc.
-However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed).
+In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks $T_k, k\in\mathbb{Z}$, such as searching a specific area, or delivering supplies to disaster area, etc.
+However, the number of agents and tasks is more than one, each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, or amout of supplies needed).
 Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation.
@@
 A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}.
-Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function.
-In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal $q_{goal}$ it needs to go at every moment.
+Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs $(\alpha_{i,j}, T_k)$ to achieve a specific cost function.
+In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment.
+$q_{goal}$ then pass to next block, i.e., path planning block, as shown in Fig.
+\ref{fig:sys}.
 % $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
@@
     \begin{remark}
-        This block is like a commander since it is used to assign task for agents.
+        The task allocation block is like a commander since it is used to assign task for agents.
 Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
@@
 \subsection{Path Planning}
-After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it.
+After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it.
 There must exist multiple feasible paths to go.
@@
 All of the above common roadmap-based planners can be applied to the proposed URTS architecture.
-
+\textit{
     \begin{remark}
@@
     \end{remark}
+}
 
@@
 
-By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or "waypoints"), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or "map") $\mathcal{C}$.
-Current configuration is obtained by GPS, inertial measurement unit, or other locating techniques.
-Goal configuration is obtained by the previous block, task allocation block.
-Configuration space $\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
+By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or occupancy map) $\mathcal{C}$.
+$q_{start}$ is obtained by GPS, an inertial measurement unit, or other locating techniques.
+$q_{goal}$ is obtained by the previous block, task allocation block.
+$\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
 $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
@@
 \end{equation}
-where $k_f$ is the time step when reaching goal.
+where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then pass to next block, i.e., behavior layer block, as shown in Fig. \ref{fig:sys}.
+
+\textit{
+    \begin{remark}
         Since the path planning is dynamic, $(\sigma_n)$ is composed of multiple segments actually.
@@
 For robot, it can be a collision detected by a dynamic roadmap-based planner.
-The resulting path $(\sigma_n)$ is passed to the next block, behavior layer block.
+    \end{remark}
+}
 
@@
 Path planning tells agents where to go but not how since we regard the agent as a point.
+Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information.
 Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario.
@@
 \ref{fig:behavior}.
+$(\beta_n)$ then pass to next block, i.e., local motion planning block, as shown in Fig.
+\ref{fig:sys}.
 
@@
 The leaves of the tree structure are the possible behaviors an agent can take.
-For UAVs, the moving behavior set is predefined in (c).
-For robots, the moving behavior set is predefined in (d).
+For UAVs, the moving behavior set is described in (c).
+For robots, the moving behavior set is described in (d).
         (c) The moving behavior set of each UAV. 
@@
 \subsection{Local Motion Planning}
-After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior.
+After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior.
 Local motion planning block is like path planning block but with smaller scale and higher resolution and precision.
@@
 Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
-Therefore, the output of this block is also a path $r[k]$ (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
+Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
 The flowchart of local motion planning block is shown in Fig.
@@
 \ref{fig:sys} of each agent in URTS.
+Some basic behaviors of UAV and robot mentioned in Fig.
+\ref{fig:behavior} are given to futher illustrate the flow of this block.
 The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer.
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
-The reference path $r[k]$ is a sequence (or discrete signal) designed by a specific behavior block.
-For UAVs, the moving block is predefined in (b).
-For robots, the moving block is predefined in (c).
-        (b) The moving block of each UAV where the flying block is predefined in Fig. \ref{fig:FandW}. 
-        (c) The moving block of each robot where the walking block is predefined in Fig. \ref{fig:FandW}.}
+The reference path $r[k]$ is a sequence (or discrete signal) planned by a specific behavior block.
+For UAVs, the moving block is described in (b).
+For robots, the moving block is described in (c).
+        (b) The moving block of each UAV. The flying block in it is described detailly in Fig. \ref{fig:FandW}. 
+        (c) The moving block of each robot. The the walking block in it is described detailly in Fig. \ref{fig:FandW}.}
     \label{fig:LMP}
@@
 
-In Fig.
-\ref{fig:LMP}, some basic behaviors of UAV and robot mentioned in Fig.
-\ref{fig:behavior} are given to futher illustrate the flow of this block.
 To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
-They are belong to the moving behavior in Fig.
-\ref{fig:LMP}.
 A more detailed description will be given in the next section.
+$r[k]$ then pass to next block, i.e., reference tracking control block, as shown in Fig.
+\ref{fig:sys}.
 
@@
 To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
-By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is designed.
+By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is planned.
 $r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation.
@@
 If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect.
-To this end, a control method needs to be designed.
+To this end, a reference tracking control method needs to be designed.
 It will be discussed detailly in Section IV.
@@
 \section{system description of UAVs and biped robots in URTS}
-In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first.
-After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig.
+In order to plan a reference trajectory $r(t)$ for the local motion of UAV and robot in URTS, their dynamic models must be given first.
+After the system description of UAV and robot in URTS, the local motion planning of flying and walking behavior as shown in Fig.
 \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
@@
     \centering
-    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in Fig.
+    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block for local motion planning in Fig.
 \ref{fig:LMP}.
-In both blocks, a smoothed path is obtained by post-processing first.
-Then the respective motion of behavior is designed.
+In both blocks, a smoothed path $(\sigma'_n)$ is obtained by post-processing first.
+Then the respective motion of behavior is planned.
     %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
-    (a) The Flying block in Fig. \ref{fig:LMP} of each UAV . By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$. 
-    (b) The Walking block in Fig. \ref{fig:LMP}of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
+    (a) For the Flying block in Fig.
+\ref{fig:LMP} of each UAV, by combining the smoothed path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we can plan the reference path $r[k]$.
+    (b) For the Walking block in Fig. \ref{fig:LMP} of each robot, following the process in Section IV-B, we can plan the reference path $r[k]$.}
     \label{fig:FandW}
 \end{figure*}
-Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
+Before the discussion of the motion planning of these two behaviors of UAV and robot in URTS, the following assumption is maded.
 \textit{
@@
 However, for these two behaviors, there exists an inevitable holonomic constraint on the curvature of local motion.
-Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem.
+Although an accurate reference trajectory without breaking the curvature constraint can be planned, it is not easy to solve this problem.
 Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant.
-At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure this error will not cause collision.
 As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$.
+The result of post-process, i.e., smoothed path $(\sigma'_n)$, will not cause collision by \textit{Assumption \ref{asm:cc again}}.
 The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig.
@@
 Besides, since $u'(t)\in\mathbb{R}^4$ has two less degrees of freedom than $r(t)\in\mathbb{R}^6$, UAV is an underactuated system.
-This makes the two degrees of freedom in the reference trajectory of UAV cannot be assigned arbitrarily but be inversely calculated through other degrees of freedom that can be assigned arbitrarily and the dynamic equation in (\ref{eq:uav}).
+This makes the two degrees of freedom in the reference trajectory of UAV not be assigned arbitrarily but be inversely calculated through other degrees of freedom that can be assigned arbitrarily by the dynamic equation in (\ref{eq:uav}).
     \end{remark}
@@
 $\phi_r[k]$ is set to zero since no need for spinning when flying.
-$\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section.
-Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
+$\theta_r[k]$ and $\psi_r[k]$ cannot be planned beforehand since UAV is an underactuated system, which will be discussed in the next section.
+Finally, the reference path $r[k]$ of UAV can be planned by combining them together, i.e., $r[k] = [
     x_r[k], y_r[k], z_r[k], \phi_r[k]
-]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.
+]^T\in\mathbb{R}^{4}$. The flowchart of flying motion planning is shown in Fig. \ref{fig:FandW} (a).
 
@@
 The detailed kinematic and dynamic parameters can be found in the online source \cite{ourrobot}.
-For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is in the joint space.
-Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to find a stable walking pattern to prevent robot from falling.
-These make the design of walking motion more difficult.
-In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to design the walking motion of each biped robot in URTS.
+For biped robot, the reference trajectory $r(t)=q_r(t)\in\mathbb{R}^{12}$ is planned in the joint space.
+Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to plan a stable walking pattern to prevent robot from falling.
+These make the planning of walking motion of robot more difficult.
+In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to plan the walking motion of each biped robot in URTS.
 
@@
 More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots.
-The ZMP in $\widehat{X_b}$ direction can be described as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
+The ZMP in $\widehat{X_b}$ direction can be described as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is in the same form):
 \begin{equation} \label{eq:x_zmp}
@@
 To simplify this complex problem, an approximate solution can be derived through 3D-LIPM.
-We find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height.
+We plan CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height.
 Many researchers have used this method to avoid complex calculations for ZMP of the actual robot dynamic model.
-Although there exists a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple.
-The overall process is shown in Fig.
-\ref{fig:FandW}.
+Although there exists a model error between the actual dynamic model and 3D-LIPM, the planning process will be more simple.
 % \begin{figure}[htbp]
@@
 
-Following the same step in UAV, the smoothed path $(\sigma_n')$ for biped robot can be obtained at first.
+Following the same motion planning step in UAV, the smoothed path $(\sigma_n')$ for biped robot can be obtained at first.
 For the convenience of explanation, suppose walking is occured between time step $1$ and $N$, i.e., $n\in\mathbb{Z}\cap[1,N]$.
-Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot need to "swinging" for balance.
+Note that $(\sigma_n')$ is not actual CoM reference in robot case since CoM of robot needs to "swinging" for balance.
 Despite of that, $(\sigma_n')$ tells the biped robot the position to go so the $\widehat{X_b}$ direction can be obtained by doing finite difference on $(\sigma_n')$ due to the expectation that the biped robot will move forward (rather than sideways or backward).
@@
 Given $\widehat{X_b}$ and $\widehat{Z_b}$, $\widehat{Y_b}$ can be obtained obviously through cross product.
-The sequence of body frame, i.e., CoM orientation path $(CO_n)$ then be obtained through the above steps.
+The sequence of body frame, i.e., CoM orientation path $(CO_n)$ then be planned through the above steps.
 
@@
     \begin{remark}
-        A frame (or homogenous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
+        A frame (or homogeneous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
 That is, given the frames of two joints in a link with known kinematics, the frames of joints between them can be found by \textnormal{IK}.
@@
 Let us denote the $x$ and $y$ component of $\sigma_n'$ in $(\sigma_n')$ as the sequence $(\sigma^{1}_{n}), \sigma^{1}_{n}\in\mathbb{R}^2$.
-The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be found by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation among $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is the feet width (or shoulder width).
-Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, respectively, can be obtained by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
-Finally, the left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are found by adding the $z$ component which is given by ground height.
-
-After foothold paths are obtained, ankle position path can also be obtained by the given step height which is customized by the designer or based on the height of the obstacle to be crossed.
+The left and right "envelopes", $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, of $(\sigma^{1}_{n})$ with a fixed distance $L_1$ can be planned by $(\sigma^{1}_{n})$ and $(CO_n)$ through the geometric relation among $(\sigma^{i}_{n}), i=1,2,3$, where $L_1$ is the feet width (or shoulder width).
+Then the $x$ and $y$ component of the left and right foothold paths, $(\sigma^{2}_{k_n})$ and $(\sigma^{3}_{k_n})$, respectively, can be planned by a given step size, which are the subsequence of $(\sigma^{2}_{n})$ and $(\sigma^{3}_{n})$, respectively.
+Finally, the left and right foothold paths $(\sigma^{i}_{k_n}), \sigma^{i}_{k_n}\in\mathbb{R}^3, i=4,5$ are planned by adding the $z$ component which is given by ground height.
+
+After foothold paths are planned, ankle position path can also be planned by the given step height which is customized by the designer or based on the height of the obstacle to be crossed.
 Taking the left foothold path as an example, $x$ and $y$ component of the highest position of ankle during stride are set as the middle point of two footholds $\sigma^{2}_{k_m}$ and $\sigma^{2}_{k_{m+1}}$ where $m\in\mathbb{Z}\cap[1,M-1]$ with $k_1 = 1$ and $k_M = N$, and the $z$ component is given by the step height.
 By using the cubic spline interpolation, we have the left and right ankle position paths, $(\sigma^{6}_{n})$ and $(\sigma^{7}_{n})$.
-To keep the soles of the feet on the ground, the ankle orientation path can be obtain by the gradient of ground.
-Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are found by combining the position and orientation path together.
+To keep the soles of the feet on the ground, the ankle orientation path can be planned by the gradient of ground.
+Finally, the left and right ankle paths, $(\sigma^{8}_{n})$ and $(\sigma^{9}_{n})$, are planned by combining the position and orientation path together.
 So far, the remaining work is to find out the CoM path and then to combine with the ankle path to calculate the joint path through IK.
 
-To obtain the CoM postion path $(CP_n)$, ZMP path needs to be obtained first.
-ZMP path can be obtained through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground.
+To plan the CoM postion path $(CP_n)$, ZMP path needs to be planned first.
+ZMP path can be planned through foothold paths $(\sigma^{4}_{k_n})$ and $(\sigma^{5}_{k_n})$ since ZMP needs to lie in the support face and the foothold path points out when the feet are on the ground.
 Suppose the CoM height $z_c$ of biped robot is kept constant when walking, then the biped robot model can be regarded as an 3D-LIPM \cite{kajita2001real}:
@@
 \end{bmatrix}$.
-Our goal is to find a control input $u_s$ in order that the output $y_s$ can track the ZMP reference trajectory $p_x$ so that the state $x_c$, i.e., the solution of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be found.
+Our goal is to find a control input $u_s$ in order that the output $y_s$ can track the ZMP reference trajectory $p_x$ so that the state $x_c$, i.e., the solution of ODE in (\ref{eq:LIPM}) can be obtained, i.e., the CoM position path can be planned.
 Unlike conventional methods, the problem is solved by the optimal control.
@@
 By combining the CoM orientation path $(CO_n)$ wtih the position path $(CP_n)$, the CoM path can be obtained.
-Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK as shown in Fig.
-\ref{fig:FandW}.
+Finally, the joint path, i.e., reference path $r[k]\in\mathbb{R}^{12}$ of robot can be found by solving IK.
+The flowchart of walking motion planning is shown in Fig.
+\ref{fig:FandW} (b).
 
 \section{Tracking control of each agent in hybrid URTS}
-Before converting the reference path $r[k]$ to reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
+Before converting the planned reference path $r[k]$ to desired reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
 Through some appropriate variable transformations, we have:
@@
 \end{equation}
-where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system robustness.
+where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness.
 For each UAV in hybrid URTS, we have $u(t)=\begin{bmatrix}
@@
     \begin{remark}
-        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
+        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
 This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$.
+While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
     \end{remark}
 }
-
-To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig.
+To complete the planning of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig.
 \ref{fig:tracking}.
@@
 For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
-So far, the design of reference trajectory $r(t)$ of each agent in hybrid URTS is done.
+So far, the planning of reference trajectory $r(t)$ of each agent in hybrid URTS is done.
 We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig.
@@
     \includegraphics[scale=.12]{fig/tracking.png}\caption{
-    (a) The flowchart of Tracking Control block in Fig.
+    (a) The flowchart of Reference Tracking Control block in Fig.
 \ref{fig:sys} of each agent in hybrid URTS.
-The controller block is predefined in (d).
+The controller block is described in (d).
 The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
@@
 The reference generator block is introduced to deal with this problem.
-For UAVs, the reference generator block is predefined in (b).
-For robots, the reference generator block is predefined in (c).
+For UAVs, the reference generator block is described in (b).
+For robots, the reference generator block is described in (c).
     (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}). 
@@
         Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
-That is, $r_{i,j}(t)$ is the reference trajectory that can complete the specific task, follow the specific path and perform the specific behavior.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
+That is, $r_{i,j}(t)$ is the reference trajectory that can accomplish the specific task, follow the specific path and perform the specific behavior.
     \end{remark}
@@
 
-To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
+To make the model more realistic, the following disturbances encountered in actual scenarios are considered:
 \begin{enumerate}
@@
     \item For each agent, there exists sensor noise.
+    \item For each UAV, there exists vortex coupling.
     \item For each UAV, there exists wind disturbance \cite{9075385}.
@@
 Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.
-The coupling disturbance $c_{i,j}(t)$ on each agent in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
+The coupling effect $c_{i,j}(t)$ on each agent from other agents in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
     c_{i,1}(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
@@
 In addition, the wind disturbance and the ground reaction force will apply extra force on an agent in (\ref{eq:agent}).
-Therefore, through appropriate conversion, the above disturbances can be equivalent to two disturbance forces $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance.
-The nominal system in (\ref{eq:agent}) of an agent in hybrid URTS then be rewrited as the following real system:
+Therefore, through an appropriate conversion, the above disturbances can be equivalent to two disturbance forces $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling external disturbance.
+The nominal system in (\ref{eq:agent}) of an agent in hybrid URTS then can be rewritten as the following real system:
 % The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
@@
 \end{equation}
-By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have the tracking error differential equation as follow:
+By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have the tracking error differential equation as follows:
 \begin{equation} \label{eq:error, state eq}
@@
     \int_{0}^{t}e^T(\tau)d\tau & e^T(t) & \dot{e}^T(t)
-\end{bmatrix}^T\in\mathbb{R}^{3n}$, the tracking error differential equation in (\ref{eq:error, state eq}) can be rewrited as the following linear tracking error system:
+\end{bmatrix}^T\in\mathbb{R}^{3n}$, the tracking error differential equation in (\ref{eq:error, state eq}) can be rewritten as the following linear tracking error system:
 \begin{equation} \label{eq:linear f1}
@@
 
-Through the above analysis, the tracking control problem of the nonlinear system of each agent in hybrid URTS with external disturbance in (\ref{eq:agent d1}) is transformed into the regulation problem of the linear tracking error system in (\ref{eq:linear f1}) with actuator fault signal $f_1(t)$ by the feedforward linearization control law $u(t)$.
-The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ to make the linear tracking error system stable.
+Through the above analysis, the tracking control problem of the nonlinear system of each agent in hybrid URTS with external disturbance in (\ref{eq:agent d1}) is transformed into the regulation problem of the linear tracking error system in (\ref{eq:linear f1}) with actuator fault signal $f_1(t)$ by the feedforward linearization control law $u(t)$ in (\ref{eq:control}).
+The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ in (\ref{eq:linear f1}) to make the linear tracking error system robustly stable.
 In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
 At the same time, the sensor noise on sensor also needs to be considered as mentioned before.
-Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but the cyber-attack signal are concerned.
+Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the cyber-attack signal are concerned.
 We consider the effect of them as a sensor fault in this paper.
@@
 Since the fault signals become a state variable of the augmented tracking error system of an agent in (\ref{eq:e_bar}), their corruption on the tracking error dynamic system in (\ref{eq:error}) can be avoided.
-A Luenberger observer is proposed to estimate them and origin state simutaniously to achieve an active FTC by the following estimation system:
+A Luenberger observer is proposed to estimate them and $\pmb{e}(t)$ simutaniously to achieve an active FTC by the following estimation system:
 \begin{equation} \label{eq:e_hat}
@@
 \end{assumption}
-The feedback control law $u_{fb}(t)$ of each agent in hybrid URTS then be designed as follow:
+The feedback control law $u_{fb}(t)$ of each agent in hybrid URTS then be designed as follows:
 \begin{equation} \label{eq:u_fb}
@@
     \begin{remark}
-        Let $u_{fb}(t) = K\hat{\bar{e}}(t) = [K_I\mathbin{,} K_P\mathbin{,} K_D\mathbin{,} K_{F_1}\mathbin{,} K_{F_2}][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t), F_1^T(t), F_2^T(t)]^T$, we can find that the control gain $K$ is composed of the PID control gains $K_I$, $K_P$ and $K_D$ for $\int_{0}^{t}\hat{e}(\tau)d\tau$, $\hat{e}(t)$ and $\dot{\hat{e}}(t)$, respectively, and the fault control gains $K_{F_i}$ for $F_i(t)$ with $i=1,2$.
+        Let $u_{fb}(t) = K\hat{\bar{e}}(t) = [K_I\mathbin{,} K_P\mathbin{,} K_D\mathbin{,} K_{F_1}\mathbin{,} K_{F_2}][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t), \hat{F_1}^T(t), \hat{F_2}^T(t)]^T$, we can find that the control gain $K$ is composed of the PID control gains $K_I$, $K_P$ and $K_D$ for $\int_{0}^{t}\hat{e}(\tau)d\tau$, $\hat{e}(t)$ and $\dot{\hat{e}}(t)$, respectively, and the fault control gains $K_{F_i}$ for $F_i(t)$ with $i=1,2$.
 This shows that the feedback control law $u_{fb}(t)$ has fault-tolerant capability and PID control characteristic.
@@
 
-In order to enable the designed control gain $K$ in (\ref{eq:u_fb}) and observer gain $L$ in (\ref{eq:e_hat}) to achieve a specific performance for the augmented system in (\ref{eq:x_tilde}) under the disturbance $\bar{v}(t)$, the robust $H_\infty$ decentralized observer-based tracking control strategy below a prescribed disturbance attenuation level $\rho^2$ for each agent in hybrid URTS is given as follow:
+In order to enable the designed control gain $K$ in (\ref{eq:u_fb}) and observer gain $L$ in (\ref{eq:e_hat}) to achieve a specific performance for the augmented system in (\ref{eq:x_tilde}) under the disturbance $\bar{v}(t)$, the robust $H_\infty$ decentralized observer-based tracking control strategy below a prescribed disturbance attenuation level $\rho^2$ for each agent in hybrid URTS is given as follows:
 \begin{equation} \label{Hinf}
@@
 \end{equation}
-where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented tracking and estimation error system in (\ref{eq:x_tilde}), and $\tilde{v}(t)$ is the total disturbance needed to be attenuated.
+where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented tracking and estimation error system in (\ref{eq:x_tilde}) which is to be extracted from the $H_\infty$ decentralized team formation tracking control performance, and $\tilde{v}(t)$ is the total disturbance whose effect on $\bar{e}(t)$, $\tilde{e}(t)$ and $u_{fb}(t)$ is needed to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented tracking error $\bar{e}(t)$ and augmented estimation error $\tilde{e}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
 \begin{theorem} \label{theorem1}
-    If there exists matrices $P=P^T>0, K,L$ such that the following Riccati-like matrix inequality holds:
+    (i) If there exists matrices $P=P^T>0, K,L$ such that the following Riccati-like matrix inequality holds:
     \begin{equation} \label{BMI1}
@@
     \end{bmatrix}$, then the $H_\infty$ decentralized observer-based team formation tracking control strategy in (\ref{Hinf}) of each agent in the hybrid URTS can be achieved. 
+    (ii) If $\tilde{v}(t)$ is of finite energy, i.e., $\tilde{v}(t)\in L_2[0, \infty)$, then $\bar{e}(t)$, $\tilde{e}(t)$ and $u_{fb}(t)$ are all quadratically asymptotically to $0$, i.e., $\bar{e}^T(t)\bar{e}(t)\rightarrow 0$, $\tilde{e}^T(t)\tilde{e}(t)\rightarrow 0$ and $u_{fb}^T(t)u_{fb}(t)\rightarrow 0$ as $t\rightarrow \infty$.
 \end{theorem}
@@
 \begin{proof}
-    Choose the Lyapunov function $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)$ for the augmented system (\ref{eq:x_tilde}) with $P=P^T>0$, we have:
+    (i) Choose the Lyapunov function $V(\tilde{x}(t))=\tilde{x}^T(t)P\tilde{x}(t)$ for the augmented system (\ref{eq:x_tilde}) with $P=P^T>0$, we have:
     \begin{equation} \label{pf:1}
@@
     \end{equation*}
-    Thus, if (\ref{BMI1}) holds then (\ref{Hinf}) holds
+    Thus, if (\ref{BMI1}) holds then (\ref{Hinf}) holds.
+
+    (ii) From (\ref{BMI1}) and $V(\tilde{x}(0))$ is finite, we get $\int_{0}^{t_f}(\bar{e}^T(t)Q_1\bar{e}(t) + \tilde{e}^T(t)Q_2\tilde{e}(t) + u_{fb}^T(t)Ru_{fb}(t))dt 
+    \leq \rho^2 \int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt + V(\tilde{x}(0)) 
+    < \infty$. Therefore, $\bar{e}^T(t)\bar{e}(t)\rightarrow 0$, $\tilde{e}^T(t)\tilde{e}(t)\rightarrow 0$ and $u_{fb}^T(t)u_{fb}(t)\rightarrow 0$ as $t\rightarrow \infty$.
 \end{proof}
 
-Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and exists strong coupling between the designed variables $K$ and $L$.
-To solve the issue, a two-step design procedure is exploited.
+Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and there exists strong coupling between the designed variables $K$ and $L$.
+To solve the issue, a two-step design procedure is exploited as follows.
 
@@
 Embed these smoothing signal models into the linearized system (\ref{eq:error}) to get the augmented tracking error system of each agent in (\ref{eq:e_bar}).
-    \item Construct the robust FTC law in (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system of each agent in (\ref{eq:x_tilde})
-    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design procedure to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
+    \item Construct the robust observer-based FTC law in (\ref{eq:e_hat}) and (\ref{eq:u_fb}) for each agent.
+    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design procedure to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for observer-based controller in (\ref{eq:e_hat}) and (\ref{eq:u_fb}) of each agent in the hybrid URTS.
 \end{enumerate}
 
-The overall flowchart of tracking control of each agent in hybrid URTS is shown in Fig.
+The overall flowchart of reference tracking control of each agent in hybrid URTS is shown in Fig.
 \ref{fig:tracking}.
@@
 The sensor measures not only the agent's own information (e.g., position or velocity) but also environmental information.
-The former, measurement output $y(t)$, is passed to observer to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
-The letter is passed back to the high-level block for positioning, mapping and object recognition.
+The former, measurement output $y(t)$, is passed to observer in (\ref{eq:e_hat}) to get the estimation $\hat{\bar{e}}(t)$ for feedback control.
+The latter is passed back to the high-level block for positioning, mapping and object recognition.
 
@@
         By the proposed agent dynamics model in (\ref{eq:agent}) and the introduction of reference generator block in Fig.
-\ref{fig:tracking} (b), a general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent $\alpha_{i,j}$ in hybrid URTS can be designed as shown in the controller block in Fig.
-\ref{fig:tracking} (c).
-The decentralized architecture also ensures the scalability of URTS scale.
+\ref{fig:tracking} (b) and (c), a general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent $\alpha_{i,j}$ in hybrid URTS can be designed as shown in the controller block in Fig.
+\ref{fig:tracking} (d).
+The decentralized architecture also ensures the scalability of URTS.
 More specifically, let us introduce subscripts $i$ and $j$ to the corresponding variables of each agent $\alpha_{i,j},i=1,2,...,N_T,j=1,2,...,N_A$ (e.g., the state $x_{i,j}(t)$, the reference trajectory $r_{i,j}(t)$, the control gain $K_{i,j}$, etc.).
@@
 
-Although the control gain in (\ref{eq:u_fb}) and observer gain in (\ref{eq:e_bar}) for each agent in URTS can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality.
+Although the control gain in (\ref{eq:u_fb}) and observer gain in (\ref{eq:e_hat}) for each agent in URTS can already be found through the previous steps, the calculation speed of solving the matrix inequality (\ref{BMI1}) and the online calculation speed of controller and observer can be further improved by reducing the dimensionality of the system.
 Observing the matrices $A,B,C,B_2$ in the linearized system (\ref{eq:error}), it can be further split into $n$ subsystems for each agent ($n=6$ for UAV and $n=12$ for robot) if the matrices $C,B_2$ in the output equation (\ref{eq:agent output}) have the same form to $A,B$ and $l=l_0n, o=o_0n$, i.e., $C = C_0\otimes I_n,B_2 = B_{2,0}\otimes I_n$ where $C_0\in\mathbb{R}^{l_0\times 3},B_{2,0}\in\mathbb{R}^{l_0\times o_0}$.
@@
 \end{equation} where $i=1,2,...,n$.
+\textit{
     \begin{remark}
-    If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that the error $\pmb{e}_i(t)$ of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via sensors to obtain the independent outputs $y_i(t)$.
+        If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that the error $\pmb{e}_i(t)$ of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via $n$ sensors to obtain the independent outputs $y_i(t)$.
 In actual systems, this is usually done.
     \end{remark}
-
+}
 By Theorem \ref{theorem1} again, the form of subsystems in (\ref{eq:linear subsys}) shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the decentralized $H_\infty$ observer-based feedforward FTC performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
-The origin control gain $K$ of the origin agent system can be reconstructed by $K = \begin{bmatrix}
+The original control gain $K$ of the original agent system can be reconstructed by $K = \begin{bmatrix}
     \mathit{k}_1 & \mathit{k}_2 & ... & \mathit{k}_n
-\end{bmatrix}^T, \mathit{k}_i=K_i^T\otimes\mathbf{e}_i$. The origin observer gain $L$ can be reconstructed in the same way.
-
-In this case, the calculation speed of finding gains $K,L$ of each agent can be improved since the dimensionality is decrease.
-Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the gains $K,L$ found by this method while maintaining estimation and tracking robustness.
+\end{bmatrix}^T, \mathit{k}_i=K_i^T\otimes\mathbf{e}_i$. The original observer gain $L$ can be reconstructed in the same way.
+
+In this case, the calculation speed of finding gains $K,L$ of each agent can be improved since the dimensionality is decreased.
+Furthermore, the online calculation speed of controller and observer can be also improved since there are more zeros in the control gain $K$ and observer gain $L$ found by this method while maintaining the same estimation and tracking robustness.
 More clearly, the number of elements in matrix $K$, i.e., the number of scalar gains, changes from $n\times sn$ to $n(1\times s)$.
 For $L$, it changes from $sn\times l_0n$ to $n(s\times l_0)$.
-The number of scalar gains to be designed between them is $n$ times different.
+The number of scalar gains to be designed is significantly reduced.
 % \textit{
@@
 \ref{fig:SR_area}.
-To simplify the description, we will focus on the UAV and robot in $i$th team and $(i+1)$th team.
-Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $i$th team as a set, $team_i=\{ \alpha_{i,j} | i=1,2,...,N_A \}$.
+To simplify the description, we will focus on the UAV and robot in the $i$th team and the $(i+1)$th team.
+Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote the $i$th team as a set, $team_i=\{ \alpha_{i,j} | j=1,2,...,5 \}$.
 
 At the beginning, the task allocation block will assign the agents in $team_i$ with some search tasks in $area_i$ to build the occupancy map and find targets.
-The search task is assumed to be obtained by dividing the unsearched region as shown in Fig.
+The search task is assumed to be allocated by dividing the unsearched region as shown in Fig.
 \ref{fig:S_task}.
 Representing the search tasks in Fig.
-\ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,N_A \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,N_A \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block.
+\ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,5 \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block.
 Suppose a goal is found after a while as shown in Fig.
@@
     \centering
-    \includegraphics[scale=.12]{fig/S_task.png}\caption{The search tasks in the $i$th team and $(i+1)$th team at the begining.
-The search tasks $T_j,j=1,2,...,6$ are to reach some consecutive goals $q_{goal}$ (black dots in figure) obtained from task allocation block.
+    \includegraphics[scale=.12]{fig/S_task.png}\caption{The allocation of search tasks in the $i$th team and $(i+1)$th team at the begining.
+The search tasks $T_j,j=1,2,...,6$ are allocated by the task allocation block.
+The content of the search tasks is to reach some consecutive goals $q_{goal}$ (black dots in figure) so that the straight path between goals $q_{goal}$ can cover the unsearched area.
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
-For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths $(\sigma_n)$.}
+For robots, $q_{goal}$ will be passed to path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
     \label{fig:S_task}
@@
 
-To explain the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
+To illustrate the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
 For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=16$ is directly assigned as shown in Fig.
@@
     \centering
-    \includegraphics[scale=.6]{fig/robot_PP.png}\caption{The path planning result of robot using RRT algorithm. The block polygons represent the obstacle space $\mathcal{C}_{obs}$.}%
+    \includegraphics[scale=.57]{fig/uav_LMP.png}\caption{The result of local motion planning of flying behavior in $(\beta_n), n\in\mathbb{Z}\cap[1,16]$ of UAV $\alpha_{i,1}$ performing the search task $T_1$.}%
+    \label{sim:flying}
+\end{figure}
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=.6]{fig/robot_PP.png}\caption{The path planning result of the robot $\alpha_{i,5}$ performing the rescue task $T_7$ using RRT algorithm.
+The block polygons represent the obstacle space $\mathcal{C}_{obs}$.}%
     \label{fig:R_task}
@@
 
-After $(\beta_n)$ is set, we can find the reference path $r[k]$ by local motion planning block.
+After $(\beta_n)$ is set, we can plan the reference path $r[k]$ by local motion planning block.
 Following the procedure in Fig.
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav_LMP.png}\caption{The result of local motion planning of UAV flying.}%
-    \label{sim:flying}
-\end{figure}
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[scale=.57]{fig/robot_LMP.png}\caption{The top view of result of local motion planning of robot walking.
+    \includegraphics[scale=.57]{fig/robot_LMP.png}\caption{The top view of result of local motion planning of walking behavior in $(\beta_n), n\in\mathbb{Z}\cap[1,3]$ of robot $\alpha_{i,5}$ performing the rescue task $T_7$.
 The joint path, i.e., reference path $r[k]$ will be obtained by solving IK with CoM, left foothold and right foothold path.}
@@
 
-Through the previous steps and the help of reference generator block, the reference trajectory $r(t)$ of flying behavior for each UAV and walking behavior for each biped robot has been designed in URTS.
+Through the previous planning steps and the help of reference generator block, the reference trajectory $r(t)$ of flying behavior for each UAV and walking behavior for each biped robot has been planned in URTS.
 The remaining parameters are set as follows:
@@
 \textit{Agents:}\begin{enumerate}
-    \item system parameters:
-    Initial value $\tilde{x}(0) = [\pmb{e}(0)^T, F_1(0)^T\mathbin{,} F_2(0)^T, \tilde{e}(0)]^T = [[0.1X, ..., 0.1X]^T, 0, 0, 0]^T$ where $X \sim \mathcal{N}(0, 1)$.
+    \item System parameters:
+    Initial value $\tilde{x}(0) = [\pmb{e}(0)^T\mathbin{,} F_1(0)^T\mathbin{,} F_2(0)^T, \tilde{e}(0)]^T = [[0.1X, ..., 0.1X]^T, 0, 0, 0]^T$ where $X \sim \mathcal{N}(0, 1)$.
 $C = C_0 \otimes I_n$ where $C_0 = I_3$.
-    \item designed parameters of subsystems: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $w_1=3$ and $w_2=4$, respectively.
+    \item Designed parameters of subsystems: $\rho^*=30$. Actuator and sensor window size of smoothing signal model are $w_1=3$ and $w_2=4$, respectively.
 \end{enumerate}
@@
 \textit{UAVs:}\begin{enumerate}
-    \item system parameters:
+    \item System parameters:
     $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0.1, 1]^T$.
@@
 
-    \item designed parameters of subsystems: 
+    \item Designed parameters of subsystems: 
     $Q_1 = 10*diag(diag(1\mathbin{,} 100\mathbin{,} 10)\mathbin{,} 0\mathbin{,} 0)$, 
@@
 
-    \item actuator coupling disturbance in (\ref{eq:UAV couple}):
+    \item Couplings from other agents in (\ref{eq:UAV couple}):
     \\$c(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)\in\mathbb{R}^6$ where $D_{i, 1, k}(x_{i, 1}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t))$ with $x_{i, 1}(t) = [x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 6}(t)]^T$.
-    \item actuator non-coupling disturbance:
+    \item External disturbance:
     \\ $d_1(t) = [100\sin(3t)\mathbin{,} ...\mathbin{,} 100\sin(3t)]^T\in\mathbb{R}^6$.
-    \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:UAV, fa}.
+    \item Sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:UAV, fa}.
 \end{enumerate}
@@
 \textit{Robots:} \begin{enumerate}
-    \item system parameters: $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0, 1]^T$. Remaining parameters can be found in Appendix E in \cite{ourrobot}. 
-    \item designed parameters of subsystems:
+    \item System parameters: $B_2=B_{2,0}\otimes I_n$ where $B_{2,0} = [0, 0, 1]^T$. Remaining parameters can be found in Appendix E in \cite{ourrobot}. 
+    \item Designed parameters of subsystems:
     $Q_1 = 50*diag(diag(1,100,10)\mathbin{,} 0\mathbin{,} 0)$, 
@@
     $R = 0.002$.
-    \item actuator coupling disturbance in (\ref{eq:robot couple}):
+    \item Couplings from other agents in (\ref{eq:robot couple}):
     \\ $c(t) = \sum_{k = 1, k \neq j'}^{N_A}D_{i, j', k}(x_{i, j'}(t))x_{i, k}(t)\in\mathbb{R}^{12}$ where $D_{i, j', k}(x_{i, j'}(t)) = diag(x_{i, 1, 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, 1, 12}(t))$ with $x_{i, j'}(t) = [x_{i, j', 1}(t)\mathbin{,}\dots\mathbin{,}x_{i, j', 12}(t)]^T$.
-    \item actuator non-coupling disturbance:
+    \item External disturbance:
     \\ $d_1(t) = [10\sin(3t)\mathbin{,} ...\mathbin{,} 10\sin(3t)]^T\in\mathbb{R}^{12}$.
-    \item sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:robot, fa}.
+    \item Sensor fault: $f_2(t)$ is set as a smoothed square wave as shown in Fig. \ref{fig:robot, fa}.
 \end{enumerate}
@@
         Since we set $C = C_0\otimes I_n$ and $B_2 = B_{2,0}\otimes I_n$, the proposed method of decomposing each agent model into $n$ subsystems is used to find $K$ and $L$.
-For the convenience of solving, we set the same design parameters $Q_1$, $Q_2$, $R$ and $\rho^*$ for each subsystem as shown above.
+For the convenience of solving the LMIs-constrained optimization problem in \ref{LMI constraint}, we set the same design parameters $Q_1$, $Q_2$, $R$ and $\rho^*$ for each subsystem as shown above.
     \end{remark}
 }
-The simulation results of tracking and estimation in tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,5}$ in $team_1$ are given as follows:
+The simulation results of tracking and estimation in reference tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,5}$ in $team_1$ are given as follows:
 
 \textit{UAV $\alpha_{1,1}$:}
-The trajectories of reference, state and estimated state are shown in Fig.
+The position trajectories of reference $r(t)$, state $x(t) = e(t) + r(t)$ and estimated state $\hat{x}(t) = \hat{e}(t) + r(t)$ are shown in Fig.
 \ref{fig:UAV, state}.
-The estimation of actuator fault $f_1(t)$ is shown in Fig.
+The estimation of actuator fault $f_1(t)$ in (\ref{eq:linear f1}) is shown in Fig.
 \ref{fig:UAV, fa}.
-The estimation of sensor fault $f_2(t)$ is shown in Fig.
+The estimation of sensor fault $f_2(t)$ in (\ref{eq:agent output}) is shown in Fig.
 \ref{fig:UAV, fs}.
-The control effort is shown in Fig.
+The actuator control input $u'(t)$ is shown in Fig.
 \ref{fig:UAV, control}.
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$.}%
+    \includegraphics[scale=.57]{fig/uav (1).png}\caption{The trajectories of components of reference $r(t)$, state $x(t)$ and estimated state $\hat{x}(t)$ of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of actuator fault of the UAV $\alpha_{1,1}$.}
+    \includegraphics[scale=.57]{fig/uav (2).png}\caption{The estimation of components of actuator fault $f_1(t)$ of the UAV $\alpha_{1,1}$.}
     \label{fig:UAV, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of sensor fault of the UAV $\alpha_{1,1}$.}%
+    \includegraphics[scale=.57]{fig/uav (3).png}\caption{The estimation of components of sensor fault $f_2(t)$ of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The control effort of the UAV $\alpha_{1,1}$.}%
+    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The actual control input $u'(t)$ of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, control}
@@
 \textit{Robot $\alpha_{1,5}$:}
-The trajectories of reference, state and estimated state are shown in Fig.
+The position trajectories of reference $r(t)$, state $x(t) = e(t) + r(t)$ and estimated state $\hat{x}(t) = \hat{e}(t) + r(t)$ are shown in Fig.
 \ref{fig:robot, state}.
-The estimation of actuator fault $f_1(t)$ is shown in Fig.
+The estimation of actuator fault $f_1(t)$ in (\ref{eq:linear f1}) is shown in Fig.
 \ref{fig:robot, fa}.
-The estimation of sensor fault $f_2(t)$ is shown in Fig.
+The estimation of sensor fault $f_2(t)$ in (\ref{eq:agent output}) is shown in Fig.
 \ref{fig:robot, fs}.
-The control effort is shown in Fig.
+The actuator control input $u'(t)$ is shown in Fig.
 \ref{fig:robot, control}.
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$.}%
+    \includegraphics[scale=.57]{fig/robot (1).png}\caption{The trajectories of components of reference $r(t)$, state $x(t)$ and estimated state $\hat{x}(t)$ of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, state}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of actuator fault of the robot $\alpha_{1,5}$.}%
+    \includegraphics[scale=.57]{fig/robot (2).png}\caption{The estimation of components of actuator fault $f_1(t)$ of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, fa}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of sensor fault of the robot $\alpha_{1,5}$.}%
+    \includegraphics[scale=.57]{fig/robot (3).png}\caption{The estimation of components of sensor fault $f_2(t)$ of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, fs}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The control effort of the robot $\alpha_{1,5}$.}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The actual control input $u'(t)$ of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, control}
@@
 \ref{fig:UAV, fs} and \ref{fig:robot, fs}, the estimation of sensor fault $f_2(t)$ has an overshot phenomenon when there is a large change and returns to a steady state after about $2$ seconds.
+This is because the sensor fault $f_2(t)$ in $y(t)$ will directly influence on the estimation of Luenberger observer in (\ref{eq:e_hat}).
 In Figs.
-\ref{fig:UAV, control} and \ref{fig:robot, control}, the control efforts have high frequency and high amplitude at the initial instance due to the high gain characteristic of the robust control.
+\ref{fig:UAV, control} and \ref{fig:robot, control}, the actual control input $u'(t)$ have high frequency and high amplitude at the initial instance due to the high gain characteristic of the robust control.
 After that, they maintain the sine wave shape to offset the estimated actuator fault value.
-Besides, it can be seen that the total force $F$ of UAV remains constant against gravity in Fig.
+Besides, it can be seen that the total force $F$ of UAV remains constant against the gravity in Fig.
 \ref{fig:UAV, control}.
@@
 
-In order to show the effect of active FTC based on the proposed embed smoothing model method, a traditional PID computed torque controller without FTC is used for comparison \cite{7456706}.
-In order to only focus on the effect of FTC, the method in \cite{7456706} was revised to oberserver based, that is, the control law become $u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t))$ where $u_{fb}(t) = [K_I, K_P, K_D][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t)]^T$.
+In order to show the effect of active FTC based on the proposed embedded smoothing model method, a traditional PID computed torque controller without FTC is used for comparison \cite{7456706}.
+In order to only focus on the effect of FTC, the method in \cite{7456706} was revised to oberserver-based output feedback control law, that is, the control law become $u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t))$ where $u_{fb}(t) = [K_I, K_P, K_D][\int_{0}^{t}\hat{e}^T(\tau)d\tau, \hat{e}^T(t), \dot{\hat{e}}^T(t)]^T$.
 The results are shown in Fig.
-\ref{fig:uav, state, noFTC} for UAV and Fig.
-\ref{fig:robot, state, noFTC} for robot.
+\ref{fig:uav, state, noFTC} for a UAV and Fig.
+\ref{fig:robot, state, noFTC} for a robot.
 From Fig.
@@
 The influence of the sensor fault $f_2(t)$ is relatively insignificant because its value is much smaller than $f_1(t)$ by our simulation setting.
-However, the fluctuation of $f_2(t)$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig.
+However, the effect of fluctuation $f_2(t)$ with a period of 10 seconds (corresponding to the period of the smoothed square wave) can still be seen from the UAV attitude state variables $x_4,x_5,x_6$ in Fig.
 \ref{fig:uav, state, noFTC} and the robot joint state variables $x_5,x_6,x_{11},x_{12}$ in Fig.
 \ref{fig:robot, state, noFTC}.
-Although it still stable, the tracking performance has dropped significantly compared to Fig.
-\ref{fig:UAV, state} and \ref{fig:robot, state}, respectively.
+Although it is still stable, the tracking performance has deteriorated significantly compared to Fig.
+\ref{fig:UAV, state} and Fig.
+\ref{fig:robot, state}, respectively.
 \begin{figure}[htbp]
     \centering
-    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the UAV $\alpha_{1,1}$ by traditional PID computed torque controller without FTC \cite{7456706}.}%
+    \includegraphics[scale=.57]{fig/uav (1) noFTC.png}\caption{The trajectories of reference $r(t)$, state $x(t)$ and estimated state $\hat{x}(t)$ of the UAV $\alpha_{1,1}$ by the traditional PID computed torque controller without FTC \cite{7456706}.}%
     \label{fig:uav, state, noFTC}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference, state and estimated state of the robot $\alpha_{1,5}$ by traditional PID computed torque controller without FTC \cite{7456706}.}%
+    \includegraphics[scale=.57]{fig/robot (1) noFTC.png}\caption{The trajectories of reference $r(t)$, state $x(t)$ and estimated state $\hat{x}(t)$ of the robot $\alpha_{1,5}$ by the traditional PID computed torque controller without FTC \cite{7456706}.}%
     \label{fig:robot, state, noFTC}
@@
 
-We use three teams $team_i, i=1, 2, 3$ to show the team tracking results of URTS as shown in Fig. \ref{fig:URTS}.
+We use three teams $team_i, i=1, 2, 3$ to show the team tracking results of hybrid URTS as shown in Fig. \ref{fig:URTS}.
 \begin{figure*}[htbp]
     \centering
-    \includegraphics[scale=.42]{fig/URTS.png}\caption{The simulation of team tracking of URTS for $team_i,i=1,2,3$ when perform search tasks.
+    \includegraphics[scale=.42]{fig/URTS.png}\caption{The simulation of team tracking of URTS for $team_i,i=1,2,3$ when they perform search tasks.
 As shown in Fig.
@@
 First, the respective tasks of each agent are determined by the task allocation algorithm.
-According to the task content, the agent will be determined a goal $q_{goal}$.
-As in Fig.
-\ref{fig:S_task}, this simulation assumes that $team_i,i=1,2,3$ are assigned search tasks.
+According to the task content, each agent will be determined a goal $q_{goal}$.
+As shown in Fig.
+\ref{fig:S_task}, this simulation assumes that $team_i,i=1,2,3$ are assigned with search tasks.
 Subsequently, the path $(\sigma_n)$ for each UAV is assigned and the collision-free path $(\sigma_n)$ for each robot is calculated by the path planning algorithm.
 Depending on the terrain environment, an appropriate behavior $(\beta_n)$ is determined to enable the agent to follow the path $(\sigma_n)$.
-A reference path $r[k]$ corresponding to a behavior is designed via local motion planning to enable an actual mechanical body to perform the behavior.
-Since this article only gives the motion planning method of flying (for UAV) and walking (for biped-robot), it is assumed that from $q_{start}$ to $q_{goal}$ are all flying or walking behaviors in this simulation.
+A reference path $r[k]$ corresponding to a behavior is planned via local motion planning to enable an actual mechanical body to perform the behavior.
+Since this article only gives the motion planning method of flying (for UAV) and walking (for biped-robot), it is assumed that the appropriate behaviors from $q_{start}$ to $q_{goal}$ are all flying or walking behaviors in this simulation.
 In this figure, we draw the smoothed path $(\sigma'_n)$ of each agent, which is the intermediate result of local motion planning as shown in Fig, \ref{fig:FandW}.
 It represents the path that the agent is going to reach in the task space.
-According to $r[k]$ and the dynamic model of UAV and robot, the reference trajectory $r(t)$ of each agent is obtained.
+According to $r[k]$ and the dynamic model of UAV and robot, the reference trajectory $r(t)$ of each agent is planned.
 Finally, through the decentralized $H_\infty$ observer-based feedforward FTC scheme proposed in this paper, the team tracking result of the agents in $team_i, i=1,2,3$ in URTS are shown.
 Note that the above process is dynamic.
-If a block in a higher layer in URTS architecture makes a new decision that produces a new output, the lower blocks must recalculate based on it.
-Relatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.}
+If a block in a higher layer in URTS architecture makes a new decision that produces a new reference planning, the lower blocks must recalculate based on it.
+Relatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.
+The real time simulation of reference planning and team formation tracking control of URTS is given in \cite{mySimulation}}
     \label{fig:URTS}
@@
 
-For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
+For further verification, we visualized the real time simulation of reference planning and team formation tracking control in hybrid URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
 The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method for agents in URTS.
@@
 \section{conclusion}
-In this study, a system architecture of URTS is given for S\&R usage.
-This gives a holistic view of the operational framework for URTS.
+In this study, a system architecture of reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given.
+This gives a holistic view of the operational framework of how to integrate motion planning and robust decentralized fault-tolerant tracking control for hybrid URTS.
 By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common roadmap-based path planning algorithm can be applied in URTS.
 Next, we focus on the local motion planning of UAV flying and robot walking behavior.
-Besides, the bridging method between the reference path designed by local motion planning and the tracking control design is also given.
-By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analysis together.
-Through a feedforward strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
+Besides, the bridging method between the reference path planned by the local motion planning block and the reference trajectory to be  followed in the reference tracking control block is also given.
+By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analyzed together.
+Through a feedforward control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
 Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system.

### 2022-12-20 src/URTS main script/UAV/oneUAV_FaFs.m

@@ -115,8 +115,8 @@ if uav.EXE_PLOT
     %% Tracking control results
     % PlotLMP(uav)
     % uav.PlotTC(); 
-    % PlotActualControl(uav) % Actual control input
-    PlotStateAndRef3D(uav) % 3D, r(t), state
+    PlotActualControl(uav) % Actual control input
+    % PlotStateAndRef3D(uav) % 3D, r(t), state
 
 end
 

### 2022-12-20 paper/paper.tex
Add Authors

@@
     \centering
-    \includegraphics[scale=.12]{fig/S_task.png}\caption{The allocation of search tasks in the $i$th team and $(i+1)$th team at the begining.
+    \includegraphics[scale=.105]{fig/S_task.png}\caption{The allocation of search tasks in the $i$th team and $(i+1)$th team at the begining.
 The search tasks $T_j,j=1,2,...,6$ are allocated by the task allocation block.
@@
 \section{conclusion}
-In this study, a system architecture of reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given.
+In this study, a system architecture of task allocation, reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given.
 This gives a holistic view of the operational framework of how to integrate motion planning and robust decentralized fault-tolerant tracking control for hybrid URTS.
@@
 Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward FTC method is also verified by the simulation results.
-In the future, we will...
 
@@
 
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author1.jpg}}]{Bor-sen chen}
+    (Life Fellow, IEEE) received the B.S.
+degree in electrical engineering from the Tatung Institute of Technology, Taipei, Taiwan, in 1970, the M.S.
+degree in geophysics from National Central University, Chungli, Taiwan, in 1973, and the Ph.D.
+degree in electrical engineering from the University of Southern California, Los Angeles, CA, USA, in 1982.
+He was a Lecturer, an Associate Professor, and a Professor with the Tatung Institute of Technology, from 1973 to 1987.
+He is currently the Tsing Hua Distinguished Chair Professor of electrical engineering and computer science with National Tsing Hua University, Hsinchu, Taiwan.
+His current research interests include control engineering, signal processing, and systems biology.
+He has received the Distinguished Research Award from the National Science Council of Taiwan four times.
+He is also the National Chair Professor of the Ministry of Education of Taiwan.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author2.jpg}}]{Ting-Wei Hung}
+    received the B.S.
+degree in the department of engineering science from the National Cheng Kung University, Tainan, Taiwan, in 2020, and the M.S.
+degree from the Department of Electrical Engineering, National Tsing Hua University, in 2022.
+His current research interests include robotics, robust control, and team formation control.
+\end{IEEEbiography}
+
 \EOD

### 2022-12-21 paper/paper.tex
Revise paper to enhance the link between sections

@@
 \begin{abstract}
-In this study, we integrate a local motion planning and robust decentralized fault-tolerant tracking control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
-The system architecture of URTS is proposed at first to illustrate the task allocation problem, path planning problem and robust tracking control problem in URTS and the relationships among these problems.
-The task allocation problem and path planning problem are first investigated and unified.
-To deal with complex S\&R terrain, we break down the path planning problem into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning.
-Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAVs and robots in the hybrid team system.
+In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
+A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage.
+In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated.
+In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated.
+To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning.
+Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS.
+By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment.
+Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system.
 The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for the agents in URTS.
+By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking control design problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
+With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved.
+Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
 \end{abstract}
@@
 Additionally, few literatures illustrate the relationship between these problems.
-This leads us to propose a system architecture of hybrid UAVs and biped robots team system (URTS) for S\&R usage to illustrate these problems and the relationship between them.
+This leads us to propose a system architecture of performing S\&R tasks for each agent in URTS to illustrate these problems and the relationship between them.
 The flowchart of the system architecture is also given.
-We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) reference tracking control.
+We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) global path planning, (iii) behavior decision, (iv) local motion planning and (v) reference tracking control.
 It is because the URTS needs to be able to assign different tasks to agents to perform first.
@@
 This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
-Although some literatures directly tackle the kinodynamic constraints on path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) path planning, (ii) behavior layer and (iii) local motion planning to deal with complex S\&R terrain.
+Although some literatures directly tackle the kinodynamic constraints on path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning to deal with complex S\&R terrain.
 Through this decomposition, we can focus on the local motion planning of specific behaviors.
@@
 Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
-Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward FTC scheme is proposed to deal with the control problem in hybrid URTS.
+Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme is proposed to deal with the control problem in hybrid URTS.
 % The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
@@
 \begin{enumerate}
-    \item A system architecture and system flow of hybrid URTS for the purpose of S\&R are proposed so that the motion planning and control issues involved in hybrid URTS and their systematic relationships can be defined and resolved.
-    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms to guide the team formation tracking control of agents in hybrid URTS.
-    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based fault-tolerant tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together to achieve search and rescue task under external disturbance and actuator and sensor fault.
+    \item A system architecture of performing S\&R tasks for each agent in hybrid URTS are proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
+    \item A transformation between the path planned by a roadmap-based path planning algorithm and the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS.
+    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved together to achieve S\&R task under external disturbance and actuator and sensor fault.
 \end{enumerate}
@@
 The remainder of the paper is organized as follows.
-In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship among its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described.
+In Section II, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed and the function and relationship among its components, i.e., task allocation, global path planning, behavior decision, local motion planning and tracking control are described.
 In Section III, the dynamics models of agents in URTS are given to plan the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
-In Section IV, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
-In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
+In Section V, a simulation example is given to illustrate the operation of the system architecture of performing S\&R tasks for each agent in hybrid URTS and to verify the effectiveness of the proposed tracking control method.
 In Section VI, a conclusion is maded.
@@
 \section{PRELIMINARIES OF URTS in S\&R usage}
-The URTS will start with a given S\&R area, and end with the S\&R mission completed.
+The URTS will start with a given S\&R area, and end with the S\&R task completed.
 The URTS is composed of $N_T$ teams and a ground station.
@@
 Sometimes they need the behavior such as stop to look around, get supplies and put supplies.
-To meet these needs, a behavioral layer is necessary.
-% The behavior layer decides an appropriate behavior based on the circumstances.
+To meet these needs, a behavioral decision is necessary.
+% The behavior decision decides an appropriate behavior based on the circumstances.
 
@@
 The agents overall have the same system architecture in URTS except for some subprocess differences.
-Followed by the concept in \cite{paden2016survey}, a system architecture for an agent employed for S\&R is proposed as shown in Fig.
+Followed by the concept in \cite{paden2016survey}, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed as shown in Fig.
 \ref{fig:sys}.
-The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$.
+The Simultaneous Localization And Mapping (SLAM) block converts sensor information and distance information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$.
 The visual object recognition block provides distance information and object information through the analysis of sensor information.
 The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decides to climb through it).
-The detailed functions of remaining 5 blocks, i.e., Task Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following subsections.
+The detailed functions of remaining 5 blocks, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Tracking Control, will be explained in the following subsections.
 
 % To determine the behavior, agent needs the information about environment.
-The sensing data which include external environment information and internal system information is feedback to Behavior Layer to assist in judging the present state (fig:system).
+The sensing data which include external environment information and internal system information is feedback to Behavior decision to assist in judging the present state (fig:system).
 
@@
     \centering
-    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of the reference trajectory planning and tracking control of each agent in URTS.
+    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of performing S\&R tasks for each agent in hybrid URTS.
 The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as occupancy map $\mathcal{C}$ of URTS, current configuration $q_{start}$ of agents and object information of environment.
-The 5 blocks on right hand side are the flowchart of an agent performing a S\&R mission.
-From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision and allocation of the behavior $(\beta_n)$ of agents, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents.
+The 5 blocks on right hand side are the flowchart of an agent performing a S\&R task.
+From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision of the behavior $(\beta_n)$ of agents, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents.
 A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses.
-The Behavior Layer block is described detailly in Fig.
+The Behavior Decision block is described detailly in Fig.
 \ref{fig:behavior}.
@@
 In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment.
-$q_{goal}$ then pass to next block, i.e., path planning block, as shown in Fig.
+$q_{goal}$ then pass to next block, i.e., global path planning block, as shown in Fig.
 \ref{fig:sys}.
@@
 
-\subsection{Path Planning}
+\subsection{Global Path Planning}
 After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it.
@@
 In this case, an unified planner will become overly complex and impracticable.
-Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning.
-The path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints.
+Therefore, we divide path planning into three subprocesses, i.e., global path planning, behavior decision and local motion planning.
+The global path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints.
 The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
@@
 By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or occupancy map) $\mathcal{C}$.
-$q_{start}$ is obtained by GPS, an inertial measurement unit, or other locating techniques.
-$q_{goal}$ is obtained by the previous block, task allocation block.
-$\mathcal{C}$ is constructed by environment information through sensors of agents online or in advance by human knowledge offline.
+$q_{start}$ and $\mathcal{C}$ is obtained by SLAM, and $q_{goal}$ is obtained by the previous block, task allocation block, as shown in Fig.
+\ref{fig:sys}.
 $\mathcal{C}$ is a space containing all possible configurations of agents which are composed of free space $\mathcal{C}_{free}$ and obstacle space $\mathcal{C}_{obs}$, where $\mathcal{C}=\mathcal{C}_{free}\cup\mathcal{C}_{obs}$ and $\mathcal{C}_{free}\cap\mathcal{C}_{obs}=\emptyset$.
@@
 \end{equation}
-where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then pass to next block, i.e., behavior layer block, as shown in Fig. \ref{fig:sys}.
+where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then pass to next block, i.e., behavior decision block, as shown in Fig. \ref{fig:sys}.
 
@@
 
-\subsection{Behavior Layer}
+\subsection{Behavior Decision}
 % Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
-Path planning tells agents where to go but not how since we regard the agent as a point.
+Global path planning block tells agents where to go but not how since we regard the agent as a point.
 Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information.
@@
 By the object information in Fig.
-\ref{fig:sys}, an appropriate behavior can be judged.
+\ref{fig:sys}, an appropriate behavior can be decided.
 However, it will be a rather complicated project, so this article will not discuss in detail.
@@
     \includegraphics[scale=.12]{fig/behavior.png}\caption{
-        (a) The flowchart of Behavior Layer block in Fig. \ref{fig:sys} of each agent in URTS. The behavior to be took at every moment by each agent will be decided in this block. 
+        (a) The flowchart of Behavior Decision block in Fig. \ref{fig:sys} of each agent in URTS. The behavior to be took at every moment by each agent will be decided in this block. 
         (b) The behavior set of each agent in URTS.
@@
 After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior.
-Local motion planning block is like path planning block but with smaller scale and higher resolution and precision.
-Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here.
+Local motion planning block is like global path planning block but with smaller scale and higher resolution and precision.
+Collision checking is needed since we consider agent as a point in global path planning block but it is a real mechanical body here.
 Furthermore, the kinodynamic constraint is handled in this block.
 Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
-Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
+Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (it is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
 The flowchart of local motion planning block is shown in Fig.
@@
 \ref{fig:behavior} are given to futher illustrate the flow of this block.
-The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer.
+The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior decision.
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
@@
 
-\subsection{Tracking Control}
+\subsection{Reference Tracking Control}
 To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
@@
 It will be discussed detailly in Section IV.
-In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper layer as shown in Fig.
+In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper decision as shown in Fig.
 \ref{fig:sys}.
@@
 
-\subsection{motion planning of flying of UAV}
+\subsection{Local motion planning of flying of UAV}
 A dynamic model about how an UAV in URTS moves in the physical world is given first. By Newton-Euler equation, the dynamic model of each UAV in URTS can be formulated as \cite{sabatino2015quadrotor}:
@@
 
-\subsection{motion planning of walking of robot}
+\subsection{Local motion planning of walking of robot}
 By Lagrange equation, the dynamic model of a biped robot in URTS can be formulated as:
@@
 
-\section{Tracking control of each agent in hybrid URTS}
+\section{Reference tracking control of each agent in hybrid URTS}
+Through the previous step, the planning of the reference path $r[k]$ of each agent in hybrid URTS has been completed.
+However, in order to calculate the unplannable reference paths, i.e., $\phi_[k]$ and $\theta_r[k]$, of UAV and analyze the reference trajectory tracking problem in the continuous domain, we have to transform $r[k]$ into the reference trajectory $r(t)$.
 Before converting the planned reference path $r[k]$ to desired reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
@@
 The controller block is described in (d).
-The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
+The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
 It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV.
@@
     (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated. 
-    (d) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
+    (d) The proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme for each agent in hybrid URTS.}
     \label{fig:tracking}
@@
         Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, global path planning, behavior decision and local motion planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
 That is, $r_{i,j}(t)$ is the reference trajectory that can accomplish the specific task, follow the specific path and perform the specific behavior.
@@
 
-Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and there exists strong coupling between the designed variables $K$ and $L$.
+Although the sufficient condition (\ref{BMI1}) for the existence of the $H_\infty$ decentralized observer-based tracking control strategy in (\ref{Hinf}) have been found, it can not be solved easily since it is a bilinear matrix inequality (BMI) and there exists strong coupling between the designed variables $K$ and $L$.
 To solve the issue, a two-step design procedure is exploited as follows.
@@
 
-The design procedure of the optimal decentralized $H_\infty$ observer-based feedforward FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
+The design procedure of the optimal decentralized $H_\infty$ observer-based feedforward reference tracking FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
 \begin{enumerate}
@@
         By the proposed agent dynamics model in (\ref{eq:agent}) and the introduction of reference generator block in Fig.
-\ref{fig:tracking} (b) and (c), a general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent $\alpha_{i,j}$ in hybrid URTS can be designed as shown in the controller block in Fig.
+\ref{fig:tracking} (b) and (c), a general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme for each agent $\alpha_{i,j}$ in hybrid URTS can be designed as shown in the controller block in Fig.
 \ref{fig:tracking} (d).
@@
 }
-By Theorem \ref{theorem1} again, the form of subsystems in (\ref{eq:linear subsys}) shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the decentralized $H_\infty$ observer-based feedforward FTC performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
+By Theorem \ref{theorem1} again, the form of subsystems in (\ref{eq:linear subsys}) shows that we can find the control gain $K_i\in\mathbb{R}^{1\times s}$ and observer gain $L_i\in\mathbb{R}^{s\times l_0}$ of the $i$th subsystem (\ref{eq:linear subsys}) that achieve the $H_\infty$ decentralized observer-based tracking control performance with a prescribed attenuation level $\rho_i$, where $s=3+(w_1+1)+(w_2+1)o_0$.
 The original control gain $K$ of the original agent system can be reconstructed by $K = \begin{bmatrix}
@@
 \section{simulation results}
-In this section, a specific S\&R procedure for URTS is given to illustrate the proposed URTS system architecture and demonstrate the effectiveness of motion planning and control strategy of a hybrid UAVs and biped robots team system.
+In this section, a specific S\&R procedure for URTS is given to illustrate the proposed system architecture of performing S\&R tasks for each agent in hybrid URTS and demonstrate the effectiveness of motion planning and control strategy in hybrid URTS.
 First, a S\&R area divided into $N_T$ areas $area_i,i=1,2,...,N_T$, is given as shown in Fig.
@@
 If the ground station assigns $\alpha_{i,5}$ and $\alpha_{i+1,2}$ to perform $T_7$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{i,5},T_5),(\alpha_{i+1,2},T_6) \})\cup\{ (\alpha_{i,5},T_7),(\alpha_{i+1,2},T_7) \}$.
-Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
+Until the S\&R task is over, the task allocation block will continuously work in the similar way.
 \begin{figure}[htbp]
@@
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
-For robots, $q_{goal}$ will be passed to path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
+For robots, $q_{goal}$ will be passed to global path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
     \label{fig:S_task}
@@
 
-To illustrate the path planning block and behavior layer block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
+To illustrate the global path planning block and behavior decision block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
 For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=16$ is directly assigned as shown in Fig.
-\ref{sim:flying} without going through path planning by \textit{Assumption \ref{asm:collision}}.
+\ref{sim:flying} without going through global path planning block by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,k_f]$.
@@
 According to $r[k]$ and the dynamic model of UAV and robot, the reference trajectory $r(t)$ of each agent is planned.
-Finally, through the decentralized $H_\infty$ observer-based feedforward FTC scheme proposed in this paper, the team tracking result of the agents in $team_i, i=1,2,3$ in URTS are shown.
+Finally, through the decentralized $H_\infty$ observer-based feedforward reference tracking FTC scheme proposed in this paper, the team tracking result of the agents in $team_i, i=1,2,3$ in URTS are shown.
 Note that the above process is dynamic.
-If a block in a higher layer in URTS architecture makes a new decision that produces a new reference planning, the lower blocks must recalculate based on it.
+If a block in a higher decision in URTS architecture makes a new decision that produces a new reference planning, the lower blocks must recalculate based on it.
 Relatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.
@@
 For further verification, we visualized the real time simulation of reference planning and team formation tracking control in hybrid URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}.
-The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method for agents in URTS.
+The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward reference tracking FTC method for agents in URTS.
 
 \section{conclusion}
-In this study, a system architecture of task allocation, reference trajectory planning and tracking control of hybrid URTS for S\&R usage is given.
-This gives a holistic view of the operational framework of how to integrate motion planning and robust decentralized fault-tolerant tracking control for hybrid URTS.
-By decomposing the path planning process into three subprocess, i.e., path planning, behavior layer, local motion planning, some common roadmap-based path planning algorithm can be applied in URTS.
+In this study, a system architecture of performing S\&R tasks for each agent in hybrid URTS is given.
+The task allocation problem and path planning problem are investigated and unified to the integration of local motion planning and robust $H_\infty$ decentralized feedforward reference tracking FTC for hybrid URTS.
+By decomposing the path planning process into three subprocess, i.e., global path planning, behavior decision, local motion planning, some common roadmap-based path planning algorithm can be applied in the global path planning of URTS.
+Through the behavior decision, the agent can decide the appropriate behavior according to the terrain environment.
 Next, we focus on the local motion planning of UAV flying and robot walking behavior.
@@
 A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works.
-Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward FTC method is also verified by the simulation results.
+Finally, the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method is also verified by the simulation results.
 

### 2022-12-25 paper/paper.tex
Revise paper. - Add description relation between  reference path and reference trajectory
Add one colume version paper

@@
     \begin{remark}
+        In Section 3.2.2 of \cite{sabatino2015quadrotor}, the dynamic system of UAV is divided into inner loop system and outer loop system to analyze the reference tracking problem of UAV.
+In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the tracking specification in (\ref{Hinf}).
+This can reduce the time cost of manually adjusting control gains.
+At the same time, the tracking control problem of UAV and robot can be analyzed simultaneously.
+    \end{remark}
+}
+\textit{
+    \begin{remark}
         The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
@@
 Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$.
+At the same time, we find $u'(t)$.
 For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
-So far, the planning of reference trajectory $r(t)$ of each agent in hybrid URTS is done.
+So far, the transformation between reference path $r[k]$ and reference trajectory $r(t)$ for each agent in hybrid URTS is done.
 We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig.

### 2022-12-25 paper/paperOneCol.tex
Add one colume version paper

--- 2022-12-21 paper/paper.tex
@@
-\documentclass{ieeeaccess}
+\documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran}
 \usepackage{cite}
@@
 
+\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}
+
+\author{Min-Yen Lee and Bor-Sen Chen, \IEEEmembership{Life Fellow, IEEE,}}
+
 \begin{document}
-% \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
-
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-
-\doi{10.1109/ACCESS.2017.DOI}
-
-\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}
-
-\author{\uppercase{Bor-Sen Chen}\authorrefmark{1,2}, \IEEEmembership{Life
-Fellow, IEEE}, \uppercase{Ting-Wei Hung\authorrefmark{1}}}
-
-\address[1]{Department of Electrical Engineering, National Tsing Hua
-University, Hsinchu 30013, Taiwan} \address[2]{Department of Electrical
-Engineering, Yuan Ze University, Taoyuan 32003, Taiwan}
-
-\tfootnote{This work was supported by the Ministry of Science and Technology
-of Taiwan under Grant MOST 108-2221-E-007-099-MY3.}
-
-\markboth
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-
-\corresp{Corresponding author: Bor-Sen Chen (bschen@ee.nthu.edu.tw)}
-% \address[1]{National Institute of Standards and 
-% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
-% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
-% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
-% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
-% 80309 USA}
-% \tfootnote{This paragraph of the first footnote will contain support 
-% information, including sponsor and financial support acknowledgment. For 
-% example, ``This work was supported in part by the U.S. Department of 
-% Commerce under Grant BS123456.''}
-
-% \markboth
-% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-
-% \corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}
-% .
+\maketitle
 
@@
 
-\begin{keywords}
-biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, hybrid UAVs-UGVs team system
-\end{keywords}
-
-\titlepgskip=-15pt
-
 \maketitle
@@
 % unmanned vvehcile
-\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power.
+In recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power.
 It not only reduces labor costs and brings convenience to life, but also more importantly can replace some dangerous jobs for humans.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author1.jpg}}]{Bor-sen chen}
-    (Life Fellow, IEEE) received the B.S.
-degree in electrical engineering from the Tatung Institute of Technology, Taipei, Taiwan, in 1970, the M.S.
-degree in geophysics from National Central University, Chungli, Taiwan, in 1973, and the Ph.D.
-degree in electrical engineering from the University of Southern California, Los Angeles, CA, USA, in 1982.
-He was a Lecturer, an Associate Professor, and a Professor with the Tatung Institute of Technology, from 1973 to 1987.
-He is currently the Tsing Hua Distinguished Chair Professor of electrical engineering and computer science with National Tsing Hua University, Hsinchu, Taiwan.
-His current research interests include control engineering, signal processing, and systems biology.
-He has received the Distinguished Research Award from the National Science Council of Taiwan four times.
-He is also the National Chair Professor of the Ministry of Education of Taiwan.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author2.jpg}}]{Ting-Wei Hung}
-    received the B.S.
-degree in the department of engineering science from the National Cheng Kung University, Tainan, Taiwan, in 2020, and the M.S.
-degree from the Department of Electrical Engineering, National Tsing Hua University, in 2022.
-His current research interests include robotics, robust control, and team formation control.
-\end{IEEEbiography}
-
-\EOD
-
 \end{document}

### 2022-12-27 paper/paper.tex
Rivise paper. (version for oral test committee)

@@
 The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS.
+By converting the dynamics models of UAV and robot into an unified agent dynamic model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
@@
 This leads us to propose a system architecture of performing S\&R tasks for each agent in URTS to illustrate these problems and the relationship between them.
-The flowchart of the system architecture is also given.
-We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) global path planning, (iii) behavior decision, (iv) local motion planning and (v) reference tracking control.
+The flowchart of the system architecture is also given in Fig.
+\ref{fig:sys}.
+We divide it into five main hierarchical processes, i.e., (i) Task Allocation, (ii) Global Path Planning, (iii) Behavior Decision, (iv) Local Motion Planning and (v) Reference Tracking Control.
 It is because the URTS needs to be able to assign different tasks to agents to perform first.
@@
 
-The tracking control is to control an agent to follow a desired trajectory.
-There are many control strategies for MAS.
+The reference tracking control is to control an agent to follow a desired reference trajectory.
+There are many reference control strategies for MAS.
 According to the way of the design of controller, it can be divided into centralized control and decentralized control in control field \cite{8931370}.
@@
 Besides, the formation control is also a topic in MAS \cite{wang2022consensus}.
-Its purpose is to keep a MAS in a formation while moving.
-Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible.
+Its purpose is to keep a MAS in a formation while moving for some allocated tasks.
+Although formation control provides a simple framework for the reference control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible.
 It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment.
-In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation.
+In this situation, it is more reasonable to treat each agent in URTS as an independent individual to be controlled to follow a specific trajectory for its allocated task to form a team formation.
 
@@
 The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it.
-In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller.
+In contrast, the active FTC will first estimate and identify the fault and then compensate it through the feedback controller.
 Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps.
@@
 \begin{enumerate}
-    \item A system architecture of performing S\&R tasks for each agent in hybrid URTS are proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
-    \item A transformation between the path planned by a roadmap-based path planning algorithm and the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS.
+    \item A system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
+    \item A transformation from the path planned by a roadmap-based path planning algorithm to the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS to reach the goal location without obstacle collision.
     \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved together to achieve S\&R task under external disturbance and actuator and sensor fault.
@@
 The remainder of the paper is organized as follows.
-In Section II, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed and the function and relationship among its components, i.e., task allocation, global path planning, behavior decision, local motion planning and tracking control are described.
+In Section II, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed and the function and relationship among its components, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Reference Tracking Control are described.
 In Section III, the dynamics models of agents in URTS are given to plan the motion of UAV flying and biped robot walking behavior and the control strategy of agents.
-In Section IV, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC is proposed for the agents in URTS with the help of a general agent dynamics model.
+In Section IV, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC is proposed for the agents in URTS with the help of a general agent dynamic model.
 In Section V, a simulation example is given to illustrate the operation of the system architecture of performing S\&R tasks for each agent in hybrid URTS and to verify the effectiveness of the proposed tracking control method.
@@
 
-\section{PRELIMINARIES OF URTS in S\&R usage}
+\section{PRELIMINARIES OF URTS for S\&R usage}
 The URTS will start with a given S\&R area, and end with the S\&R task completed.
@@
 Besides, there are communication channels between agents and ground station through wireless network.
-% The system architecture if URTS is shown in Fig. \ref{fig:1}.
-% \begin{figure}[htbp]
-% \centering
-% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
-% \label{fig:1}
-% \end{figure}
 
@@
 Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station.
-The ground station will combine this information with the goal location determined by the task and then make a decision to avoid obstacles and other agents nearby through a path planning algorithm.
+The ground station will combine this information with the goal location determined by the task and then plan a path to avoid obstacles and other agents nearby through a path planning algorithm.
 % That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
@@
 To meet these needs, a behavioral decision is necessary.
-% The behavior decision decides an appropriate behavior based on the circumstances.
-
-In order to make a behavior, we must plan a corresponding motion by local motion planning.
+
+In order for the agent to make a behavior, we must plan a corresponding motion by local motion planning.
 The motion is a prescribed reference path for an actual mechanical system to follow.
@@
 \ref{fig:sys}.
-The Simultaneous Localization And Mapping (SLAM) block converts sensor information and distance information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$.
-The visual object recognition block provides distance information and object information through the analysis of sensor information.
-The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decides to climb through it).
-The detailed functions of remaining 5 blocks, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Tracking Control, will be explained in the following subsections.
+The detailed functions of remaining 5 blocks, i.e., Task Allocation, Global Path Planning, Behavior Decision, Local Motion Planning and Reference Tracking Control, will be explained in the following subsections.
 
@@
     \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of performing S\&R tasks for each agent in hybrid URTS.
-The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as occupancy map $\mathcal{C}$ of URTS, current configuration $q_{start}$ of agents and object information of environment.
+The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information.
+The Simultaneous Localization And Mapping (SLAM) block converts sensor information and distance information into the current configuration $q_{start}$ of agents and an occupancy map $\mathcal{C}$ of URTS.
+The visual object recognition block provides distance information and object information through the analysis of sensor information.
+The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see an obstacle and decide to climb through it).
 The 5 blocks on right hand side are the flowchart of an agent performing a S\&R task.
-From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision of the behavior $(\beta_n)$ of agents, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents.
+From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$ of agents, the planning of the path $(\sigma_n)$ of agents, the decision of the behavior $(\beta_n)$ of agents corresponding to the path, the planning of the reference path $r[k]$ of agents corresponding to the behavior, and the low-level reference tracking control of agents.
 A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses.
-The Behavior Decision block is described detailly in Fig.
+Behavior Decision block is described detailly in Fig.
 \ref{fig:behavior}.
-The Local Motion Planning block to generate the desired reference is described detailly in Fig.
+Local Motion Planning block to generate the desired reference is described detailly in Fig.
 \ref{fig:LMP}.
-The Reference Tracking Control block is described detailly in Fig.
+Reference Tracking Control block is described detailly in Fig.
 \ref{fig:tracking}.}
@@
 In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment.
-$q_{goal}$ then pass to next block, i.e., global path planning block, as shown in Fig.
+$q_{goal}$ then passes to next block, i.e., the global path planning block, as shown in Fig.
 \ref{fig:sys}.
@@
 \subsection{Global Path Planning}
-After a goal $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it.
+After a goal configuration $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it.
 There must exist multiple feasible paths to go.
@@
 Multi-query planner will first construct a roadmap and then use a graph search method on it to query the best path, such as Probability Road Map (PRM), Visibility Graph, and Voronoi Diagrams \cite{liu2018survey}.
-Single-query planner will complete the pathfinding by constructing and querying simultaneously,
-%  i.e., the roadmap will be constructed incrementally and toward the goal, 
-such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}.
+Single-query planner will complete the pathfinding by constructing and querying simultaneously, such as Rapidly-exploring Random Tree (RRT), Expansice Space Tree (EST), and Ariadne's Clew \cite{elbanhawi2014sampling}.
 However, the environment is dynamic rather static for URTS so some extra structures need to impose on the aforementioned planner.
 Some common dynamic planners can also be found in \cite{elbanhawi2014sampling}, such as PRM with D* search algorithm, dynamic RRT, and extended RRT.
-All of the above common roadmap-based planners can be applied to the proposed URTS architecture.
 \textit{
@@
 Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
-The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for biped robot).
+The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for a biped robot).
 In this case, an unified planner will become overly complex and impracticable.
 Therefore, we divide path planning into three subprocesses, i.e., global path planning, behavior decision and local motion planning.
-The global path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints.
-The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
+The global path planning block becomes a global planner to regard an agent as a point without kinodynamic constraints.
+This enables the common roadmap-based path planning algorithms mentioned above to be used for global path planning in UTRS.
+The local motion planning block becomes a local planner to consider the motion planning of a specific behavior.
 % In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
@@
 By treating a roadmap-based path planning algorithm as a black box, the output is a sequence (or waypoints), and the three inputs are current configuration $q_{start}$, goal configuration $q_{goal}$, and configuration space (or occupancy map) $\mathcal{C}$.
-$q_{start}$ and $\mathcal{C}$ is obtained by SLAM, and $q_{goal}$ is obtained by the previous block, task allocation block, as shown in Fig.
+$q_{start}$ and $\mathcal{C}$ is obtained by SLAM, and $q_{goal}$ is obtained by the previous block, Task Allocation block, as shown in Fig.
 \ref{fig:sys}.
@@
 
-From above assumptions, a path of agent can be expressed as a sequence
+From above assumptions, a path of agent can be expressed as a sequence:
 \begin{equation}
@@
 \end{equation}
-where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then pass to next block, i.e., behavior decision block, as shown in Fig. \ref{fig:sys}.
+where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then passes to next block, i.e., the behavior decision block, as shown in Fig. \ref{fig:sys}.
 
@@
 Then, the segments of path from the result of the replanning in time step $k_n$ can be expressed as sequences $(\sigma_m), m\in\mathbb{Z}\cap[k_n, k_{n+1})$.
-For agents, the replanning decision can be due to a goal changing that is made by human or task allocation block.
-For robot, it can be a collision detected by a dynamic roadmap-based planner.
+For agents, the replanning decision can be due to a goal changing that is made by human or Task Allocation block.
+For robot, it can be due to a collision detected by a dynamic roadmap-based planner.
     \end{remark}
@@
 % Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
-Global path planning block tells agents where to go but not how since we regard the agent as a point.
+The global path planning block tells agents where to go but not how since we regard the agent as a point.
 Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information.
 Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario.
-These behaviors with changing position are classified as "moving" behavior in this paper.
+These behaviors with changing position are classified as "Moving" behavior in this paper.
 Besides, the agents in the hybrid URTS do not always moving.
 Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
-These behaviors without changing position are classified as "action" behavior in this paper.
+These behaviors without changing position are classified as "Action" behavior in this paper.
 More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control.
@@
 However, it will be a rather complicated project, so this article will not discuss in detail.
-The behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig.
+The flowchart of Behavior Decision and the behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig.
 \ref{fig:behavior}.
-$(\beta_n)$ then pass to next block, i.e., local motion planning block, as shown in Fig.
+$(\beta_n)$ then passes to next block, i.e., the local motion planning block, as shown in Fig.
 \ref{fig:sys}.
@@
 After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior.
-Local motion planning block is like global path planning block but with smaller scale and higher resolution and precision.
-Collision checking is needed since we consider agent as a point in global path planning block but it is a real mechanical body here.
+Local motion planning block is like the global path planning block but with smaller scale and higher resolution and precision.
+Collision checking is needed since we consider agent as a point in the global path planning block but it is a real mechanical body here.
 Furthermore, the kinodynamic constraint is handled in this block.
@@
 \ref{fig:behavior} are given to futher illustrate the flow of this block.
-The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior decision.
+The corresponding motion planning of an agent will be executed according to the behavior determined by Behavior Decision block.
 The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors.
 The reference path $r[k]$ is a sequence (or discrete signal) planned by a specific behavior block.
-For UAVs, the moving block is described in (b).
-For robots, the moving block is described in (c).
-        (b) The moving block of each UAV. The flying block in it is described detailly in Fig. \ref{fig:FandW}. 
-        (c) The moving block of each robot. The the walking block in it is described detailly in Fig. \ref{fig:FandW}.}
+For UAVs, Moving block is described in (b).
+For robots, Moving block is described in (c).
+        (b) Moving block of each UAV. Flying block in it is described detailly in Fig. \ref{fig:FandW}. 
+        (c) Moving block of each robot. Walking block in it is described detailly in Fig. \ref{fig:FandW}.}
     \label{fig:LMP}
@@
 A more detailed description will be given in the next section.
-$r[k]$ then pass to next block, i.e., reference tracking control block, as shown in Fig.
+$r[k]$ then passes to next block, i.e., Reference Tracking Control block, as shown in Fig.
 \ref{fig:sys}.
@@
 \subsection{Reference Tracking Control}
-To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period.
+To analyze the reference tracking control problem in the continuous time domain, the reference path $r[k]$ will be first converted to a continuous signal $r'(t)$ by D/A convertor with a timescale, i.e., sampling period.
 By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is planned.
@@
 It will be discussed detailly in Section IV.
-In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper decision as shown in Fig.
+In addition, the sensing information collected by the sensors in this block is not only used for reference tracking control but also fed back to the high-level block as shown in Fig.
 \ref{fig:sys}.
@@
 
-Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$.
-The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density.
+Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, i.e., $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$.
+The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+d(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $d\in\mathbb{Z}$ is the interpolation density.
 Then, $(\sigma_n')$ will be the position reference path $[
@@
 Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to plan a stable walking pattern to prevent robot from falling.
-These make the planning of walking motion of robot more difficult.
-In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to plan the walking motion of each biped robot in URTS.
+These make the motion planning of walking behavior of robot more difficult.
+In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used for the motion planning of walking behavior of each biped robot in URTS.
 
@@
         A frame (or homogeneous transformation) in $\mathbb{R}^3$ can be determined by giving the "position" and "orientation" with respect to a reference frame.
-That is, given the frames of two joints in a link with known kinematics, the frames of joints between them can be found by \textnormal{IK}.
-Hence, we need to find the position paths and orientation paths, which compose the desired path.
+That is, given the frames of two joints in links with known kinematics, the frames of joints between them can be found by \textnormal{IK}.
+Hence, we need to find the position path and orientation path, which compose the desired path of the frame.
     \end{remark}
@@
 The system is discretized first and the discrete LQ optimal tracker is employed to achieve the output tracking.
-The formulation can be found in TABLE 4.4-1 in \cite{lewis2012optimal}.
+The formulation of the discrete LQ optimal tracker can be found in TABLE 4.4-1 in \cite{lewis2012optimal}.
 The CoM position path $(CP_n)$ can then be obtained by combining $x_c$ and $y_c$ with $z_c$.
@@
 Through the previous step, the planning of the reference path $r[k]$ of each agent in hybrid URTS has been completed.
-However, in order to calculate the unplannable reference paths, i.e., $\phi_[k]$ and $\theta_r[k]$, of UAV and analyze the reference trajectory tracking problem in the continuous domain, we have to transform $r[k]$ into the reference trajectory $r(t)$.
+However, in order to calculate the unplannable reference paths, i.e., $\phi_r[k]$ and $\theta_r[k]$, of UAV and analyze the reference trajectory tracking problem in the continuous domain, we have to transform $r[k]$ into the reference trajectory $r(t)$.
 Before converting the planned reference path $r[k]$ to desired reference trajectory $r(t)$, we first convert the UAV dynamic model in (\ref{eq:uav}) and robot dynamic model in (\ref{eq:robot}) into a form called agent dynamic model in a hybrid team to analyze their team formation tracking control problems together.
@@
         In Section 3.2.2 of \cite{sabatino2015quadrotor}, the dynamic system of UAV is divided into inner loop system and outer loop system to analyze the reference tracking problem of UAV.
-In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the tracking specification in (\ref{Hinf}).
+In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the observer-based tracking specification in (\ref{Hinf}).
 This can reduce the time cost of manually adjusting control gains.
@@
         The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
-This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$.
+This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be used in control law $u(t)$.
 While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
@@
         0 \\ 0 \\ F
-\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given.
+\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because the component forces $f_x$, $f_y$ and $f_z$, and the yaw angle $\psi_r$ are given.
 Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$.
@@
 For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
-So far, the transformation between reference path $r[k]$ and reference trajectory $r(t)$ for each agent in hybrid URTS is done.
+So far, the transformation from reference path $r[k]$ to reference trajectory $r(t)$ for each agent in hybrid URTS is done.
 We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig.
@@
     \begin{remark}
-        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted.
+        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted for the convenience of notation in the following.
 For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
@@
         Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc.
-As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, global path planning, behavior decision and local motion planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
+As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, Task Allocation, Global Path Planning, Behavior Decision and Local Motion Planning, have completed their respective responsibilities and planned their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$.
 That is, $r_{i,j}(t)$ is the reference trajectory that can accomplish the specific task, follow the specific path and perform the specific behavior.
@@
 \end{enumerate}
-Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$.
+Let $x_{i,j}(t)$ denote the state vector of agents $\alpha_{i,j}$ where $i=1,2,\dots,N_T, j=1,2,\dots,N_A$.
 The coupling effect $c_{i,j}(t)$ on each agent from other agents in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
@@
 \end{equation} for biped robot $\alpha_{i, j}$ where $i=1,2,\dots,N_T$ and $j=2,3,\dots,N_A$ \cite{9834947}.
-For the convenience of reading, we use $c(t)$ to represent $c_{i,j}(t)$.
+For the convenience of notation, we use $c(t)$ to represent $c_{i,j}(t)$.
 Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in hybrid URTS.
@@
 \end{equation}
-By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have the tracking error differential equation as follows:
+By multipling $M(x(t))^{-1}$ on both sides of (\ref{eq:agent1}) and with some arrangments, we have the tracking error differential equation as follows:
 \begin{equation} \label{eq:error, state eq}
@@
 At the same time, the sensor noise on sensor also needs to be considered as mentioned before.
-Since the sensor information will transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the cyber-attack signal are concerned.
+Since the sensor information will be transmitted back to the ground station for calculating control command through the network channel in URTS, not only the sensor noise but also the cyber-attack signal are concerned.
 We consider the effect of them as a sensor fault in this paper.
@@
 where $y(t)\in\mathbb{R}^{l}$ is the output vector, $C\in\mathbb{R}^{l\times 3n}$ is the output matrix, $B_2\in\mathbb{R}^{l\times o}$ is the input matrix of sensor fault signal $f_2(t)\in\mathbb{R}^o$.
+\textit{
+    \begin{remark}
+        We consider the integral of the agent's state $\int_{0}^{t}x^T(\tau)d\tau$ to be measurable because $\int_{0}^{t}x^T(\tau)d\tau$ can be calculated indirectly via agent's state $x(t)$ and an integrator.
+For UAV, $x(t)$ can be measured by GPS and inertial measurement unit.
+For biped robot, $x(t)$ can be measured by the sensor of motor on the joints.
+    \end{remark}
+}
+
 Let us define $\pmb{r}(t)=\begin{bmatrix}
@@
 \end{equation}
-where $t_f$ is the final time, $Q_1 \geq 0$ is the tracking error weighting matrix, $Q_2 \geq 0$ is the estimation error weighting matrix, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented tracking and estimation error system in (\ref{eq:x_tilde}) which is to be extracted from the $H_\infty$ decentralized team formation tracking control performance, and $\tilde{v}(t)$ is the total disturbance whose effect on $\bar{e}(t)$, $\tilde{e}(t)$ and $u_{fb}(t)$ is needed to be attenuated.
+where $t_f$ is the final time, $Q_1 \geq 0$ is the weighting matrix of tracking error, $Q_2 \geq 0$ is the weighting matrix of estimation error, $R > 0$ is the weighting matrix of control effort, $V(\tilde{x}(0))$ is the initial condition effect on the augmented tracking and estimation error system in (\ref{eq:x_tilde}) which is to be extracted from the $H_\infty$ decentralized team formation tracking control performance, and $\tilde{v}(t)$ is the total disturbance whose effect on $\bar{e}(t)$, $\tilde{e}(t)$ and $u_{fb}(t)$ is needed to be attenuated.
 If we can find the control gain $K$ and observer gain $L$ such that (\ref{Hinf}) holds, then the effect of total disturbance $\tilde{v}(t)$ on augmented tracking error $\bar{e}(t)$ and augmented estimation error $\tilde{e}(t)$ can be attenuated to a prescribed level $\rho^2$ from the viewpoint of energy.
@@
     \begin{remark}
-        Since the Riccati-like inequality of each agent $\alpha_{i,j}$ in URTS has not involved the system information of other agents (e.g., the coupling term $c(t)$ in (\ref{eq:UAV couple}) and (\ref{eq:robot couple})), therefore, the robust decentralized team formation tracking control can be achieved.
+        Since the Riccati-like inequality in (\ref{BMI1}) of each agent $\alpha_{i,j}$ in URTS has not involved the system information of other agents (e.g., the coupling term $c_{i,j}(t)$ in (\ref{eq:UAV couple}) and (\ref{eq:robot couple})), therefore, the robust decentralized team formation tracking control can be achieved.
     \end{remark}
@@
 
-    (ii) From (\ref{BMI1}) and $V(\tilde{x}(0))$ is finite, we get $\int_{0}^{t_f}(\bar{e}^T(t)Q_1\bar{e}(t) + \tilde{e}^T(t)Q_2\tilde{e}(t) + u_{fb}^T(t)Ru_{fb}(t))dt 
+    (ii) From (\ref{Hinf}), $\tilde{v}(t)\in L_2[0, \infty)$ and $V(\tilde{x}(0))$ is finite, we get $\int_{0}^{t_f}(\bar{e}^T(t)Q_1\bar{e}(t) + \tilde{e}^T(t)Q_2\tilde{e}(t) + u_{fb}^T(t)Ru_{fb}(t))dt
     \leq \rho^2 \int_{0}^{t_f}\tilde{v}^T(t)\tilde{v}(t)dt + V(\tilde{x}(0)) 
@@
 
-If we want to find the optimal $H_\infty$ decentralized observer-based tracking control strategy for the augmented tracking and estimation error system in (\ref{eq:x_tilde}) of each agent in hybrid URTS , we need to solve the following LMIs-constrained optimization problem:
+If we want to find the optimal $H_\infty$ decentralized observer-based tracking control strategy for the augmented tracking and estimation error system in (\ref{eq:x_tilde}) of each agent in hybrid URTS, we need to solve the following LMIs-constrained optimization problem:
 \begin{equation} \label{LMI constraint}
@@
 the error $\pmb{e}(t)=\sum_{i=1}^{n} \pmb{e}_i(t)\otimes\mathbf{e}_i$, 
-the control $u_{fb,i}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, 
-the acuaor fault $f_{1,i}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, 
+the control $u_{fb}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, 
+the acuaor fault $f_{1}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, 
 the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, 
-and the sensor fault $f_{2,i}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ 
+and the sensor fault $f_{2}(t)=\sum_{i=1}^{n} {f}_{2,i}(t)\otimes\mathbf{e}_i$ in (\ref{eq:error})
 where $\pmb{e}_i(t)\in\mathbb{R}^3$, $u_{fb,i}(t)\in\mathbb{R}$, $f_{1,i}(t)\in\mathbb{R}$, $y_i(t)\in\mathbb{R}^{l_0}$, $f_{2,i}(t)\in\mathbb{R}^{o_0}$ and $\mathbf{e}_i$ is standard unit column vectors in $\mathbb{R}^n$, we get the $n$ subsystems for each agent:
@@
         If the linearized system (\ref{eq:error}) can be splited into $n$ subsystems, this means that the error $\pmb{e}_i(t)$ of each state variable $x(t)$ of each agent in (\ref{eq:agent}), can be measured independently via $n$ sensors to obtain the independent outputs $y_i(t)$.
-In actual systems, this is usually done.
+In actual UAV system or biped robot system, this is usually done.
     \end{remark}
@@
 \section{simulation results}
-In this section, a specific S\&R procedure for URTS is given to illustrate the proposed system architecture of performing S\&R tasks for each agent in hybrid URTS and demonstrate the effectiveness of motion planning and control strategy in hybrid URTS.
+In this section, a specific S\&R procedure for URTS is given to illustrate the proposed system architecture of performing S\&R tasks for each agent in hybrid URTS and demonstrate the effectiveness of local motion planning and reference control strategy in hybrid URTS.
 First, a S\&R area divided into $N_T$ areas $area_i,i=1,2,...,N_T$, is given as shown in Fig.
@@
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
-For robots, $q_{goal}$ will be passed to global path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
+For robots, $q_{goal}$ will be passed to the global path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
     \label{fig:S_task}
@@
 For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=16$ is directly assigned as shown in Fig.
-\ref{sim:flying} without going through global path planning block by \textit{Assumption \ref{asm:collision}}.
+\ref{sim:flying} without going through the global path planning block by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,k_f]$.
@@
         Since we set $C = C_0\otimes I_n$ and $B_2 = B_{2,0}\otimes I_n$, the proposed method of decomposing each agent model into $n$ subsystems is used to find $K$ and $L$.
-For the convenience of solving the LMIs-constrained optimization problem in \ref{LMI constraint}, we set the same design parameters $Q_1$, $Q_2$, $R$ and $\rho^*$ for each subsystem as shown above.
+For the convenience of solving the LMIs-constrained optimization problem in (\ref{LMI constraint}), we set the same design parameters $Q_1$, $Q_2$, $R$ and $\rho^*$ for each subsystem as shown above.
     \end{remark}
@@
     \centering
-    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The actual control input $u'(t)$ of the UAV $\alpha_{1,1}$.}%
+    \includegraphics[scale=.57]{fig/uav (4).png}\caption{The actuator control input $u'(t)$ of the UAV $\alpha_{1,1}$.}%
     \label{fig:UAV, control}
@@
     \centering
-    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The actual control input $u'(t)$ of the robot $\alpha_{1,5}$.}%
+    \includegraphics[scale=.57]{fig/robot (4).png}\caption{The actuator control input $u'(t)$ of the robot $\alpha_{1,5}$.}%
     \label{fig:robot, control}
@@
 In Figs.
-\ref{fig:UAV, control} and \ref{fig:robot, control}, the actual control input $u'(t)$ have high frequency and high amplitude at the initial instance due to the high gain characteristic of the robust control.
+\ref{fig:UAV, control} and \ref{fig:robot, control}, the actuator control input $u'(t)$ have high frequency and high amplitude at the initial instance due to the high gain characteristic of the robust control.
 After that, they maintain the sine wave shape to offset the estimated actuator fault value.
@@
 \ref{fig:S_task}, this simulation assumes that $team_i,i=1,2,3$ are assigned with search tasks.
-Subsequently, the path $(\sigma_n)$ for each UAV is assigned and the collision-free path $(\sigma_n)$ for each robot is calculated by the path planning algorithm.
-Depending on the terrain environment, an appropriate behavior $(\beta_n)$ is determined to enable the agent to follow the path $(\sigma_n)$.
+Subsequently, the path $(\sigma_n)$ for each UAV is assigned and the collision-free path $(\sigma_n)$ for each robot is planned by the path planning algorithm to reach the goal configuration $q_{goal}$.
+Depending on the terrain environment, an appropriate behavior $(\beta_n)$ is decided to enable the agent to follow the path $(\sigma_n)$.
 A reference path $r[k]$ corresponding to a behavior is planned via local motion planning to enable an actual mechanical body to perform the behavior.
@@
 Note that the above process is dynamic.
-If a block in a higher decision in URTS architecture makes a new decision that produces a new reference planning, the lower blocks must recalculate based on it.
+If a higher block in Fig.
+\ref{fig:sys} makes a new decision that produces a new reference planning, the lower blocks must recalculate based on it.
 Relatively, this simulation is the static result, that is, there is no re-decision from $q_{start}$ to $q_{goal}$.
@@
 The task allocation problem and path planning problem are investigated and unified to the integration of local motion planning and robust $H_\infty$ decentralized feedforward reference tracking FTC for hybrid URTS.
-By decomposing the path planning process into three subprocess, i.e., global path planning, behavior decision, local motion planning, some common roadmap-based path planning algorithm can be applied in the global path planning of URTS.
+By decomposing the path planning process into three subprocess, i.e., global path planning, behavior decision and local motion planning, some common roadmap-based path planning algorithm can be applied in the global path planning of URTS.
 Through the behavior decision, the agent can decide the appropriate behavior according to the terrain environment.
@@
 Besides, the bridging method between the reference path planned by the local motion planning block and the reference trajectory to be followed in the reference tracking control block is also given.
-By a general nonlinear agent dynamics model, the tracking control problem of UAV and robot can be analyzed together.
+By a general nonlinear agent dynamic model, the tracking control problem of UAV and robot can be analyzed together.
 Through a feedforward control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
-Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic system.
-After that, a robust $H_\infty$ decentralized observer-based feedforward FTC strategy is proposed for each agent in the hybrid URTS.
-To solve the robust $H_\infty$ decentralized observer-based feedforward FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
+Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic model.
+After that, a robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in the hybrid URTS.
+To solve the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problem, we transform it into a LMI-constrained optimization problem by a two-step design procedure, which can be effectively solved by MATLAB LMI Toolbox.
 A simulation example is given to illustrate more concretely how the proposed hybrid URTS architecture actually works.

### 2023-01-06 paper/paper.tex
IEEE Contributed Version

@@
 \documentclass{ieeeaccess}
+% For one column
+% \documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran} 
 \usepackage{cite}
@@
 
-\begin{document}
 % \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% No need for one columne
 \history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
@@
 
-\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}
+\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue Task of Hybrid UAVs and Biped Robots Team System}
 
@@
 \corresp{Corresponding author: Bor-Sen Chen (bschen@ee.nthu.edu.tw)}
-% \address[1]{National Institute of Standards and 
-% Technology, Boulder, CO 80305 USA (e-mail: author@boulder.nist.gov)}
-% \address[2]{Department of Physics, Colorado State University, Fort Collins, 
-% CO 80523 USA (e-mail: author@lamar.colostate.edu)}
-% \address[3]{Electrical Engineering Department, University of Colorado, Boulder, CO 
-% 80309 USA}
-% \tfootnote{This paragraph of the first footnote will contain support 
-% information, including sponsor and financial support acknowledgment. For 
-% example, ``This work was supported in part by the U.S. Department of 
-% Commerce under Grant BS123456.''}
-
-% \markboth
-% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-% {Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-
-% \corresp{Corresponding author: First A. Author (e-mail: author@ boulder.nist.gov).}
-% .
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{document}
 
 \begin{abstract}
-In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
+In this study, we integrate a local motion planning and robust $H_\infty$ decentralized observer-based feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
 A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage.
@@
 The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into an unified agent dynamic model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS.
+By a proposed novel feedforward linearization control scheme, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design is significantly simplified for each agent in URTS.
 A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
+Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
 With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% No need for one columne
 \begin{keywords}
@@
 \end{keywords}
-
 \titlepgskip=-15pt
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \item A system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed so that the local motion planning and reference tracking control issues involved in each agent of hybrid URTS and their systematic relationships can be defined and resolved.
-    \item A transformation from the path planned by a roadmap-based path planning algorithm to the reference trajectory required for team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS to reach the goal location without obstacle collision.
-    \item A general agent dynamic model is proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved together to achieve S\&R task under external disturbance and actuator and sensor fault.
+    \item A transformation from the path planned by a roadmap-based path planning algorithm to the reference trajectory required for S\&R task of team formation tracking control design is proposed to enable some common roadmap-based path planning algorithms to guide the team formation tracking control of agents in hybrid URTS to reach the goal location without obstacle collision.
+    \item A general agent dynamic model and a novel feedforward linearization control scheme are proposed so that the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC problems of the heterogeneous agents in URTS, i.e., UAVs and biped robots, can be solved simultaneously to achieve S\&R task under external disturbance and actuator and sensor fault.
 \end{enumerate}
@@
 A dynamic model about how an UAV in URTS moves in the physical world is given first. By Newton-Euler equation, the dynamic model of each UAV in URTS can be formulated as \cite{sabatino2015quadrotor}:
+
 \begin{equation} \label{eq:uav} 
@@
 These make the motion planning of walking behavior of robot more difficult.
-In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used for the motion planning of walking behavior of each biped robot in URTS.
+In this paper, a Three-Dimensional Linear Inverted Pendulum Model (3D-LIPM) \cite{kajita2001real} is used for the motion planning of walking behavior of each biped robot in URTS.
 
@@
 where $u(t)\in\mathbb{R}^n$ is the control input vector, $x(t)\in\mathbb{R}^n$ is the state vector, $M(x(t))\in\mathbb{R}^{n\times n}$ is the inertia matrix, and $H(x(t),\dot{x}(t))\in\mathbb{R}^n$ is the non-inertial force vector.
-The control law for an agent in URTS is given as:
-\begin{equation} \label{eq:control}
-    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
-\end{equation}
-where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness.
 For each UAV in hybrid URTS, we have $u(t)=\begin{bmatrix}
@@
 
+The feedforward linearization control law for an agent in URTS is proposed as:
+\begin{equation} \label{eq:control}
+    u(t)= M(r(t))(\ddot{r}(t) + u_{fb}(t)) + H(r(t),\dot{r}(t)) 
+\end{equation}
+where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness.
+
 \textit{
@@
         In Section 3.2.2 of \cite{sabatino2015quadrotor}, the dynamic system of UAV is divided into inner loop system and outer loop system to analyze the reference tracking problem of UAV.
-In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the observer-based tracking specification in (\ref{Hinf}).
+In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design the feedforward linearization control law $u(t)\in\mathbb{R}^6$ to achieve the observer-based tracking specification in (\ref{Hinf}).
 This can reduce the time cost of manually adjusting control gains.
@@
     \begin{remark}
-        The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
-This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be used in control law $u(t)$.
-While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
+        The difference between the feedforward linearization control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ in (\ref{eq:control}) instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
+This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be used in feedforward linearization control law $u(t)$.
+While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, the feedforward linearization control will be achieved too.
     \end{remark}
@@
 \ref{fig:tracking}.
-For UAV, we get $r'(t) = [x_r, y_r, z_r, \phi_r]^T\in\mathbb{R}^{4}$.
+For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$.
 Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system.
@@
 At the same time, we find $u'(t)$.
-For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
+For biped robot, we directly have $r(t)=r'(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system.
 So far, the transformation from reference path $r[k]$ to reference trajectory $r(t)$ for each agent in hybrid URTS is done.
@@
 The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward reference tracking FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system.
-It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV.
+It makes the designed feedforward linearization control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV.
 The reference generator block is introduced to deal with this problem.
@@
 
-Now, substituting the control law $u(t)$ in (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
+Now, substituting the feedforward linearization control law $u(t)$ in (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:
 \begin{equation} \label{eq:agent1}
@@
 Since the fault signals become a state variable of the augmented tracking error system of an agent in (\ref{eq:e_bar}), their corruption on the tracking error dynamic system in (\ref{eq:error}) can be avoided.
-A Luenberger observer is proposed to estimate them and $\pmb{e}(t)$ simutaniously to achieve an active FTC by the following estimation system:
+A Luenberger observer is proposed to estimate them and $\pmb{e}(t)$ simultaneously to achieve an active FTC by the following estimation system:
 \begin{equation} \label{eq:e_hat}
@@
 \ref{fig:tracking}.
-The reference generator is used to compute the desired reference trajectory $r(t)$ and actuator control input $u'(t)$ for each agent according to the continuous signal $r'(t)$ obtained by D/A and the control law $u(t)$ we design in (\ref{eq:control}).
+The reference generator is used to compute the desired reference trajectory $r(t)$ and actuator control input $u'(t)$ for each agent according to the continuous signal $r'(t)$ obtained by D/A and the feedforward linearization control law $u(t)$ we design in (\ref{eq:control}).
 Passing $r(t)$ through the integrator and differentiator, we get $\pmb{r}(t)$.
@@
 the control $u_{fb}(t)=\sum_{i=1}^{n} {u}_{fb,i}(t)\otimes\mathbf{e}_i$, 
-the acuaor fault $f_{1}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, 
+the acuator fault $f_{1}(t)=\sum_{i=1}^{n} {f}_{1,i}(t)\otimes\mathbf{e}_i$, 
 the output $y(t)=\sum_{i=1}^{n} {y}_i(t)\otimes\mathbf{e}_i$, 
@@
         & \dot{\pmb{e}}_i(t)=A_0\pmb{e}_i(t)+B_0(u_{fb,i}(t)+f_{1,i}(t)) \\
-        & {y}_i(t)=C_0\pmb{e}_i(t)+B_{2,0}f_{2,i}(t)   
+        & {y}_i(t)=C_0\pmb{e}_i(t) + C_0\pmb{r}_i(t) + B_{2,0}f_{2,i}(t)   
     \end{split}
@@
 Representing the search tasks in Fig.
-\ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,5 \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_i=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block.
+\ref{fig:S_task} as a set $task_1=\{ T_j | j=1,2,...,5 \}\cup\{T_6\}$, then the proper agent-task pairs $allocation_1=\{ (\alpha_{i,j},T_j) | j=1,2,...,5 \}\cup\{(\alpha_{i+1,2},T_6)\}$ can be obtained through the task allocation block.
 Suppose a goal is found after a while as shown in Fig.
@@
     \centering
-    \includegraphics[scale=.4]{fig/SR_area.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$.}%
+    \includegraphics[scale=.12]{fig/SR_area.png}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $team_i$ is responsible for $area_i$.}%
     \label{fig:SR_area}
@@
 For the robot $\alpha_{i,5}$, we have the goal configuration $q_{goal}$ from the task $T_7$.
-With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be found as shown in Fig.
+With the current configuration $q_{start}$ and configuration space $\mathcal{C}$ obtained by SLAM, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=27$ can be planned as shown in Fig.
 \ref{fig:R_task}.
@@
     \centering
-    \includegraphics[scale=.6]{fig/robot_PP.png}\caption{The path planning result of the robot $\alpha_{i,5}$ performing the rescue task $T_7$ using RRT algorithm.
+    \includegraphics[scale=.6]{fig/robot_PP.png}\caption{The global path planning result of the robot $\alpha_{i,5}$ performing the rescue task $T_7$ using RRT algorithm.
 The block polygons represent the obstacle space $\mathcal{C}_{obs}$.}%
@@
 By a general nonlinear agent dynamic model, the tracking control problem of UAV and robot can be analyzed together.
-Through a feedforward control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
+Through a novel feedforward linearization control strategy, the nonlinear tracking control problem with external disturbances is transformed to a regulation problem with fault signals.
 Then, a smoothing signal model is introduced to embed the fault signals into the state vector to avoid the corruption on the agent dynamic model.

### 2023-01-06 paper/paperOneCol.tex
IEEE Contributed Version

@@
 
-\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue of Hybrid UAVs and Biped Robots Team System}
-
-\author{Min-Yen Lee and Bor-Sen Chen, \IEEEmembership{Life Fellow, IEEE,}}
-
 \begin{document}
-\maketitle
-
-\begin{abstract}
-In this study, we integrate a local motion planning and robust $H_\infty$ decentralized feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
-A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage.
-In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated.
-In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated.
-To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning.
-Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS.
-By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment.
-Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system.
-The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By converting the dynamics models of UAV and robot into an unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is proposed for each agent in URTS.
-A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
-\end{abstract}
-
-\maketitle
 
@@
 Furthermore, the walking of biped robot suffers from the falling problem, i.e, how to plan a stable walking pattern to prevent robot from falling.
-These make the planning of walking motion of robot more difficult.
-In this paper, a three-dimensional linear inverted pendulum Model (3D-LIPM) \cite{kajita2001real} is used to plan the walking motion of each biped robot in URTS.
+These make the motion planning of walking behavior of robot more difficult.
+In this paper, a Three-Dimensional Linear Inverted Pendulum Model (3D-LIPM) \cite{kajita2001real} is used for the motion planning of walking behavior of each biped robot in URTS.
 
@@
     \begin{remark}
+        In Section 3.2.2 of \cite{sabatino2015quadrotor}, the dynamic system of UAV is divided into inner loop system and outer loop system to analyze the reference tracking problem of UAV.
+In order to improve the problem that the control gains in four state equations ($z$, $\phi$, $\theta$ and $\psi$) of inner loop system and the two states of outer loop system ($x$ and $y$) in \cite{sabatino2015quadrotor} has no design specifications, we changed the controller design method so that the control gains of the six states of UAV can be designed together via the given specifications, i.e., design control law $u(t)\in\mathbb{R}^6$ to achieve the observer-based tracking specification in (\ref{Hinf}).
+This can reduce the time cost of manually adjusting control gains.
+At the same time, the tracking control problem of UAV and robot can be analyzed simultaneously.
+    \end{remark}
+}
+\textit{
+    \begin{remark}
         The difference between the control law $u(t)$ in (\ref{eq:control}) of this article and the traditional feedback linearization control (or computed torque control) is that we use the "feedforward" linearization control, i.e., use $M(r(t))$ and $H(r(t),\dot{r}(t))$ instead of $M(x(t))$ and $H(x(t),\dot{x}(t))$.
-This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be use in control law $u(t)$.
+This is because the state $x(t)$ is assumed to be unavailable in this paper so $x(t)$ cannot be used in control law $u(t)$.
 While the asymptotical tracking control is achieved, i.e., $x(t)\rightarrow r(t)$, feedforward linearization control will be achieved too.
@@
 \bibliography{citation}
-% \begin{thebibliography}{00}
-%     \bibitem{9700861} L. Kloeker, T. Moers, L. Vater, A. Zlocki, and L. Eckstein, “Utilization
-%     and potentials of unmanned aerial vehicles (uavs) in the field of automated
-%     driving: A survey,” in 2021 5th International Conference on Vision, Image
-%     and Signal Processing (ICVISP), pp. 9–17, 2021
-% \end{thebibliography}
 

### 2023-01-07 examples/signal_smoothing.m
Refactor

@@ -1,7 +1,7 @@
 %An example of eliminating the non-smooth properties and outliers that result from numerical differentiation of a signal
 
 clc; clear; close all;
-qr = load('../data/qr.mat').qr;
+qr = load('../src/URTS main script/Robot/data/Robot.mat').qr;
 
 DIM_F   = size(qr, 1);
 dt      = 0.001;
@@ -11,24 +11,52 @@ t       = linspace(0,1,size(qr, 2));
 for i = 1 : DIM_F
 r = qr(i,:);
 
+%% First difference
+% Origin
 dr = diff(r, 1, 2)/dt;
-dr = filloutliers(dr,'clip','movmedian', 10, 'ThresholdFactor', 1); % numercial differenciation will produce outliers 
-dr = smoothdata(dr);
+% Smoothed
+dr_Smoothed = filloutliers(dr,'clip','movmedian', 10, 'ThresholdFactor', 1); % numercial differenciation will produce outliers 
+dr_Smoothed = smoothdata(dr_Smoothed);
 
-ddr = diff(dr, 1, 2)/dt;    
-ddr = smoothdata(ddr);
+%% Second difference
+% Origin
+ddr = diff(dr_Smoothed, 1, 2)/dt;
+% Smoothed
+ddr_Smoothed = smoothdata(ddr);
 
-dr = [zeros(1, 1) dr]; % diff() will result in 1 missing data, resize it
-ddr = [zeros(1, 2) ddr]; % diff() will result in 1 missing data, resize it
+%% Resize
+dr = AddZerosToFrontOfArray(dr, 1);
+ddr = AddZerosToFrontOfArray(ddr, 2);
+dr_Smoothed = AddZerosToFrontOfArray(dr_Smoothed, 1);
+ddr_Smoothed = AddZerosToFrontOfArray(ddr_Smoothed, 2);
 
+%% Store results
 tr.r(i,:) = r;
 tr.dr(i,:) = dr;
 tr.ddr(i,:) = ddr;
+
+tr.dr_Smoothed(i,:) = dr_Smoothed;
+tr.ddr_Smoothed(i,:) = ddr_Smoothed;
 end
 
+%% Plot
 figure
 plot(t, tr.r)
+title('r(t)')
 figure
 plot(t, tr.dr)
+title('r''(t)')
+figure
+plot(t, tr.dr_Smoothed)
+title('r''(t), smoothed')
 figure
 plot(t, tr.ddr)
+title('r''''(t)')
+figure
[…]

### 2023-01-09 paper/paperOneColumn.tex
Copy twoColumn to oneColumn. - The opinion of the oral exam committee will revised in oneClomun

--- 2023-01-06 paper/paper.tex
@@
-\documentclass{ieeeaccess}
-% For one column
-% \documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran} 
+\documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran}
 \usepackage{cite}
@@
 
-% \setcounter{MaxMatrixCols}{30}
-% \providecommand{\U}[1]{\protect\rule{.1in}{.1in}}
 \newtheorem{theorem}{Theorem}
-% \newtheorem{acknowledgement}[theorem]{Acknowledgement}
-% \newtheorem{algorithm}[theorem]{Algorithm}
-% \newtheorem{case}[theorem]{Case}
-% \newtheorem{conclusion}[theorem]{Conclusion}
-% \newtheorem{corollary}[theorem]{Corollary}
-% \newtheorem{definition}[theorem]{Definition}
 \newtheorem{lemma}{Lemma}
-% \newtheorem{notation}{Notation}
-% \newtheorem{problem}[theorem]{Problem}
 \newtheorem{remark}{Remark}
-% \newtheorem{solution}[theorem]{Solution}
 \newtheorem{assumption}{Assumption}[section]
@@
 
-% \captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig.}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% No need for one columne
-\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
-
-\doi{10.1109/ACCESS.2017.DOI}
-
-\title{Integrating Local Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control for Search and Rescue Task of Hybrid UAVs and Biped Robots Team System}
-
-\author{\uppercase{Bor-Sen Chen}\authorrefmark{1,2}, \IEEEmembership{Life
-Fellow, IEEE}, \uppercase{Ting-Wei Hung\authorrefmark{1}}}
-
-\address[1]{Department of Electrical Engineering, National Tsing Hua
-University, Hsinchu 30013, Taiwan} \address[2]{Department of Electrical
-Engineering, Yuan Ze University, Taoyuan 32003, Taiwan}
-
-\tfootnote{This work was supported by the Ministry of Science and Technology
-of Taiwan under Grant MOST 108-2221-E-007-099-MY3.}
-
-\markboth
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-{Author \headeretal: Preparation of Papers for IEEE TRANSACTIONS and JOURNALS}
-
-\corresp{Corresponding author: Bor-Sen Chen (bschen@ee.nthu.edu.tw)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
-
-\begin{abstract}
-In this study, we integrate a local motion planning and robust $H_\infty$ decentralized observer-based feedforward reference tracking fault-tolerant control (FTC) of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R).
-A system architecture of performing S\&R tasks for each agent in URTS is proposed to explain how to integrate reference trajectory planning and tracking control in URTS for S\&R usage.
-In order to optimally allocate tasks to each agent in URTS, a task allocate problem is investigated.
-In order to optimally plan a path for each agent in URTS to reach these allocated task locations, a path planning problem is formulated.
-To deal with complex S\&R terrain, we decompose the path planning problem into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning.
-Through such decomposition, some roadmap-based path planning algorithms can be applied to the global path planning of agents in URTS.
-By the behavior decision, we can decide what behavior to follow the global path according to the terrain environment.
-Next, we focus on the local motion planning problem of flying behavior for UAV and walking behavior for robot, and then the tracking control problem for UAVs and robots in the hybrid team system.
-The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail.
-By a proposed novel feedforward linearization control scheme, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design is significantly simplified for each agent in URTS.
-A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation.
-Then, the design of the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure.
-With the help of MATLAB LMI Toolbox, the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC design problem of each UAV and robot in URTS is effectively solved.
-Finally, the simulation results are used to demonstrate the integration of local motion planning with the S\&R tasks of hybrid URTS and to verify the effectiveness of the proposed robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC method of hybrid URTS under the external disturbance and the actuator and sensor fault.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% No need for one columne
-\begin{keywords}
-biped robot, fault-tolerant control, heterogeneous multi-agent system, robust $H_\infty$ control, S\&R, smoothing signal model, UAV, hybrid UAVs-UGVs team system
-\end{keywords}
-\titlepgskip=-15pt
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\maketitle
 
@@
     \includegraphics[scale=.12]{fig/behavior.png}\caption{
-        (a) The flowchart of Behavior Decision block in Fig. \ref{fig:sys} of each agent in URTS. The behavior to be took at every moment by each agent will be decided in this block. 
+        (a) The flowchart of Behavior Decision block in Fig.
+\ref{fig:sys} of each agent in URTS.
+The behavior to be took at every moment by each agent will be decided in this block.
+% Remember to fill in the blanks in this way
         (b) The behavior set of each agent in URTS.
@@
 \bibliography{citation}
-% \begin{thebibliography}{00}
-%     \bibitem{9700861} L. Kloeker, T. Moers, L. Vater, A. Zlocki, and L. Eckstein, “Utilization
-%     and potentials of unmanned aerial vehicles (uavs) in the field of automated
-%     driving: A survey,” in 2021 5th International Conference on Vision, Image
-%     and Signal Processing (ICVISP), pp. 9–17, 2021
-% \end{thebibliography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author1.jpg}}]{Bor-sen chen}
-    (Life Fellow, IEEE) received the B.S.
-degree in electrical engineering from the Tatung Institute of Technology, Taipei, Taiwan, in 1970, the M.S.
-degree in geophysics from National Central University, Chungli, Taiwan, in 1973, and the Ph.D.
-degree in electrical engineering from the University of Southern California, Los Angeles, CA, USA, in 1982.
-He was a Lecturer, an Associate Professor, and a Professor with the Tatung Institute of Technology, from 1973 to 1987.
-He is currently the Tsing Hua Distinguished Chair Professor of electrical engineering and computer science with National Tsing Hua University, Hsinchu, Taiwan.
-His current research interests include control engineering, signal processing, and systems biology.
-He has received the Distinguished Research Award from the National Science Council of Taiwan four times.
-He is also the National Chair Professor of the Ministry of Education of Taiwan.
-\end{IEEEbiography}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/Author2.jpg}}]{Ting-Wei Hung}
-    received the B.S.
-degree in the department of engineering science from the National Cheng Kung University, Tainan, Taiwan, in 2020, and the M.S.
-degree from the Department of Electrical Engineering, National Tsing Hua University, in 2022.
-His current research interests include robotics, robust control, and team formation control.
-\end{IEEEbiography}
-
-\EOD
 

### 2023-01-10 paper/paperOneColumn.tex
Rivise paper, base on: - Oral committe suggestion - Oral PPT

@@
 
-The local motion planning is the bridge between path planning and tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same.
+The local motion planning is the bridge between path planning and reference tracking control since the path found by path planning algorithm and the path enforced to follow by a controller are not necessarily the same.
 The reason is that path planning algorithm usually treats the agent as a point, while the actual agent in the physical world is a mechanical system for the tracking control design.
@@
 This makes certain paths impossible to follow for an actual agent, such as paths that are not smooth, have too large curvature, or require too large velocity and acceleration.
-Although some literatures directly tackle the kinodynamic constraints on path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) global path planning, (ii) behavior decision and (iii) local motion planning to deal with complex S\&R terrain.
+Although some literatures directly tackle the kinodynamic constraints on path planning problem \cite{9384209}, this paper splits path planning into three steps, i.e., (i) Global Path Planning, (ii) Behavior Decision and (iii) Local Motion Planning to deal with complex S\&R terrain.
 Through this decomposition, we can focus on the local motion planning of specific behaviors.
@@
 \textbf{Notation 1:} 
-$diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1, A_2, \dots, A_n$.
+$diag(A_1, A_2, \dots, A_n)$: a block diagonal matrix with main diagonal blocks $A_1\mathbin{,} A_2\mathbin{,} \dots\mathbin{,} A_n$.
 $A^T$: transpose of $A$.
@@
 Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station.
-The ground station will combine this information with the goal location determined by the task and then plan a path to avoid obstacles and other agents nearby through a path planning algorithm.
+The ground station will combine this information with the goal location determined by the task content and then plan a path to avoid obstacles and other agents nearby through a path planning algorithm.
 % That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.
 
-We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots if the algorithm treat the agent as a point.
+Since URTS operates in a complex terrain environment and the agents in URTS have multiple behaviors to act with environment, it is impossible to use a unified path planning algorithm in URTS.
+In other words, it is difficult to find a path that simultaneously satisfies obstacle avoidance, reaches the goal location, satisfies the kinematic constraints induced by the mechanical body of agents, and can be used as a reference trajectory for the dynamic model of agents.
+Therefore, this article splits path planning into three steps, i.e., (i) Global Path Planning, (ii) Behavior Decision and (iii) Local Motion Planning.
+Global Path Panning plans a global path by regarding the agent as a point.
+The global path tells the agent where to go.
+Behavio Decision decides what behavior to follow the global path according to the global path and its surrounding terrain environment (e.g., the biped robot decides to follow it by walking or running behavior).
+Local Motion Planning plans local motion for specific behaviors by regarding the agent as a mechanical body.
+% We need to determine specific behavior to follow the path found by path planning algorithm according to the terrain situation especially for agents with complex mechanical systems like robots if the algorithm treat the agent as a point.
 Since such a system has a high degree of freedom, there are many ways to follow the same path (e.g., a robot can walk or run to follow the same path).
@@
 To meet these needs, a behavioral decision is necessary.
-
 In order for the agent to make a behavior, we must plan a corresponding motion by local motion planning.
-The motion is a prescribed reference path for an actual mechanical system to follow.
-Finally, a tracking controller is designed for each agent to follow this desired reference path.
-
-The agents overall have the same system architecture in URTS except for some subprocess differences.
+The local motion is a prescribed reference path for an actual mechanical system to follow.
+After the reference path is converted into a reference trajectory, the agent can follow the global path to reach the goal location by tracking the reference trajectory through the reference tracking controller.
+
+The UAV and biped robot overall have the same system architecture for performing S\&R task in URTS except for some subprocess differences.
 Followed by the concept in \cite{paden2016survey}, a system architecture of performing S\&R tasks for each agent in hybrid URTS is proposed as shown in Fig.
@@
 
+\textit{
+    \begin{remark}
+        In this paper, we will only state and solve the problems in Local Motion Planning and Reference Tracking Control, i.e., how to plan the local motion of UAV flying and biped robot walking and how to design the robust $H_\infty$ decentralized observer-based feedforward reference tracking FTC strategy for each agent in URTS.
+Nevertheless, the reason why we still state the problems in Task Allocation, Global Path Planning and Behavior Decision is to clarify the systematic relationship between these blocks, which provides a blueprint for those who want to construct a system like URTS.
+    \end{remark}
+}
+
 % To determine the behavior, agent needs the information about environment.
@@
     \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of performing S\&R tasks for each agent in hybrid URTS.
+In the figure, the three capabilities required for unmanned systems are marked, i.e., perception, decision-making and control.
 The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information.
@@
 Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs $(\alpha_{i,j}, T_k)$ to achieve a specific cost function.
-In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal configuration $q_{goal}$ it needs to go at every moment.
-$q_{goal}$ then passes to next block, i.e., the global path planning block, as shown in Fig.
+In this paper, we assume that the tasks have been properly assigned and every agent knows a goal configuration $q_{goal}$ it needs to go at every moment form the task content.
+$q_{goal}$ then passes to next block, i.e., Global Path Planning block, as shown in Fig.
 \ref{fig:sys}.
@@
 \subsection{Global Path Planning}
-After a goal configuration $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ to arrive  it.
+After a goal configuration $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current configuration $q_{start}$ obtained by SLAM to arrive $q_{goal}$.
 There must exist multiple feasible paths to go.
@@
 There are several path planning algorithms to handle this problem.
-Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS.
+Due to regarding agent as a point in this block and the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method in Global Path Planning of URTS.
 This method attempts to discretize the search space into interconnected roads and find the path on it.
@@
 
-Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
+% Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with.
 The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for a biped robot).
 In this case, an unified planner will become overly complex and impracticable.
-Therefore, we divide path planning into three subprocesses, i.e., global path planning, behavior decision and local motion planning.
+Therefore, we divide path planning into three subprocesses, i.e., Global Path Planning, Behavior Decision and Local Motion Planning.
 The global path planning block becomes a global planner to regard an agent as a point without kinodynamic constraints.
-This enables the common roadmap-based path planning algorithms mentioned above to be used for global path planning in UTRS.
+This enables the common roadmap-based path planning algorithms mentioned above to be used for Global Path Planning in UTRS.
 The local motion planning block becomes a local planner to consider the motion planning of a specific behavior.
-% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.
 
@@
 
-From above assumptions, a path of agent can be expressed as a sequence:
+From above assumptions, a global path of agent can be expressed as a sequence:
 \begin{equation}
@@
 \end{equation}
-where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then passes to next block, i.e., the behavior decision block, as shown in Fig. \ref{fig:sys}.
+where $k_f$ is the time step when reaching goal. $(\sigma_n)$ then passes to next block, i.e., Behavior Decision block, as shown in Fig. \ref{fig:sys}.
 
@@
 % Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
-The global path planning block tells agents where to go but not how since we regard the agent as a point.
-Therefore, agents need to determine an appropriate behavior to follow the path $(\sigma_n)$ according to the machine vision provided by the object information.
-Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario.
+The global path $(\sigma_n)$ tells agents where to go but not how since it regards the agent as a point.
+Therefore, agents need to determine an appropriate behavior to follow $(\sigma_n)$ according to the machine vision provided by the object information.
+Taking robot as an example, it may walk, run, climb, or jump to follow $(\sigma_n)$ according to real scenario.
 These behaviors with changing position are classified as "Moving" behavior in this paper.
 Besides, the agents in the hybrid URTS do not always moving.
-Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
+Sometimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls).
 These behaviors without changing position are classified as "Action" behavior in this paper.
@@
 where $\mathcal{B}$ is the set of behaviors.
-It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
+It means that the global path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior.
 By the object information in Fig.
@@
 \ref{fig:behavior}.
-$(\beta_n)$ then passes to next block, i.e., the local motion planning block, as shown in Fig.
+$(\beta_n)$ then passes to next block, i.e., Local Motion Planning block, as shown in Fig.
 \ref{fig:sys}.
@@
 \subsection{Local Motion Planning}
-After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a motion to achieve the specific behavior.
-Local motion planning block is like the global path planning block but with smaller scale and higher resolution and precision.
-Collision checking is needed since we consider agent as a point in the global path planning block but it is a real mechanical body here.
+After a specific behavior $\beta_n\in\mathcal{B}$ is determined, the next step is to plan a local motion to achieve the specific behavior.
+Local Motion Planning block is like Global Path Planning block but with smaller scale and higher resolution and precision.
+Collision checking is needed since we consider agent as a point in Global Path Planning block but it is a real mechanical body here.
 Furthermore, the kinodynamic constraint is handled in this block.
-Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature.
-Therefore, the output of this block, i.e., reference path $r[k]$, is also a path (it is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it).
-The flowchart of local motion planning block is shown in Fig.
+A local motion is a reference path $r[k]$ (it is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it) which describes how a mechanical body changes in space over time in the physical world.
+The flowchart of Local Motion Planning block is shown in Fig.
 \ref{fig:LMP}.
@@
 
-To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot.
+To limit the scope of this article, we only focus on the local motion planning of flying behavior for UAV and walking behavior for robot.
 A more detailed description will be given in the next section.
@@
 \end{figure*}
-Before the discussion of the motion planning of these two behaviors of UAV and robot in URTS, the following assumption is maded.
+Before the discussion of the local motion planning of these two behaviors of UAV and robot in URTS, the following assumption is maded.
 \textit{
@@
 $g$ is the gravity acceleration, $m$ and $J$ are the mass and inertia matrix of UAV, respectively, $\tau_u$ and $F$ are the total torque and force acting on UAV, respectively, $\Theta$ is the Euler angles in body frame as shown in Fig.
-2.8 in \cite{sabatino2015quadrotor}, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
+2.8 in \cite{sabatino2015quadrotor} with $\phi\in[ -\pi, \pi ]$, $\theta\in[ -\pi/2, \pi/2 ]$ and $\psi\in[ -\pi, \pi ]$, $X$ is the postion of center of mass (CoM) in inertial frame, $K_\tau$ and $K_F$ are the aerodynamic damping coefficients, and $R(\Theta)$ is the intrinsic rotation matrix from body frame to inertial frame.
 This model treats the UAV as a mass point and can control the total force $F$ and the total torque $\tau_u$.
@@
 
-The feedforward linearization control law for an agent in URTS is proposed as:
+The decentralized feedforward linearization control law for an agent in URTS is proposed as:
 \begin{equation} \label{eq:control}
@@
 where $r(t)\in\mathbb{R}^n$ is the desired reference trajectory, $M(r(t))$, $\ddot{r}(t)$ and $H(r(t), \dot{r}(t))$ are the feedfoward control terms for canceling system nonlinearity, and $u_{fb}(t)$ is the feedback control law to be futher designed for improving system tracking robustness.
+
+\textit{
+    \begin{remark}
+        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted for the convenience of notation in the following.
+For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
+    \end{remark}
+}
 
@@
 \ref{fig:tracking}.
+\textit{
+    \begin{remark}
+        The solution of $\phi_r$ and $\theta_r$ must satisfy the constraints $\phi_r\in[-\pi,\pi]$ and $\theta_r\in[-\pi/2,\pi/2]$ in UAV dynamic model in (\ref{eq:uav}).
+In addition, since $\phi_r$ and $\theta_r$ are calculated at each time step and there may be multiple solutions due to inverse dynamic calculation, the solution of $\phi_r$ and $\theta_r$ must be selected to be continuous with the previous time step.
+    \end{remark}
+}
+
 \begin{figure*}[htbp]
@@
 
-\textit{
-    \begin{remark}
-        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted for the convenience of notation in the following.
-For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
-    \end{remark}
-}
 \textit{
@@
 % where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
+\textit{
+    \begin{remark}
+        Under the decentralized control architecture, the coupling effect $c(t)$ between agents becomes their own external disturbance, which greatly reduces the difficulty of controller design.
+    \end{remark}
+}
 
@@
 
-Through the above analysis, the tracking control problem of the nonlinear system of each agent in hybrid URTS with external disturbance in (\ref{eq:agent d1}) is transformed into the regulation problem of the linear tracking error system in (\ref{eq:linear f1}) with actuator fault signal $f_1(t)$ by the feedforward linearization control law $u(t)$ in (\ref{eq:control}).
+Through the above analysis, the tracking control problem of the nonlinear system of each agent in hybrid URTS with external disturbance in (\ref{eq:agent d1}) is transformed into the regulation problem of the linear tracking error system in (\ref{eq:linear f1}) with actuator fault signal $f_1(t)$ by the feedforward "linearization" control law $u(t)$ in (\ref{eq:control}).
 The remaining step is to design an appropriate feedback control law $u_{fb}(t)$ in (\ref{eq:linear f1}) to make the linear tracking error system robustly stable.
+\textit{
+    \begin{remark}
+        It can be easily shown that $(A,B)$ is controllable, i.e., $rank([B\mathbin{,} AB\mathbin{,} \dots\mathbin{,} A^{3n-1}B])=3n$.
+This means that the linear tracking error system in (\ref{eq:linear f1}) can be stabilized through $u_{fb}(t)$.
+    \end{remark}
+}
+
 In a real system, the feedback information is measured by sensor, i.e, the state $x(t)$ in (\ref{eq:agent}) is unavailable.
@@
 Since the fault signals become a state variable of the augmented tracking error system of an agent in (\ref{eq:e_bar}), their corruption on the tracking error dynamic system in (\ref{eq:error}) can be avoided.
+In addition, the amplitude of the fault signals $f_i(t),i=1,2$ no longer affect the augmented tracking error system in (\ref{eq:e_bar}), but the smoothness of $f_i(t),i=1,2$, i.e., the amplitude of the smoothing signal model error $\bar{v}(t)$.
+This allows the augmented tracking error system in (\ref{eq:e_bar}) to tolerate the fault signals with larger amplitudes.
 A Luenberger observer is proposed to estimate them and $\pmb{e}(t)$ simultaneously to achieve an active FTC by the following estimation system:
@@
 For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption \textit{Assumption \ref{asm:collision}}.
-For robots, $q_{goal}$ will be passed to the global path planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
+For robots, $q_{goal}$ will be passed to Global Path Planning block together with current configuration $q_{start}$ and occupancy map $\mathcal{C}$ to find collision-free paths $(\sigma_n)$.}
     \label{fig:S_task}
@@
 
-To illustrate the global path planning block and behavior decision block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
+To illustrate Global Path Planning block and Behavior Decision block, we choose the pairs $(\alpha_{i,5},T_7)$ and $(\alpha_{i,1}, T_1)$ as example.
 For the UAV $\alpha_{i,1}$, the path $(\sigma_n),n\in\mathbb{Z}\cap[1,k_f],k_f=16$ is directly assigned as shown in Fig.
-\ref{sim:flying} without going through the global path planning block by \textit{Assumption \ref{asm:collision}}.
+\ref{sim:flying} without going through Global Path Planning block by \textit{Assumption \ref{asm:collision}}.
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[1,k_f]$.
@@
 The behavior sequence $(\beta_n)$ is set as $\beta_n=\mathit{walking}$ for $n\in\mathbb{Z}\cap[1,5]$, $\beta_n=\mathit{climbing}$ for $n\in\mathbb{Z}\cap[6,15]$ and $\beta_n=\mathit{running}$ for $n\in\mathbb{Z}\cap[16,27]$.
-We choose the walking behavior $\beta_n, n\in\mathbb{Z}\cap[1,5]$ to illustrate the local motion planning block of robots.
+We choose the walking behavior $\beta_n, n\in\mathbb{Z}\cap[1,5]$ to illustrate Local Motion Planning block of robots.
 \begin{figure}[htbp]
@@
 
-After $(\beta_n)$ is set, we can plan the reference path $r[k]$ by local motion planning block.
+After $(\beta_n)$ is set, we can plan the reference path $r[k]$ by Local Motion Planning block.
 Following the procedure in Fig.
@@
 }
-The simulation results of tracking and estimation in reference tracking control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,5}$ in $team_1$ are given as follows:
+The simulation results of tracking and estimation in Reference Tracking Control block of the UAV $\alpha_{1,1}$ and the robot $\alpha_{1,5}$ in $team_1$ are given as follows:
 
@@
 The task allocation problem and path planning problem are investigated and unified to the integration of local motion planning and robust $H_\infty$ decentralized feedforward reference tracking FTC for hybrid URTS.
-By decomposing the path planning process into three subprocess, i.e., global path planning, behavior decision and local motion planning, some common roadmap-based path planning algorithm can be applied in the global path planning of URTS.
+By decomposing the path planning process into three subprocess, i.e., Global Path Planning, Behavior Decision and Local Motion Planning, some common roadmap-based path planning algorithm can be applied in the global path planning of URTS.
 Through the behavior decision, the agent can decide the appropriate behavior according to the terrain environment.
